### 2024-03-14 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Template first version

---
title: "Identifying Heterogeneity in SAR Data with New Test Statistics"
author:
  - name: Alejandro C. Frery
    affil: 1,*
    orcid: 0000-0002-8002-5341
  - name: Janeth Alpala
    affil: 2 
    orcid: 0000-0002-0265-6236
  - name: Abraão D. C. Nascimento
    affil: 2
    orcid: 0000-0003-2673-219X
affiliation:
  - num: 1
    address: |
      School of Mathematics and Statistics, Victoria University of Wellington, Wellington 6140, New Zealand
#email: alejandro.frery@vuw.ac.nz
  - num: 2
    address: |
      Departamento de Estatística, Universidade Federal de Pernambuco, Recife 50670-901, PE, Brazil
#email: janeth.alpala@ufpe.br, abraao@de.ufpe.br

# author citation list in chicago format
authorcitation: |
  Frery, A.C.; Alpala, J.; Nascimento,A.D.C.
# firstnote to eighthnote
#firstnote: |
 # Current address: Updated affiliation
#secondnote: |
  #These authors contributed equally to this work.
correspondence: |
  alejandro.frery@vuw.ac.nz
# document options
journal: remotesensing
type: article
status: submit
# front matter
#simplesummary: |
  #A Simple summary goes here.
abstract: |
  This paper presents a statistical approach to identify the underlying roughness characteristics in synthetic aperture radar (SAR) intensity data. The physical modeling of this kind of data allows to use the Gamma distribution in the presence of fully-developed speckle, i.e., when there are infinitely many independent backscatterers per resolution cell. This situation is often called "homogeneous" or 
  "textureless" areas. The $\mathcal{G}_I^0$ distribution is also a widely accepted law for heterogeneous and extremely heterogeneous areas. We propose three test statistics for discriminating between homogeneous and non-homogeneous areas, i.e., between Gamma and GI0 distributed data, both with a known number of looks. The first test statistic utilizes a bootstrapped non-parametric estimator of the Shannon entropy, offering a robust evaluation in the face of uncertain distributional assumptions. The second test uses the classic coefficient of variation. The third test employs an alternative form of estimating the CV based on the ratio of the median absolute deviation to the median. We apply our test statistic to produce maps of $p$-values for the hypothesis of homogeneity. These maps identify different types of targets. We show that our proposal outperforms its competitors using simulated and SAR data.
# back matter
keywords: |
  SAR; heterogeneity; entropy;  coefficient of variation; hypothesis tests
acknowledgement: |
  This study was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior - Brasil (CAPES) - Finance Code 001.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
funding: |
  Please add: "This research received no external funding" or "This research 
  was funded by NAME OF FUNDER grant number XXX."  and ``The APC was funded 
  by XXX''. Check carefully that the details given are accurate and use the 
  standard spelling of funding agency names at 
  \url{https://search.crossref.org/funding}, any errors may affect your future 
  funding.
institutionalreview: |
 Not applicable.
#informedconsent: |
  # Any research article describing a study involving humans should contain this 
  # statement. Please add ``Informed consent was obtained from all subjects 
  # involved in the study.'' OR ``Patient consent was waived due to REASON 
  # (please provide a detailed justification).'' OR ``Not applicable'' for 
  # studies not involving humans. You might also choose to exclude this statement 
  # if the study did not involve humans.

  # Written informed consent for publication must be obtained from participating 
  # patients who can be identified (including by the patients themselves). Please 
  # state ``Written informed consent has been obtained from the patient(s) to 
  # publish this paper'' if applicable.
dataavailability: |
  Not applicable.
conflictsofinterest: |
  The authors declare no conflict of interest.
supplementary: |
 This article is fully reproducible using RMarkdown. All code and data are accessible at
 \url{https://github.com/rjaneth/Janeth-Alpala} (accessed on 10 March 2024).
abbreviations:
  - short: MDPI
    long: Multidisciplinary Digital Publishing Institute
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{amsmath}

bibliography: references.bib
#appendix: appendix.tex
endnotes: false
output: 
  rticles::mdpi_article:
    extra_dependencies: longtable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
#knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
#library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)
library(e1071)# kurtosis
library(viridis)
library(nortest)# AD

theme_set(theme_minimal() +
            theme(text=element_text(family="serif"),
                  legend.position = "bottom")#  top , right , bottom , or left#, panel.grid = element_blank()
)

# if(!require("rstudioapi")) install("rstudioapi")
# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

# opts_chunk$set(comment="",
#                message=FALSE,
#                tidy.opts=list(keep.blank.line=TRUE, width.cutoff=120),
#                options(width=100), 
#                # cache=TRUE,
#                fig.align='center',
#                fig.height=6, fig.width=10,
#                fig.show='hold',
#                cache=TRUE)

source("../Code/R/MainFunctions/gamma_sar_sample.R")
source("../Code/R/MainFunctions/entropy_gamma_sar.R")
source("../Code/R/MainFunctions/entropy_gI0.R")
source("../Code/R/MainFunctions/gi0_sample.R")

source("../Code/R/MainFunctions/van_es_estimator.R")
source("../Code/R/MainFunctions/correa_estimator.R")
source("../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
source("../Code/R/MainFunctions/ebrahimi_estimator.R")
source("../Code/R/MainFunctions/noughabi_arghami_estimator.R")
source("../Code/R/MainFunctions/vasicek_estimator.R")
source("../Code/R/MainFunctions/al_omari_1_estimator.R")
source("../Code/R/MainFunctions/al_omari_2_estimator.R")

source("../Code/R/MainFunctions/bootstrap_van_es_estimator.R")
source("../Code/R/MainFunctions/bootstrap_correa_estimator.R")
source("../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
source("../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.R")
source("../Code/R/MainFunctions/bootstrap_vasicek_estimator.R")
source("../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
source("../Code/R/MainFunctions/bootstrap_al_omari_2_estimator.R")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../Code/R/Programs/functions_sample_bias_mse.R")# read_ENVI_images
source("../Code/R/Programs/read_ENVI_images.R")

```

```{r DefinitionSimulationRoutines, echo=FALSE}
#set.seed(1234567890, kind="Mersenne-Twister")
```
\setlength{\tabcolsep}{6pt} 
\newcommand{\bias}{\operatorname{Bias}}
\newcommand{\widebar}[1]{\overline{#1}}

# Introduction {#sec:Introduction}

Synthetic Aperture Radar (SAR) technology has become an important tool for environmental monitoring and disaster management, providing valuable imagery in different conditions, including day or night and diverse weather situations&nbsp;\cite{Mu2019}.
However, the effective utilization of SAR data depends on a thorough understanding of its statistical properties, especially the impact of speckle effects, which are inherent in SAR data due to the coherent nature of the imaging process.

In the presence of non-Gaussian speckle interference, SAR data requires a reliable statistical model for accurate processing. The $\mathcal{G}^0$ distribution, suitable for SAR data, includes the Gamma law as a specific case for fully developed speckle, providing flexibility with fewer parameters for analysis.

Our work is motivated to improve the identification of potential roughness features in SAR intensity data. 
Physical modeling of SAR data allows to take advantage of the gamma distribution in the presence of fully developed speckle, creating a scenario with an infinite number of independent backscatterers per unit of resolution, often referred to as homogeneous areas.

In this context, we present a set of three novel test statistics designed to discriminate between homogeneous and non-homogeneous areas, specifically aimed at differentiating between Gamma and $\mathcal{G}^0$ distributed data, each with a known number of appearances. 
Hence, to understand the core ideas behind our approach, we explore into the use of properties such as entropy and coefficient of variation.

The entropy is a fundamental concept in information theory with broad applications to pattern recognition, statistical physics, stochastic dynamics, and statistics. 
Shannon introduced it for a random variable in 1948&nbsp;\cite{Shannon1948} as a measure of information and uncertainty.  
In statistics, Shannon entropy is a crucial descriptive parameter, particularly for assessing data dispersion and conducting tests for normality, exponentiality, and uniformity&nbsp;\cite{Wieczorkowski1999}. 
Entropy estimation involves several practical difficulties, especially when the model is unknown; in these cases, non-parametric methods are used.
Among the non-parametric approaches, Subhash et al.&nbsp;\cite{Subhash2021} discussed the use of spacing methods.
This non-parametric strategy offers flexibility to address a wide range of models without imposing specific parametric restrictions.
In our study, entropy serves as the fundamental parameter, providing a robust assessment by means of a bootstrapped non-parametric estimator of Shannon entropy.

Simultaneously, we used the classic coefficient of variation (CV) and an alternative form based on the ratio between the median absolute deviation and the median.
The coefficient of variation, recognised as an efficient and robust index of textural information, measures the homogeneity of the image.

Applying these test statistics to generate $p$-value maps facilitates testing of the homogeneity hypothesis, revealing diverse types of targets within the SAR data. 
Through extensive experimentation involving real and simulated SAR data, we demonstrate the superiority of our proposed methodology over existing approaches.

The article is structured as follows: 
Section&nbsp;\ref{sec:Background} covers statistical modeling and entropy estimation for Intensity SAR data. Section&nbsp;\ref{sec:test} outlines hypothesis testing based on non-parametric entropy estimators and and coefficient of variation. 
In Section&nbsp;\ref{sec:results}, we present experimental results. 
Finally, in Section&nbsp;\ref{sec:conclusion} conclusions are exhibited.

# Background {#sec:Background}

## Statistical modeling of Intensity SAR data

The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$  distributions&nbsp;[@Frery1997]. 
The first is suitable for fully developed speckle and is a limiting case of the second, which is appealing due to its versatility in accurately representing regions with various roughness characteristics&nbsp;[@Cassetti2022].
We denote $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and $Z \sim G_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the respective probability density functions:
\begin{align}
	f_Z(z;L, \mu)&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gamma1}\\
	f_Z(z; \alpha, \gamma, L)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
\end{align}
where, in&nbsp;\eqref{E:gamma1} $\mu > 0$ is the mean; in&nbsp;\eqref{E:gi01}  $\gamma > 0$ is the scale, $\alpha < -1$ measures the roughness,  $L \geq 1$ is the number of looks, $\Gamma(\cdot)$ is the gamma function, and $\mathbbm 1_{A}(z)$ is the indicator function of the set $A$.

From \eqref{E:gi01}, the $r$th moment of $Z$ is expressed as:
\begin{align}
	E_{G_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\gamma(L)}, \quad \alpha <-r. 
	\label{E:rmom}
\end{align}

Even though the $\mathcal{G}_I^0$  distribution is defined by the parameters $\alpha$ and $\gamma$, SAR literature commonly utilizes the texture $\alpha$ and the mean $\mu$&nbsp;\cite{Nascimento2010}.
In this way, we compute the expected value $\mu$ using the expression in&nbsp;\eqref{E:rmom}, and we reparametrize&nbsp;\eqref{E:gi01} using $\mu$, $\alpha$, and $L$. Then
\begin{align*}
	\mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
\end{align*}
Thus, the probability density function that characterize the $G_I^0(\mu, \alpha, L)$ law is
\begin{equation}
		f_Z(z; \mu, \alpha, L)=\frac{L^L\Gamma(L-\alpha)}{\big(-\mu(\alpha+1)\big)^{\alpha}\Gamma(-\alpha)\Gamma(L)} \frac{z^{L-1}}{\big(-\mu(\alpha+1)+Lz\big)^{L-\alpha}}.\label{E:gi02}
\end{equation}

## The Shannon Entropy
The parametric representation of Shannon entropy for a system described by a continuous random variable is:
\begin{equation}
  \label{E:entropy2}
  H(Z)=-\int_{-\infty }^\infty \ f(z)\ln f(z)\, \mathrm{d}z,
\end{equation}
here, $f(\cdot)$ is the probability density function that characterizes the distribution of the real-valued random variable $Z$.

Using&nbsp;\eqref{E:entropy2}, we can express the Shannon entropy of $\Gamma_{\text{SAR}}$in&nbsp;\eqref{E:gamma1} and $G_I^0$ in&nbsp;\eqref{E:gi02} based on&nbsp;\cite{Cassetti2022} and&nbsp;\cite{Ferreira2020}:
\begin{equation}
\label{E:E-gamma}
H_{\Gamma_{\text{SAR}}}(L, \mu) =   L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu, 
\end{equation}
\begin{multline}
\label{E:E-GIO}
H_{G_I^0}(\mu, \alpha, L) =L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) +\ln \mu -\ln\Gamma(L-\alpha)\\
+ (L-\alpha) \psi^{(0)}(L-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L,
\end{multline}
where $\psi^{(0)}(\cdot)$ is the digamma function. Fig.&nbsp;\ref{fig:Plot_GI0_to_gamma1}, shows the behaviour of the entropy of \(G_I^0\) when when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), observing its convergence towards the entropy of \(\Gamma_{\text{SAR}}\) as \(\alpha\) takes large negative values.

```{r Plot_GI0_to_gamma1, echo=FALSE, message=FALSE, warning=FALSE, out.width="70%", fig.show="hold", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ with $L=8$."}

L <- c(8)
alphas <- c(  -3, -8, -20, -1000)
alpha_labels <- c( expression(italic(alpha) == -3), expression(italic(alpha) == -8), expression(italic(alpha) == -20), expression(italic(alpha) == -1000))

mu <- seq(0.1, 10, length.out = 500)

# Entropy GI0

muEntropy <- data.frame()

for (alpha in alphas) {
  entropies_GI0 <- sapply(L, function(L) entropy_gI0(mu, alpha, L))
  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
}

muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"),  value.name = "Entropy")

# Entropy Gamma SAR

entropies_gamma <- sapply(L, function(L) entropy_gamma_sar(L, mu))

Entropy_gamma <- data.frame(mu, entropies_gamma)

Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy Gamma")

#plot

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "solid",linewidth = 1.5) + 
  geom_line(linetype = "longdash",  linewidth = 2, alpha=.7) +
  annotate("text", x = max(mu)+0.2, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
  theme_minimal() +
  scale_color_manual(values = brewer.pal(7, "Dark2")[1:5], labels = alpha_labels) +
  #scale_color_manual(values = pal_jama()(7)[2:5], labels = alpha_labels) +
  #scale_color_manual(values = 	pal_cosmic()(7)[1:5], labels = alpha_labels) +
  labs(col = "Roughness", linetype = NULL) +
  xlab(expression(paste(mu))) +
  ylab("Entropy") +  
  theme(text = element_text(family = "serif"),
        legend.position = "bottom")

```

## Estimation of the Shannon Entropy

The problem of non-parametric estimating of $H(Z)$ has been considered by many authors including&nbsp;\cite{vasicek1976test, Wieczorkowski1999,correa1995new,AlOmari2019}, who proposed estimators based on spacings.

One of the earliest non-parametric estimators relying on spacings was introduced by Vasicek&nbsp;\cite{vasicek1976test}. 
Assuming that $\bm{Z}=(Z_1, Z_2,\ldots,Z_n)$ is a random sample from the distribution $F(z)$, the estimator is defined as:
\begin{equation*}
\label{E:Vas}
	\widehat{H}_{\text{V}}(\bm{Z})=\frac{1}{n}\sum_{i=1}^{n}\ln\left[\frac{n}{2m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
	\end{equation*}
where $m<n/2$ is a positive integer, $Z_{(i+m)}-Z_{(i-m)}$ is the $m$-spacing and $Z_{(1)}\leq Z_{(2)}\leq\ldots\leq Z_{(n)}$ are the order statistics and $Z_{(i)}= Z_{(1)}$ if $i<1$, $Z_{(i)}= Z_{(n)}$ if $i>n$.

Several authors have explored adaptations to Vasicek's estimator. 
We consider three estimators known for their superior performance&nbsp;\cite{Cassetti2022}:

* Correa&nbsp;\cite{correa1995new}: $\widehat{H}_{\text{C}}$.

* Ebrahimi et al&nbsp;\cite{Ebrahimi1994}: $\widehat{H}_{\mathrm{E}}$.

* Al Omary&nbsp;\cite{IbrahimAlOmari2014}: $\widehat{H}_{\mathrm{AO}}$.

## Enhanced Bootstrap Technique

We employ the bootstrap technique to refine the precision of existing non-parametric entropy estimators. 
This approach involves generating new datasets through resampling with repetition from an existing one&nbsp;\cite{Michelucci2021}.

<!-- This approach involves generating new datasets through resampling with repetition from an existing one. -->

Let's assume that non-parametric entropy estimators \(\widehat{H}=\widehat{\theta}(\bm{Z})\) are inherently biased, that is:
\begin{equation}
\label{Eq:bias1}
\bias\big(\widehat{\theta}(\bm{Z})\big) = E\big[\widehat{\theta}(\bm{Z})\big] - \theta \neq 0.
\end{equation}
Our bootstrap-improved estimators are of the form:
<!-- introducing an "ideal unbiased estimator" \(\check{\theta}(\bm{Z})\): -->
<!-- \begin{equation} -->
<!-- \label{Eq:bias2} -->
<!-- \widecheck{\theta}(\bm{Z}) = \widehat{\theta}(\bm{Z}) - \bias\big(\widehat{\theta}(\bm{Z})\big). -->
<!-- \end{equation} -->
<!-- However, \(\check{\theta}(\bm{Z})\) is not an estimator, because it depends on the true parameter \(\theta\), prompting the formulation of a new estimator \(\widetilde{H}\).  -->
<!-- From&nbsp;\eqref{Eq:bias1} and&nbsp;\eqref{Eq:bias2} we have: -->
\begin{align*}
\widetilde{H} &= 2\widehat{\theta}(\bm{Z}) - \frac{1}{B}\sum_{b=1}^B \widehat{\theta}_b(\bm{Z}^{(b)}),
\end{align*}
where $B$ is the number of replications in the bootstrap technique.
Applying this methodology, the original estimators by Correa, Ebrahimi, and Al-Omari are now denoted as the proposed bootstrap-enhanced versions: $\widetilde{H}_{\text{C}}$, $\widetilde{H}_{\text{E}}$, and $\widetilde{H}_{\text{AO}}$, respectively.

We analyzed the performance of these estimators with a Monte Carlo study:
$500$ samples of $G_I^0$ of size \(n\in\left\{9, 25, 49, 81, 121\right\}\) and several values of the mean, number of looks and roughness.
We present the results with \(mu\in\left\{1, 10\right\}\), \(\alpha=-10\), and \(L=5\). 
The results are consistent for the other situations. 
In the case of the bootstrap technique, each sample is replicated $100$ times with replacement.
We choose to use the following heuristic formula for spacing, $m=\left[\sqrt{n}+0.5\right]$.

In Fig.&nbsp;\ref{fig:Plot_bias_mse_gi0} we depict comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions. 
The use of the bootstrap technique exhibits more precision, reduced bias and MSE, and improved convergence.
The results of simulation are exhibited in Table&nbsp;\ref{tab:table2}.

The precision of estimators, as evidenced by bias and MSE comparisons, benefits significantly from the bootstrap technique, particularly for sample sizes below 81.

```{r Simulated_data_gi0, echo=FALSE, message=FALSE}

set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121 )

# Number of replications
R <-200

# Number of bootstrap replications
B1 <- 5
mu_values <- c(1, 10)
alpha <- -20
L <- 5

estimators <- list(
  "Correa" = correa_estimator,
  "Ebrahimi" = ebrahimi_estimator,
  "Al Omari" = al_omari_1_estimator,
  "Correa Bootstrap" = bootstrap_correa_estimator,
  "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
  "Al Omari Bootstrap" = bootstrap_al_omari_1_estimator
)

calculate_results_gi0 <- function(sample_sizes, R, B1, mu_values, alpha, L, estimators) {
  results_list <- list()

  for (mu_val in mu_values) {

    results <- calculate_bias_mse_gi0(sample_sizes, R, B1, mu_val, alpha, L, estimators)
    df <- as.data.frame(results)

    results_list[[as.character(mu_val)]] <- df
  }

  return(results_list)
}

results_gi0 <- calculate_results_gi0(sample_sizes, R, B1, mu_values, alpha, L, estimators)

save(results_gi0, file = "./Data/resultsgi0_1.Rdata")

```

```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.pos="hbt",  fig.cap="Bias and MSE, $L=5$ and  $\\alpha=-10$.", fig.width=8, fig.height=5.5}

load("./Data/resultsgi0_1.Rdata")

estimators_to_plot <- c("Correa", "Ebrahimi", "Al Omari",  "Correa Bootstrap", "Ebrahimi Bootstrap", "Al Omari Bootstrap" )
  latex_estimator_names <- c("Correa" = expression("$\\widehat{italic(H)}_{C}$"),
                             "Correa Bootstrap" = expression("$\\widetilde{italic(H)}_{C}$"),
                            "Ebrahimi" = expression("$\\widehat{italic(H)}_{E}$"),
                            "Al Omari" = expression("$\\widehat{italic(H)}_{AO}$"),
                            "Ebrahimi Bootstrap" = expression("$\\widetilde{italic(H)}_{E}$"),
                            "Al Omari Bootstrap" = expression("$\\widetilde{italic(H)}_{AO}$"))
selected_estimators_latex <- latex_estimator_names[estimators_to_plot]

combined_plot_gi0 <- generate_plot_gi0_esp(results_gi0, mu_values, selected_estimators_latex, ncol = 1, nrow = 2)

print(combined_plot_gi0)

```

```{r Table_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#cat("\\setlength{\\tabcolsep}{0.5pt}\n")
load("./Data/resultsgi0_1.Rdata")

# Define estimators
estimators_to_table <- c( "Al Omari","Correa", "Ebrahimi", "Al Omari Bootstrap",  "Correa Bootstrap","Ebrahimi Bootstrap")

# Filter and reshape data
filtered_results <- purrr::map_dfr(results_gi0, ~ .x %>% filter(Estimator %in% estimators_to_table), .id = "mu")

reshaped_results <- filtered_results %>%
  pivot_wider(names_from = Estimator, values_from = c(Bias, MSE))

colnames(reshaped_results) <- c("$\\mu$", "$n$", "$\\widehat{H}_{\\text{AO}}$", "$\\widehat{H}_{\\text{C}}$", "$\\widehat{H}_{\\text{E}}$", "$\\widetilde{H}_{\\text{AO}}$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$",  "$\\widehat{H}_{\\text{AO}}$", "$\\widehat{H}_{\\text{C}}$", "$\\widehat{H}_{\\text{E}}$","$\\widetilde{H}_{\\text{AO}}$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$")

reshaped_results[] <- lapply(reshaped_results, function(x, col_name) {
  if (is.numeric(x)) {
    if (col_name == "\\mu") {
      formatted_numbers <- sprintf("$\\scriptstyle %d$", x)
    } else {
      if (all(x %% 1 == 0)) {
        formatted_numbers <- sprintf("$%d$", x)
      } else {
        formatted_numbers <- ifelse(x < 0, sprintf("$%.3f$", x), sprintf("$\\phantom{-}%.3f$", x))
      }
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
}, col_name = names(reshaped_results)[1])

#print(
 # kbl(
knitr::kable(
    reshaped_results,
    caption = "Bias and MSE of non-parametric entropy estimators and bootstrap versions.",
    format = "latex",
    booktabs = TRUE,
    align = "lrrrrrrrrrrrrrrr",
    escape = FALSE, 
    digits = 2,  
    label = "table2",
    centering = FALSE,
    table.envir = "table", position = "H") %>%
    add_header_above(c(" ", " ", "Bias" = 6,  "MSE" = 6)) %>%
    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
    row_spec(0,  align = "c")%>%
    kable_styling(latex_options = "scale_down")
  #)
  #kable_styling(latex_options = c("scale_down"))

```

# Hypothesis testing based on non-parametric entropy {#sec:test}

General asymptotic results for functions of spacings are detailed in Ref.&nbsp;\cite{Khashimov1990}, while Van Es&nbsp;\cite{Bert1992} developed a correction for the case of Shannon entropy.
Following the work of these authors, the next result applies: 
<!-- \begin{lemma} -->
<!-- Suppose that $f(\cdot)$ is a bounded density bounded away from zero and satisfies a Lipschitz condition on its support. -->
<!-- Then, if $m,n\rightarrow \infty$ and $m=o(n^{1/2})$, one holds that: -->
<!-- \begin{equation*} -->
<!-- \sqrt{n}\,\Big(\label{Eq:bias_t} -->
<!-- \widetilde{H}_{i}+\int_{-\infty}^\infty f(z)\ln f(z) \mathrm{d}z\Big) -->
<!-- \xrightarrow[]{\mathcal{D}} -->
<!-- \mathcal{N}\big(0,\operatorname{Var}(\ln f(Z))\big), -->
<!-- \end{equation*} -->
<!-- where $o(\cdot)$ represents the little-o. -->
<!-- \end{lemma}  -->

We aim at testing the following hypotheses:

$$
 \begin{cases}\mathcal{H}_0: \widetilde{H}= H_{\Gamma_{\text{SAR}}}\\ 
  \mathcal{H}_1:\widetilde{H}\neq H_{\Gamma_{\text{SAR}}}.\end{cases}
$$
In other words, we verify the hypothesis that the data are fully-developed speckle with the following test statistic:
\begin{equation}
\label{Eq:test_e}
S(\bm{Z};L)= \widetilde{H}-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{\bm{Z}}\right].
\end{equation}
<!-- This test statistic assess the behavior of the data under the null hypothesis, through the empirical distribution.  -->
The values should be around zero under the null hypothesis and far otherwise. 
<!-- This suggests significant differences and implies the presence of heterogeneous clutter. -->

# Results {#sec:results}

## The Proposed Test
Fig.&nbsp;\ref{fig:Plot_density} depicts empirical test statistic densities for various sample sizes, and Table&nbsp;\ref{tab:table_stat_combined} summarizes key statistics, including mean, SD, variance (Var), skewness (SK), excess kurtosis (EK), and Anderson–Darling $p$-values for normality. 
<!-- ACF Only show L=2 and L=8 -->
Results with $p$-values larger than $0.05$  indicate no evidence against normality. 
Small variance and near-zero skewness and excess kurtosis suggest limited spread, symmetry, and light tails.  
Normal QQ-plots, confirm that there is no evidence to reject the normal distribution.

<!-- In Fig.&nbsp;\ref{fig:Plot_normality_qq}, normal QQ-plots visually affirm distributional similarity with the expected normal line. -->

```{r Simulated_density, echo=FALSE, message=FALSE}
#, cache = TRUE, autodep = TRUE
set.seed(1234567890, kind = "Mersenne-Twister")

R <- 500
mu <- 1
B <- 1

sample.size <- c(25,49, 81, 121)
L_values <- c(3,  5, 8, 11)

all_summary_stats <- list()
all_TestStatistics <- list()

# For each L
for (L in L_values) {
  TestStatistics1 <- list()  
  summary_stats <- data.frame( LValue = character(),
                              SampleSize = numeric(),
                              Mean = numeric(),
                              SD = numeric(),
                              Variance = numeric(),
                              #CV= numeric(),
                              Skewness = numeric(),
                              Kurtosis = numeric(),
                              adpvalue = numeric()
                              )

  for (s in sample.size) {
    TestStat1 <- numeric(R)

    for (r in 1:R) {
      z <- gamma_sar_sample(L, mu, s)
      #z <- gi0_sample(mu, alpha1, L, s)
      TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
    }

    TestStatistics1[[as.character(s)]] <- data.frame("SampleSize" = rep(s, R), "Test_Statistics" = TestStat1)

    mean_val <- mean(TestStat1)
    sd_val <- sd(TestStat1)
    var_val <- var(TestStat1)
    skewness_val <- skewness(TestStat1)
    kurtosis_val <- kurtosis(TestStat1)
   # lillie_p_value <- lillie.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
    ad_p_value <- ad.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
    #cv_val <- abs(sd_val / mean_val)

    summary_stats <- rbind(summary_stats, data.frame(LValue = as.character(L),
                                                     SampleSize = s,
                                                     Mean = mean_val,
                                                     SD = sd_val,
                                                     Variance = var_val,
                                                      #CV = cv_val,
                                                     Skewness = skewness_val,
                                                     Kurtosis = kurtosis_val,
                                                     adpvalue = ad_p_value
                                                     ))

  }

  all_TestStatistics[[as.character(L)]] <- TestStatistics1
  all_summary_stats[[as.character(L)]] <- summary_stats

  save(all_TestStatistics, all_summary_stats, file = paste0("./Data/results1_", L, ".Rdata"))
}

```

```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.pos="hbt",  fig.cap="Empirical density  under null hypothesis.", fig.width=6, fig.height=5.0}

theme_set(theme_minimal() +
            theme(text = element_text(family = "serif"),
                  legend.position = "bottom",
                  legend.text = element_text(angle = 0, vjust = 0.5)))

all_plots <- list()

for (L in L_values) {
  load(paste0("./Data/results1_", L, ".Rdata"))

  combined_data <- do.call(rbind, all_TestStatistics[[as.character(L)]])
  combined_data$L <- L

  p <- ggplot(combined_data, aes(x = Test_Statistics, col = factor(SampleSize), linetype = factor(SampleSize))) +
    geom_line(stat = "density", linewidth = 1.0) +
    scale_color_viridis(discrete = TRUE, option = "C", direction = -1, begin = 0.1, end = 0.8, name = "Sample Size") +
    scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
    labs(x = "Test Statistics", y = "Density") +
    ggtitle(bquote(italic(L) == .(L))) +
    theme(plot.title = element_text(hjust = 0.5))#titulo centrado

  if (!any(L == L_values)) {
    p = p
  }

  all_plots[[as.character(L)]] <- p
}

combined_plot <- wrap_plots(all_plots, ncol = 2, nrow = 2) +
  plot_layout(guides = "collect")

print(combined_plot)

```

```{r Table_statistic, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

#cat("\\setlength{\\tabcolsep}{1.0pt}\n")

load("./Data/results1_3.Rdata")
summary_stats_2 <- all_summary_stats[["3"]]

load("./Data/results1_5.Rdata")
summary_stats_5 <- all_summary_stats[["5"]]

load("./Data/results1_8.Rdata")
summary_stats_8 <- all_summary_stats[["8"]]

combined_summary_stats <- rbind(
  transform(summary_stats_2),
  transform(summary_stats_5),
  transform(summary_stats_8)

)
colnames(combined_summary_stats) <- c("$L$", "$n$", "Mean", "SD", "Var", "SK", "EK", "$p$-value")

# LaTeX notation 
combined_summary_stats[] <- lapply(combined_summary_stats, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.4f$", x), sprintf("$\\phantom{-}%.4f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})

table_result_combined <- knitr::kable(
  combined_summary_stats,
  caption = "Descriptive analysis of $S(\\bm Z; L)$ with $L\\in\\left\\{3,5, 8\\right\\}$ and $\\mu=1$.",
  format = "latex",
  booktabs = TRUE,
  align = "lrrrrrrr",
  escape = FALSE,
  digits = 4,
  label = "table_stat_combined",
  centering = FALSE,
  table.envir = "table", position = "H") %>%
  #table.env = 'table*' # to span multiple columns
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")

print(table_result_combined)

```

```{r Plot_normality_qq, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.pos="hbt",  fig.cap="Normal QQ-plots for  $n=121$.", fig.width=6, fig.height=5}

theme_set(theme_minimal() +
            theme(text = element_text(family = "serif"),
                  legend.position = "bottom",
                  legend.text = element_text(angle = 0, vjust = 0.5)))

# Load saved results
load("./Data/results1_3.Rdata")
load("./Data/results1_5.Rdata")
load("./Data/results1_8.Rdata")
load("./Data/results1_11.Rdata")

# Specific sample size
selected_sample_size <- 121

# 
ggplot_list <- list()

#  L
for (L in c(3, 5, 8, 11)) {
  TestStatistics1 <- all_TestStatistics[[as.character(L)]]

  # 
  if (as.character(selected_sample_size) %in% names(TestStatistics1)) {
    p <- ggplot(TestStatistics1[[as.character(selected_sample_size)]], 
                aes(sample = Test_Statistics)) +
      geom_qq(col = "blue", shape = 20) +
      geom_qq_line(col = "darkgreen", linetype = 2) +
      labs(title = bquote(italic(L) == .(L)),
           x = "Theoretical Quantiles",
           y = "Sample Quantiles") +
      theme(plot.title = element_text(hjust = 0.5))#titulo centrado

    ggplot_list[[as.character(L)]] <- p
  } else {
    warning(paste("No size sample", selected_sample_size, " L =", L))
  }
}
combined_plot1 <- wrap_plots(ggplot_list, ncol = 2, nrow = 2) +
  plot_layout(guides = "collect")

print(combined_plot1)

# }

```

After verifying the normality of the data, we proceeded to explore the capabilities of the proposed test in terms of size and power.
Under $\mathcal{H}_0$, the distribution of test statistic is asymptotically normal. Therefore, the $p$-value  is calculated as $2\Phi(-\mid \varepsilon\mid)$, where  $\Phi$ is the standard Gaussian cumulative distribution and $\varepsilon$ is the standardized test statistic given by:
$$
\varepsilon=\frac{\tilde{H}-H_{\Gamma_{\text{SAR}}}}{\hat\sigma}.
$$

We considered nominal levels of \SI{1}{\percent}, \SI{5}{\percent}, and \SI{10}{\percent}. 
In reference to the size, $1000$ simulations have been used for various sample sizes with  satisfactory results. In all cases, the nominal level has been achieved. 
The power, in general, improves with the increase in the sample size and the number of looks. 
The results are presented in Table&nbsp;\ref{tab:table_size_power}.

```{r Simulated_error_type_I, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")

# 
calculate_p_value <- function(test_statistic, mu_W, sigma_W, alpha_nominal) {
  epsilon <- test_statistic / sigma_W
  p_value <- 2 * (1 - pnorm(abs(epsilon)))

  return(p_value < alpha_nominal)  
}

R <- 100
mu <- 1
B <- 1
L_values <- c( 3, 5, 8, 11)
sample_sizes <- c( 25, 49, 81, 121)
alpha_nominals <- c(0.01, 0.05, 0.1)

results <- data.frame()

for (L in L_values) {
  for (alpha_nominal in alpha_nominals) {
    TestStatistics <- NULL
    mean_entropy <- numeric(length(sample_sizes))
    sd_entropy <- numeric(length(sample_sizes))

    for (s in sample_sizes) {
      TestStat <- numeric(R)

      for (r in 1:R) {
        z <- gamma_sar_sample(L, mu, s)
        TestStat[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
      }
      mean_entropy[sample_sizes == s] <- mean(TestStat)
      sd_entropy[sample_sizes == s] <- sd(TestStat)

      TestStatistics <- rbind(TestStatistics, data.frame("L" = rep(L, R), "Sample_Size" = rep(s, R), "Test_Statistics" = TestStat))
    }

    mu_W <- mean_entropy
    sigma_W <- sqrt(sd_entropy^2)

    p_values <- apply(TestStatistics, 1, function(row) {
      calculate_p_value(row["Test_Statistics"], mu_W[sample_sizes == row["Sample_Size"]], sigma_W[sample_sizes == row["Sample_Size"]], alpha_nominal)
    })

    result <- data.frame("L" = TestStatistics$L, "Sample_Size" = TestStatistics$Sample_Size, "Alpha_Nominal" = alpha_nominal, "P_Value" = p_values)
    results <- rbind(results, result)
  }
}

save(results, file = "./Data/type_I_results1.Rdata")

```

```{r Simulated_power, echo=FALSE, message=FALSE}

set.seed(1234567890, kind = "Mersenne-Twister")

calculate_p_value <- function(test_statistic, mu_W, sigma_W) {
  epsilon <- test_statistic  / sigma_W
  p_value <- 2 * (1 - pnorm(abs(epsilon)))

  return(p_value)
}

calculate_type_II_error_rate <- function(p_values, alpha_nominal) {
  type_II_error_rate <- sum(p_values >= alpha_nominal) / length(p_values)
  return(type_II_error_rate)
}

# Function to calculate power for different L values and alpha_nominals
calculate_power <- function(R, mu, L_values, B, sample_sizes, alpha_nominals) {
  results <- data.frame()

  for (L in L_values) {
    for (alpha_nominal in alpha_nominals) {
      TestStatistics <- list()
      mean_entropy <- numeric(length(sample_sizes))
      sd_entropy <- numeric(length(sample_sizes))

      for (s in sample_sizes) {
        TestStat <- numeric(R)

        for (r in 1:R) {
          z <- gi0_sample(mu, -5, L, s)
          TestStat[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
        }

        mean_entropy[sample_sizes == s] <- mean(TestStat)
        sd_entropy[sample_sizes == s] <- sd(TestStat)

        TestStatistics[[as.character(s)]] <- TestStat
      }

      mu_W <-  mean_entropy  
      sigma_W <- sqrt(sd_entropy^2)

      p_values <- lapply(TestStatistics, function(TestStat) {
        apply(data.frame("Test_Statistics" = TestStat), 1, function(row) {
          calculate_p_value(row["Test_Statistics"], mu_W, sigma_W[as.numeric(names(TestStatistics)) == as.numeric(s)])
        })
      })

      type_II_error_rates <- sapply(p_values, function(p_values_for_size) {
        calculate_type_II_error_rate(p_values_for_size, alpha_nominal)
      })

      power <- 1 - type_II_error_rates

      result_row <- data.frame(
        L = L,
        alpha_nominal = alpha_nominal,
        Sample_Size = sample_sizes,
        power = power
      )

      results <- rbind(results, result_row)
    }
  }

  return(results)
}

R <- 100
mu <- 1
L_values <- c(3, 5,  8, 11)
B <- 1
sample_sizes <- c(25, 49, 81, 121)
alpha_nominals <- c(0.01, 0.05, 0.1)

results_power <- calculate_power(R, mu, L_values, B, sample_sizes, alpha_nominals)
save(results_power, file = "./Data/results_power1.Rdata")

```

```{r Table_size_and_power, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#cat("\\setlength{\\tabcolsep}{4pt}\n")

load("./Data/type_I_results1.Rdata")

type_I_error_rates <- tapply(results$P_Value, INDEX = list(results$L, results$Sample_Size, results$Alpha_Nominal), FUN = function(p_values) {
  sum(p_values) / length(p_values)  
})

type_I_error_results <- as.data.frame(as.table(type_I_error_rates))

colnames(type_I_error_results) <- c("L", "Sample_Size", "Alpha_Nominal", "Type_I_Error_Rate")

spread_results <- spread(type_I_error_results, key = Alpha_Nominal, value = Type_I_Error_Rate)

spread_results <- spread_results %>% 
  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)

load("./Data/results_power1.Rdata")

summary_stats <- results_power %>%
  spread(key = alpha_nominal, value = power) %>%
  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)

combined_results <- merge(spread_results, summary_stats, by = c("L", "Sample_Size"))
combined_results <- combined_results %>% 
  arrange(L, Sample_Size)

combined_results <- combined_results %>% 
  select(L, Sample_Size, `0.01.x`, `0.05.x`, `0.1.x`, `0.01.y`, `0.05.y`, `0.1.y`)

colnames(combined_results) <- c("$L$", "$n$", "$1\\%$", "$5\\%$", "$10\\%$", "$1\\%$", "$5\\%$", "$10\\%$")

# LaTeX notation 
combined_results[] <- lapply(combined_results, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.3f$", x), sprintf("$\\phantom{-}%.3f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})

table_combined_result <- knitr::kable(
  combined_results,
  caption = "Size and Power of the proposed test.",
  format = "latex",
  booktabs = TRUE,
  align = "lcccccccc",
  escape = FALSE,
  digits = 3,
  label = "table_size_power",
  centering = FALSE,
  linesep = "",
  table.envir = "table", position = "H")%>%
  add_header_above(c(" ", " ", "Size" = 3,  "Power" = 3)) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")

print(table_combined_result)

```

# Conclusion {#sec:conclusion}

### 2024-03-14 Code/R/MainFunctions/adaptive_al_omari_1_estimator.R

@@ -1,0 +1,108 @@
+# adaptive_al_omari_1_estimator <- function(data) {
+#   n <- length(data)
+#   data_sorted <- sort(data)
+#   sum_term <- numeric(n-1)
+#   
+#   for (m in 1:(n-1)) {
+#     #sum_term <- 0
+#     
+#     for (i in 1:n) {
+#       if (i <= m) {
+#         omega_i <- 3/2
+#         diff_term <- data_sorted[i + m] - data_sorted[1]
+#       } else if (i >= n - m + 1) {
+#         omega_i <- 3/2
+#         diff_term <- data_sorted[n] - data_sorted[i - m]
+#       } else {
+#         omega_i <- 2
+#         diff_term <- data_sorted[i + m] - data_sorted[i - m]
+#       }
+#       
+#       sum_term <- sum_term + log((n / (omega_i * m)) * diff_term)
+#     }
+#     
+#     sum_term <- sum_term / n
+#   }
+#   
+#   estimated_entropy <-  (1/(n-1)) * sum_term
+#   
+#   #cat("Debug info: sum_term =", sum_term, "\n")
+#   
+#   return(estimated_entropy)
+# }
+
+adaptive_al_omari_1_estimator <- function(data) {
+  n <- length(data)
+  data_sorted <- sort(data)
+  sum_term <- numeric(n-1)
+
+  for (m in 1:(n-1)) {
+    sum_term[m] <- 0
+
+    for (i in 1:n) {
+      if (i <= m) {
+        omega_i <- 3/2
+        diff_term <- data_sorted[i + m] - data_sorted[1]
+      } else if (i >= n - m + 1) {
+        omega_i <- 3/2
+        diff_term <- data_sorted[n] - data_sorted[i - m]
+      } else {
+        omega_i <- 2
+        diff_term <- data_sorted[i + m] - data_sorted[i - m]
+      }
+
+      if (!is.na(diff_term) && diff_term != 0) {
+        sum_term[m] <- sum_term[m] + log((n / (omega_i * m)) * diff_term)
+      }
+    }
+
+    sum_term[m] <- sum_term[m] / n
+  }
+
+  estimated_entropy <- mean(sum_term, na.rm = TRUE)
+
+  #cat("Debug info: sum_term =", sum_term, "\n")
+
+  return(estimated_entropy)
+}
+
+# al_omari_estimator <- function(X) {
+#   n <- length(X)
[…]

### 2024-03-14 Code/R/MainFunctions/adaptive_correa_estimator.R

@@ -1,0 +1,32 @@
+adaptive_correa_estimator <- function(data) {
+  n <- length(data)
+  X_sorted <- sort(data)
+  C_mn <- numeric(n-1)
+  
+  for (m in 1:(n-1)) {
+    C_mn[m] <- 0
+    
+    for (i in 1:n) {
+      i_minus_m <- max(1, i - m)
+      i_plus_m <- min(n, i + m)
+      
+      X_i <- X_sorted[i]
+      X_window <- X_sorted[i_minus_m:i_plus_m]
+      X_bar_i <- mean(X_window)
+      
+      differences <- X_window - X_bar_i
+      num <- sum(differences * (i_minus_m:i_plus_m - i))
+      den <- n * sum(differences^2)
+      
+      b_i <- ifelse(den == 0, 0, num / den)
+      
+      C_mn[m] <- C_mn[m] - log(pmax(b_i, 0))
+    }
+    
+    C_mn[m] <- C_mn[m] / n
+  }
+  
+  estimated_entropy <- mean(C_mn)
+  
+  return(estimated_entropy)
+}

### 2024-03-14 Code/R/MainFunctions/al_omari_2_estimator.R

@@ -1,0 +1,28 @@
+al_omari_2_estimator <- function(data) {
+  n <- length(data)
+  m <- round(sqrt(n) + 0.5)  # m-spacing
+  data_sorted <- sort(data)
+  sum_term <- 0
+  
+  for (i in 1:n) {
+    if (i <= m) {
+      vi <- 1 + (i - 1) / m
+      diff_term <- data_sorted[i + m] - data_sorted[1]
+    } else if (i >= n - m + 1) {
+      vi <- 1 + (n - i) / (2 * m)
+      diff_term <- data_sorted[n] - data_sorted[i - m]
+    } else {
+      vi <- 2
+      diff_term <- data_sorted[i + m] - data_sorted[i - m]
+    }
+    
+    sum_term <- sum_term + log((n / (vi * m)) * diff_term)
+  }
+  
+  return(sum_term / n)
+}
+
+# # Example usage:
+# data <- c(1.2, 1.5,3.6, 2.0, 2.1, 2.5, 2.6, 3.0, 3.1, 3.5)
+# result <- al_omari_2_estimator(data)
+# cat("Al-Omari-2 Estimator:", result, "\n")

### 2024-03-14 Code/R/MainFunctions/bootstrap.Estimator.R

@@ -1,0 +1,92 @@
+#
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/correa_estimator.r")
+source("../MainFunctions/ebrahimi_estimator.r")
+source("../MainFunctions/noughabi_arghami_estimator.r")
+source("../MainFunctions/vasicek_estimator.r")
+source("../MainFunctions/al_omari_1_estimator.r")
+source("../MainFunctions/al_omari_2_estimator.r")
+
+# bootstrap.Estimator <- function(x, B){
+#   sample_size <- length(x)
+#   t <- van_es_estimator(x)
+#   
+#   v.Bootstrap <- rep(0, B) 
+#   for(b in 1:B) {
+#     bx <- sample(x, replace = TRUE, size = sample_size)  # Toma muestras del mismo tamaño que la muestra original
+#     
+#     # Añade una condición para verificar si todos los valores son iguales en la muestra Bootstrap
+#     if (!all(bx == bx[1])) {
+#       est_bx <- van_es_estimator(bx)
+#       
+#       # Añade una condición para descartar estimaciones donde la entropía es cero
+#       if (est_bx == 0) {
+#         v.Bootstrap[b] <- NA
+#       } else {
+#         v.Bootstrap[b] <- est_bx
+#       }
+#     } else {
+#       v.Bootstrap[b] <- NA  # Descarta la muestra Bootstrap con todos los valores iguales
+#     }
+#   }
+#   
+#   bootstrap_mean <- mean(v.Bootstrap, na.rm = TRUE)
+#   
+#   improved_estimator <- 2 * t - bootstrap_mean
+#   
+#   return(improved_estimator)
+# }
+
+
+
+# bootstrap.Estimator <- function(x, B){
+#   sample_size <- length(x)
+#   t <- van_es_estimator(x)
+#   
+#   # Define B en función del tamaño de la muestra
+#   #B <- sample_size * 2  # Puedes ajustar esto según tus necesidades
+#   
+#   v.Bootstrap <- rep(0, B) 
+#   for(b in 1:B) {
+#     bx <- sample(x, replace = TRUE, size = sample_size)  # Toma muestras del mismo tamaño que la muestra original
+#     est_bx <- van_es_estimator(bx)
+#     
[…]

### 2024-03-14 Code/R/MainFunctions/bootstrap_Estimator1.R

@@ -1,0 +1,60 @@
+
+rm(list = ls())
+library(ggplot2)
+library(gtools)
+library(stats4)
+library(rmutil)
+#library(gsl)
+library(invgamma)
+library(ggplot2)
+library(ggthemes)
+theme_set(theme_pander() +
+            theme(text=element_text(family="serif"),
+                  legend.position = "top")
+)
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/correa_estimator.r")
+source("../MainFunctions/ebrahimi_estimator.r")
+source("../MainFunctions/noughabi_arghami_estimator.r")
+source("../MainFunctions/vasicek_estimator.r")
+source("../MainFunctions/al_omari_1_estimator.r")
+source("../MainFunctions/al_omari_2_estimator.r")
+source("../MainFunctions/bootstrap_estimator.r")
+
+# genera muestras con repeticion:
+bootstrap_estimator1 <- function(data, B, seed = NULL, verbose = FALSE) {
+  if (!is.null(seed)) set.seed(seed)
+  n <- length(data)
+  t <- van_es_estimator(data)
+  bx <- numeric(B)
+  
+  for (i in 1:B) {
+    sampled_indices <- sample(1:n, n, replace = TRUE)
+    sampled_data <- data[sampled_indices]
+    bx[i] <- van_es_estimator(sampled_data)
+    
+    if (verbose) {
+      cat("Bootstrap Sample", i, ": ", sampled_data, "\n")
+    }
+  }
+ 
+  estimated_mean <- mean(bx)
+  
+  # cat("mean_entropies: ", estimated_mean, "\n")
+  # cat("t: ", t, "\n")
+  
+  
+  return(2*t - estimated_mean)
+}
+
+# seed1 <- set.seed(1234567890, kind = "Mersenne-Twister")
+# # # Use
+data <- c(3, 5, 1)
+result <- bootstrap_estimator1(data, 5, seed = 123, verbose = TRUE)
+ correa1 <- van_es_estimator(data)
+#
+ cat("entropy: ", result, "\n")
+ cat("correa: ", correa1, "\n")

### 2024-03-14 Code/R/MainFunctions/bootstrap_al_omari_2_estimator.R

@@ -1,0 +1,33 @@
+
+
+
+
+#source("../MainFunctions/al_omari_2_estimator.r")
+
+
+bootstrap_al_omari_2_estimator <- function(x, B){
+  
+  v.Bootstrap <- rep(0, B)
+  
+  for(b in 1:B) {
+    same_values <- TRUE
+    while (same_values) {
+      bx <- sample(x, replace = TRUE)
+      if (!all(bx == bx[1])) {
+        same_values <- FALSE
+        entropy_result <- al_omari_2_estimator(bx)
+        if (is.finite(entropy_result)) {
+          v.Bootstrap[b] <- entropy_result
+          #cat("Entropy for Bootstrap Sample", b, ": ", v.Bootstrap[b], "\n")
+        }
+      }
+    }
+  }
+  
+  
+  t <- al_omari_2_estimator(x)
+  estimated_mean <- mean(v.Bootstrap[!is.na(v.Bootstrap)])
+  
+  return(2*t - estimated_mean)
+  
+}

### 2024-03-14 Code/R/MainFunctions/bootstrap_correa_estimator.R

@@ -1,0 +1,41 @@
+
+
+
+
+#source("../MainFunctions/correa_estimator.R")
+
+
+bootstrap_correa_estimator <-  function(x, B){
+  
+  v.Bootstrap <- rep(0, B)
+  
+  for(b in 1:B) {
+    same_values <- TRUE
+    while (same_values) {
+      bx <- sample(x, replace = TRUE)
+      if (!all(bx == bx[1])) {
+        same_values <- FALSE
+        entropy_result <- correa_estimator(bx)
+        if (is.finite(entropy_result)) {
+          v.Bootstrap[b] <- entropy_result
+          #cat("Bootstrap Sample", b, ": ", bx, "\n")
+          #cat("Entropy for Bootstrap Sample", b, ": ", v.Bootstrap[b], "\n")
+        }
+      }
+    }
+  }
+  
+  
+  t <- correa_estimator(x)
+  estimated_mean <- mean(v.Bootstrap[!is.na(v.Bootstrap)])
+  
+  return(2*t - estimated_mean)
+  
+}
+
+# data <- c(1.2, 1.5,3.6, 2.0, 2.1, 2.5, 2.6, 3.0, 3.1, 3.5)
+# result <- bootstrap_correa_estimator(data, 10)
+# cat("Al-Omari-1 Estimator:", result, "\n")
+
+
+

### 2024-03-14 Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R

@@ -1,0 +1,41 @@
+
+# 
+# rm(list = ls())
+# 
+#  source("../MainFunctions/correa_estimator.r")
+#  source("../MainFunctions/bootstrap_correa_estimator.R")
+
+
+bootstrap_correa_estimator_log_mean <-  function(x, B){
+  
+  v.Bootstrap <- rep(0, B)
+  
+  for(b in 1:B) {
+    same_values <- TRUE
+    while (same_values) {
+      bx <- sample(x, replace = TRUE)
+      if (!all(bx == bx[1])) {
+        same_values <- FALSE
+        entropy_result <-  bootstrap_correa_estimator(bx, B) - log(mean(bx))
+        if (is.finite(entropy_result)) {
+          v.Bootstrap[b] <- entropy_result
+          #cat("Bootstrap Sample", b, ": ", bx, "\n")
+          #cat("Entropy for Bootstrap Sample", b, ": ", v.Bootstrap[b], "\n")
+        }
+      }
+    }
+  }
+  
+  
+  #t <- correa_estimator(x)
+  estimated_mean <- mean(v.Bootstrap[!is.na(v.Bootstrap)])
+  
+  return(estimated_mean)
+  
+}
+
+# data <- c(1.2, 1.5,3.6, 2.0, 2.1, 2.5, 2.6, 3.0, 3.1, 3.5)
+# result <- bootstrap_correa_estimator_log_mean(data, 10)
+# cat("Al-Omari-1 Estimator:", result, "\n")
+
+

### 2024-03-14 Code/R/MainFunctions/bootstrap_correa_estimator_opt.R

@@ -1,0 +1,30 @@
+bootstrap_correa_estimator_opt <- function(x, B) {
+  v.Bootstrap <- numeric(B)
+  
+  for (b in seq_len(B)) {
+    same_values <- TRUE
+    while (same_values) {
+      bx <- sample(x, replace = TRUE)
+      if (!all(bx == bx[1])) {
+        same_values <- FALSE
+        entropy_result <- adaptive_correa_estimator(bx)
+        if (is.finite(entropy_result)) {
+          v.Bootstrap[b] <- entropy_result
+          #cat("Entropy for Bootstrap Sample", b, ": ", v.Bootstrap[b], "\n")
+        }
+      }
+    }
+  }
+  
+  t <- adaptive_correa_estimator(x)
+  estimated_mean <- mean(v.Bootstrap[!is.na(v.Bootstrap)])
+  
+  return(2 * t - estimated_mean)
+}
+
+# # Ejemplo de uso
+# set.seed(123)  # Para reproducibilidad
+# X <- rnorm(1000)  # Reemplaza esto con tu conjunto de datos
+# B <- 1000
+# system.time(result <- bootstrap_yee_estimator_optimized(X, B))
+# print(paste("Resultado:", result))

### 2024-03-14 Code/R/MainFunctions/bootstrap_estimator.R

@@ -1,0 +1,83 @@
+
+
+
+# source("../MainFunctions/van_es_estimator.r")
+# source("../MainFunctions/correa_estimator.r")
+# source("../MainFunctions/ebrahimi_estimator.r")
+# source("../MainFunctions/noughabi_arghami_estimator.r")
+# source("../MainFunctions/vasicek_estimator.r")
+# source("../MainFunctions/al_omari_1_estimator.r")
+# source("../MainFunctions/al_omari_2_estimator.r")
+# #source("../MainFunctions/bootstrap_estimator.r")
+
+bootstrap_estimator <- function(data, B, verbose = TRUE) {
+  n <- length(data)
+  t <- van_es_estimator(data)
+  bx <- numeric(B)
+  
+  for (i in 1:B) {
+    same_values <- TRUE
+    while (same_values) {
+      sampled_indices <- sample(1:n, n, replace = TRUE)
+      sampled_data <- data[sampled_indices]
+      if (!all(sampled_data == sampled_data[1])) {
+        same_values <- FALSE
+        entropy_result <- van_es_estimator(sampled_data)
+        if (is.finite(entropy_result)) {
+          bx[i] <- entropy_result
+          
+          if (verbose) {
+            #cat("Bootstrap Sample", i, ": ", sampled_data, "\n")
+            #cat("Entropy for Bootstrap Sample", i, ": ", bx[i], "\n")
+          }
+        }
+      }
+    }
+  }
+  
+  bx <- bx[!is.na(bx)]  # Elimina valores NA (si los hay)
+  estimated_mean <- mean(bx)
+  
+  return(2*t - estimated_mean)
+}
+
+# bootstrap_estimator <- function(data, B, verbose = TRUE) {
+#   #if (!is.null(seed)) set.seed(seed)
+#   n <- length(data)
+#   t <- van_es_estimator(data)
+#   bx <- numeric(B)
+#   
+#   for (i in 1:B) {
+#     same_values <- TRUE
+#     while (same_values) {
+#       sampled_indices <- sample(1:n, n, replace = TRUE)
+#       sampled_data <- data[sampled_indices]
+#       if (!all(sampled_data == sampled_data[1])) {
+#         same_values <- FALSE
+#         bx[i] <- van_es_estimator(sampled_data)
+#         
+#         if (verbose) {
[…]

### 2024-03-14 Code/R/MainFunctions/bootstrap_main_one_plot.R

@@ -1,0 +1,91 @@
+rm(list = ls())
+library(ggplot2)
+library(tidyr)
+library(gtools)
+library(stats4)
+library(rmutil)
+
+library(invgamma)
+library(ggplot2)
+library(ggthemes)
+theme_set(theme_pander() +
+            theme(text=element_text(family="serif"),
+                  legend.position = "top")
+)
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/correa_estimator.r")
+source("../MainFunctions/ebrahimi_estimator.r")
+source("../MainFunctions/noughabi_arghami_estimator.r")
+source("../MainFunctions/vasicek_estimator.r")
+source("../MainFunctions/al_omari_1_estimator.r")
+source("../MainFunctions/al_omari_2_estimator.r")
+
+source("../MainFunctions/bootstrap_estimator.r")
+source("../MainFunctions/bootstrap_van_es_estimator.r")
+source("../MainFunctions/bootstrap_correa_estimator.r")
+source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
+source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
+source("../MainFunctions/bootstrap_vasicek_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+sample_sizes <- c(9, 25, 49)
+#sample_sizes <- c(9, 25)
+R <-5
+mu <- 1
+L <- 1
+
+
+output <- NULL
+
+
+for(ssize in sample_sizes) {
+  v.bootstrap.entropy <- NULL
+  v.nonparametric.entropy <- NULL
+  for(r in 1:R) {
+    sample <- gamma_sar_sample(L, mu, ssize)
+    cat("muestra: ", sample, "\n")
+    v.bootstrap.entropy[r] <- bootstrap_van_es_estimator(sample, B=3)
+    cat("boot: ", v.bootstrap.entropy, "\n")
+    #v.bootstrap.entropy[r] <- est_bootstrap
+    v.nonparametric.entropy[r] <- van_es_estimator(sample)
[…]

### 2024-03-14 Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.R

@@ -1,0 +1,33 @@
+
+
+
+
+#source("../MainFunctions/noughabi_arghami_estimator.r")
+
+
+bootstrap_noughabi_arghami_estimator <- function(x, B){
+  
+  v.Bootstrap <- rep(0, B)
+  
+  for(b in 1:B) {
+    same_values <- TRUE
+    while (same_values) {
+      bx <- sample(x, replace = TRUE)
+      if (!all(bx == bx[1])) {
+        same_values <- FALSE
+        entropy_result <- noughabi_arghami_estimator(bx)
+        if (is.finite(entropy_result)) {
+          v.Bootstrap[b] <- entropy_result
+          #cat("Entropy for Bootstrap Sample", b, ": ", v.Bootstrap[b], "\n")
+        }
+      }
+    }
+  }
+  
+  
+  t <- noughabi_arghami_estimator(x)
+  estimated_mean <- mean(v.Bootstrap[!is.na(v.Bootstrap)])
+  
+  return(2*t - estimated_mean)
+  
+}

### 2024-03-14 Code/R/MainFunctions/bootstrap_van_es_estimator.R

@@ -1,0 +1,72 @@
+
+
+
+ #source("../MainFunctions/van_es_estimator.r")
+ 
+ bootstrap_van_es_estimator <- function(x, B){
+
+   v.Bootstrap <- rep(0, B)
+
+   for(b in 1:B) {
+     same_values <- TRUE
+     while (same_values) {
+       bx <- sample(x, replace = TRUE)
+       if (!all(bx == bx[1])) {
+         same_values <- FALSE
+         entropy_result <- van_es_estimator(bx)
+         if (is.finite(entropy_result)) {
+           v.Bootstrap[b] <- entropy_result
+           #cat("Bootstrap Sample", b, ": ", bx, "\n")
+           #cat("Entropy for Bootstrap Sample", b, ": ", v.Bootstrap[b], "\n")
+         }
+       }
+     }
+   }
+
+
+   t <- van_es_estimator(x)
+   estimated_mean <- mean(v.Bootstrap[!is.na(v.Bootstrap)])
+   #cat("mean boot", estimated_mean, "\n")
+
+   return(2*t - estimated_mean)
+
+ }
+
+
+# bootstrap_van_es_estimator <- function(data, B) {
+#   n <- length(data)
+#   t <- van_es_estimator(data)
+#   bx <- numeric(B)
+# 
+#   for (i in 1:B) {
+#     same_values <- TRUE
+#     while (same_values) {
+#       sampled_indices <- sample(1:n, n, replace = TRUE)
+#       sampled_data <- data[sampled_indices]
+#       if (!all(sampled_data == sampled_data[1])) {
+#         same_values <- FALSE
+#         entropy_result <- van_es_estimator(sampled_data)
+#         if (is.finite(entropy_result)) {
+#           bx[i] <- entropy_result
+# 
+#           #if (verbose) {
+#             #cat("Bootstrap Sample", i, ": ", sampled_data, "\n")
+#             #cat("Entropy for Bootstrap Sample", i, ": ", bx[i], "\n")
+#           #}
+#         }
+#       }
+#     }
+#   }
+# 
+#   bx <- bx[!is.na(bx)]  # Elimina valores NA (si los hay)
+#   estimated_mean <- mean(bx)
+# 
+#   return(2*t - estimated_mean)
+# }
+
+ # set.seed(1234567890, kind = "Mersenne-Twister")
[…]

### 2024-03-14 Code/R/MainFunctions/bootstrap_vasicek_estimator.R

@@ -1,0 +1,33 @@
+
+
+
+
+#source("../MainFunctions/vasicek_estimator.r")
+
+
+bootstrap_vasicek_estimator <- function(x, B){
+  
+  v.Bootstrap <- rep(0, B)
+  
+  for(b in 1:B) {
+    same_values <- TRUE
+    while (same_values) {
+      bx <- sample(x, replace = TRUE)
+      if (!all(bx == bx[1])) {
+        same_values <- FALSE
+        entropy_result <- vasicek_estimator(bx)
+        if (is.finite(entropy_result)) {
+          v.Bootstrap[b] <- entropy_result
+          #cat("Entropy for Bootstrap Sample", b, ": ", v.Bootstrap[b], "\n")
+        }
+      }
+    }
+  }
+  
+  
+  t <- vasicek_estimator(x)
+  estimated_mean <- mean(v.Bootstrap[!is.na(v.Bootstrap)])
+  
+  return(2*t - estimated_mean)
+  
+}

### 2024-03-14 Code/R/MainFunctions/bootstrap_yee_estimator.R

@@ -1,0 +1,29 @@
+
+
+
+bootstrap_yee_estimator <- function(x, B){
+  
+  v.Bootstrap <- rep(0, B)
+  
+  for(b in 1:B) {
+    same_values <- TRUE
+    while (same_values) {
+      bx <- sample(x, replace = TRUE)
+      if (!all(bx == bx[1])) {
+        same_values <- FALSE
+        entropy_result <- yee_estimator(bx)
+        if (is.finite(entropy_result)) {
+          v.Bootstrap[b] <- entropy_result
+          #cat("Entropy for Bootstrap Sample", b, ": ", v.Bootstrap[b], "\n")
+        }
+      }
+    }
+  }
+  
+  
+  t <- yee_estimator(x)
+  estimated_mean <- mean(v.Bootstrap[!is.na(v.Bootstrap)])
+  
+  return(2*t - estimated_mean)
+  
+}

### 2024-03-14 Code/R/MainFunctions/bootstrap_yee_estimator_optimized.R

@@ -1,0 +1,30 @@
+bootstrap_yee_estimator_optimized <- function(x, B) {
+  v.Bootstrap <- numeric(B)
+  
+  for (b in seq_len(B)) {
+    same_values <- TRUE
+    while (same_values) {
+      bx <- sample(x, replace = TRUE)
+      if (!all(bx == bx[1])) {
+        same_values <- FALSE
+        entropy_result <- yee_estimator(bx)
+        if (is.finite(entropy_result)) {
+          v.Bootstrap[b] <- entropy_result
+          #cat("Entropy for Bootstrap Sample", b, ": ", v.Bootstrap[b], "\n")
+        }
+      }
+    }
+  }
+  
+  t <- yee_estimator(x)
+  estimated_mean <- mean(v.Bootstrap[!is.na(v.Bootstrap)])
+  
+  return(2 * t - estimated_mean)
+}
+
+# # Ejemplo de uso
+# set.seed(123)  # Para reproducibilidad
+# X <- rnorm(1000)  # Reemplaza esto con tu conjunto de datos
+# B <- 1000
+# system.time(result <- bootstrap_yee_estimator_optimized(X, B))
+# print(paste("Resultado:", result))

### 2024-03-14 Code/R/MainFunctions/correa_estimator.R

@@ -1,0 +1,41 @@
+correa_estimator <- function(data) {
+  n <- length(data)
+  m <- round(sqrt(n) + 0.5)
+  X_sorted <- sort(data)
+  C_mn <- 0
+  
+  for (i in 1:n) {
+    i_minus_m <- max(1, i - m)
+    i_plus_m <- min(n, i + m)
+    
+    X_i <- X_sorted[i]
+    X_window <- X_sorted[i_minus_m:i_plus_m]
+    X_bar_i <- mean(X_window)
+    
+    num <- sum((X_window - X_bar_i) * (i_minus_m:i_plus_m - i))
+    den <- n * sum((X_window - X_bar_i)^2)
+    
+    if (den == 0) {
+      b_i <- 0
+    } else {
+      b_i <- num / den
+    }
+    
+    if (b_i > 0) {
+      C_mn <- C_mn - log(b_i)
+    }
+  }
+  
+  C_mn <- C_mn / n
+  
+  return(C_mn)
+}
+
+
+# # # Example usage:
+# data <- data <- c( 0.429283, 0.429283, 0.9444219, 0.9608317, 1.451404, 1.451404, 0.429283, 0.429283, 0.429283 )#c(1.2, 1.5,3.6, 2.0, 2.1, 2.5, 2.6, 3.0, 3.1, 3.5 )
+# result <- correa_estimator(data)
+# cat("Correa Estimator:", result, "\n")
+
+
+

### 2024-03-14 Code/R/MainFunctions/correa_estimator_opt.R

@@ -1,0 +1,33 @@
+correa_estimator_opt <- function(data) {
+  n <- length(data)
+  m <- round(sqrt(n) + 0.5)
+  X_sorted <- sort(data)
+  C_mn <- 0
+  
+  for (i in 1:n) {
+    i_minus_m <- max(1, i - m)
+    i_plus_m <- min(n, i + m)
+    
+    X_i <- X_sorted[i]
+    X_window <- X_sorted[i_minus_m:i_plus_m]
+    X_bar_i <- mean(X_window)
+    
+    differences <- X_window - X_bar_i
+    num <- sum(differences * (i_minus_m:i_plus_m - i))
+    den <- n * sum(differences^2)
+    
+    b_i <- ifelse(den == 0, 0, num / den)
+    
+    C_mn <- C_mn - log(pmax(b_i, 0))
+  }
+  
+  C_mn <- C_mn / n
+  
+  return(C_mn)
+}
+
+# set.seed(123)  
+# X <- rnorm(100000)  
+# #system.time(entropy_estimate_large <- yee_entropy_estimator_optimized(X_large))
+# system.time(entropy_estimate <- correa_estimator_3(X))
+# print(paste("Estimación de entropía:", entropy_estimate))

### 2024-03-14 Code/R/MainFunctions/ebrahimi_estimator.R

@@ -1,0 +1,28 @@
+ebrahimi_estimator <- function(data) {
+  n <- length(data)
+  m <- round(sqrt(n) + 0.5)  # m-spacing
+  data_sorted <- sort(data)
+  sum_term <- 0
+  
+  for (i in 1:n) {
+    if (i <= m) {
+      ci <- 1 + (i - 1) / m
+      diff_term <- data_sorted[i + m] - data_sorted[1]
+    } else if (i >= n - m + 1) {
+      ci <- 1 + (n - i) / m
+      diff_term <- data_sorted[n] - data_sorted[i - m]
+    } else {
+      ci <- 2
+      diff_term <- data_sorted[i + m] - data_sorted[i - m]
+    }
+    
+    sum_term <- sum_term + log((n / (ci * m)) * diff_term)
+  }
+  
+  return(sum_term / n)
+}
+
+# # Example usage:
+# data <- c(1.2, 1.5, 2.0, 2.1, 2.5, 2.6, 3.0, 3.1, 3.5, 3.6)
+# result <- ebrahimi_estimatori(data)
+# cat("Ebrahimi Estimator:", result, "\n")

### 2024-03-14 Code/R/MainFunctions/entropy_gamma_sar.R

@@ -1,0 +1,17 @@
+# Function for Entropy Calculation of the Gamma SAR Distribution
+# Description: This function calculates the entropy of the Gamma SAR distribution
+# based on provided parameters L and mu.
+#
+# Input:
+#   - L: Shape parameter of the Gamma distribution.
+#   - mu: Mean parameter of the distribution.
+#
+# Output:
+#   - Entropy value of the Gamma SAR distribution.
+
+entropy_gamma_sar <- function(L, mu) {
+  
+  return(L - log(L) + lgamma(L) + (1 - L) * digamma(L) + log(mu))
+  
+}
+

### 2024-03-14 Code/R/MainFunctions/functions_bias_mse.R

@@ -1,0 +1,17 @@
+# functions_bias_mse.R
+
+generate_samples <- function(sample_size, replication, mu, L) {
+  samples <- vector("list", replication)
+  for (r in 1:replication) {
+    samples[[r]] <- gamma_sar_sample(L, mu, sample_size)
+  }
+  return(samples)
+}
+
+calculate_bias_mse <- function(sample_sizes, R, mu, L) {
+  true_entropy <- entropy_gamma_sar(L, mu)
+  
+  # Resto del código...
+  
+  return(output)
+}

### 2024-03-14 Code/R/MainFunctions/van_es_estimator.R

@@ -1,0 +1,40 @@
+# Non-Parametric Shannon Entropy Estimator
+# Description: This function calculates Shannon entropy using a non-parametric estimator,
+# known as the van Es estimator. 
+# It is based on spacings between data points 
+#
+# Input:
+#   - data: sample or dataset 
+#
+# Output:
+#   - Estimated Shannon entropy 
+
+van_es_estimator <- function(data) {
+  n <- length(data)
+  m <- round(sqrt(n)+0.5)# round(sqrt(n))# m-spacing # round(sqrt(n)+0.5)
+  data_sorted <- sort(data)
+  #cat("sort data ", data_sorted ,   "\n")
+  sum_term1 <- 0
+  sum_term2 <- 0
+  
+  for (i in 1:(n - m)) {
+    term1 <-  log(((n + 1) / m) * (data_sorted[i + m] - data_sorted[i]))
+    sum_term1 <-  sum_term1 + term1
+    
+  }
+ 
+  for (k in m:n) {
+    sum_term2 <- sum_term2 + 1 / k
+   
+  }
+  term3 <- log(m / (n + 1))
+ 
+  return((sum_term1 / (n - m)) + sum_term2+ term3)
+  
+}
+
+# # Example usage:
+# data <- c(1.229641, 1.451404, 1.229641, 0.9444219, 1.229641, 0.429283, 0.6902405, 1.904591, 0.4554712)
+# # data <- c( 0.429283, 0.429283, 0.9444219, 0.9608317, 1.451404, 1.451404, 0.429283, 0.429283, 0.429283 ) # -inf
+#  result <- van_es_estimator(data)
+#  cat("van es :", result, "\n")

### 2024-03-14 Code/R/MainFunctions/yee_estimator.R

@@ -1,0 +1,67 @@
+
+
+yee_estimator<- function(X) {
+  n <- length(X)
+  H_Y <- numeric(n-1)
+  
+  sorted_X <- sort(X)
+  
+  for (m in 1:(n-1)) {
+    differences <- sorted_X[(m+1):n] - sorted_X[1:(n-m)]
+    term_sum <- sum(log((n/m) * differences))
+    
+    H_Y[m] <- (1/(n-m)) * term_sum - digamma(m) + log(m)
+  }
+  
+  estimated_entropy <- (1/(n-1)) * sum(H_Y)
+  
+  return(estimated_entropy)
+}
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+# yee_estimator<- function(X) {
+#   n <- length(X)
+#   H_Y <- numeric(n-1)
+#   
+#   sorted_X <- sort(X)
+#   
+#   for (m in 1:(n-1)) {
+#     differences <- sorted_X[(m+1):n] - sorted_X[1:(n-m)]
+#     term_sum <- sum(log((n/m) * differences))
+#     
+#     H_Y[m] <- (1/(n-m)) * term_sum - digamma(m) + log(m)
+#   }
+#   
+#   estimated_entropy <- (1/(n-1)) * sum(H_Y)
+#   
+#   return(estimated_entropy)
+# }
+
+
+# set.seed(123)  # Para reproducibilidad
+# X_large <- rnorm(1000)  # Reemplaza esto con tu conjunto de datos
+# system.time(entropy_estimate_large <- yee_entropy_estimator_optimized(X_large))
+# print(paste("Estimación de entropía:", entropy_estimate_large))

### 2024-03-14 Code/R/PlottingFunctions/Plot_SAR_real.R

@@ -1,0 +1,368 @@
+
+rm(list = ls())
+
+library(raster)
+if(!require("rstudioapi")) install("rstudioapi")
+setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+source("../../../Code/R/Programs/read_ENVI_images.R")
+
+
+x <- myread.ENVI(file='../../../Data/SAR/Ottawa/Intensity_VV.img', headerfile='../../../Data/SAR/Ottawa/Intensity_VV.hdr')
+
+nCols_Ottawa <- 512
+nRows_Ottawa <- 512
+
+centerRow_Ottawa <- floor(nRows_Ottawa / 2)
+centerCol_Ottawa <- floor(nCols_Ottawa / 2)
+
+roiSize_Ottawa <- 200
+
+roiUpperStartRow <- 1
+roiUpperEndRow <- roiUpperStartRow + roiSize_Ottawa - 1
+
+roiUpperStartCol <- centerCol_Ottawa - floor(roiSize_Ottawa / 2) + 1
+roiUpperEndCol <- roiUpperStartCol + roiSize_Ottawa - 1
+
+# ROI en la parte superior
+roi <- x[roiUpperStartRow:roiUpperEndRow, roiUpperStartCol:roiUpperEndCol]
+escala_log <- 0.01
+subx_log <- log10(roi + escala_log)
+
+# Crear un objeto raster
+raster_obj <- raster(subx_log)
+media_valor2 <- mean(raster_obj)
+
+# Guardar el ROI como PNG
+savepng <- function(imagen, nombre) {
+  png(file = nombre, width = dim(imagen)[2], height = dim(imagen)[1])
+  vectorzeros <- replicate(4, 0)
+  par(mar = vectorzeros, oma = vectorzeros, omi = vectorzeros)
+  image(imagen, col = gray(seq(0, 1, length.out = 256)))
+  #image(imagen, col = gray(seq(0, 0.6, length.out = 51)))
+  dev.off()
+  return(0)
+}
+
+savepng(raster_obj, "./ROIs/Ottawa_roi3.png")
+
+# Crear una copia de la imagen completa
+x_copy <- x
+
+# Dibujar un cuadro de contorno azul alrededor del ROI
+max_roi_value <- max(roi)
+
+# Dibujar un cuadro de contorno azul alrededor del ROI
[…]

### 2024-03-14 Code/R/PlottingFunctions/Plot_empirical.R

@@ -1,0 +1,109 @@
+rm(list = ls())
+library(ggplot2)
+library(tidyr)
+library(gtools)
+library(stats4)
+library(rmutil)
+
+library(invgamma)
+library(ggplot2)
+library(tidyverse)
+library(scales)
+library(RColorBrewer)
+library(ggsci)
+library(wesanderson)
+library(ggthemes)
+library(ggthemes)
+theme_set(theme_bw()  +
+            theme(text=element_text(family="serif"),
+                  legend.position = "top")
+)
+
+
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+source("../MainFunctions/entropy_gI0.r")
+source("../MainFunctions/gi0_sample.r")
+
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/correa_estimator.r")
+source("../MainFunctions/ebrahimi_estimator.r")
+source("../MainFunctions/noughabi_arghami_estimator.r")
+source("../MainFunctions/vasicek_estimator.r")
+source("../MainFunctions/al_omari_1_estimator.r")
+source("../MainFunctions/al_omari_2_estimator.r")
+
+source("../MainFunctions/bootstrap_van_es_estimator.r")
+source("../MainFunctions/bootstrap_correa_estimator.r")
+source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
+source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
+source("../MainFunctions/bootstrap_vasicek_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
+#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
+source("../Programs/functions_sample_bias_mse.R")# 
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+sample_sizes <- c( 121)
+R <- 1000
+mu <- 100
+L <- 5
+alpha <- -10
+
+# Function to generate samples for a given sample size and replication
+generate_samples <- function(sample_size, replication, mu, alpha, L) {
+  samples <- vector("list", replication)
+  for (r in 1:replication) {
+    samples[[r]] <- gi0_sample(mu, alpha, L, sample_size)
+  }
+  return(samples)
+}
+
+# Function to calculate Variance for both non-parametric and bootstrap estimators
[…]

### 2024-03-14 Code/R/PlottingFunctions/best_estimators.R

@@ -1,0 +1,118 @@
+rm(list = ls())
+library(ggplot2)
+library(tidyr)
+library(gtools)
+library(stats4)
+library(rmutil)
+library(invgamma)
+library(ggplot2)
+library(tidyverse)
+library(scales)
+library(RColorBrewer)
+library(ggsci)
+library(wesanderson)
+library(ggpubr)
+
+# Load the source files (make sure you have the correct file paths)
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/correa_estimator.r")
+source("../MainFunctions/ebrahimi_estimator.r")
+source("../MainFunctions/noughabi_arghami_estimator.r")
+source("../MainFunctions/vasicek_estimator.r")
+source("../MainFunctions/al_omari_1_estimator.r")
+source("../MainFunctions/al_omari_2_estimator.r")
+source("../MainFunctions/bootstrap_van_es_estimator.r")
+source("../MainFunctions/bootstrap_correa_estimator.r")
+source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
+source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
+source("../MainFunctions/bootstrap_vasicek_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+sample_sizes <- c( 9, 25, 49, 81, 121, 225)
+R <- 100
+mu <- 1
+L <- 1
+
+# Function to calculate Bias and MSE for both non-parametric and bootstrap estimators
+calculate_bias_mse <- function(sample_sizes, R, mu, L) {
+  true_entropy <- entropy_gamma_sar(L, mu)
+  
+  # Define a list of estimators
+  estimators <- list(
+    "Van Es" = van_es_estimator,
+    "Correa" = correa_estimator,
+    "Ebrahimi" = ebrahimi_estimator,
+    "Noughabi Arghami" = noughabi_arghami_estimator,
+    "Vasicek" = vasicek_estimator,
+    "Al Omari 1" = al_omari_1_estimator,
+    "Al Omari 2" = al_omari_2_estimator,
[…]

### 2024-03-14 Code/R/PlottingFunctions/bias_mse_al_omari_1.R

@@ -1,0 +1,101 @@
+rm(list = ls())
+library(ggplot2)
+library(gtools)
+library(stats4)
+library(rmutil)
+#library(gsl)
+library(invgamma)
+
+library(ggthemes)
+library(grid)
+library(gridExtra)
+library(gtable)
+#install.packages("cowplot")
+library(cowplot)
+library(ggpubr)
+theme_set(theme_bw()  +
+            theme(text=element_text(family="serif"),
+                  legend.position = "top")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
+)
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/correa_estimator.r")
+source("../MainFunctions/ebrahimi_estimator.r")
+source("../MainFunctions/noughabi_arghami_estimator.r")
+source("../MainFunctions/vasicek_estimator.r")
+source("../MainFunctions/al_omari_1_estimator.r")
+source("../MainFunctions/al_omari_2_estimator.r")
+
+source("../MainFunctions/bootstrap_van_es_estimator.r")
+source("../MainFunctions/bootstrap_correa_estimator.r")
+source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
+source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
+source("../MainFunctions/bootstrap_vasicek_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
+
+set.seed(1234567890, kind="Mersenne-Twister")
+
+sample_sizes <- c(9, 25, 49, 81, 121)
+R <- 100
+mu <- 1
+L <- 1
+
+# 
+results <- data.frame()
+
+for (n in sample_sizes) {
+  true_entropy <- entropy_gamma_sar(L, mu)
+  bias_est <- rep(0, R)
+  mse_est <- rep(0, R)
+  bias_bootstrap <- rep(0, R)
+  mse_bootstrap <- rep(0, R)
+  
+  for (r in 1:R) {
+    # Samples
+    data <- gamma_sar_sample(L, mu, n)
+    
+    # Entropy estimations
+    est <- al_omari_1_estimator(data)
[…]

### 2024-03-14 Code/R/PlottingFunctions/bias_mse_correa.R

@@ -1,0 +1,101 @@
+rm(list = ls())
+library(ggplot2)
+library(gtools)
+library(stats4)
+library(rmutil)
+#library(gsl)
+library(invgamma)
+
+library(ggthemes)
+library(grid)
+library(gridExtra)
+library(gtable)
+#install.packages("cowplot")
+library(cowplot)
+library(ggpubr)
+theme_set(theme_bw()  +
+            theme(text=element_text(family="serif"),
+                  legend.position = "top")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
+)
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/correa_estimator.r")
+source("../MainFunctions/ebrahimi_estimator.r")
+source("../MainFunctions/noughabi_arghami_estimator.r")
+source("../MainFunctions/vasicek_estimator.r")
+source("../MainFunctions/al_omari_1_estimator.r")
+source("../MainFunctions/al_omari_2_estimator.r")
+
+source("../MainFunctions/bootstrap_van_es_estimator.r")
+source("../MainFunctions/bootstrap_correa_estimator.r")
+source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
+source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
+source("../MainFunctions/bootstrap_vasicek_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
+
+set.seed(1234567890, kind="Mersenne-Twister")
+
+sample_sizes <- c(9, 25, 49, 81, 121)
+R <- 10
+mu <- 1
+L <- 1
+
+# 
+results <- data.frame()
+
+for (n in sample_sizes) {
+  true_entropy <- entropy_gamma_sar(L, mu)
+  bias_est <- rep(0, R)
+  mse_est <- rep(0, R)
+  bias_bootstrap <- rep(0, R)
+  mse_bootstrap <- rep(0, R)
+  
+  for (r in 1:R) {
+    # Samples
+    data <- gamma_sar_sample(L, mu, n)
+    
+    # Entropy estimations
+    est <- correa_estimator(data)
[…]

### 2024-03-14 Code/R/PlottingFunctions/bias_mse_ebrahimi.R

@@ -1,0 +1,101 @@
+rm(list = ls())
+library(ggplot2)
+library(gtools)
+library(stats4)
+library(rmutil)
+#library(gsl)
+library(invgamma)
+
+library(ggthemes)
+library(grid)
+library(gridExtra)
+library(gtable)
+#install.packages("cowplot")
+library(cowplot)
+library(ggpubr)
+theme_set(theme_bw()  +
+            theme(text=element_text(family="serif"),
+                  legend.position = "top")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
+)
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/correa_estimator.r")
+source("../MainFunctions/ebrahimi_estimator.r")
+source("../MainFunctions/noughabi_arghami_estimator.r")
+source("../MainFunctions/vasicek_estimator.r")
+source("../MainFunctions/al_omari_1_estimator.r")
+source("../MainFunctions/al_omari_2_estimator.r")
+
+source("../MainFunctions/bootstrap_van_es_estimator.r")
+source("../MainFunctions/bootstrap_correa_estimator.r")
+source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
+source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
+source("../MainFunctions/bootstrap_vasicek_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
+
+set.seed(1234567890, kind="Mersenne-Twister")
+
+sample_sizes <- c(9, 25, 49, 81, 121)
+R <- 10
+mu <- 1
+L <- 1
+
+# 
+results <- data.frame()
+
+for (n in sample_sizes) {
+  true_entropy <- entropy_gamma_sar(L, mu)
+  bias_est <- rep(0, R)
+  mse_est <- rep(0, R)
+  bias_bootstrap <- rep(0, R)
+  mse_bootstrap <- rep(0, R)
+  
+  for (r in 1:R) {
+    # Samples
+    data <- gamma_sar_sample(L, mu, n)
+    
+    # Entropy estimations
+    est <- ebrahimi_estimator(data)
[…]

### 2024-03-14 Code/R/PlottingFunctions/bias_mse_noughabi_arghami.R

@@ -1,0 +1,101 @@
+rm(list = ls())
+library(ggplot2)
+library(gtools)
+library(stats4)
+library(rmutil)
+#library(gsl)
+library(invgamma)
+
+library(ggthemes)
+library(grid)
+library(gridExtra)
+library(gtable)
+#install.packages("cowplot")
+library(cowplot)
+library(ggpubr)
+theme_set(theme_bw()  +
+            theme(text=element_text(family="serif"),
+                  legend.position = "top")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
+)
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/correa_estimator.r")
+source("../MainFunctions/ebrahimi_estimator.r")
+source("../MainFunctions/noughabi_arghami_estimator.r")
+source("../MainFunctions/vasicek_estimator.r")
+source("../MainFunctions/al_omari_1_estimator.r")
+source("../MainFunctions/al_omari_2_estimator.r")
+
+source("../MainFunctions/bootstrap_van_es_estimator.r")
+source("../MainFunctions/bootstrap_correa_estimator.r")
+source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
+source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
+source("../MainFunctions/bootstrap_vasicek_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
+
+set.seed(1234567890, kind="Mersenne-Twister")
+
+sample_sizes <- c(9, 25, 49, 81, 121)
+R <- 10
+mu <- 1
+L <- 1
+
+# 
+results <- data.frame()
+
+for (n in sample_sizes) {
+  true_entropy <- entropy_gamma_sar(L, mu)
+  bias_est <- rep(0, R)
+  mse_est <- rep(0, R)
+  bias_bootstrap <- rep(0, R)
+  mse_bootstrap <- rep(0, R)
+  
+  for (r in 1:R) {
+    # Samples
+    data <- gamma_sar_sample(L, mu, n)
+    
+    # Entropy estimations
+    est <- noughabi_arghami_estimator(data)
[…]

### 2024-03-14 Code/R/PlottingFunctions/bias_mse_van_es.R

@@ -1,0 +1,108 @@
+rm(list = ls())
+library(ggplot2)
+library(tidyr)
+library(gtools)
+library(stats4)
+library(rmutil)
+
+library(invgamma)
+library(ggplot2)
+library(tidyverse)
+library(scales)
+library(RColorBrewer)
+library(ggsci)
+library(wesanderson)
+library(ggthemes)
+library(ggthemes)
+theme_set(theme_bw()  +
+            theme(text=element_text(family="serif"),
+                  legend.position = "top")
+)
+
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/correa_estimator.r")
+source("../MainFunctions/ebrahimi_estimator.r")
+source("../MainFunctions/noughabi_arghami_estimator.r")
+source("../MainFunctions/vasicek_estimator.r")
+source("../MainFunctions/al_omari_1_estimator.r")
+source("../MainFunctions/al_omari_2_estimator.r")
+
+source("../MainFunctions/bootstrap_estimator.r")
+source("../MainFunctions/bootstrap_van_es_estimator.r")
+source("../MainFunctions/bootstrap_correa_estimator.r")
+source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
+source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
+source("../MainFunctions/bootstrap_vasicek_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+sample_sizes <- c(9, 25,49, 81, 121)
+R <- 100
+mu <- 1
+L <- 1
+
+true_entropy <- entropy_gamma_sar(L, mu)
+#output <- NULL
+results <- data.frame()
+for(ssize in sample_sizes) {
+  v.bootstrap.entropy <- NULL
+  v.nonparametric.entropy <- NULL
+  
+  for(r in 1:R) {
+    sample <- gamma_sar_sample(L, mu, ssize)
+   
+    v.bootstrap.entropy[r] <- bootstrap_van_es_estimator(sample, B = 100) 
+    
[…]

### 2024-03-14 Code/R/PlottingFunctions/bias_mse_vasicek.R

@@ -1,0 +1,101 @@
+rm(list = ls())
+library(ggplot2)
+library(gtools)
+library(stats4)
+library(rmutil)
+#library(gsl)
+library(invgamma)
+library(ggplot2)
+library(ggthemes)
+library(grid)
+library(gridExtra)
+library(gtable)
+#install.packages("cowplot")
+library(cowplot)
+library(ggpubr)
+theme_set(theme_bw()  +
+            theme(text=element_text(family="serif"),
+                  legend.position = "top")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
+)
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/correa_estimator.r")
+source("../MainFunctions/ebrahimi_estimator.r")
+source("../MainFunctions/noughabi_arghami_estimator.r")
+source("../MainFunctions/vasicek_estimator.r")
+source("../MainFunctions/al_omari_1_estimator.r")
+source("../MainFunctions/al_omari_2_estimator.r")
+
+source("../MainFunctions/bootstrap_van_es_estimator.r")
+source("../MainFunctions/bootstrap_correa_estimator.r")
+source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
+source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
+source("../MainFunctions/bootstrap_vasicek_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
+
+set.seed(1234567890, kind="Mersenne-Twister")
+
+sample_sizes <- c(9, 25, 49, 81, 121)
+R <- 100
+mu <- 1
+L <- 1
+
+#
+true_entropy <- entropy_gamma_sar(L, mu)
+results <- data.frame()
+for(ssize in sample_sizes) {
+  v.bootstrap.entropy <- NULL
+  v.nonparametric.entropy <- NULL
+  
+  for(r in 1:R) {
+    sample <- gamma_sar_sample(L, mu, ssize)
+    
+    v.bootstrap.entropy[r] <- bootstrap_vasicek_estimator(sample, B = 100) 
+    
[…]

### 2024-03-14 Code/R/PlottingFunctions/bias_plot_bootstrap.R

@@ -1,0 +1,86 @@
+rm(list = ls())
+library(ggplot2)
+library(gtools)
+library(stats4)
+library(rmutil)
+#library(gsl)
+library(invgamma)
+library(ggplot2)
+library(ggthemes)
+theme_set(theme_pander() +
+            theme(text=element_text(family="serif"),
+                  legend.position = "top")
+)
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/correa_estimator.r")
+source("../MainFunctions/ebrahimi_estimator.r")
+source("../MainFunctions/noughabi_arghami_estimator.r")
+source("../MainFunctions/vasicek_estimator.r")
+source("../MainFunctions/al_omari_1_estimator.r")
+source("../MainFunctions/al_omari_2_estimator.r")
+
+source("../MainFunctions/bootstrap_van_es_estimator.r")
+source("../MainFunctions/bootstrap_correa_estimator.r")
+source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
+source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
+source("../MainFunctions/bootstrap_vasicek_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
+
+set.seed(1234567890, kind="Mersenne-Twister")
+
+sample_sizes <- c( 9, 25)
+R <- 5
+mu <- 1
+L <- 1
+
+#  True entropy value for the gamma SAR distribution
+true_entropy <- entropy_gamma_sar(L, mu)
+
+
+output <- data.frame(SampleSize = integer(0), Estimator = character(0), Bias = numeric(0))
+
+#List of estimator
+estimators <- list(
+  list(func = bootstrap_van_es_estimator, label = " bootstrap Van Es"),
+  list(func = bootstrap_correa_estimator, label = " bootstrap Correa"),
+  # list(func = bootstrap_ebrahimi_estimator, label = "bootstrap Ebrahimi"),
+  # list(func = bootstrap_noughabi_arghami_estimator, label = "bootstrap Noughabi Arghami"),
+  # list(func = bootstrap_vasicek_estimator, label = "bootstrap Vasicek"),
[…]

### 2024-03-14 Code/R/PlottingFunctions/bias_plot_one_estimator.R

@@ -1,0 +1,67 @@
+rm(list = ls())
+library(ggplot2)
+library(gtools)
+#library(stats4)
+#library(rmutil)
+#library(gsl)
+library(invgamma)
+library(ggplot2)
+library(ggthemes)
+theme_set(theme_pander() +
+            theme(text=element_text(family="serif"),
+                  legend.position = "top")
+)
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/correa_estimator.r")
+source("../MainFunctions/ebrahimi_estimator.r") 
+source("../MainFunctions/noughabi_arghami_estimator.r") 
+source("../MainFunctions/vasicek_estimator.r") 
+source("../MainFunctions/al_omari_1_estimator.r") 
+source("../MainFunctions/al_omari_2_estimator.r") 
+
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+
+
+# Set sample sizes, the number of repetitions, and parameters
+sample_sizes <- c(9, 25, 49, 81, 121, 225)
+R <- 1000
+mu <- 1
+L <- 1
+
+
+# Define the true entropy value for the gamma SAR distribution
+true_entropy <- entropy_gamma_sar(L, mu)  # Replace with the true entropy value
+# Initialize the output data frame
+output <- NULL
+
+# Perform non-parametric entropy estimation for different sample sizes
+for (ssize in sample_sizes) {
+  v.nonparametric.entropy <- NULL
+  for (r in 1:R) {
+    sample <- gamma_sar_sample(L, mu, ssize)
+    v.nonparametric.entropy[r] <- van_es_estimator(sample)
+  }
+  
+  # Calculate the bias by subtracting the true entropy value
+  bias <- mean(v.nonparametric.entropy) - true_entropy
+  
+  # Store the bias in the output data frame
+  output <- rbind(output, c(bias, ssize))
+}
+
+# Create a data frame with results
+output <- data.frame(output)
+names(output) <- c("Bias")
+output$SampleSize <- sample_sizes
+
+# Plot the bias as a function of the sample size
+ggplot(output, aes(x=SampleSize, y=Bias)) +
+  geom_line() +
+  geom_point() +
+  xlab("Sample Size") +
+  ylab("Bias of Non-parametric Entropy Estimator")

### 2024-03-14 Code/R/PlottingFunctions/gamma_sar_L1.R

@@ -1,0 +1,56 @@
+
+# This code demonstrates non-parametric entropy estimation for Gamma SAR data.
+# It uses non-parametric estimators to calculate the sample mean and standard deviation 
+# of the entropy for various sample sizes.
+# The code also includes error bars based on the standard deviation for visualization.
+
+
+rm(list = ls())
+library(ggplot2)
+
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+set.seed(1234567890, kind="Mersenne-Twister")
+
+# Define sample sizes, the number of repetitions, and parameters
+sample_sizes <- c(9, 25, 49, 81, 121, 225)
+R <- 100
+mu <- 1
+L <- 1
+true_entropy <- entropy_gamma_sar(2, 2)
+#cat( "True entropy:", tru2_entropy)
+# Initialize the output data frame
+output <- NULL
+
+# Perform non-parametric entropy estimation for different sample sizes
+for(ssize in sample_sizes) {
+  v.nonparametric.entropy <- NULL
+  for(r in 1:R) {
+    sample <- gamma_sar_sample(L, mu, ssize)
+    v.nonparametric.entropy[r] <- van_es_estimator(sample)
+  }
+  output <- rbind(output, c(mean(v.nonparametric.entropy), sd(v.nonparametric.entropy)))
+  cat( "Sample Size:", ssize, "entropy:", mean(v.nonparametric.entropy),"True entropy:", true_entropy, "\n")
+}
+
+# Create a data frame with results
+output <- data.frame(output)
+names(output) <- c("Mean", "Std")
+output$SampleSize <- sample_sizes
+
+#cat( "True entropy:", tru2_entropy)
+#Plot
+ggplot(output, aes(x=SampleSize, y=Mean)) +
+  geom_hline(yintercept = entropy_gamma_sar(1, 1)) +
+  geom_line() +
+  geom_point() +
+  #geom_errorbar(aes(ymin = Mean - Std, ymax = Mean + Std), width = 0.1) +
+  xlab("Sample Size") +
+  #scale_x_log10(breaks=output$SampleSize) +
+  ylab("Mean Non-parametric Entropy")
+
+# Save the plot as a PDF file
+#ggsave("myplot.pdf")
+
+

### 2024-03-14 Code/R/PlottingFunctions/main_plots.R

@@ -1,0 +1,92 @@
+rm(list = ls())
+
+#options(digits = 5)
+
+# Resto de tu código aquí
+
+# Restaurar la opción digits a su valor original si es necesario
+#on.exit(options(digits = getOption("digits")))
+library(ggplot2)
+library(tidyr)
+library(gtools)
+library(stats4)
+library(rmutil)
+library(invgamma)
+library(tidyverse)
+library(scales)
+library(RColorBrewer)
+library(ggsci)
+library(wesanderson)
+library(ggpubr)
+library(patchwork)
+theme_set(theme_bw()  +
+            theme(text=element_text(family="serif"),
+                  legend.position = "top", panel.grid = element_blank())# Gridtop , right , bottom , or left#, panel.grid = element_blank()
+)
+
+
+# Load the source files (make sure you have the correct file paths)
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/correa_estimator.r")
+source("../MainFunctions/ebrahimi_estimator.r")
+source("../MainFunctions/noughabi_arghami_estimator.r")
+source("../MainFunctions/vasicek_estimator.r")
+source("../MainFunctions/al_omari_1_estimator.r")
+source("../MainFunctions/al_omari_2_estimator.r")
+source("../MainFunctions/bootstrap_van_es_estimator.r")
+source("../MainFunctions/bootstrap_correa_estimator.r")
+source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
+source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
+source("../MainFunctions/bootstrap_vasicek_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
+
+#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
+source("../Programs/functions_sample_bias_mse.R")# 
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+
+# Define sample sizes for analysis
+sample_sizes <- c(9, 25, 49, 81, 121, 225)
+
+# Number of replications
[…]

### 2024-03-14 Code/R/PlottingFunctions/plot_3d_entropy_with_orca.R

@@ -1,0 +1,45 @@
+library(plotly)
+library(latex2exp)
+
+# Entropy
+entropy_gI0 <- function(mu, alpha, L) {
+  term1 <- L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu)   
+  term2 <- -L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha))
+  entropy <- term1 + term2 
+  return(entropy)
+}
+
+mu <- seq(1, 10, length.out = 200)
+alpha <- seq(-20, -2, length.out = 200)
+
+entropyL1 <- outer(alpha, mu, function(alpha, mu) entropy_gI0(mu, alpha, L = 1))
+entropyL3 <- outer(alpha, mu, function(alpha, mu) entropy_gI0(mu, alpha, L = 3))
+entropyL8 <- outer(alpha, mu, function(alpha, mu) entropy_gI0(mu, alpha, L = 8))
+entropyL12 <- outer(alpha, mu, function(alpha, mu) entropy_gI0(mu, alpha, L = 12))
+entropyL100 <- outer(alpha, mu, function(alpha, mu) entropy_gI0(mu, alpha, L = 100))
+
+fig <- plot_ly(x = mu, y = alpha, showscale = FALSE)
+
+fig <- fig %>% add_surface(z = ~entropyL1, colorscale = list(c(0, 1), c("rgb(255,107,184)", "rgb(128,0,64)")), name = "L=1")
+fig <- fig %>% add_surface(z = ~entropyL3, colorscale = list(c(0, 1), c("rgb(247,226,157)", "rgb(255,192,7)")), name = "L=3")
+fig <- fig %>% add_surface(z = ~entropyL8,colorscale = list(c(0, 1), c("rgb(107,255,184)", "rgb(0,124,90)")),  name = "L=8")
+fig <- fig %>% add_surface(z = ~entropyL12,colorscale = list(c(0,1),c("rgb(129,212,247)","rgb(12,177,247)")),  name = "L=12")
+fig <- fig %>% add_surface(z = ~entropyL100, colorscale = list(c(0, 1), c("rgb(182,142,242)", "rgb(104,3,255)")), name = "L=100")
+
+# 
+fig <- fig %>% layout(
+  scene = list(
+    camera = list(
[…]

### 2024-03-14 Code/R/PlottingFunctions/plot_MSE.R

@@ -1,0 +1,65 @@
+rm(list = ls())
+library(ggplot2)
+library(invgamma)
+library(ggthemes)
+library(latex2exp)
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/correa_estimator.r")
+source("../MainFunctions/ebrahimi_estimator.r")
+source("../MainFunctions/noughabi_arghami_estimator.r")
+source("../MainFunctions/vasicek_estimator.r")
+source("../MainFunctions/al_omari_1_estimator.r")
+source("../MainFunctions/al_omari_2_estimator.r")
+
+
+sample_sizes <- c(9, 25, 49, 81, 121, 225)
+R <- 1000
+mu <- 1
+L <- 2
+
+# True entropy value for the gamma SAR distribution
+true_entropy <- entropy_gamma_sar(L, mu)
+
+
+
+output_mse <- data.frame(SampleSize = integer(0), Estimator = character(0), MSE = numeric(0))
+#List of estimator
+estimators <- list(
+  list(func = van_es_estimator, label = "Van Es"),
+  list(func = correa_estimator, label = "Correa"),
+  list(func = ebrahimi_estimator, label = "Ebrahimi"),
+  list(func = noughabi_arghami_estimator, label = "Noughabi Arghami"),
+  list(func = vasicek_estimator, label = "Vasicek"),
+  list(func = al_omari_1_estimator, label = "Al Omari 1"),
+  list(func = al_omari_2_estimator, label = "Al Omari 2")
+)
+
+
+
+for (estimator in estimators) {
+  for (ssize in sample_sizes) {
+    squared_errors <- numeric(R)
+    for (r in 1:R) {
+      sample <- gamma_sar_sample(L, mu, ssize)
+      estimated_entropy <- estimator$func(sample)
+      squared_errors[r] <- (estimated_entropy - true_entropy)^2
+    }
+    
+    # Calculate the MSE
+    mse <- mean(squared_errors)
+    
+    output_mse <- rbind(output_mse, data.frame(SampleSize = ssize, Estimator = estimator$label, MSE = mse))
+  }
+}
+
+# Plot the MSE as a function of the sample size
+ggplot(output_mse, aes(x = SampleSize, y = MSE, color = Estimator)) +
+  geom_line() +
+  geom_point() +
+  xlab("Sample Size") +
+  ylab("MSE") 
+
+  

### 2024-03-14 Code/R/Programs/ExperimentTestStatisticL5.R

@@ -1,0 +1,96 @@
+library(ggplot2)
+library(ggsci)
+
+
+if(!require("rstudioapi")) install("rstudioapi")
+setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+
+source("../MainFunctions/ebrahimi_estimator.R")
+source("../MainFunctions/gamma_sar_sample.R")
+source("../MainFunctions/correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator_log_mean.R")
+
+
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+
+
+
+
+
+
+set.seed(1234567890, kind="Mersenne-Twister")
+
+R <- 1000
+mu <- 1
+L <- 5
+B <- 5
+
+sample.size <- c(81)
+
+TestStatistics <- NULL
+
+for(s in sample.size){
+  for(r in 1:R){
+    
+    z <- gamma_sar_sample(L, mu, s)
+    
+    TestStat <- bootstrap_correa_estimator(z, B) - log(mean(z))  + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L)) 
+    
+    TestStatistics <- rbind(TestStatistics,
+                            c(s, TestStat))
+  }
+  
+  mean_entropy <- mean(TestStat)
+  cat(" mean", mean_entropy, "\n" )
+}
+
+TestStatistics <- data.frame(TestStatistics)
+names(TestStatistics) <- c("Sample Size", "Test Statistics")
+
+#print(TestStatistics)
+
+
+# ggplot(TestStatistics, aes(x=`Test Statistics`, col=`Sample Size`, group=`Sample Size`)) +
+#    geom_density()
+
+difference.betweeen.GammaSAR.GI0.OneLook <- function(alpha) {
+  return(
+    -lgamma(1-alpha) +
+      (1-alpha) * digamma(1-alpha) -
+      (1-alpha) * digamma(-alpha) +
+      log(-1-alpha) +
+      lgamma(-alpha) -1
+  )
+}
+
+
+ggplot(TestStatistics, aes(x = `Test Statistics`, col = factor(`Sample Size`), linetype = factor(`Sample Size`))) +
+  geom_line(stat = "density", linewidth = 1.0) +  
+  scale_color_manual(
+    values = pal_cosmic()(length(sample.size)),
+    name = "Sample Size"
+  ) +
[…]

### 2024-03-14 Code/R/Programs/FirstExperimentTestStatisticL1.R

@@ -1,0 +1,80 @@
+library(ggplot2)
+library(ggsci)
+
+
+if(!require("rstudioapi")) install("rstudioapi")
+setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+
+source("../MainFunctions/ebrahimi_estimator.R")
+source("../MainFunctions/gamma_sar_sample.R")
+
+
+
+
+set.seed(1234567890, kind="Mersenne-Twister")
+
+R <- 500
+mu <- 1
+sample.size <- c(49, 81, 121)
+
+TestStatistics <- NULL
+
+for(s in sample.size){
+  for(r in 1:R){
+    
+    z <- gamma_sar_sample(1, mu, s)
+    TestStat <- ebrahimi_estimator(z) - (1 + log(mean(z)))
+    #TestStat <-sqrt(R) *(ebrahimi_estimator(z) - (1 + log(mean(z))))/ sd(z)
+    #cat(" test2", TestStat, "\n")
+    TestStatistics <- rbind(TestStatistics,
+                            c(s, TestStat))
+  }
+  mean_test <- mean(TestStat)
+  cat(" mean", mean_test, "\n")
+}
+
+TestStatistics <- data.frame(TestStatistics)
+names(TestStatistics) <- c("Sample Size", "Test Statistics")
+
+# ggplot(TestStatistics, aes(x=`Test Statistics`, col=`Sample Size`, group=`Sample Size`)) +
+#    geom_density()
+
+difference.betweeen.GammaSAR.GI0.OneLook <- function(alpha) {
+  return(
+    -log(gamma(1-alpha)) +
+      (1-alpha) * digamma(1-alpha) -
+      (1-alpha) * digamma(-alpha) +
+      log(-1-alpha) +
+      log(gamma(-alpha)) -1
+  )
+}
+
+
+ggplot(TestStatistics, aes(x = `Test Statistics`, col = factor(`Sample Size`), linetype = factor(`Sample Size`))) +
+  geom_line(stat = "density", linewidth = 1.0) +  
+  scale_color_manual(
+    values = pal_cosmic()(length(sample.size)),
+    name = "Sample Size"
+  ) +
+  scale_linetype_manual(
+    values = rep("solid", length(sample.size)),  
+    name = "Sample Size"
+  ) +
+  #Expected values under H1
+  geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.OneLook(-1.01), col="red") +
[…]

### 2024-03-14 Code/R/Programs/Phantom_code.R

@@ -1,0 +1,102 @@
+library(png)
+source("../imagematrix.R")
+
+
+
+#reparametrized distribution for mu
+rGI0 <- function(n, p_alpha, p_mu, p_Looks) {
+  return(rgamma(n, shape = p_Looks, rate = p_Looks) / rgamma(n, shape = -p_alpha, rate = p_mu * (-p_alpha - 1)))
+}
+
+
+Z <- Phantom1 <- readPNG("../../../Figures/PNG/Phantom1.png")[,,1]
+dim(Phantom1)
+plot(imagematrix(Phantom1))
+
+E <- function(a, g) {-g/(a+1)}
+H <- function(a, g) {(a-1)/a - log(-a/g, base=exp(1))}
+HE1 <- function(a) {(a-1)/a - log(a/(a+1), base=exp(1))}
+
+HE1(-10)
+H(-2,50)
+H(-2,5)
+E(-6, 10)
+
+# Phantom
+
+## Return
+## z: return
+## up: upper, lo: lower
+## le: left, ri: right
+## b: black, w: white
+
+p.up.le <- Phantom1[1:250,1:250]
+p.up.ri <- Phantom1[1:250,251:500]
+p.bo.le <- Phantom1[251:500,1:250]
+p.bo.ri <- Phantom1[251:500,251:500]
+
+
+### Upper Left (means 1 and 1)
+z.up.le.b <- rGI0(n=sum(1-p.up.le), 
+                  p_alpha=-2, p_mu=1, p_Looks=2)
+mean(z.up.le.b)
+
+z.up.le.w <- rGI0(n=sum(p.up.le), 
+                  p_alpha=-10, p_mu=9, p_Looks=2)
+mean(z.up.le.w)
+z.up.le <- p.up.le
+z.up.le[p.up.le==0] <- z.up.le.b
+z.up.le[p.up.le==1] <- z.up.le.w
+#plot(imagematrix(equalize(z.up.le)))
+
+### Upper Right (means 50 and 5)
+z.up.ri.b <- rGI0(n=sum(1-p.up.ri), 
+                  p_alpha=-2, p_mu=50, p_Looks=2)
+mean(z.up.ri.b)
+z.up.ri.w <- rGI0(n=sum(p.up.ri), 
+                  p_alpha=-2, p_mu=5, p_Looks=2)
[…]

### 2024-03-14 Code/R/Programs/SAR_cqv_values.R

@@ -1,0 +1,57 @@
+#rm(list = ls())
+
+# if(!require("rstudioapi")) install("rstudioapi")
+# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+source("../../../Code/R/Programs/read_ENVI_images.R")
+source("../../../Code/R/MainFunctions/correa_estimator.R")
+
+#x <- myread.ENVI(file='../../../Data/SAR/Ottawa/Intensity_VV.img', headerfile='../../../Data/SAR/Ottawa/Intensity_VV.hdr')
+# x_Flevoland2 <- myread.ENVI(file='../../../Data/SAR/Flevoland_100/Intensity_VV.img', 
+#                             headerfile='../../../Data/SAR/Flevoland_100/Intensity_VV.hdr')
+
+ x <- myread.ENVI(file='../../../Data/SAR/Flevoland_300/Intensity_VV.img', 
+                  headerfile='../../../Data/SAR/Flevoland_300/Intensity_VV.hdr')
+
+x <- myread.ENVI(file='../../../Data/SAR/Ottawa_512/Intensity_VV.img', 
+                 headerfile='../../../Data/SAR/Ottawa_512/Intensity_VV.hdr')
+
+
+
+L <- 5
+#B <- 1
+
+
+
+
+window_size <- 5
+
+
+rows <- nrow(x)
+cols <- ncol(x)
+
+
+
+
+cv_values_cqv <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Seleccionar ventana local
+    window_data <- x[i:(i + window_size - 1), j:(j + window_size - 1)]
+    
+    # Calcular los cuartiles
+    q1 <- quantile(window_data, 0.25)
+    q3 <- quantile(window_data, 0.75)
+    
+    # Calcular el CQV
+    cv_values_cqv[i, j] <- (q3 - q1) / (q3 + q1)
+  }
+}
+
+# Guardar el resultado en un archivo
+save(cv_values_cqv, x, file = "./Data/results_data_Ottawa_cqv_512_5.Rdata")
+
+

### 2024-03-14 Code/R/Programs/SAR_cv_values.R

@@ -1,0 +1,92 @@
+#rm(list = ls())
+
+# if(!require("rstudioapi")) install("rstudioapi")
+# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+source("../../../Code/R/Programs/read_ENVI_images.R")
+source("../../../Code/R/MainFunctions/correa_estimator.R")
+
+#x <- myread.ENVI(file='../../../Data/SAR/Ottawa/Intensity_VV.img', headerfile='../../../Data/SAR/Ottawa/Intensity_VV.hdr')
+# x_Flevoland2 <- myread.ENVI(file='../../../Data/SAR/Flevoland_100/Intensity_VV.img', 
+#                             headerfile='../../../Data/SAR/Flevoland_100/Intensity_VV.hdr')
+
+# x <- myread.ENVI(file='../../../Data/SAR/Flevoland_300/Intensity_VV.img', 
+#                  headerfile='../../../Data/SAR/Flevoland_300/Intensity_VV.hdr')
+
+x <- myread.ENVI(file='../../../Data/SAR/Ottawa_512/Intensity_VV.img', 
+                 headerfile='../../../Data/SAR/Ottawa_512/Intensity_VV.hdr')
+
+
+
+L <- 5
+#B <- 1
+
+
+
+
+window_size <- 5
+
+
+rows <- nrow(x)
+cols <- ncol(x)
+
+
+cv_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+
+#test_difference_vector <- numeric()
+
+# 
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Seleccionar ventana local
+    window_data <- x[i:(i + window_size - 1), j:(j + window_size - 1)]
+    
+     
+    x_values <- window_data
+    
+    
+    # 
+    mean_values <- mean(window_data)
+    sd_values <- sd(window_data)
+    
+    # 
+    cv_values[i, j] <- sd_values / mean_values
+    
+
+   
+  }
+}
+
+
+#save(test_difference_vector, file = "./Data/results_data_Flevoland_100_5.Rdata")
+save( cv_values, x, file = "./Data/results_data_Ottawa_cv_512_5.Rdata")
+
+
+
+# print(mean_values)
[…]

### 2024-03-14 Code/R/Programs/Sar_test_each_window.R

@@ -1,0 +1,223 @@
+
+# rm(list = ls())
+# if(!require("rstudioapi")) install("rstudioapi")
+# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+
+library(ggplot2)
+library(e1071)
+library(nortest)
+library(fitdistrplus)
+
+#load("./Data/results_data_Flevoland_cv_300_5.Rdata")
+load("./Data/results_data_Flevoland_300_9.Rdata")
+#summary(difference_values)
+
+
+#load("results_data_Flevoland_300_9.Rdata")
+
+
+p_values_matrix <- matrix(NA, nrow = nrow(difference_values), ncol = ncol(difference_values))
+
+
+for (i in 1:nrow(difference_values)) {
+  for (j in 1:ncol(difference_values)) {
+    # Calcular z-score para cada diferencia
+    z_score <- (difference_values[i, j] - mean(difference_values)) / sd(difference_values)
+    
+    # Calcular p-value para una prueba de dos colas
+    p_value <- 2 * pnorm(-abs(z_score))
+    
+    # Almacenar p-value en la matriz
+    p_values_matrix[i, j] <- p_value
+  }
+}
+
+
+# # Calcular z-scores para toda la matriz
+# all_z_scores <- as.vector((difference_values - mean(difference_values)) / sd(difference_values))
+# 
+# # Crear un marco de datos con los datos
+# df_z_scores <- data.frame(z_scores = all_z_scores)
+# 
+# # Graficar la densidad de los z-scores
+# ggplot(df_z_scores, aes(x = z_scores)) +
+#   geom_density(fill = "blue", alpha = 0.5) +
+#   labs(title = "Densidad de Z-scores", x = "Z-score", y = "Densidad")
+
+# Convertir la matriz de p-values en un vector
+all_p_values <- as.vector(p_values_matrix)
+
+# Crear un marco de datos con los datos
+df_p_values <- data.frame(p_values = all_p_values)
+
+# Graficar la densidad de los p-values
+ggplot(df_p_values, aes(x = p_values)) +
+  geom_density(fill = "green", alpha = 0.5) +
+  labs(title = "Densidad de P-values", x = "P-value", y = "Densidad")
+
+
+# Imprimir los primeros resultados
+#head(p_values_matrix)
+
+
+
+# ggplot() +
[…]

### 2024-03-14 Code/R/Programs/csv_file.R

@@ -1,0 +1,8 @@
+
+load("./Data/results_data_Ottawa_cqv_512_5.Rdata")
+x1 <- as.vector(cv_values)
+
+ruta_del_archivo <- "./Data/Ottawa_cqv_5.csv"
+
+
+write.csv(data.frame(x1), file = "./Data/Ottawa_cqv_5.csv", row.names = FALSE)

### 2024-03-14 Code/R/Programs/data_gamma.R

@@ -1,0 +1,107 @@
+rm(list = ls())
+
+library(ggplot2)
+library(ggsci)
+library(invgamma)
+library(latex2exp)
+if(!require("rstudioapi")) install("rstudioapi")
+setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+
+source("../MainFunctions/ebrahimi_estimator.R")
+source("../MainFunctions/gamma_sar_sample.R")
+source("../MainFunctions/correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator_log_mean.R")
+
+source("../MainFunctions/al_omari_1_estimator.R")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.R")
+
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+R <- 1000
+mu <- 1
+L <- 5
+B <- 2
+alpha1 <- -6
+sample.size <- c(81)
+
+TestStatistics1 <- NULL
+TestStatistics2 <- NULL
+TestStatistics3 <- NULL
+TestStatistics4 <- NULL
+mean_entropy1 <- numeric(length(sample.size))
+mean_entropy2 <- numeric(length(sample.size))
+mean_entropy3 <- numeric(length(sample.size))
+mean_entropy4 <- numeric(length(sample.size))
+for (s in sample.size) {
+  TestStat1 <- numeric(R)
+  TestStat2 <- numeric(R)
+  TestStat3 <- numeric(R)
+  TestStat4 <- numeric(R)
+  
+  
+  for (r in 1:R) {
+    #z <- gi0_sample(mu, alpha1, L, s)
+    z <- gamma_sar_sample(L, mu, s)
+    #TestStat1[r] <- log(mean(z))  - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L)+L + lgamma(L-alpha1) - (L-alpha1)*(digamma(L - alpha1))+(1-alpha1)*digamma(- alpha1)-log(-1 - alpha1)-lgamma(-alpha1) ) 
+    #TestStat1[r] <- log(mean(z))  - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
[…]

### 2024-03-14 Code/R/Programs/data_gi0.R

@@ -1,0 +1,72 @@
+rm(list = ls())
+
+library(ggplot2)
+library(ggsci)
+library(invgamma)
+library(latex2exp)
+if(!require("rstudioapi")) install("rstudioapi")
+setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+
+source("../MainFunctions/ebrahimi_estimator.R")
+source("../MainFunctions/gamma_sar_sample.R")
+source("../MainFunctions/correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator_log_mean.R")
+
+source("../MainFunctions/al_omari_1_estimator.R")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.R")
+
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+
+set.seed(1234567890, kind="Mersenne-Twister")
+
+R <- 1000
+mu <- 1
+L <- 5
+B <- 2
+alpha1<- -600
+sample.size <- c(9, 25, 49, 81)
+
+
+
+TestStatistics <- NULL
+
+for(s in sample.size){
+  for(r in 1:R){
+    z <- gi0_sample(mu, alpha1, L,  s)
+   
+    #TestStat <- log(mean(z))  - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
+    TestStat <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
+    #TestStat <- bootstrap_correa_estimator(z, B) -log(mean(z))  + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L)+L + lgamma(L-alpha1) - (L-alpha1)*(digamma(L - alpha1))+(1-alpha1)*digamma(- alpha1)-log(-1 - alpha1)-lgamma(-alpha1) ) 
+    TestStatistics <- rbind(TestStatistics,
+                            c(s, TestStat))
+  }
+  mean_entropy1 <- mean(TestStat)
+  cat(" mean", mean_entropy1, "\n" )
+}
+
+TestStatistics <- data.frame(TestStatistics)
+names(TestStatistics) <- c("Sample Size", "Test Statistics")
+
+
+
+
+ggplot(TestStatistics, aes(x = `Test Statistics`, col = factor(`Sample Size`), linetype = factor(`Sample Size`))) +
[…]

### 2024-03-14 Code/R/Programs/p_value_plot_color.R

@@ -1,0 +1,48 @@
+rm(list = ls())
+# if(!require("rstudioapi")) install("rstudioapi")
+# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+# for normal distribution
+library(ggplot2)
+library(e1071)
+library(nortest)
+library(fields)
+#load("./Data/results_data_Ottawa_100_5.Rdata") # difference_value
+#load("./Data/results_data_Flevoland_300_5.Rdata")
+
+load("./Data/results_data_Flevoland_300_7.Rdata")
+#load("./Data/results_data_Flevoland_300_9.Rdata")
+
+calculate_p_values_matrix <- function(data_matrix, sigma) {
+  rows <- nrow(data_matrix)
+  cols <- ncol(data_matrix)
+  
+  p_values_matrix <- matrix(NA, nrow = rows, ncol = cols)
+  
+  for (i in 1:rows) {
+    for (j in 1:cols) {
+      test_difference <- data_matrix[i, j]
+      
+      epsilon <-(test_difference - 0.0) / (sigma)
+      p_value <-p_value <- 2 * pnorm(abs(epsilon))-1#  
+      
+      p_values_matrix[i, j] <- p_value
+    }
+  }
+  
+  return(p_values_matrix )
+}
+
+
+
+
+mean_difference_values <- mean(difference_values, na.rm = TRUE)
+sd_difference_values <- sd(difference_values, na.rm = TRUE)
+
+
+p_values_matrix <- calculate_p_values_matrix(difference_values, sd_difference_values)
+
+
+source("../imagematrix.R")
+#hist(p_values_matrix)
+plot(imagematrix(p_values_matrix),significance_level = 0.05)
+

### 2024-03-14 Code/R/Programs/plot_pvalue.R

@@ -1,0 +1,202 @@
+# 
+ rm(list = ls())
+# if(!require("rstudioapi")) install("rstudioapi")
+# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+# for normal distribution
+library(ggplot2)
+library(e1071)
+library(nortest)
+
+#load("./Data/results_data_Ottawa_100_5.Rdata") # difference_value
+#load("./Data/results_data_Flevoland_300_5.Rdata")
+
+load("./Data/results_data_Flevoland_300_7.Rdata")
+#load("./Data/results_data_Flevoland_300_9.Rdata")
+
+calculate_p_values_matrix <- function(data_matrix, sigma) {
+  rows <- nrow(data_matrix)
+  cols <- ncol(data_matrix)
+  
+  p_values_matrix <- matrix(NA, nrow = rows, ncol = cols)
+  
+  for (i in 1:rows) {
+    for (j in 1:cols) {
+      test_difference <- data_matrix[i, j]
+      
+      epsilon <- (test_difference - 0.0) / sigma
+      p_value <-2 * pnorm(-abs(epsilon))  
+      
+      p_values_matrix[i, j] <- p_value
+    }
+  }
+  
+  return(p_values_matrix )
+}
+
+
+mean_difference_values <- mean(difference_values, na.rm = TRUE)
+sd_difference_values <- sd(difference_values, na.rm = TRUE)
+
+
+p_values_matrix <- calculate_p_values_matrix(difference_values, sd_difference_values)
+
+save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_300_7_n.Rdata")
+
+aspect_ratio <- ncol(p_values_matrix) / nrow(p_values_matrix)
+
+# Create a sequence of values for x and y axes based on the aspect ratio
+x_values <- seq(0, 1, length.out = ncol(p_values_matrix) + 1)
+y_values <- seq(0, aspect_ratio, length.out = nrow(p_values_matrix) + 1)
+
+# Plot the p_values_matrix with adjusted axes
+image(x = x_values, y = y_values, z = p_values_matrix, 
+      col = colorRampPalette(c("navy", "yellow", "orange"))(100),
+      main = "Heatmap de p-values",
+      xlab = "Columnas",
+      ylab = "Filas")
+
+# Add grid lines to visualize the pixel positions
+abline(v = x_values, h = y_values, col = "gray", lty = 2)
+
[…]

### 2024-03-14 Code/R/Programs/plot_pvalue_cv.R

@@ -1,0 +1,28 @@
+
+load("./Data/results_data_Flevoland_cv_300_5.Rdata")
+alpha <- 5.452
+beta <- 2.061
+
+
+pgamma_inv <- function(x, alpha, beta) {
+  1 - pgamma(1/x, shape = alpha, rate = beta)
+}
+
+
+p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))
+
+for (i in 1:nrow(cv_values)) {
+  for (j in 1:ncol(cv_values)) {
+    cv_value <- cv_values[i, j]
+    
+    
+    p_values_matrix[i, j] <- pgamma_inv(cv_value, alpha, beta)
+  }
+}
+
+
+save(p_values_matrix, file = "./Data/results_pvalue_cv_Flevoland_cv_300_5.Rdata")
+
+
+source("../imagematrix.R")
+plot(imagematrix(p_values_matrix > 0.05))

### 2024-03-14 Code/R/Programs/power_example.R

@@ -1,0 +1,69 @@
+
+
+rm(list = ls())
+
+library(ggplot2)
+library(ggsci)
+library(invgamma)
+library(latex2exp)
+library(data.table)
+source("../MainFunctions/ebrahimi_estimator.R")
+source("../MainFunctions/gamma_sar_sample.R")
+source("../MainFunctions/correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator_log_mean.R")
+
+source("../MainFunctions/al_omari_1_estimator.R")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.R")
+
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+
+
+
+alpha <- 0.05
+
+
+R <- 3000
+mu <- 1
+L <- 5
+B <- 2
+alpha1 <- -600
+
+sample_sizes <- c( 25, 49, 81, 121)
+
+
+power_results <- numeric(length(sample_sizes))
+
+# Escenarios bajo H1 (por ejemplo, clutter heterogéneo)
+for (i in seq_along(sample_sizes)) {
+  s <- sample_sizes[i]
+  reject_H0_count <- 0
+  
+  for (r in 1:R) {
+   
+    z1 <- gi0_sample(1, -600, 5, s)
+    
+   
+    TestStat <- sqrt(R) * (bootstrap_correa_estimator_log_mean(z1, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))) / sd(z1)
+    
+    
+    if (abs(TestStat) > qnorm(1 - alpha/2)) {
+      reject_H0_count <- reject_H0_count + 1
+    }
+  }
+  
+  # Calcular y almacenar el poder (1 - beta)
+  power <- reject_H0_count / R
+  power_results[i] <- power
+  
+  cat(paste("Power (1 - beta) for Sample Size", s, ":", power, "\n"))
+}
+
+# Graficar resultados
+plot(sample_sizes, power_results, type = "b", pch = 16, col = "blue",
+     xlab = "Sample Size", ylab = "Power (1 - beta)",
+     main = "Power Analysis")

### 2024-03-14 Code/R/Programs/sar_test_calculation.R

@@ -1,0 +1,99 @@
+#rm(list = ls())
+
+if(!require("rstudioapi")) install("rstudioapi")
+setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+source("../../../Code/R/Programs/read_ENVI_images.R")
+source("../../../Code/R/MainFunctions/correa_estimator.R")
+
+#x <- myread.ENVI(file='../../../Data/SAR/Ottawa/Intensity_VV.img', headerfile='../../../Data/SAR/Ottawa/Intensity_VV.hdr')
+# x_Flevoland2 <- myread.ENVI(file='../../../Data/SAR/Flevoland_100/Intensity_VV.img', 
+#                             headerfile='../../../Data/SAR/Flevoland_100/Intensity_VV.hdr')
+
+x <- myread.ENVI(file='../../../Data/SAR/Flevoland_300/Intensity_VV.img', 
+                             headerfile='../../../Data/SAR/Flevoland_300/Intensity_VV.hdr')
+x <- myread.ENVI(file='../../../Data/SAR/Ottawa_512/Intensity_VV.img', 
+                 headerfile='../../../Data/SAR/Ottawa_512/Intensity_VV.hdr')
+
+
+
+
+L <- 5
+B <- 1
+
+#difference_total <- bootstrap_correa_estimator_log_mean(x_Flevoland2, B)-  (L - log(L) + lgamma(L) + (1 - L) * digamma(L)) 
+
+
+window_size <- 5
+
+
+rows <- nrow(x)
+cols <- ncol(x)
+
+# 
+mean_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+entropy_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+true_entropy_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+difference_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+
+test_difference_vector <- numeric()
+
+# Iterar sobre ventanas deslizantes
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Seleccionar ventana local
[…]

### 2024-03-14 Code/R/Programs/sar_test_calculation_AO.R

@@ -1,0 +1,81 @@
+rm(list = ls())
+
+library(ggplot2)
+library(ggsci)
+library(invgamma)
+library(latex2exp)
+library(data.table)
+
+# if(!require("rstudioapi")) install("rstudioapi")
+# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+source("../MainFunctions/ebrahimi_estimator.R")
+source("../MainFunctions/gamma_sar_sample.R")
+source("../MainFunctions/correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator_log_mean.R")
+
+source("../MainFunctions/al_omari_1_estimator.R")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.R")
+
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+source("../MainFunctions/gamma_sar_sample.R")
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+# Function to calculate p-value
+calculate_p_value <- function(test_statistic, mu_W, sigma_W) {
+  epsilon <- test_statistic  / sigma_W
+  p_value <- 2 * (1 - pnorm(abs(epsilon)))
+  
+  cat("epsilon:", epsilon, "\n")
+  return(p_value)
+}
+
+# Function to calculate Type II Error Rate
+calculate_type_II_error_rate <- function(p_values, alpha_nominal) {
+  type_II_error_rate <- sum(p_values >= alpha_nominal) / length(p_values)
+  return(type_II_error_rate)
+}
+
+R <- 1000
+mu <- 1
+L <- 5
+B <- 1
+sample.size <- c(50, 100, 200, 300)
+
+alpha1 <- -8
+
+TestStatistics1 <- NULL
+
+mean_entropy1 <- numeric(length(sample.size))
+sd_entropy1 <- numeric(length(sample.size))
+
+for (s in sample.size) {
+  TestStat1 <- numeric(R)
+  
+  for (r in 1:R) {
+    # Generate samples under the alternative hypothesis
+    z <- gi0_sample(mu, alpha1, L, s) # H1: los datos provienen de gi0
+    
+    TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
+  }
+  
[…]

### 2024-03-14 Code/R/Programs/test_differences.R

@@ -1,0 +1,108 @@
+rm(list = ls())
+
+library(ggplot2)
+library(ggsci)
+library(invgamma)
+library(latex2exp)
+if(!require("rstudioapi")) install("rstudioapi")
+setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+
+source("../MainFunctions/ebrahimi_estimator.R")
+source("../MainFunctions/gamma_sar_sample.R")
+source("../MainFunctions/correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator_log_mean.R")
+
+source("../MainFunctions/al_omari_1_estimator.R")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.R")
+
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+R <- 10
+mu <- 1
+L <- 5
+B <- 1
+alpha1 <- -6
+sample.size <- c( 9, 25, 49, 81, 121)
+
+TestStatistics1 <- NULL
+TestStatistics2 <- NULL
+TestStatistics3 <- NULL
+TestStatistics4 <- NULL
+mean_entropy1 <- numeric(length(sample.size))
+mean_entropy2 <- numeric(length(sample.size))
+mean_entropy3 <- numeric(length(sample.size))
+mean_entropy4 <- numeric(length(sample.size))
+for (s in sample.size) {
+  TestStat1 <- numeric(R)
+  TestStat2 <- numeric(R)
+  TestStat3 <- numeric(R)
+  TestStat4 <- numeric(R)
+  
+  
+  for (r in 1:R) {
+    #z <- gi0_sample(mu, alpha1, L, s)
+    z <- gamma_sar_sample(L, mu, s)
+
+    #TestStat1[r] <- -bootstrap_correa_estimator_log_mean(z, B) - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L) + L + lgamma(L - alpha1) - (L - alpha1) * (digamma(L - alpha1)) + (1 - alpha1) * digamma(-alpha1) - log(-1 - alpha1) - lgamma(-alpha1))
+    TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
[…]

### 2024-03-14 Code/R/Programs/test_differences_gi0.R

@@ -1,0 +1,102 @@
+rm(list = ls())
+
+library(ggplot2)
+library(ggsci)
+library(invgamma)
+library(latex2exp)
+source("../MainFunctions/ebrahimi_estimator.R")
+source("../MainFunctions/gamma_sar_sample.R")
+source("../MainFunctions/correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator_log_mean.R")
+
+source("../MainFunctions/al_omari_1_estimator.R")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.R")
+
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+R <- 3000
+mu <- 1
+L <- 5
+B <- 2
+alpha1 <- -6
+sample.size <- c(81)
+
+TestStatistics1 <- NULL
+TestStatistics2 <- NULL
+TestStatistics3 <- NULL
+TestStatistics4 <- NULL
+mean_entropy1 <- numeric(length(sample.size))
+mean_entropy2 <- numeric(length(sample.size))
+mean_entropy3 <- numeric(length(sample.size))
+mean_entropy4 <- numeric(length(sample.size))
+for (s in sample.size) {
+  TestStat1 <- numeric(R)
+  TestStat2 <- numeric(R)
+  TestStat3 <- numeric(R)
+  TestStat4 <- numeric(R)
+
+  
+  for (r in 1:R) {
+    z <- gi0_sample(mu, alpha1, L, s)
+    TestStat1[r] <- log(mean(z))  - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
+    TestStat2[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L) + L + lgamma(L - alpha1) - (L - alpha1) * (digamma(L - alpha1)) + (1 - alpha1) * digamma(-alpha1) - log(-1 - alpha1) - lgamma(-alpha1))
+    TestStat3[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
+    TestStat4[r] <- bootstrap_correa_estimator(z, B)
+  }
+  
+  mean_entropy1[sample.size == s] <- mean(TestStat1)
[…]

### 2024-03-14 Code/R/Programs/test_differences_subplots_gi0.R

@@ -1,0 +1,179 @@
+rm(list = ls())
+
+library(ggplot2)
+
+library(grid)
+library(ggsci)
+library(invgamma)
+library(latex2exp)
+library(gridExtra)
+source("../MainFunctions/ebrahimi_estimator.R")
+source("../MainFunctions/gamma_sar_sample.R")
+source("../MainFunctions/correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator_log_mean.R")
+
+source("../MainFunctions/al_omari_1_estimator.R")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.R")
+
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+R <- 3000
+mu <- 1
+L <- 5
+B <- 2
+sample.size <- c( 81)
+
+alpha1_values <- c( -3, -8, -20, -100)
+
+
+plots_list <- list()
+
+for (alpha_val in alpha1_values) {
+
+  alpha1 <- alpha_val
+  
+  TestStatistics1 <- NULL
+  TestStatistics2 <- NULL
+  
+  mean_entropy1 <- numeric(length(sample.size))
+  mean_entropy2 <- numeric(length(sample.size))
+  
+  for (s in sample.size) {
+    TestStat1 <- numeric(R)
+    TestStat2 <- numeric(R)
+    
+    for (r in 1:R) {
+      z <- gi0_sample(mu, alpha1, L, s)
+      
+      TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
+      TestStat2[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L) - L - lgamma(L - alpha1) + (L - alpha1) * (digamma(L - alpha1))- (1 - alpha1) * digamma(-alpha1) + log(-1 - alpha1) + lgamma(-alpha1))
+      
[…]

### 2024-03-14 Code/R/Programs/tipe1_error_example.R

@@ -1,0 +1,75 @@
+rm(list = ls())
+
+library(ggplot2)
+library(ggsci)
+library(invgamma)
+library(latex2exp)
+library(data.table)
+
+if(!require("rstudioapi")) install("rstudioapi")
+setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+source("../MainFunctions/ebrahimi_estimator.R")
+source("../MainFunctions/gamma_sar_sample.R")
+source("../MainFunctions/correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator_log_mean.R")
+
+source("../MainFunctions/al_omari_1_estimator.R")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.R")
+
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+
+alpha <- 0.05
+
+
+R <- 100
+mu <- 1
+L <- 5
+B <- 2
+alpha1 <- -6
+
+
+sample_sizes <- c(25, 49, 81, 121)
+
+
+error_type_I_results <- numeric(length(sample_sizes))
+
+
+for (i in seq_along(sample_sizes)) {
+  s <- sample_sizes[i]
+  false_positives_count <- 0
+  
+  for (r in 1:R) {
+    #
+    z0 <- gi0_sample(1, -6, 5, s)
+    
+    # prueba bajo H0
+    TestStat <- sqrt(R) * (bootstrap_correa_estimator_log_mean(z0, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))) / sd(z0)
+    #TestStat <- bootstrap_correa_estimator_log_mean(z0, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L)) 
+    
+
+    
+    # 
+    if (abs(TestStat) > qnorm(1 - alpha/2)) {
+      false_positives_count <- false_positives_count + 1
+    }
+  }
+  
+ 
+  cat(paste("False Positives for Sample Size", s, ":", false_positives_count, "\n"))
+  
+  # Calcular y almacenar el error tipo I
+  error_type_I <- false_positives_count / R
+  error_type_I_results[i] <- error_type_I
+  
+  cat(paste("Error Type I for Sample Size", s, ":", error_type_I, "\n"))
+}
+
[…]

### 2024-03-14 Code/R/imagematrix.R

@@ -1,0 +1,200 @@
+##
+## imagematrix class definition
+##
+## $Header: /database/repository/rimage/R/Attic/imagematrix.R,v 1.1.2.5 2004/03/17 06:35:18 tomo Exp $
+##
+## Copyright (c) 2003 Nikon Systems Inc.
+## For complete license terms see file LICENSE
+
+
+
+imagematrix <- function(mat, type = NULL, ncol = dim(mat)[1], nrow = dim(mat)[2],
+                        noclipping = FALSE) {
+  if (is.null(dim(mat)) && is.null(type)) stop("Type should be specified.")
+  if (length(dim(mat)) == 2 && is.null(type)) type <- "grey"
+  if (length(dim(mat)) == 3 && is.null(type)) type <- "rgb"
+  if (type != "rgb" && type != "grey") stop("Type is incorrect.")
+  if (is.null(ncol) || is.null(nrow)) stop("Dimension is uncertain.")
+
+  imgdim <- c(ncol, nrow, if (type == "rgb") 3 else NULL)
+
+  if (length(imgdim) == 3 && type == "grey") {
+    # force to convert grey image
+    mat <- rgb2grey(mat)
+  }
+
+  if (noclipping == FALSE && ((min(mat, na.rm = TRUE) < 0) || (1 < max(mat, na.rm = TRUE)))) {
+    warning("Pixel values were automatically clipped because of range over.")
+    mat <- clipping(mat)
+  }
+
+  mat <- array(mat, dim = imgdim)
+  attr(mat, "type") <- type
+  class(mat) <- c("imagematrix", class(mat))
+  mat
+}
+
+
+imageType <- function(x) {
+  attr(x, "type")
+}
+
+
+
+#"#9ECAE1",
+plot.imagematrix <- function(x, significance_level = 0.05, colors = colorRampPalette(c("#FF6600","#253494" ))(100), ...) {
+  if (is.null(attr(x, "type"))) stop("Type should be specified.")
+
+  colmat <- matrix(0, nrow = nrow(x), ncol = ncol(x))
+
+  
+  colmat[x > 1 - significance_level] <- 1
+
+  
+  colmat[x <= 1 - significance_level & x > significance_level] <- (x[x <= 1 - significance_level & x > significance_level] - significance_level) / (1 - significance_level)
+
+  
+  colmat[x <= significance_level] <- -x[x <= significance_level] / significance_level
+
[…]

### 2024-04-04 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
updated paper version

@@
 The second test uses the classic coefficient of variation.
-The third test employs an alternative form of estimating the CV based on the ratio of the median absolute deviation to the median.
+The third test employs an alternative form of estimating the CV based on the ratio of the mean absolute deviation from the median to the median.
 We apply our test statistic to produce maps of $p$-values for the hypothesis of homogeneity.
@@
  This article is fully reproducible using RMarkdown. All code and data are accessible at
- \url{https://github.com/rjaneth/Janeth-Alpala} (accessed on 10 March 2024).
-abbreviations:
-  - short: MDPI
-    long: Multidisciplinary Digital Publishing Institute
-  - short: DOAJ
-    long: Directory of open access journals
-  - short: TLA
-    long: Three letter acronym
-  - short: LD 
-    long: linear dichroism
+ \url{https://github.com/rjaneth/identifying-heterogeneity-in-sar-data-with-new-test-statistics} (accessed on 5 April 2024).
+# abbreviations:
+#   - short: MDPI
+#     long: Multidisciplinary Digital Publishing Institute
+#   - short: DOAJ
+#     long: Directory of open access journals
+#   - short: TLA
+#     long: Three letter acronym
+#   - short: LD 
+#     long: linear dichroism
 
@@
    - \usepackage{amsmath}
+   - \usepackage{multirow}
+   - \usepackage{subcaption}
+   - \captionsetup[sub]{labelfont=bf,textfont=bf}
 
@@
 library(nortest)# AD
+library(MASS)#
+library(fitdistrplus)# model selection AIC and BIC
 
@@
 
-Synthetic Aperture Radar (SAR) technology has become an important tool for environmental monitoring and disaster management, providing valuable imagery in different conditions, including day or night and diverse weather situations&nbsp;\cite{Mu2019}.
-However, the effective utilization of SAR data depends on a thorough understanding of its statistical properties, especially the impact of speckle effects, which are inherent in SAR data due to the coherent nature of the imaging process.
+Synthetic Aperture Radar (SAR) technology has become an important tool for environmental monitoring and disaster management, providing valuable imagery in different conditions, including day or night and diverse weather situations&nbsp;\cite{Moreira2013,Mu2019}.
+However, the effective utilization of SAR data depends on a thorough understanding of its statistical properties, especially the impact of speckle effects, which are inherent in SAR data due to the coherent nature of the imaging process&nbsp;\cite{Argenti2013}.
 
 In the presence of non-Gaussian speckle interference, SAR data requires a reliable statistical model for accurate processing.
-The $\mathcal{G}^0$ distribution, suitable for SAR data, includes the Gamma law as a specific case for fully developed speckle, providing flexibility with fewer parameters for analysis.
+The $\mathcal{G}^0$ distribution, suitable for SAR data, includes the Gamma law as a limit case for fully developed speckle&nbsp;\cite{Ferreira2020}, providing flexibility with fewer parameters for analysis.
 
@@
 Shannon introduced it for a random variable in 1948&nbsp;\cite{Shannon1948} as a measure of information and uncertainty.  
-In statistics, Shannon entropy is a crucial descriptive parameter, particularly for assessing data dispersion and conducting tests for normality, exponentiality, and uniformity&nbsp;\cite{Wieczorkowski1999}.
+In statistics, Shannon entropy is a crucial descriptive parameter, particularly for assessing data dispersion and conducting tests for normality, exponentiality, and uniformity&nbsp;\cite{Wieczorkowski1999,Zamanzade2012}.
 Entropy estimation involves several practical difficulties, especially when the model is unknown; in these cases, non-parametric methods are used.
-Among the non-parametric approaches, Subhash et al.&nbsp;\cite{Subhash2021} discussed the use of spacing methods.
-This non-parametric strategy offers flexibility to address a wide range of models without imposing specific parametric restrictions.
+
+Spacing methods have been discussed as a non-parametric approach in&nbsp;\cite{AlizadehNoughabi2010,Subhash2021}. 
+This strategy offers flexibility to address a wide range of models without imposing specific parametric restrictions.
+
 In our study, entropy serves as the fundamental parameter, providing a robust assessment by means of a bootstrapped non-parametric estimator of Shannon entropy.
 
-Simultaneously, we used the classic coefficient of variation (CV) and an alternative form based on the ratio between the median absolute deviation and the median.
-The coefficient of variation, recognised as an efficient and robust index of textural information, measures the homogeneity of the image.
+Simultaneously, we use the classic coefficient of variation (CV) and an alternative form based on the ratio between the median absolute deviation and the median. 
+The CV is known as an efficient and robust index of textural information, measures the homogeneity of the image&nbsp;\cite{Lopes1990}.
+
+The CV, introduced by Pearson&nbsp;\cite{Pearson1896} in 1896, is a relative measure of dispersion widely used in various areas of applied statistics including sampling, biostatistics, medical and biological research, climatology, and other fields \cite{hendricks1936sampling, Tian2005,SubrahmanyaNairy2003,Chankham2024}.
+It facilitates the comparison of variability between different populations and is especially valuable for comparing variables with different units. 
+This is because when the main purpose is to compare variations of several variables, the standard deviation cannot serve as an adequate measure of variation unless all variables are expressed in the same unit of measurement and have identical mean values.
+When these requirements are not hold for the variables under study, CV is the relative measure typically used in real applications. 
+The variable with the highest CV value is the one with the highest relative dispersion around the mean&nbsp;\cite{Banik2011}.
 
@@
 Section&nbsp;\ref{sec:test} outlines hypothesis testing based on non-parametric entropy estimators and and coefficient of variation.
-In Section&nbsp;\ref{sec:results}, we present experimental results. 
+In Section&nbsp;\ref{sec:Results}, we present experimental results. 
 Finally, in Section&nbsp;\ref{sec:conclusion} conclusions are exhibited.
@@
 
-## Statistical modeling of Intensity SAR data
+## Statistical Modeling of Intensity SAR data
 
@@
 where $\psi^{(0)}(\cdot)$ is the digamma function.
-Fig.&nbsp;\ref{fig:Plot_GI0_to_gamma1}, shows the behaviour of the entropy of \(G_I^0\) when when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), observing its convergence towards the entropy of \(\Gamma_{\text{SAR}}\) as \(\alpha\) takes large negative values.
+Figure&nbsp;\ref{fig:Plot_GI0_to_gamma1}, shows the behaviour of the entropy of \(G_I^0\) when when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), observing its convergence towards the entropy of \(\Gamma_{\text{SAR}}\) as \(\alpha\) takes large negative values.
 
@@
 
-In Fig.&nbsp;\ref{fig:Plot_bias_mse_gi0} we depict comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions.
+In Figure&nbsp;\ref{fig:Plot_bias_mse_gi0} we depict comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions.
 The use of the bootstrap technique exhibits more precision, reduced bias and MSE, and improved convergence.
@@
 
-# Hypothesis testing based on non-parametric entropy {#sec:test}
-
-General asymptotic results for functions of spacings are detailed in Ref.&nbsp;\cite{Khashimov1990}, while Van Es&nbsp;\cite{Bert1992} developed a correction for the case of Shannon entropy.
-Following the work of these authors, the next result applies: 
-<!-- \begin{lemma} -->
-<!-- Suppose that $f(\cdot)$ is a bounded density bounded away from zero and satisfies a Lipschitz condition on its support. -->
-<!-- Then, if $m,n\rightarrow \infty$ and $m=o(n^{1/2})$, one holds that: -->
-<!-- \begin{equation*} -->
-<!-- \sqrt{n}\,\Big(\label{Eq:bias_t} -->
-<!-- \widetilde{H}_{i}+\int_{-\infty}^\infty f(z)\ln f(z) \mathrm{d}z\Big) -->
-<!-- \xrightarrow[]{\mathcal{D}} -->
-<!-- \mathcal{N}\big(0,\operatorname{Var}(\ln f(Z))\big), -->
-<!-- \end{equation*} -->
-<!-- where $o(\cdot)$ represents the little-o. -->
-<!-- \end{lemma}  -->
+## Coefficient of variation and a robust alternative
+
+The population CV is defined as a ratio of the population standard deviation $(\sigma)$ to the population mean $(\mu)$:
+
+\begin{align}
+	\text{CV}=\frac{\sigma}{\mu}, \quad \mu \neq 0.
+\end{align}
+
+<!-- In practice, the population CV is unknown and needs to be estimated.  -->
+<!-- The typical sample estimate of the population CV is given as: -->
+<!-- \begin{align} -->
+<!-- 	\text{CV}=\frac{S}{\bar{X}},  -->
+<!-- \end{align} -->
+<!-- where $S$ and $\bar{X}$ are the sample standard deviation and the sample mean, respectively. -->
+
+We explore a robust alternative to the CV as discussed in \cite{Ospina2019}, involving the ratio of the mean absolute deviation from the median (MnAD) to the median, two well-known robust measures of scale and location, respectively.
+The MnAD is defined as $n^{-1}\sum_{i=1}^n|x_i-\widehat{Q}_2|$, where $\widehat{Q}_2$ represents an estimate of the population median, which can be approximated by the sample median.
+
+# Hypothesis Testing  {#sec:test}
 
@@
 $$
- \begin{cases}\mathcal{H}_0: \widetilde{H}= H_{\Gamma_{\text{SAR}}}\\ 
-  \mathcal{H}_1:\widetilde{H}\neq H_{\Gamma_{\text{SAR}}}.\end{cases}
+ \begin{cases}\mathcal{H}_0: \text{ The data comes from the } \Gamma_{\text{SAR}}\\ 
+  \mathcal{H}_1:\text{ The data comes from the } G_I^0.\end{cases}
 $$
-In other words, we verify the hypothesis that the data are fully-developed speckle with the following test statistic:
+In other words, we verify the hypothesis that the data are fully-developed speckle.
+The proposed tests are described below.
+
+## The Proposed Test Based on Non-parametric Entropy
+
+The first test statistic assess the behavior of the data under the null hypothesis, through the empirical distribution.
 \begin{equation}
 \label{Eq:test_e}
-S(\bm{Z};L)= \widetilde{H}-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{\bm{Z}}\right].
+S_H= \widetilde{H}-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{Z}\right].
 \end{equation}
-<!-- This test statistic assess the behavior of the data under the null hypothesis, through the empirical distribution.  -->
 The values should be around zero under the null hypothesis and far otherwise. 
@@
 
-# Results {#sec:results}
-
-## The Proposed Test
-Fig.&nbsp;\ref{fig:Plot_density} depicts empirical test statistic densities for various sample sizes, and Table&nbsp;\ref{tab:table_stat_combined} summarizes key statistics, including mean, SD, variance (Var), skewness (SK), excess kurtosis (EK), and Anderson–Darling $p$-values for normality.
+Figure&nbsp;\ref{fig:Plot_density} depicts empirical test statistic densities for various sample sizes, and Table&nbsp;\ref{tab:table_stat_combined} summarizes key statistics, including mean, SD, variance (Var), skewness (SK), excess kurtosis (EK), and Anderson–Darling $p$-values for normality.
 <!-- ACF Only show L=2 and L=8 -->
@@
 
-```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.pos="hbt",  fig.cap="Empirical density  under null hypothesis.", fig.width=6, fig.height=5.0}
+```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.pos="hbt",  fig.cap="Empirical density  under the null hypothesis.", fig.width=6, fig.height=5.0}
 
@@
 
+load("./Data/results1_11.Rdata")
+summary_stats_11 <- all_summary_stats[["11"]]
+
 combined_summary_stats <- rbind(
@@
   transform(summary_stats_5),
-  transform(summary_stats_8)
+  transform(summary_stats_8),
+  transform(summary_stats_11)
 
@@
   combined_summary_stats,
-  caption = "Descriptive analysis of $S(\\bm Z; L)$ with $L\\in\\left\\{3,5, 8\\right\\}$ and $\\mu=1$.",
+  caption = "Descriptive analysis of $S_H$ with $L\\in\\left\\{3,5, 8,11\\right\\}$ and $\\mu=1$.",
   format = "latex",
@@
 
-```{r Table_size_and_power, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-#cat("\\setlength{\\tabcolsep}{4pt}\n")
-
-load("./Data/type_I_results1.Rdata")
-
-type_I_error_rates <- tapply(results$P_Value, INDEX = list(results$L, results$Sample_Size, results$Alpha_Nominal), FUN = function(p_values) {
-  sum(p_values) / length(p_values)  
-})
-
-type_I_error_results <- as.data.frame(as.table(type_I_error_rates))
-
-colnames(type_I_error_results) <- c("L", "Sample_Size", "Alpha_Nominal", "Type_I_Error_Rate")
-
-spread_results <- spread(type_I_error_results, key = Alpha_Nominal, value = Type_I_Error_Rate)
-
-spread_results <- spread_results %>% 
-  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)
-
-load("./Data/results_power1.Rdata")
-
-summary_stats <- results_power %>%
-  spread(key = alpha_nominal, value = power) %>%
-  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)
-
-combined_results <- merge(spread_results, summary_stats, by = c("L", "Sample_Size"))
-combined_results <- combined_results %>% 
-  arrange(L, Sample_Size)
-
-combined_results <- combined_results %>% 
-  select(L, Sample_Size, `0.01.x`, `0.05.x`, `0.1.x`, `0.01.y`, `0.05.y`, `0.1.y`)
-
-colnames(combined_results) <- c("$L$", "$n$", "$1\\%$", "$5\\%$", "$10\\%$", "$1\\%$", "$5\\%$", "$10\\%$")
+## The Proposed Test Based on Coefficient of Variation and a Robust Alternative
+
+In addition to the entropy-based test, we also propose a test statistic based on the classical CV. This test statistic is defined as follows:
+\begin{align}
+	T_{\text{CV}}=\frac{S}{\widebar{Z}},
+\end{align}
+where $S$ and $\widebar{Z}$ are the sample standard deviation and the sample mean, respectively.
+
+Similarly, we use another test statistic based on the ratio of the MnAD to the median. This statistic is given by:
+\begin{align}
+	T_{\text{CV}_{\text{MnAD}}}=\frac{\text{MnAD}}{\text{Median}}.
+\end{align}
+These test statistics allow assessing the variability of the data.
+
+The situations where the use of CV and $\text{CV}_{\text{MnAD}}$ may be appropriate, i.e.
+where the observations are positive, the log-normal (LN) and inverse Gaussian (IG) distribution are often more justified compared to Gamma and Weibull distributions \cite{Chaubey2017,takagi1997application}.
+
+The inverse Gaussian distribution is shown to be well approximated by the log-normal distribution \cite{whitmore1978} which implies that the IG distribution also does not share the problem of non-existence of fixed width confidence interval with the Gaussian case.
+
+The LN distribution in two parameters has the following density function.
+\begin{align}
+	f_Z(z;\mu, \sigma )=\frac{1}{\sigma z\sqrt{2\pi}}\exp\left\{-\frac{(\ln z- \mu)^2}{2\sigma^2}\right\}, \quad z>0, \sigma>0, -\infty < \mu < \infty,
+\end{align}
+here, $\mu$ is the log-scale parameter and $\sigma$ is the shape parameter.
+
+## Model Selection Criterion
+
+Akaike information criterion (AIC) and Bayesian information criterion (BIC) are used to select the best fitting distribution.
+
+The AIC is a fine technique that deals with the trade-off between the goodness-of-fit of the model and the simplicity of the model in terms of the number of model parameters&nbsp;\cite{Burnham2004}. 
+The model or distribution with the lowest value of AIC is chosen to be the best.
+The BIC assesses goodness-of-fit of a distribution or model, but avoids overfitting by penalising an additional degree of freedom&nbsp;\cite{Dziak2019}. 
+The model with the lowest BIC value is chosen as the best.
+
+The AIC and BIC results in Tables&nbsp;\ref{tab:table_aic_gamma}-\ref{tab:table_aic_gio_MnADmedian} indicate that the CV and $\text{CV}_{\text{MnAD}}$ data from different synthetic sample sizes, extracted from the Gamma SAR and $G_I^0$ distributions, respectively, adhere to the characteristics of an LN distribution.
+The AIC and BIC values of the IG distribution and the LN distribution are not significantly different because both distributions are based on the right-skewed characteristic.
+In this situation, the model for the LN distribution was considered to be the best due to it providing the lowest AIC and BIC values.
+
+Figures&nbsp;\ref{fig:Plot_cv}-\ref{fig:Plot_madmed_gi0_MnADmedian} present density plots, Q-Q plots, P-P plots, and Cumulative Distribution Function plots, which offer an additional measure of goodness-of-fit and confirm that the most suitable distribution to be considered is the LN distribution.
+
+```{r Simulated_AIC_BIC_gamma, echo=FALSE, message=FALSE, warning=FALSE}
+set.seed(1234567890, kind = "Mersenne-Twister")
+R <- 15000
+mu <- 1
+L <- 5
+#B <- 5
+#alpha1 <- -3
+sample.sizes <- c(25, 49, 81, 121)
+
+results_AIC <- data.frame(Test = character(),
+                          SampleSize = integer(),
+                          Normal = numeric(),
+                          Lognormal = numeric(),
+                          Gamma = numeric(),
+                          Weibull = numeric(),
+                          InverseGaussian = numeric())
+
+results_BIC <- data.frame(Test = character(),
+                          SampleSize = integer(),
+                          Normal = numeric(),
+                          Lognormal = numeric(),
+                          Gamma = numeric(),
+                          Weibull = numeric(),
+                          InverseGaussian = numeric())
+
+for (s in sample.sizes) {
+  TestStatistics <- numeric(0)
+
+  for (r in 1:R) {
+    z <- gamma_sar_sample(L, mu, s)
+    #z <- gi0_sample(mu, alpha1, L, s)
+    TestStat <- sd(z) / mean(z)
+    TestStatistics <- c(TestStatistics, TestStat)
+  }
+
+  fit_weibull <- fitdistr(TestStatistics, "weibull")
+  fit_lognormal <- fitdistr(TestStatistics, "lognormal")
+  fit_gamma <- fitdistr(TestStatistics, "gamma")
+  fit_normal <- fitdistr(TestStatistics, "normal")
+
+  AIC_values <- c(AIC(fit_weibull), AIC(fit_lognormal), AIC(fit_gamma), AIC(fit_normal))
+  BIC_values <- c(BIC(fit_weibull), BIC(fit_lognormal), BIC(fit_gamma), BIC(fit_normal))
+
+  dinvgauss <- function(x, mu, lambda) {
+    sqrt(lambda / (2 * pi * x^3)) * exp(-lambda * (x - mu)^2 / (2 * mu^2 * x))
+  }
+
+  negLL_invgauss <- function(params, data) {
+    mu <- params[1]
+    lambda <- params[2]
+    CV <- data
+
+    -sum(log(dinvgauss(CV, mu, lambda)))
+  }
+
+  fit_invGauss <- fitdist(data = TestStatistics, distr = "invgauss", method = "mle",
+                          start = list(mu = mean(TestStatistics), lambda = var(TestStatistics)))
+
+  log_likelihood <- logLik(fit_invGauss)
+  num_params <- length(coef(fit_invGauss))
+  n <- length(TestStatistics)
+  AIC_manual <- -2 * log_likelihood + 2 * num_params
+  BIC_manual <- -2 * log_likelihood + num_params * log(n)
+
+  results_AIC <- rbind(results_AIC, data.frame(Test = "AIC",
+                                               SampleSize = s,
+                                               Normal = AIC_values[4],
+                                               Lognormal = AIC_values[2],
+                                               Gamma = AIC_values[3],
+                                               Weibull = AIC_values[1],
+                                               InverseGaussian = AIC_manual))
+
+  results_BIC <- rbind(results_BIC, data.frame(Test = "BIC",
+                                               SampleSize = s,
+                                               Normal = BIC_values[4],
+                                               Lognormal = BIC_values[2],
+                                               Gamma = BIC_values[3],
+                                               Weibull = BIC_values[1],
+                                               InverseGaussian = BIC_manual))
+}
+
+save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC_gamma.Rdata")
+
+```
+
+```{r Table_AIC_BIC_gamma, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+load("./Data/results_AIC_BIC_gamma.Rdata")
+
+combined <- rbind(results_AIC, results_BIC)
+rownames(combined) <- NULL
+
+colnames(combined) <- c("\\textbf{Criterion}", "$\\bm{n}$", "\\textbf{Normal}", "\\textbf{Lognormal}", "\\textbf{Gamma}", "\\textbf{Weibull}", "\\textbf{Inverse Gaussian}")
+
+#combined$`Inverse Gaussian` <- c("\\multirow{2}{*}{Inverse}", "Gaussian")
 
 # LaTeX notation 
-combined_results[] <- lapply(combined_results, function(x) {
+combined[] <- lapply(combined, function(x) {
   if (is.numeric(x)) {
@@
     } else {
-      formatted_numbers <- ifelse(x < 0, sprintf("$%.3f$", x), sprintf("$\\phantom{-}%.3f$", x))
+      formatted_numbers <- ifelse(x < 0, sprintf("$%.2f$", x), sprintf("$\\phantom{-}%.2f$", x))
     }
@@
 
-table_combined_result <- knitr::kable(
-  combined_results,
-  caption = "Size and Power of the proposed test.",
+table_result_combined <- knitr::kable(
+  combined,
+  caption = "AIC and BIC values for evaluating the best distribution with CV data from Gamma SAR.",
   format = "latex",
   booktabs = TRUE,
-  align = "lcccccccc",
+  align = "lccccccc",
   escape = FALSE,
-  digits = 3,
-  label = "table_size_power",
+  digits = 2,
+  label = "table_aic_gamma",
   centering = FALSE,
-  linesep = "",
-  table.envir = "table", position = "H")%>%
-  add_header_above(c(" ", " ", "Size" = 3,  "Power" = 3)) %>%
-  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
+  table.envir = "table", position = "H") %>%
+  collapse_rows(latex_hline = "major", valign = "middle") %>%
   row_spec(0,  align = "c")
 
-print(table_combined_result)
+print(table_result_combined)
+```
+
+```{r Simulated_AIC_BIC_GI0, echo=FALSE, message=FALSE, warning=FALSE}
+set.seed(1234567890, kind = "Mersenne-Twister")
+R <- 15000
+mu <- 1
+L <- 5
+B <- 5
+alpha1 <- -3
+sample.sizes <- c(25, 49, 81, 121)
+
+# Simulación y cálculo de resultados
+results_AIC <- data.frame(Test = character(),
+                          SampleSize = integer(),
+                          Normal = numeric(),
+                          Lognormal = numeric(),
+                          Gamma = numeric(),
+                          Weibull = numeric(),
+                          InverseGaussian = numeric())
+
+results_BIC <- data.frame(Test = character(),
+                          SampleSize = integer(),
+                          Normal = numeric(),
+                          Lognormal = numeric(),
+                          Gamma = numeric(),
+                          Weibull = numeric(),
+                          InverseGaussian = numeric())
+
+for (s in sample.sizes) {
+  TestStatistics <- numeric(0)
+
+  for (r in 1:R) {
+    z <- gi0_sample(mu, alpha1, L, s)
+    TestStat <- sd(z) / mean(z)
+    TestStatistics <- c(TestStatistics, TestStat)
+  }
+
+  fit_weibull <- fitdistr(TestStatistics, "weibull")
+  fit_lognormal <- fitdistr(TestStatistics, "lognormal")
+  fit_gamma <- fitdistr(TestStatistics, "gamma")
+  fit_normal <- fitdistr(TestStatistics, "normal")
+
+  AIC_values <- c(AIC(fit_weibull), AIC(fit_lognormal), AIC(fit_gamma), AIC(fit_normal))
+  BIC_values <- c(BIC(fit_weibull), BIC(fit_lognormal), BIC(fit_gamma), BIC(fit_normal))
+
+  dinvgauss <- function(x, mu, lambda) {
+    sqrt(lambda / (2 * pi * x^3)) * exp(-lambda * (x - mu)^2 / (2 * mu^2 * x))
+  }
+
+  negLL_invgauss <- function(params, data) {
+    mu <- params[1]
+    lambda <- params[2]
+    CV <- data
+
+    -sum(log(dinvgauss(CV, mu, lambda)))
+  }
+
+  fit_invGauss <- fitdist(data = TestStatistics, distr = "invgauss", method = "mle",
+                          start = list(mu = mean(TestStatistics), lambda = var(TestStatistics)))
+
+  log_likelihood <- logLik(fit_invGauss)
+  num_params <- length(coef(fit_invGauss))
+  n <- length(TestStatistics)
+  AIC_manual <- -2 * log_likelihood + 2 * num_params
+  BIC_manual <- -2 * log_likelihood + num_params * log(n)
+
+  results_AIC <- rbind(results_AIC, data.frame(Test = "AIC",
+                                               SampleSize = s,
+                                               Normal = AIC_values[4],
+                                               Lognormal = AIC_values[2],
+                                               Gamma = AIC_values[3],
+                                               Weibull = AIC_values[1],
+                                               InverseGaussian = AIC_manual))
+
+  results_BIC <- rbind(results_BIC, data.frame(Test = "BIC",
+                                               SampleSize = s,
+                                               Normal = BIC_values[4],
+                                               Lognormal = BIC_values[2],
+                                               Gamma = BIC_values[3],
+                                               Weibull = BIC_values[1],
+                                               InverseGaussian = BIC_manual))
+}
+
+# Guardar los resultados en un archivo .Rdata
+save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC.Rdata")
+
+```
+
+```{r Table_AIC_BIC, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+load("./Data/results_AIC_BIC.Rdata")
+
+combined <- rbind(results_AIC, results_BIC)
+rownames(combined) <- NULL
+
+colnames(combined) <- c("\\textbf{Criterion}", "$\\bm{n}$", "\\textbf{Normal}", "\\textbf{Lognormal}", "\\textbf{Gamma}", "\\textbf{Weibull}", "\\textbf{Inverse Gaussian}")
+
+# Modificar el nombre de la última columna para que esté en dos líneas
+#combined$`Inverse Gaussian` <- c("\\multirow{2}{*}{Inverse}", "Gaussian")
+
+# LaTeX notation 
+combined[] <- lapply(combined, function(x) {
+  if (is.numeric(x)) {
+    if (all(x %% 1 == 0)) {
+      formatted_numbers <- sprintf("$%d$", x)
+    } else {
+      formatted_numbers <- ifelse(x < 0, sprintf("$%.2f$", x), sprintf("$\\phantom{-}%.2f$", x))
+    }
+    return(formatted_numbers)
+  } else {
+    return(x)
+  }
+})
+
+table_result_combined <- knitr::kable(
+  combined,
+  caption = "AIC and BIC values for evaluating the best distribution with CV data from $G_I^0$.",
+  format = "latex",
+  booktabs = TRUE,
+  align = "lccccccc",
+  escape = FALSE,
+  digits = 2,
+  label = "table_aic",
+  centering = FALSE,
+  table.envir = "table", position = "H") %>%
+  collapse_rows(latex_hline = "major", valign = "middle") %>%
+  row_spec(0,  align = "c")
+
+print(table_result_combined)
+```
+
+```{r Simulated_AIC_BIC_gamma_MnADmedian, echo=FALSE, message=FALSE, warning=FALSE}
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+R <- 15000
+mu <- 1
+L <- 5
+sample.sizes <- c(25, 49, 81, 121)
+
+# madmedian <- function(x){
+#   mdn <- median(x)
+#   MAD <- 1.4826 * median(abs(x - mdn))
+#   MAD/mdn
+# }
+
+MnADmedian <- function(x){
+  mdn <- median(x)
+  MnAD <- mean(abs(x - mdn))
+  MnAD/mdn
+}
+
+results_AIC <- data.frame(Test = character(),
+                          SampleSize = integer(),
+                          Normal = numeric(),
+                          Lognormal = numeric(),
+                          Gamma = numeric(),
+                          Weibull = numeric(),
+                          InverseGaussian = numeric())
+
+results_BIC <- data.frame(Test = character(),
+                          SampleSize = integer(),
+                          Normal = numeric(),
+                          Lognormal = numeric(),
+                          Gamma = numeric(),
+                          Weibull = numeric(),
+                          InverseGaussian = numeric())
+
+for (s in sample.sizes) {
+  TestStatistics <- numeric(0)
+
+  for (r in 1:R) {
+    z <- gamma_sar_sample(L, mu, s)
+    # z <- gi0_sample(mu, alpha1, L, s)
+    madmed <- MnADmedian(z)  
+    TestStatistics <- c(TestStatistics, madmed)
+  }
+
+  fit_weibull <- fitdistr(TestStatistics, "weibull")
+  fit_lognormal <- fitdistr(TestStatistics, "lognormal")
+  fit_gamma <- fitdistr(TestStatistics, "gamma")
+  fit_normal <- fitdistr(TestStatistics, "normal")
+
+  AIC_values <- c(AIC(fit_weibull), AIC(fit_lognormal), AIC(fit_gamma), AIC(fit_normal))
+  BIC_values <- c(BIC(fit_weibull), BIC(fit_lognormal), BIC(fit_gamma), BIC(fit_normal))
+
+  dinvgauss <- function(x, mu, lambda) {
+    sqrt(lambda / (2 * pi * x^3)) * exp(-lambda * (x - mu)^2 / (2 * mu^2 * x))
+  }
+
+  negLL_invgauss <- function(params, data) {
+    mu <- params[1]
+    lambda <- params[2]
+    CV <- data
+
+    -sum(log(dinvgauss(CV, mu, lambda)))
+  }
+
+  fit_invGauss <- fitdist(data = TestStatistics, distr = "invgauss", method = "mle",
+                          start = list(mu = mean(TestStatistics), lambda = var(TestStatistics)))
+
+  log_likelihood <- logLik(fit_invGauss)
+  num_params <- length(coef(fit_invGauss))
+  n <- length(TestStatistics)
+  AIC_manual <- -2 * log_likelihood + 2 * num_params
+  BIC_manual <- -2 * log_likelihood + num_params * log(n)
+
+  results_AIC <- rbind(results_AIC, data.frame(Test = "AIC",
+                                               SampleSize = s,
+                                               Normal = AIC_values[4],
+                                               Lognormal = AIC_values[2],
+                                               Gamma = AIC_values[3],
+                                               Weibull = AIC_values[1],
+                                               InverseGaussian = AIC_manual))
+
+  results_BIC <- rbind(results_BIC, data.frame(Test = "BIC",
+                                               SampleSize = s,
+                                               Normal = BIC_values[4],
+                                               Lognormal = BIC_values[2],
+                                               Gamma = BIC_values[3],
+                                               Weibull = BIC_values[1],
+                                               InverseGaussian = BIC_manual))
+}
+
+save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC_gamma_MnADmedian.Rdata")
+
+```
+
+```{r Table_AIC_BIC_gamma_MnADmedian, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+load("./Data/results_AIC_BIC_gamma_MnADmedian.Rdata")
+
+combined <- rbind(results_AIC, results_BIC)
+rownames(combined) <- NULL
+
+colnames(combined) <- c("\\textbf{Criterion}", "$\\bm{n}$", "\\textbf{Normal}", "\\textbf{Lognormal}", "\\textbf{Gamma}", "\\textbf{Weibull}", "\\textbf{Inverse Gaussian}")
+
+#combined$`Inverse Gaussian` <- c("\\multirow{2}{*}{Inverse}", "Gaussian")
+
+# LaTeX notation 
+combined[] <- lapply(combined, function(x) {
+  if (is.numeric(x)) {
+    if (all(x %% 1 == 0)) {
+      formatted_numbers <- sprintf("$%d$", x)
+    } else {
+      formatted_numbers <- ifelse(x < 0, sprintf("$%.2f$", x), sprintf("$\\phantom{-}%.2f$", x))
+    }
+    return(formatted_numbers)
+  } else {
+    return(x)
+  }
+})
+
+table_result_combined <- knitr::kable(
+  combined,
+  caption = "AIC and BIC values for evaluating the best distribution with $\\text{CV}_{\\text{MnAD}}$ data from Gamma SAR.",
+  format = "latex",
+  booktabs = TRUE,
+  align = "lccccccc",
+  escape = FALSE,
+  digits = 2,
+  label = "table_aic_gamma_madmed",
+  centering = FALSE,
+  table.envir = "table", position = "H") %>%
+  collapse_rows(latex_hline = "major", valign = "middle") %>%
+  row_spec(0,  align = "c")
+
+print(table_result_combined)
+```
+
+```{r Simulated_AIC_BIC_GI0_MnADmedian, echo=FALSE, message=FALSE, warning=FALSE}
+set.seed(1234567890, kind = "Mersenne-Twister")
+R <- 15000
+mu <- 1
+L <- 5
+B <- 5
+alpha1 <- -5
+sample.sizes <- c(25, 49, 81, 121)
+
+# madmedian <- function(x){
+#   mdn <- median(x)
+#   MAD <- 1.4826 * median(abs(x - mdn))
+#   return(MAD/mdn)
+# }
+
+MnADmedian <- function(x){
+  mdn <- median(x)
+  MnAD <- mean(abs(x - mdn))
+  MnAD/mdn
+}
+results_AIC <- data.frame(Test = character(),
+                          SampleSize = integer(),
+                          Normal = numeric(),
+                          Lognormal = numeric(),
+                          Gamma = numeric(),
+                          Weibull = numeric(),
+                          InverseGaussian = numeric())
+
+results_BIC <- data.frame(Test = character(),
+                          SampleSize = integer(),
+                          Normal = numeric(),
+                          Lognormal = numeric(),
+                          Gamma = numeric(),
+                          Weibull = numeric(),
+                          InverseGaussian = numeric())
+
+for (s in sample.sizes) {
+  TestStatistics <- numeric(0)
+
+  for (r in 1:R) {
+    z <- gi0_sample(mu, alpha1, L, s)
+    madmed <- MnADmedian(z) 
+    TestStatistics <- c(TestStatistics, madmed)
+  }
+
+  fit_weibull <- fitdistr(TestStatistics, "weibull")
+  fit_lognormal <- fitdistr(TestStatistics, "lognormal")
+  fit_gamma <- fitdistr(TestStatistics, "gamma")
+  fit_normal <- fitdistr(TestStatistics, "normal")
+
+  AIC_values <- c(AIC(fit_weibull), AIC(fit_lognormal), AIC(fit_gamma), AIC(fit_normal))
+  BIC_values <- c(BIC(fit_weibull), BIC(fit_lognormal), BIC(fit_gamma), BIC(fit_normal))
+
+  dinvgauss <- function(x, mu, lambda) {
+    sqrt(lambda / (2 * pi * x^3)) * exp(-lambda * (x - mu)^2 / (2 * mu^2 * x))
+  }
+
+  negLL_invgauss <- function(params, data) {
+    mu <- params[1]
+    lambda <- params[2]
+    CV <- data
+
+    -sum(log(dinvgauss(CV, mu, lambda)))
+  }
+
+  fit_invGauss <- fitdist(data = TestStatistics, distr = "invgauss", method = "mle",
+                          start = list(mu = mean(TestStatistics), lambda = var(TestStatistics)))
+
+  log_likelihood <- logLik(fit_invGauss)
+  num_params <- length(coef(fit_invGauss))
+  n <- length(TestStatistics)
+  AIC_manual <- -2 * log_likelihood + 2 * num_params
+  BIC_manual <- -2 * log_likelihood + num_params * log(n)
+
+  results_AIC <- rbind(results_AIC, data.frame(Test = "AIC",
+                                               SampleSize = s,
+                                               Normal = AIC_values[4],
+                                               Lognormal = AIC_values[2],
+                                               Gamma = AIC_values[3],
+                                               Weibull = AIC_values[1],
+                                               InverseGaussian = AIC_manual))
+
+  results_BIC <- rbind(results_BIC, data.frame(Test = "BIC",
+                                               SampleSize = s,
+                                               Normal = BIC_values[4],
+                                               Lognormal = BIC_values[2],
+                                               Gamma = BIC_values[3],
+                                               Weibull = BIC_values[1],
+                                               InverseGaussian = BIC_manual))
+}
+
+save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC_GI0_MnADmedian.Rdata")
+
+```
+
+```{r Table_AIC_BIC_GI0_MnADmedian, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+load("./Data/results_AIC_BIC_GI0_MnADmedian.Rdata")
+
+combined <- rbind(results_AIC, results_BIC)
+rownames(combined) <- NULL
+
+colnames(combined) <- c("\\textbf{Criterion}", "$\\bm{n}$", "\\textbf{Normal}", "\\textbf{Lognormal}", "\\textbf{Gamma}", "\\textbf{Weibull}", "\\textbf{Inverse Gaussian}")
+
+#combined$`Inverse Gaussian` <- c("\\multirow{2}{*}{Inverse}", "Gaussian")
+
+# LaTeX notation 
+combined[] <- lapply(combined, function(x) {
+  if (is.numeric(x)) {
+    if (all(x %% 1 == 0)) {
+      formatted_numbers <- sprintf("$%d$", x)
+    } else {
+      formatted_numbers <- ifelse(x < 0, sprintf("$%.2f$", x), sprintf("$\\phantom{-}%.2f$", x))
+    }
+    return(formatted_numbers)
+  } else {
+    return(x)
+  }
+})
+
+table_result_combined <- knitr::kable(
+  combined,
+  caption = "AIC and BIC values for evaluating the best distribution with $\\text{CV}_{\\text{MnAD}}$ data from $G_I^0$.",
+  format = "latex",
+  booktabs = TRUE,
+  align = "lccccccc",
+  escape = FALSE,
+  digits = 2,
+  label = "table_aic_gio_MnADmedian",
+  centering = FALSE,
+  table.envir = "table", position = "H") %>%
+  collapse_rows(latex_hline = "major", valign = "middle") %>%
+  row_spec(0,  align = "c")
+
+print(table_result_combined)
+```
+
+```{r Simulated_cv_gamma, echo=FALSE, message=FALSE, warning=FALSE}
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+sample.size <- c(49)
+R <- 15000
+mu <- 1
+L <- 5
+B <- 5
+alpha1 <- -2
+
+TestStatistics <- numeric(0)
+
+for (s in sample.size) {
+  for (r in 1:R) {
+    z <- gamma_sar_sample(L, mu, s)
+    #z <- gi0_sample(mu, alpha1, L, s)
+    TestStat <- sd(z) / mean(z)
+    TestStatistics <- c(TestStatistics, TestStat)  
+  }
+}
+
+save(TestStatistics, file = "./Data/rTestStatistics_gamma_49.Rdata")
+```
+
+```{r Plot_cv_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with CV data from Gamma SAR, with  $n=49$, $L=5$ and $\\mu=1$.", fig.width=8, fig.height=6}
+
+load("./Data/rTestStatistics_gamma_49.Rdata")
+
+# Ajustar las distribuciones a los datos
+fln <- fitdist(TestStatistics, "lnorm")
+fg <- fitdist(TestStatistics, "gamma")
+fn <- fitdist(TestStatistics, "norm")  # Ajuste para la distribución normal
+fw <- fitdist(TestStatistics, "weibull")
+
+# Graficar las comparaciones
+par(mfrow = c(2, 2), mar = c(4, 4, 2, 1))
+plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
+denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlab = "CV")
+qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
+cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlab = "CV")
+ppcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
+
+```
+
+```{r Simulated_cv_gi0, echo=FALSE, message=FALSE, warning=FALSE}
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+sample.size <- c(49)
+R <- 15000
+mu <- 1
+L <- 5
+B <- 5
+alpha1 <- -2
+
+TestStatistics <- numeric(0)
+
+for (s in sample.size) {
+  for (r in 1:R) {
+    z <- gi0_sample(mu, alpha1, L, s)
+    TestStat <- sd(z) / mean(z)
+    TestStatistics <- c(TestStatistics, TestStat)  
+  }
+}
+
+save(TestStatistics, file = "./Data/rTestStatistics_gi0_49.Rdata")
+```
+
+```{r Plot_cv, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with $\\text{CV}_{\\text{MnAD}}$ data from $G_I^0$, with  $n=49$, $L=5$, $\\mu=1$ and $\\alpha=-2$.", fig.width=8, fig.height=6}
+
+load("./Data/rTestStatistics_gi0_49.Rdata")
+
+#
+fln <- fitdist(TestStatistics, "lnorm")
+fg <- fitdist(TestStatistics, "gamma")
+fn <- fitdist(TestStatistics, "norm")  
+fw <- fitdist(TestStatistics, "weibull")
+
+# 
+par(mfrow = c(2, 2), mar = c(4, 4, 2, 1))
+plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
+denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlab = "CV")
+qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
+cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlab = "CV")
+ppcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
+
+```
+
+```{r Simulated_MnADmedian_gamma, echo=FALSE, message=FALSE, warning=FALSE}
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+sample.size <- c(49)
+R <- 15000
+mu <- 1
+L <- 5
+B <- 5
+alpha1 <- -2
+
+MnADmedian <- function(x){
+  mdn <- median(x)
+  MnAD <- mean(abs(x - mdn))
+  MnAD/mdn
+}
+
+TestStatistics <- numeric(0)
+
+for (s in sample.size) {
+  for (r in 1:R) {
+    z <- gamma_sar_sample(L, mu, s)
+    #z <- gi0_sample(mu, alpha1, L, s)
+    TestStat <- MnADmedian(z)
+    TestStatistics <- c(TestStatistics, TestStat)  
+  }
+}
+
+save(TestStatistics, file = "./Data/rTestStatistics_gamma_49_MnADmedian.Rdata")
+```
+
+```{r Plot_MnADmedian_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with $\\text{CV}_{\\text{MnAD}}$ data from Gamma SAR, with  $n=49$, $L=5$ and $\\mu=1$.", fig.width=8, fig.height=6}
+
+load("./Data/rTestStatistics_gamma_49_MnADmedian.Rdata")
+
+# Ajustar las distribuciones a los datos
+fln <- fitdist(TestStatistics, "lnorm")
+fg <- fitdist(TestStatistics, "gamma")
+fn <- fitdist(TestStatistics, "norm")  # Ajuste para la distribución normal
+fw <- fitdist(TestStatistics, "weibull")
+
+# Graficar las comparaciones
+par(mfrow = c(2, 2), mar = c(4, 4, 2, 1))
+plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
+denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlab = "CV")
+qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
+cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlab = "CV")
+ppcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
+
+```
+
+```{r Simulated_MnADmedian_gi0, echo=FALSE, message=FALSE, warning=FALSE}
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+sample.size <- c(49)
+R <- 12000
+mu <- 1
+L <- 5
+#B <- 5
+alpha1 <- -5
+
+MnADmedian <- function(x){
+  mdn <- median(x)
+  MnAD <- mean(abs(x - mdn))
+  MnAD/mdn
+}
+
+TestStatistics_mad <- numeric(0)
+
+for (s in sample.size) {
+  for (r in 1:R) {
+    z <- gi0_sample(mu, alpha1, L, s)
+    madmed <- MnADmedian(z)
+    TestStatistics_mad <- c(TestStatistics_mad, madmed)  
+  }
+}
+
+save(TestStatistics_mad, file = "./Data/rTestStatistics_MnADmedian_gi0_49.Rdata")
+```
+
+```{r Plot_madmed_gi0_MnADmedian, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.pos="hbt",  fig.cap="Goodness of fit plots for evaluating the best distribution with $CV_{\\text{MnAD}}$ data from $G_I^0$, with  $n=49$, $L=5$, $\\mu=1$ and $\\alpha=-5$.", fig.width=8, fig.height=6}
+
+load("./Data/rTestStatistics_MnADmedian_gi0_49.Rdata")
+
+#
+fln <- fitdist(TestStatistics_mad, "lnorm")
+fg <- fitdist(TestStatistics_mad, "gamma")
+fn <- fitdist(TestStatistics_mad, "norm")  
+fw <- fitdist(TestStatistics_mad, "weibull")
+
+# 
+par(mfrow = c(2, 2), mar = c(4, 4, 2, 1))
+plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
+denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlab = "CV")
+qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
+cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlab = "CV")
+ppcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
+
+```
+
+# Simulation Results {#sec:Results}
+
+This section presents simulations performed to obtain an assessment of the performances of the proposed test statistics.
+
+## Simulated Data
+
+Figure 1a shows the phantom used for a simulated image with dimensions of $250\times 250$ pixels to illustrate the differences between heterogeneous (dark, $\alpha=-2$) and homogeneous (light, $\alpha=-10$) regions, with $L = 5$.
+The areas are formed by independent draws from the $G^0_I$ distribution.
+
+The three test statistics are applied to the simulated image using local sliding windows of size $7\times 7$.
+
+The resulting $p$-values for the tests $S_H$, $T_{\text{CV}}$, and $T_{\text{CV}_{\text{MnAD}}}$ are shown in Figures&nbsp;\ref{fig:sim_SAR_Images}(b)-(d) and Figures&nbsp;\ref{fig:sim_SAR_Images_p05}(a)-(c), respectively.
+The new images reveal that a darker background indicates homogeneity, while lighter backgrounds represent heterogeneous areas.
+
+```{r sim_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics.
+(a) Simulated image; $P$-values from the entropy-based test; (c) $P$-values from the CV test; (d) $P$-values from the   $\\text{CV}_{\\text{MnAD}}$ test; ',  fig.subcap=c('', '', '', ''), out.width = c("40mm", "40mm","40mm", "40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/simulated7x7.png")
+knitr::include_graphics("../Figures/PNG/sim_pvalue7x7_total_H.png")
+knitr::include_graphics("../Figures/PNG/sim_pvalue7x7_total_cv.png")
+knitr::include_graphics("../Figures/PNG/sim_pvalue7x7_total_mnad.png")
+```
+```{r sim_SAR_Images_p05, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of tests on simulated data with a threshold of $0.1$ of the $p$-value.
+(a) Entropy-based test; (b) CV test; (c) $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/sim_pvalue7x7_H.png")
+knitr::include_graphics("../Figures/PNG/sim_pvalue7x7_cv.png")
+knitr::include_graphics("../Figures/PNG/sim_pvalue7x7_mnad.png")
+
+```
+
+## Real Data
+
+We applied the proposed test statistics in actual SAR images acquired over cities, including Flevoland, Netherlands and Ottawa, Canada.   
+These images were captured by the Sentinel-1A satellite operating in the C band,  with  VV polarization, intensity format, and $L=5$ nominal looks.
+Both images have dimensions of $512 \times 512$ pixels and contain urban areas, water forest regions, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)-(b).
+
+The $p$-values obtained for the $S_H$, $T_{\text{CV}}$, and $T_{\text{CV}_{\text{MnAD}}}$ tests are presented in Figures&nbsp;\ref{fig:sim_SAR_Images_Frankfurt}-\ref{fig:sim_SAR_Images_01_Ottawa}, respectively.
+
+```{r real_SAR_Images_coe, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='SAR images.
+(a) Frankfurt; (b) Ottawa.
+',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm"),  fig.ncol=2, fig.width = 20, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/Intensity_Frankfurt_512_n.png")
+knitr::include_graphics("../Figures/PNG/Intensity_Ottawa_512_n.png")
+#knitr::include_graphics("../Figures/PNG/sim_pvalue7x7_mnad.png")
+
+```
+```{r sim_SAR_Images_Frankfurt, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics, Frankfurt.
+(a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\\text{CV}_{\\text{MnAD}}$ test; ',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/Frankfurt_512_pvalue7x7_total_H.png")
+knitr::include_graphics("../Figures/PNG/Frankfurt_512_pvalue7x7_total_CV.png")
+knitr::include_graphics("../Figures/PNG/Frankfurt_512_mnad_7_total.png")
+
+```
+```{r sim_SAR_Images_01Frankfurt, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of tests on simulated data with a threshold of $0.1$ of the $p$-value, Frankfurt.
+(a) Entropy-based test; (b) CV test; (c) $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/Frankfurt_512_pvalue7x7_H_01.png")
+knitr::include_graphics("../Figures/PNG/Frankfurt_512_pvalue7x7_CV.png")
+knitr::include_graphics("../Figures/PNG/Frankfurt_512_mnad_7_0.1.png")
+
+```
+
+```{r sim_SAR_Images_Ottawa, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics, Ottawa.
+(a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\\text{CV}_{\\text{MnAD}}$ test; ',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/Ottawa_512_pvalue7x7_total_H.png")
+knitr::include_graphics("../Figures/PNG/Ottawa_512_CV_pvalue7x7_total_CV.png")
+knitr::include_graphics("../Figures/PNG/Ottawa_512_mnad_7_total.png")
+
+```
+```{r sim_SAR_Images_01_Ottawa, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of tests on simulated data with a threshold of $0.1$ of the $p$-value, Ottawa.
+(a) Entropy-based test; (b) CV test; (c) $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/Ottawa_512_pvalue7x7_H_01.png")
+knitr::include_graphics("../Figures/PNG/Ottawa_512_CV_pvalue7x7_CV.png")
+knitr::include_graphics("../Figures/PNG/Ottawa_512_mnad_7_0.1.png")
 
@@
 # Conclusion {#sec:conclusion}
+
+In this article,...

### 2024-04-04 Text/Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics.tex
updated paper version

%  LaTeX support: latex@mdpi.com
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
% pandoc conditionals added to preserve backwards compatibility with previous versions of rticles

\documentclass[remotesensing,article,submit,moreauthors,pdftex]{Definitions/mdpi}

%% Some pieces required from the pandoc template
\setlist[itemize]{leftmargin=*,labelsep=5.8mm}
\setlist[enumerate]{leftmargin=*,labelsep=4.9mm}

%--------------------
% Class Options:
%--------------------

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by:
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. Remove "pdftex" for (1) compiling with LaTeX & dvi2pdf (if eps figures are used) or for (2) compiling with XeLaTeX.

%=================================================================
% MDPI internal commands - do not modify
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2023}
\copyrightyear{2023}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{ }
\daterevised{ } % Comment out if no revised date
\dateaccepted{ }
\datepublished{ }
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
% cleveref: load \crefname definitions after \begin{document}

%=================================================================
% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Identifying Heterogeneity in SAR Data with New Test Statistics}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Identifying Heterogeneity in SAR Data with New Test
Statistics}

% Author Orchid ID: enter ID or remove command
%\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Alejandro C.
Frery$^{1,*}$\href{https://orcid.org/0000-0002-8002-5341}
{\orcidicon}, Janeth
Alpala$^{2}$\href{https://orcid.org/0000-0002-0265-6236}
{\orcidicon}, Abraão D. C.
Nascimento$^{2}$\href{https://orcid.org/0000-0003-2673-219X}
{\orcidicon}}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Alejandro C. Frery, Janeth Alpala, Abraão D. C. Nascimento}

% MDPI internal command: Authors, for citation in the left column
%\AuthorCitation{Lastname, F.; Lastname, F.; Lastname, F.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
\AuthorCitation{Frery, A.C.; Alpala, J.; Nascimento,A.D.C.}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad School of Mathematics and Statistics, Victoria University
of Wellington, Wellington 6140, New Zealand; \\
$^{2}$ \quad Departamento de Estatística, Universidade Federal de
Pernambuco, Recife 50670-901, PE, Brazil; \\
}

% Contact information of the corresponding author
\corres{Correspondence: \href{mailto:alejandro.frery@vuw.ac.nz}{\nolinkurl{alejandro.frery@vuw.ac.nz}}}

% Current address and/or shared authorship

% The commands \thirdnote{} till \eighthnote{} are available for further notes

% Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{This paper presents a statistical approach to identify the
underlying roughness characteristics in synthetic aperture radar (SAR)
intensity data. The physical modeling of this kind of data allows to use
the Gamma distribution in the presence of fully-developed speckle, i.e.,
when there are infinitely many independent backscatterers per resolution
cell. This situation is often called ``homogeneous'' or ``textureless''
areas. The \(\mathcal{G}_I^0\) distribution is also a widely accepted
law for heterogeneous and extremely heterogeneous areas. We propose
three test statistics for discriminating between homogeneous and
non-homogeneous areas, i.e., between Gamma and GI0 distributed data,
both with a known number of looks. The first test statistic utilizes a
bootstrapped non-parametric estimator of the Shannon entropy, offering a
robust evaluation in the face of uncertain distributional assumptions.
The second test uses the classic coefficient of variation. The third
test employs an alternative form of estimating the CV based on the ratio
of the mean absolute deviation from the median to the median. We apply
our test statistic to produce maps of \(p\)-values for the hypothesis of
homogeneity. These maps identify different types of targets. We show
that our proposal outperforms its competitors using simulated and SAR
data.}

% Keywords
\keyword{SAR; heterogeneity; entropy; coefficient of variation;
hypothesis tests}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Advances in Respiratory Medicine
%\addhighlights{yes}
%\renewcommand{\addhighlights}{%

%\noindent This is an obligatory section in “Advances in Respiratory Medicine”, whose goal is to increase the discoverability and readability of the article via search engines and other scholars. Highlights should not be a copy of the abstract, but a simple text allowing the reader to quickly and simplified find out what the article is about and what can be cited from it. Each of these parts should be devoted up to 2~bullet points.\vspace{3pt}\\
%\textbf{What are the main findings?}
% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
% \item First bullet.
% \item Second bullet.
% \end{itemize}\vspace{3pt}
%\textbf{What is the implication of the main finding?}
% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
% \item First bullet.
% \item Second bullet.
% \end{itemize}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage[english]{babel}
\usepackage{bm,bbm}
\usepackage{mathrsfs}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{url}
\usepackage[T1]{fontenc}
\usepackage{polski}
\usepackage{booktabs}
\usepackage{color}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{subcaption}
\captionsetup[sub]{labelfont=bf,textfont=bf}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\tabcolsep}{6pt} 
\newcommand{\bias}{\operatorname{Bias}}
\newcommand{\widebar}[1]{\overline{#1}}

\hypertarget{sec:Introduction}{%
\section{Introduction}\label{sec:Introduction}}

Synthetic Aperture Radar (SAR) technology has become an important tool
for environmental monitoring and disaster management, providing valuable
imagery in different conditions, including day or night and diverse
weather situations~\cite{Moreira2013,Mu2019}. However, the effective
utilization of SAR data depends on a thorough understanding of its
statistical properties, especially the impact of speckle effects, which
are inherent in SAR data due to the coherent nature of the imaging
process~\cite{Argenti2013}.

In the presence of non-Gaussian speckle interference, SAR data requires
a reliable statistical model for accurate processing. The
\(\mathcal{G}^0\) distribution, suitable for SAR data, includes the
Gamma law as a limit case for fully developed
speckle~\cite{Ferreira2020}, providing flexibility with fewer parameters
for analysis.

Our work is motivated to improve the identification of potential
roughness features in SAR intensity data. Physical modeling of SAR data
allows to take advantage of the gamma distribution in the presence of
fully developed speckle, creating a scenario with an infinite number of
independent backscatterers per unit of resolution, often referred to as
homogeneous areas.

In this context, we present a set of three novel test statistics
designed to discriminate between homogeneous and non-homogeneous areas,
specifically aimed at differentiating between Gamma and
\(\mathcal{G}^0\) distributed data, each with a known number of
appearances. Hence, to understand the core ideas behind our approach, we
explore into the use of properties such as entropy and coefficient of
variation.

The entropy is a fundamental concept in information theory with broad
applications to pattern recognition, statistical physics, stochastic
dynamics, and statistics. Shannon introduced it for a random variable in
1948~\cite{Shannon1948} as a measure of information and uncertainty.\\
In statistics, Shannon entropy is a crucial descriptive parameter,
particularly for assessing data dispersion and conducting tests for
normality, exponentiality, and
uniformity~\cite{Wieczorkowski1999,Zamanzade2012}. Entropy estimation
involves several practical difficulties, especially when the model is
unknown; in these cases, non-parametric methods are used.

Spacing methods have been discussed as a non-parametric approach
in~\cite{AlizadehNoughabi2010,Subhash2021}. This strategy offers
flexibility to address a wide range of models without imposing specific
parametric restrictions.

In our study, entropy serves as the fundamental parameter, providing a
robust assessment by means of a bootstrapped non-parametric estimator of
Shannon entropy.

Simultaneously, we use the classic coefficient of variation (CV) and an
alternative form based on the ratio between the median absolute
deviation and the median. The CV is known as an efficient and robust
index of textural information, measures the homogeneity of the
image~\cite{Lopes1990}.

The CV, introduced by Pearson~\cite{Pearson1896} in 1896, is a relative
measure of dispersion widely used in various areas of applied statistics
including sampling, biostatistics, medical and biological research,
climatology, and other fields
\cite{hendricks1936sampling, Tian2005,SubrahmanyaNairy2003,Chankham2024}.
It facilitates the comparison of variability between different
populations and is especially valuable for comparing variables with
different units. This is because when the main purpose is to compare
variations of several variables, the standard deviation cannot serve as
an adequate measure of variation unless all variables are expressed in
the same unit of measurement and have identical mean values. When these
requirements are not hold for the variables under study, CV is the
relative measure typically used in real applications. The variable with
the highest CV value is the one with the highest relative dispersion
around the mean~\cite{Banik2011}.

Applying these test statistics to generate \(p\)-value maps facilitates
testing of the homogeneity hypothesis, revealing diverse types of
targets within the SAR data. Through extensive experimentation involving
real and simulated SAR data, we demonstrate the superiority of our
proposed methodology over existing approaches.

The article is structured as follows: Section~\ref{sec:Background}
covers statistical modeling and entropy estimation for Intensity SAR
data. Section~\ref{sec:test} outlines hypothesis testing based on
non-parametric entropy estimators and and coefficient of variation. In
Section~\ref{sec:Results}, we present experimental results. Finally, in
Section~\ref{sec:conclusion} conclusions are exhibited.

\hypertarget{sec:Background}{%
\section{Background}\label{sec:Background}}

\hypertarget{statistical-modeling-of-intensity-sar-data}{%
\subsection{Statistical Modeling of Intensity SAR
data}\label{statistical-modeling-of-intensity-sar-data}}

The primary models used for intensity SAR data include the Gamma and
\(\mathcal{G}_I^0\) distributions~\citep{Frery1997}. The first is
suitable for fully developed speckle and is a limiting case of the
second, which is appealing due to its versatility in accurately
representing regions with various roughness
characteristics~\citep{Cassetti2022}. We denote
\(Z \sim \Gamma_{\text{SAR}}(L, \mu)\) and
\(Z \sim G_I^0(\alpha, \gamma, L)\) to indicate that \(Z\) follows the
distributions characterized by the respective probability density
functions: \begin{align}
    f_Z(z;L, \mu)&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gamma1}\\
    f_Z(z; \alpha, \gamma, L)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
\end{align} where, in~\eqref{E:gamma1} \(\mu > 0\) is the mean;
in~\eqref{E:gi01} \(\gamma > 0\) is the scale, \(\alpha < -1\) measures
the roughness, \(L \geq 1\) is the number of looks, \(\Gamma(\cdot)\) is
the gamma function, and \(\mathbbm 1_{A}(z)\) is the indicator function
of the set \(A\).

From \eqref{E:gi01}, the \(r\)th moment of \(Z\) is expressed as:
\begin{align}
    E_{G_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\gamma(L)}, \quad \alpha <-r. 
    \label{E:rmom}
\end{align}

Even though the \(\mathcal{G}_I^0\) distribution is defined by the
parameters \(\alpha\) and \(\gamma\), SAR literature commonly utilizes
the texture \(\alpha\) and the mean \(\mu\)~\cite{Nascimento2010}. In
this way, we compute the expected value \(\mu\) using the expression
in~\eqref{E:rmom}, and we reparametrize~\eqref{E:gi01} using \(\mu\),
\(\alpha\), and \(L\). Then \begin{align*}
    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
\end{align*} Thus, the probability density function that characterize
the \(G_I^0(\mu, \alpha, L)\) law is \begin{equation}
        f_Z(z; \mu, \alpha, L)=\frac{L^L\Gamma(L-\alpha)}{\big(-\mu(\alpha+1)\big)^{\alpha}\Gamma(-\alpha)\Gamma(L)} \frac{z^{L-1}}{\big(-\mu(\alpha+1)+Lz\big)^{L-\alpha}}.\label{E:gi02}
\end{equation}

\hypertarget{the-shannon-entropy}{%
\subsection{The Shannon Entropy}\label{the-shannon-entropy}}

The parametric representation of Shannon entropy for a system described
by a continuous random variable is: \begin{equation}
  \label{E:entropy2}
  H(Z)=-\int_{-\infty }^\infty \ f(z)\ln f(z)\, \mathrm{d}z,
\end{equation} here, \(f(\cdot)\) is the probability density function
that characterizes the distribution of the real-valued random variable
\(Z\).

Using~\eqref{E:entropy2}, we can express the Shannon entropy of
\(\Gamma_{\text{SAR}}\)in~\eqref{E:gamma1} and \(G_I^0\)
in~\eqref{E:gi02} based on~\cite{Cassetti2022} and~\cite{Ferreira2020}:
\begin{equation}
\label{E:E-gamma}
H_{\Gamma_{\text{SAR}}}(L, \mu) =   L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu, 
\end{equation} \begin{multline}
\label{E:E-GIO}
H_{G_I^0}(\mu, \alpha, L) =L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) +\ln \mu -\ln\Gamma(L-\alpha)\\
+ (L-\alpha) \psi^{(0)}(L-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L,
\end{multline} where \(\psi^{(0)}(\cdot)\) is the digamma function.
Figure~\ref{fig:Plot_GI0_to_gamma1}, shows the behaviour of the entropy
of \(G_I^0\) when when
\(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), observing its
convergence towards the entropy of \(\Gamma_{\text{SAR}}\) as \(\alpha\)
takes large negative values.

\begin{figure}[hbt]
\includegraphics[width=0.7\linewidth]{Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_GI0_to_gamma1-1} \caption{$H_{ G_I^0}$ converges to the $H_{\Gamma_{\text{SAR}}}$ with $L=8$.}\label{fig:Plot_GI0_to_gamma1}
\end{figure}

\hypertarget{estimation-of-the-shannon-entropy}{%
\subsection{Estimation of the Shannon
Entropy}\label{estimation-of-the-shannon-entropy}}

The problem of non-parametric estimating of \(H(Z)\) has been considered
by many authors
including~\cite{vasicek1976test, Wieczorkowski1999,correa1995new,AlOmari2019},
who proposed estimators based on spacings.

One of the earliest non-parametric estimators relying on spacings was
introduced by Vasicek~\cite{vasicek1976test}. Assuming that
\(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) is a random sample from the
distribution \(F(z)\), the estimator is defined as: \begin{equation*}
\label{E:Vas}
    \widehat{H}_{\text{V}}(\bm{Z})=\frac{1}{n}\sum_{i=1}^{n}\ln\left[\frac{n}{2m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
    \end{equation*} where \(m<n/2\) is a positive integer,
\(Z_{(i+m)}-Z_{(i-m)}\) is the \(m\)-spacing and
\(Z_{(1)}\leq Z_{(2)}\leq\ldots\leq Z_{(n)}\) are the order statistics
and \(Z_{(i)}= Z_{(1)}\) if \(i<1\), \(Z_{(i)}= Z_{(n)}\) if \(i>n\).

Several authors have explored adaptations to Vasicek's estimator. We
consider three estimators known for their superior
performance~\cite{Cassetti2022}:

\begin{itemize}
\item
  Correa~\cite{correa1995new}: \(\widehat{H}_{\text{C}}\).
\item
  Ebrahimi et al~\cite{Ebrahimi1994}: \(\widehat{H}_{\mathrm{E}}\).
\item
  Al Omary~\cite{IbrahimAlOmari2014}: \(\widehat{H}_{\mathrm{AO}}\).
\end{itemize}

\hypertarget{enhanced-bootstrap-technique}{%
\subsection{Enhanced Bootstrap
Technique}\label{enhanced-bootstrap-technique}}

We employ the bootstrap technique to refine the precision of existing
non-parametric entropy estimators. This approach involves generating new
datasets through resampling with repetition from an existing
one~\cite{Michelucci2021}.

Let's assume that non-parametric entropy estimators
\(\widehat{H}=\widehat{\theta}(\bm{Z})\) are inherently biased, that is:
\begin{equation}
\label{Eq:bias1}
\operatorname{Bias}\big(\widehat{\theta}(\bm{Z})\big) = E\big[\widehat{\theta}(\bm{Z})\big] - \theta \neq 0.
\end{equation} Our bootstrap-improved estimators are of the form:
\begin{align*}
\widetilde{H} &= 2\widehat{\theta}(\bm{Z}) - \frac{1}{B}\sum_{b=1}^B \widehat{\theta}_b(\bm{Z}^{(b)}),
\end{align*} where \(B\) is the number of replications in the bootstrap
technique. Applying this methodology, the original estimators by Correa,
Ebrahimi, and Al-Omari are now denoted as the proposed
bootstrap-enhanced versions: \(\widetilde{H}_{\text{C}}\),
\(\widetilde{H}_{\text{E}}\), and \(\widetilde{H}_{\text{AO}}\),
respectively.

We analyzed the performance of these estimators with a Monte Carlo
study: \(500\) samples of \(G_I^0\) of size
\(n\in\left\{9, 25, 49, 81, 121\right\}\) and several values of the
mean, number of looks and roughness. We present the results with
\(mu\in\left\{1, 10\right\}\), \(\alpha=-10\), and \(L=5\). The results
are consistent for the other situations. In the case of the bootstrap
technique, each sample is replicated \(100\) times with replacement. We
choose to use the following heuristic formula for spacing,
\(m=\left[\sqrt{n}+0.5\right]\).

In Figure~\ref{fig:Plot_bias_mse_gi0} we depict comparisons of bias and
mean squared error (MSE) between the original non-parametric entropy
estimators and their respective bootstrap-enhanced versions. The use of
the bootstrap technique exhibits more precision, reduced bias and MSE,
and improved convergence. The results of simulation are exhibited in
Table~\ref{tab:table2}.

The precision of estimators, as evidenced by bias and MSE comparisons,
benefits significantly from the bootstrap technique, particularly for
sample sizes below 81.

\begin{figure}[hbt]
\includegraphics[width=0.8\linewidth]{Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_bias_mse_gi0-1} \caption{Bias and MSE, $L=5$ and  $\alpha=-10$.}\label{fig:Plot_bias_mse_gi0}
\end{figure}

\begin{table}[H]
\centering
\caption{\label{tab:table2}Bias and MSE of non-parametric entropy estimators and bootstrap versions.}
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{tabular}[t]{lrrrrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{6}{c}{Bias} & \multicolumn{6}{c}{MSE} \\
\cmidrule(l{3pt}r{3pt}){3-8} \cmidrule(l{3pt}r{3pt}){9-14}
\multicolumn{1}{c}{$\mu$} & \multicolumn{1}{c}{$n$} & \multicolumn{1}{c}{$\widehat{H}_{\text{AO}}$} & \multicolumn{1}{c}{$\widehat{H}_{\text{C}}$} & \multicolumn{1}{c}{$\widehat{H}_{\text{E}}$} & \multicolumn{1}{c}{$\widetilde{H}_{\text{AO}}$} & \multicolumn{1}{c}{$\widetilde{H}_{\text{C}}$} & \multicolumn{1}{c}{$\widetilde{H}_{\text{E}}$} & \multicolumn{1}{c}{$\widehat{H}_{\text{AO}}$} & \multicolumn{1}{c}{$\widehat{H}_{\text{C}}$} & \multicolumn{1}{c}{$\widehat{H}_{\text{E}}$} & \multicolumn{1}{c}{$\widetilde{H}_{\text{AO}}$} & \multicolumn{1}{c}{$\widetilde{H}_{\text{C}}$} & \multicolumn{1}{c}{$\widetilde{H}_{\text{E}}$}\\
\midrule
 & $9$ & $-0.188$ & $-0.261$ & $-0.358$ & $-0.083$ & $-0.030$ & $-0.114$ & $\phantom{-}0.131$ & $\phantom{-}0.157$ & $\phantom{-}0.217$ & $\phantom{-}0.140$ & $\phantom{-}0.124$ & $\phantom{-}0.140$\\

 & $25$ & $-0.081$ & $-0.120$ & $-0.157$ & $-0.042$ & $\phantom{-}0.001$ & $-0.049$ & $\phantom{-}0.040$ & $\phantom{-}0.046$ & $\phantom{-}0.057$ & $\phantom{-}0.042$ & $\phantom{-}0.044$ & $\phantom{-}0.044$\\

 & $49$ & $-0.032$ & $-0.059$ & $-0.080$ & $-0.007$ & $\phantom{-}0.024$ & $-0.005$ & $\phantom{-}0.018$ & $\phantom{-}0.021$ & $\phantom{-}0.023$ & $\phantom{-}0.022$ & $\phantom{-}0.021$ & $\phantom{-}0.022$\\

 & $81$ & $-0.007$ & $-0.024$ & $-0.038$ & $\phantom{-}0.004$ & $\phantom{-}0.033$ & $\phantom{-}0.025$ & $\phantom{-}0.010$ & $\phantom{-}0.010$ & $\phantom{-}0.011$ & $\phantom{-}0.011$ & $\phantom{-}0.014$ & $\phantom{-}0.013$\\

\multirow{-5}{*}[2\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash 1} & $121$ & $\phantom{-}0.000$ & $-0.010$ & $-0.020$ & $\phantom{-}0.007$ & $\phantom{-}0.037$ & $\phantom{-}0.025$ & $\phantom{-}0.006$ & $\phantom{-}0.006$ & $\phantom{-}0.006$ & $\phantom{-}0.008$ & $\phantom{-}0.009$ & $\phantom{-}0.008$\\
\cmidrule{1-14}
 & $9$ & $-0.239$ & $-0.322$ & $-0.418$ & $-0.116$ & $-0.084$ & $-0.180$ & $\phantom{-}0.169$ & $\phantom{-}0.218$ & $\phantom{-}0.289$ & $\phantom{-}0.164$ & $\phantom{-}0.172$ & $\phantom{-}0.176$\\

 & $25$ & $-0.062$ & $-0.108$ & $-0.145$ & $-0.007$ & $\phantom{-}0.006$ & $-0.026$ & $\phantom{-}0.040$ & $\phantom{-}0.048$ & $\phantom{-}0.057$ & $\phantom{-}0.051$ & $\phantom{-}0.048$ & $\phantom{-}0.047$\\

 & $49$ & $-0.018$ & $-0.044$ & $-0.064$ & $-0.001$ & $\phantom{-}0.033$ & $\phantom{-}0.017$ & $\phantom{-}0.016$ & $\phantom{-}0.017$ & $\phantom{-}0.019$ & $\phantom{-}0.018$ & $\phantom{-}0.020$ & $\phantom{-}0.018$\\

 & $81$ & $-0.015$ & $-0.032$ & $-0.046$ & $-0.006$ & $\phantom{-}0.025$ & $\phantom{-}0.015$ & $\phantom{-}0.010$ & $\phantom{-}0.010$ & $\phantom{-}0.011$ & $\phantom{-}0.011$ & $\phantom{-}0.013$ & $\phantom{-}0.011$\\

\multirow{-5}{*}[2\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash 10} & $121$ & $-0.009$ & $-0.022$ & $-0.031$ & $-0.005$ & $\phantom{-}0.025$ & $\phantom{-}0.016$ & $\phantom{-}0.007$ & $\phantom{-}0.008$ & $\phantom{-}0.008$ & $\phantom{-}0.009$ & $\phantom{-}0.010$ & $\phantom{-}0.009$\\
\bottomrule
\end{tabular}}
\end{table}

\hypertarget{coefficient-of-variation-and-a-robust-alternative}{%
\subsection{Coefficient of variation and a robust
alternative}\label{coefficient-of-variation-and-a-robust-alternative}}

The population CV is defined as a ratio of the population standard
deviation \((\sigma)\) to the population mean \((\mu)\):

\begin{align}
    \text{CV}=\frac{\sigma}{\mu}, \quad \mu \neq 0.
\end{align}

We explore a robust alternative to the CV as discussed in
\cite{Ospina2019}, involving the ratio of the mean absolute deviation
from the median (MnAD) to the median, two well-known robust measures of
scale and location, respectively. The MnAD is defined as
\(n^{-1}\sum_{i=1}^n|x_i-\widehat{Q}_2|\), where \(\widehat{Q}_2\)
represents an estimate of the population median, which can be
approximated by the sample median.

\hypertarget{sec:test}{%
\section{Hypothesis Testing}\label{sec:test}}

We aim at testing the following hypotheses:

\[
 \begin{cases}\mathcal{H}_0: \text{ The data comes from the } \Gamma_{\text{SAR}}\\ 
  \mathcal{H}_1:\text{ The data comes from the } G_I^0.\end{cases}
\] In other words, we verify the hypothesis that the data are
fully-developed speckle. The proposed tests are described below.

\hypertarget{the-proposed-test-based-on-non-parametric-entropy}{%
\subsection{The Proposed Test Based on Non-parametric
Entropy}\label{the-proposed-test-based-on-non-parametric-entropy}}

The first test statistic assess the behavior of the data under the null
hypothesis, through the empirical distribution. \begin{equation}
\label{Eq:test_e}
S_H= \widetilde{H}-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \overline{Z}\right].
\end{equation} The values should be around zero under the null
hypothesis and far otherwise.

Figure~\ref{fig:Plot_density} depicts empirical test statistic densities
for various sample sizes, and Table~\ref{tab:table_stat_combined}
summarizes key statistics, including mean, SD, variance (Var), skewness
(SK), excess kurtosis (EK), and Anderson--Darling \(p\)-values for
normality. Results with \(p\)-values larger than \(0.05\) indicate no
evidence against normality. Small variance and near-zero skewness and
excess kurtosis suggest limited spread, symmetry, and light tails.\\
Normal QQ-plots, confirm that there is no evidence to reject the normal
distribution.

\begin{figure}[hbt]
\includegraphics[width=0.8\linewidth]{Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_density-1} \caption{Empirical density  under the null hypothesis.}\label{fig:Plot_density}
\end{figure}

\begin{table}[H]

\caption{\label{tab:table_stat_combined}Descriptive analysis of $S_H$ with $L\in\left\{3,5, 8,11\right\}$ and $\mu=1$.}
\begin{tabular}[t]{lrrrrrrr}
\toprule
\multicolumn{1}{c}{$L$} & \multicolumn{1}{c}{$n$} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Var} & \multicolumn{1}{c}{SK} & \multicolumn{1}{c}{EK} & \multicolumn{1}{c}{$p$-value}\\
\midrule
 & $25$ & $-0.0596$ & $\phantom{-}0.2491$ & $\phantom{-}0.0620$ & $\phantom{-}0.2206$ & $\phantom{-}0.8568$ & $\phantom{-}0.0051$\\

 & $49$ & $-0.0232$ & $\phantom{-}0.1767$ & $\phantom{-}0.0312$ & $\phantom{-}0.2322$ & $\phantom{-}0.5200$ & $\phantom{-}0.2622$\\

 & $81$ & $\phantom{-}0.0047$ & $\phantom{-}0.1297$ & $\phantom{-}0.0168$ & $\phantom{-}0.3550$ & $\phantom{-}0.5413$ & $\phantom{-}0.0725$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash 3} & $121$ & $\phantom{-}0.0011$ & $\phantom{-}0.1018$ & $\phantom{-}0.0104$ & $-0.0065$ & $\phantom{-}0.5275$ & $\phantom{-}0.2092$\\
\cmidrule{1-8}
 & $25$ & $-0.0692$ & $\phantom{-}0.2563$ & $\phantom{-}0.0657$ & $\phantom{-}0.0527$ & $\phantom{-}0.5330$ & $\phantom{-}0.0336$\\

 & $49$ & $-0.0197$ & $\phantom{-}0.1786$ & $\phantom{-}0.0319$ & $\phantom{-}0.4864$ & $\phantom{-}0.5653$ & $\phantom{-}0.0008$\\

 & $81$ & $-0.0075$ & $\phantom{-}0.1389$ & $\phantom{-}0.0193$ & $\phantom{-}0.2414$ & $\phantom{-}0.2546$ & $\phantom{-}0.0183$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash 5} & $121$ & $\phantom{-}0.0019$ & $\phantom{-}0.1083$ & $\phantom{-}0.0117$ & $\phantom{-}0.0857$ & $\phantom{-}0.4701$ & $\phantom{-}0.1208$\\
\cmidrule{1-8}
 & $25$ & $-0.0669$ & $\phantom{-}0.2745$ & $\phantom{-}0.0753$ & $\phantom{-}0.4127$ & $\phantom{-}0.7551$ & $\phantom{-}0.0033$\\

 & $49$ & $-0.0366$ & $\phantom{-}0.1808$ & $\phantom{-}0.0327$ & $\phantom{-}0.3316$ & $\phantom{-}0.7583$ & $\phantom{-}0.0802$\\

 & $81$ & $-0.0064$ & $\phantom{-}0.1221$ & $\phantom{-}0.0149$ & $\phantom{-}0.0012$ & $-0.0649$ & $\phantom{-}0.9260$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash 8} & $121$ & $-0.0083$ & $\phantom{-}0.1173$ & $\phantom{-}0.0138$ & $-0.1351$ & $\phantom{-}0.0770$ & $\phantom{-}0.1648$\\
\cmidrule{1-8}
 & $25$ & $-0.0954$ & $\phantom{-}0.2552$ & $\phantom{-}0.0651$ & $\phantom{-}0.2723$ & $\phantom{-}0.6899$ & $\phantom{-}0.2190$\\

 & $49$ & $-0.0549$ & $\phantom{-}0.1716$ & $\phantom{-}0.0294$ & $\phantom{-}0.0352$ & $\phantom{-}0.2073$ & $\phantom{-}0.2847$\\

 & $81$ & $-0.0159$ & $\phantom{-}0.1309$ & $\phantom{-}0.0171$ & $\phantom{-}0.0199$ & $-0.2283$ & $\phantom{-}0.4678$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash 11} & $121$ & $\phantom{-}0.0020$ & $\phantom{-}0.1182$ & $\phantom{-}0.0140$ & $-0.0046$ & $\phantom{-}0.1101$ & $\phantom{-}0.8906$\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}[hbt]
\includegraphics[width=0.8\linewidth]{Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_normality_qq-1} \caption{Normal QQ-plots for  $n=121$.}\label{fig:Plot_normality_qq}
\end{figure}

After verifying the normality of the data, we proceeded to explore the
capabilities of the proposed test in terms of size and power. Under
\(\mathcal{H}_0\), the distribution of test statistic is asymptotically
normal. Therefore, the \(p\)-value is calculated as
\(2\Phi(-\mid \varepsilon\mid)\), where \(\Phi\) is the standard
Gaussian cumulative distribution and \(\varepsilon\) is the standardized
test statistic given by: \[
\varepsilon=\frac{\tilde{H}-H_{\Gamma_{\text{SAR}}}}{\hat\sigma}.
\]

We considered nominal levels of \SI{1}{\percent}, \SI{5}{\percent}, and
\SI{10}{\percent}. In reference to the size, \(1000\) simulations have
been used for various sample sizes with satisfactory results. In all
cases, the nominal level has been achieved. The power, in general,
improves with the increase in the sample size and the number of looks.
The results are presented in Table~\ref{tab:table_size_power}.

\hypertarget{the-proposed-test-based-on-coefficient-of-variation-and-a-robust-alternative}{%
\subsection{The Proposed Test Based on Coefficient of Variation and a
Robust
Alternative}\label{the-proposed-test-based-on-coefficient-of-variation-and-a-robust-alternative}}

In addition to the entropy-based test, we also propose a test statistic
based on the classical CV. This test statistic is defined as follows:
\begin{align}
    T_{\text{CV}}=\frac{S}{\overline{Z}},
\end{align} where \(S\) and \(\overline{Z}\) are the sample standard
deviation and the sample mean, respectively.

Similarly, we use another test statistic based on the ratio of the MnAD
to the median. This statistic is given by: \begin{align}
    T_{\text{CV}_{\text{MnAD}}}=\frac{\text{MnAD}}{\text{Median}}.
\end{align} These test statistics allow assessing the variability of the
data.

The situations where the use of CV and \(\text{CV}_{\text{MnAD}}\) may
be appropriate, i.e.~where the observations are positive, the log-normal
(LN) and inverse Gaussian (IG) distribution are often more justified
compared to Gamma and Weibull distributions
\cite{Chaubey2017,takagi1997application}.

The inverse Gaussian distribution is shown to be well approximated by
the log-normal distribution \cite{whitmore1978} which implies that the
IG distribution also does not share the problem of non-existence of
fixed width confidence interval with the Gaussian case.

The LN distribution in two parameters has the following density
function. \begin{align}
    f_Z(z;\mu, \sigma )=\frac{1}{\sigma z\sqrt{2\pi}}\exp\left\{-\frac{(\ln z- \mu)^2}{2\sigma^2}\right\}, \quad z>0, \sigma>0, -\infty < \mu < \infty,
\end{align} here, \(\mu\) is the log-scale parameter and \(\sigma\) is
the shape parameter.

\hypertarget{model-selection-criterion}{%
\subsection{Model Selection Criterion}\label{model-selection-criterion}}

Akaike information criterion (AIC) and Bayesian information criterion
(BIC) are used to select the best fitting distribution.

The AIC is a fine technique that deals with the trade-off between the
goodness-of-fit of the model and the simplicity of the model in terms of
the number of model parameters~\cite{Burnham2004}. The model or
distribution with the lowest value of AIC is chosen to be the best. The
BIC assesses goodness-of-fit of a distribution or model, but avoids
overfitting by penalising an additional degree of
freedom~\cite{Dziak2019}. The model with the lowest BIC value is chosen
as the best.

The AIC and BIC results in
Tables~\ref{tab:table_aic_gamma}-\ref{tab:table_aic_gio_MnADmedian}
indicate that the CV and \(\text{CV}_{\text{MnAD}}\) data from different
synthetic sample sizes, extracted from the Gamma SAR and \(G_I^0\)
distributions, respectively, adhere to the characteristics of an LN
distribution. The AIC and BIC values of the IG distribution and the LN
distribution are not significantly different because both distributions
are based on the right-skewed characteristic. In this situation, the
model for the LN distribution was considered to be the best due to it
providing the lowest AIC and BIC values.

Figures~\ref{fig:Plot_cv}-\ref{fig:Plot_madmed_gi0_MnADmedian} present
density plots, Q-Q plots, P-P plots, and Cumulative Distribution
Function plots, which offer an additional measure of goodness-of-fit and
confirm that the most suitable distribution to be considered is the LN
distribution.

\begin{table}[H]

\caption{\label{tab:table_aic_gamma}AIC and BIC values for evaluating the best distribution with CV data from Gamma SAR.}
\begin{tabular}[t]{lcccccc}
\toprule
\multicolumn{1}{c}{\textbf{Criterion}} & \multicolumn{1}{c}{$\bm{n}$} & \multicolumn{1}{c}{\textbf{Normal}} & \multicolumn{1}{c}{\textbf{Lognormal}} & \multicolumn{1}{c}{\textbf{Gamma}} & \multicolumn{1}{c}{\textbf{Weibull}} & \multicolumn{1}{c}{\textbf{Inverse Gaussian}}\\
\midrule
 & $25$ & $-38031.95$ & $-38266.75$ & $-38311.84$ & $-36413.23$ & $-38261.60$\\

 & $49$ & $-47698.20$ & $-47913.72$ & $-47905.63$ & $-45553.97$ & $-47911.65$\\

 & $81$ & $-55382.11$ & $-55494.72$ & $-55494.88$ & $-53220.44$ & $-55493.85$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash AIC} & $121$ & $-61344.92$ & $-61470.83$ & $-61453.83$ & $-58876.04$ & $-61470.48$\\
\cmidrule{1-7}
 & $25$ & $-38016.72$ & $-38251.52$ & $-38296.61$ & $-36397.99$ & $-38246.37$\\

 & $49$ & $-47682.96$ & $-47898.49$ & $-47890.40$ & $-45538.73$ & $-47896.42$\\

 & $81$ & $-55366.88$ & $-55479.49$ & $-55479.65$ & $-53205.21$ & $-55478.62$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash BIC} & $121$ & $-61329.68$ & $-61455.60$ & $-61438.60$ & $-58860.81$ & $-61455.25$\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]

\caption{\label{tab:table_aic}AIC and BIC values for evaluating the best distribution with CV data from $G_I^0$.}
\begin{tabular}[t]{lcccccc}
\toprule
\multicolumn{1}{c}{\textbf{Criterion}} & \multicolumn{1}{c}{$\bm{n}$} & \multicolumn{1}{c}{\textbf{Normal}} & \multicolumn{1}{c}{\textbf{Lognormal}} & \multicolumn{1}{c}{\textbf{Gamma}} & \multicolumn{1}{c}{\textbf{Weibull}} & \multicolumn{1}{c}{\textbf{Inverse Gaussian}}\\
\midrule
 & $25$ & $\phantom{-}8254.04$ & $\phantom{-}2186.31$ & $\phantom{-}3628.40$ & $\phantom{-}8383.58$ & $\phantom{-}2257.63$\\

 & $49$ & $\phantom{-}8821.79$ & $\phantom{-}1689.03$ & $\phantom{-}3483.10$ & $\phantom{-}9533.53$ & $\phantom{-}1835.29$\\

 & $81$ & $\phantom{-}8525.81$ & $\phantom{-}866.29$ & $\phantom{-}2853.31$ & $\phantom{-}9822.48$ & $\phantom{-}1057.91$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash AIC} & $121$ & $\phantom{-}8708.81$ & $\phantom{-}131.86$ & $\phantom{-}2341.06$ & $\phantom{-}10506.49$ & $\phantom{-}398.53$\\
\cmidrule{1-7}
 & $25$ & $\phantom{-}8269.27$ & $\phantom{-}2201.54$ & $\phantom{-}3643.63$ & $\phantom{-}8398.81$ & $\phantom{-}2272.86$\\

 & $49$ & $\phantom{-}8837.02$ & $\phantom{-}1704.26$ & $\phantom{-}3498.33$ & $\phantom{-}9548.76$ & $\phantom{-}1850.52$\\

 & $81$ & $\phantom{-}8541.04$ & $\phantom{-}881.52$ & $\phantom{-}2868.55$ & $\phantom{-}9837.72$ & $\phantom{-}1073.14$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash BIC} & $121$ & $\phantom{-}8724.04$ & $\phantom{-}147.09$ & $\phantom{-}2356.29$ & $\phantom{-}10521.72$ & $\phantom{-}413.76$\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]

\caption{\label{tab:table_aic_gamma_madmed}AIC and BIC values for evaluating the best distribution with $\text{CV}_{\text{MnAD}}$ data from Gamma SAR.}
\begin{tabular}[t]{lcccccc}
\toprule
\multicolumn{1}{c}{\textbf{Criterion}} & \multicolumn{1}{c}{$\bm{n}$} & \multicolumn{1}{c}{\textbf{Normal}} & \multicolumn{1}{c}{\textbf{Lognormal}} & \multicolumn{1}{c}{\textbf{Gamma}} & \multicolumn{1}{c}{\textbf{Weibull}} & \multicolumn{1}{c}{\textbf{Inverse Gaussian}}\\
\midrule
 & $25$ & $-38375.56$ & $-39147.85$ & $-39066.29$ & $-36652.49$ & $-39143.61$\\

 & $49$ & $-48386.11$ & $-48795.32$ & $-48745.48$ & $-46240.91$ & $-48793.83$\\

 & $81$ & $-56072.87$ & $-56322.32$ & $-56290.02$ & $-53836.04$ & $-56322.12$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash AIC} & $121$ & $-62217.14$ & $-62394.77$ & $-62369.32$ & $-59861.80$ & $-62394.57$\\
\cmidrule{1-7}
 & $25$ & $-38360.32$ & $-39132.62$ & $-39051.05$ & $-36637.26$ & $-39128.38$\\

 & $49$ & $-48370.87$ & $-48780.09$ & $-48730.25$ & $-46225.67$ & $-48778.60$\\

 & $81$ & $-56057.64$ & $-56307.09$ & $-56274.79$ & $-53820.81$ & $-56306.89$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash BIC} & $121$ & $-62201.91$ & $-62379.54$ & $-62354.09$ & $-59846.56$ & $-62379.33$\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]

\caption{\label{tab:table_aic_gio_MnADmedian}AIC and BIC values for evaluating the best distribution with $\text{CV}_{\text{MnAD}}$ data from $G_I^0$.}
\begin{tabular}[t]{lcccccc}
\toprule
\multicolumn{1}{c}{\textbf{Criterion}} & \multicolumn{1}{c}{$\bm{n}$} & \multicolumn{1}{c}{\textbf{Normal}} & \multicolumn{1}{c}{\textbf{Lognormal}} & \multicolumn{1}{c}{\textbf{Gamma}} & \multicolumn{1}{c}{\textbf{Weibull}} & \multicolumn{1}{c}{\textbf{Inverse Gaussian}}\\
\midrule
 & $25$ & $-13302.39$ & $-15575.23$ & $-15158.42$ & $-11933.35$ & $-15565.03$\\

 & $49$ & $-23265.27$ & $-24529.72$ & $-24284.47$ & $-20986.94$ & $-24522.28$\\

 & $81$ & $-29908.19$ & $-30960.38$ & $-30747.90$ & $-25233.41$ & $-30946.54$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash AIC} & $121$ & $-36496.78$ & $-37128.07$ & $-36991.41$ & $-32366.52$ & $-37123.20$\\
\cmidrule{1-7}
 & $25$ & $-13287.16$ & $-15559.99$ & $-15143.19$ & $-11918.12$ & $-15549.80$\\

 & $49$ & $-23250.04$ & $-24514.48$ & $-24269.24$ & $-20971.71$ & $-24507.05$\\

 & $81$ & $-29892.96$ & $-30945.15$ & $-30732.67$ & $-25218.17$ & $-30931.31$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash BIC} & $121$ & $-36481.55$ & $-37112.84$ & $-36976.18$ & $-32351.28$ & $-37107.97$\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_cv_gamma-1}

}

\caption{Goodness of fit plots for evaluating the best distribution with CV data from Gamma SAR, with  $n=49$, $L=5$ and $\mu=1$.}\label{fig:Plot_cv_gamma}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_cv-1}

}

\caption{Goodness of fit plots for evaluating the best distribution with $\text{CV}_{\text{MnAD}}$ data from $G_I^0$, with  $n=49$, $L=5$, $\mu=1$ and $\alpha=-2$.}\label{fig:Plot_cv}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_MnADmedian_gamma-1}

}

\caption{Goodness of fit plots for evaluating the best distribution with $\text{CV}_{\text{MnAD}}$ data from Gamma SAR, with  $n=49$, $L=5$ and $\mu=1$.}\label{fig:Plot_MnADmedian_gamma}
\end{figure}

\begin{figure}[hbt]
\includegraphics[width=1\linewidth]{Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_madmed_gi0_MnADmedian-1} \caption{Goodness of fit plots for evaluating the best distribution with $CV_{\text{MnAD}}$ data from $G_I^0$, with  $n=49$, $L=5$, $\mu=1$ and $\alpha=-5$.}\label{fig:Plot_madmed_gi0_MnADmedian}
\end{figure}

\hypertarget{sec:Results}{%
\section{Simulation Results}\label{sec:Results}}

This section presents simulations performed to obtain an assessment of
the performances of the proposed test statistics.

\hypertarget{simulated-data}{%
\subsection{Simulated Data}\label{simulated-data}}

Figure 1a shows the phantom used for a simulated image with dimensions
of \(250\times 250\) pixels to illustrate the differences between
heterogeneous (dark, \(\alpha=-2\)) and homogeneous (light,
\(\alpha=-10\)) regions, with \(L = 5\). The areas are formed by
independent draws from the \(G^0_I\) distribution.

The three test statistics are applied to the simulated image using local
sliding windows of size \(7\times 7\).

The resulting \(p\)-values for the tests \(S_H\), \(T_{\text{CV}}\), and
\(T_{\text{CV}_{\text{MnAD}}}\) are shown in
Figures~\ref{fig:sim_SAR_Images}(b)-(d) and
Figures~\ref{fig:sim_SAR_Images_p05}(a)-(c), respectively. The new
images reveal that a darker background indicates homogeneity, while
lighter backgrounds represent heterogeneous areas.

\begin{figure}[H]

{\centering \subfloat[\label{fig:sim_SAR_Images-1}]{\includegraphics[width=40mm]{../Figures/PNG/simulated7x7} }\subfloat[\label{fig:sim_SAR_Images-2}]{\includegraphics[width=40mm]{../Figures/PNG/sim_pvalue7x7_total_H} }\subfloat[\label{fig:sim_SAR_Images-3}]{\includegraphics[width=40mm]{../Figures/PNG/sim_pvalue7x7_total_cv} }\newline\subfloat[\label{fig:sim_SAR_Images-4}]{\includegraphics[width=40mm]{../Figures/PNG/sim_pvalue7x7_total_mnad} }

}

\caption{Results of applying the test statistics. (a) Simulated image; $P$-values from the entropy-based test; (c) $P$-values from the CV test; (d) $P$-values from the   $\text{CV}_{\text{MnAD}}$ test; }\label{fig:sim_SAR_Images}
\end{figure}
\begin{figure}[H]

{\centering \subfloat[ \label{fig:sim_SAR_Images_p05-1}]{\includegraphics[width=40mm]{../Figures/PNG/sim_pvalue7x7_H} }\subfloat[ \label{fig:sim_SAR_Images_p05-2}]{\includegraphics[width=40mm]{../Figures/PNG/sim_pvalue7x7_cv} }\subfloat[ \label{fig:sim_SAR_Images_p05-3}]{\includegraphics[width=40mm]{../Figures/PNG/sim_pvalue7x7_mnad} }

}

\caption{Results of tests on simulated data with a threshold of $0.1$ of the $p$-value. (a) Entropy-based test; (b) CV test; (c) $\text{CV}_{\text{MnAD}}$ test.}\label{fig:sim_SAR_Images_p05}
\end{figure}

\hypertarget{real-data}{%
\subsection{Real Data}\label{real-data}}

We applied the proposed test statistics in actual SAR images acquired
over cities, including Flevoland, Netherlands and Ottawa, Canada.\\
These images were captured by the Sentinel-1A satellite operating in the
C band, with VV polarization, intensity format, and \(L=5\) nominal
looks. Both images have dimensions of \(512 \times 512\) pixels and
contain urban areas, water forest regions, as shown in
Figures~\ref{fig:real_SAR_Images_coe}(a)-(b).

The \(p\)-values obtained for the \(S_H\), \(T_{\text{CV}}\), and
\(T_{\text{CV}_{\text{MnAD}}}\) tests are presented in
Figures~\ref{fig:sim_SAR_Images_Frankfurt}-\ref{fig:sim_SAR_Images_01_Ottawa},
respectively.

\begin{figure}[H]

{\centering \subfloat[ \label{fig:real_SAR_Images_coe-1}]{\includegraphics[width=40mm]{../Figures/PNG/Intensity_Frankfurt_512_n} }\subfloat[ \label{fig:real_SAR_Images_coe-2}]{\includegraphics[width=40mm]{../Figures/PNG/Intensity_Ottawa_512_n} }

}

\caption{SAR images. (a) Frankfurt; (b) Ottawa. }\label{fig:real_SAR_Images_coe}
\end{figure}
\begin{figure}[H]

{\centering \subfloat[ \label{fig:sim_SAR_Images_Frankfurt-1}]{\includegraphics[width=40mm]{../Figures/PNG/Frankfurt_512_pvalue7x7_total_H} }\subfloat[ \label{fig:sim_SAR_Images_Frankfurt-2}]{\includegraphics[width=40mm]{../Figures/PNG/Frankfurt_512_pvalue7x7_total_CV} }\subfloat[ \label{fig:sim_SAR_Images_Frankfurt-3}]{\includegraphics[width=40mm]{../Figures/PNG/Frankfurt_512_mnad_7_total} }

}

\caption{Results of applying the test statistics, Frankfurt. (a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\text{CV}_{\text{MnAD}}$ test; }\label{fig:sim_SAR_Images_Frankfurt}
\end{figure}
\begin{figure}[H]

{\centering \subfloat[ \label{fig:sim_SAR_Images_01Frankfurt-1}]{\includegraphics[width=40mm]{../Figures/PNG/Frankfurt_512_pvalue7x7_H_01} }\subfloat[ \label{fig:sim_SAR_Images_01Frankfurt-2}]{\includegraphics[width=40mm]{../Figures/PNG/Frankfurt_512_pvalue7x7_CV} }\subfloat[ \label{fig:sim_SAR_Images_01Frankfurt-3}]{\includegraphics[width=40mm]{../Figures/PNG/Frankfurt_512_mnad_7_0.1} }

}

\caption{Results of tests on simulated data with a threshold of $0.1$ of the $p$-value, Frankfurt. (a) Entropy-based test; (b) CV test; (c) $\text{CV}_{\text{MnAD}}$ test.}\label{fig:sim_SAR_Images_01Frankfurt}
\end{figure}

\begin{figure}[H]

{\centering \subfloat[ \label{fig:sim_SAR_Images_Ottawa-1}]{\includegraphics[width=40mm]{../Figures/PNG/Ottawa_512_pvalue7x7_total_H} }\subfloat[ \label{fig:sim_SAR_Images_Ottawa-2}]{\includegraphics[width=40mm]{../Figures/PNG/Ottawa_512_CV_pvalue7x7_total_CV} }\subfloat[ \label{fig:sim_SAR_Images_Ottawa-3}]{\includegraphics[width=40mm]{../Figures/PNG/Ottawa_512_mnad_7_total} }

}

\caption{Results of applying the test statistics, Ottawa. (a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\text{CV}_{\text{MnAD}}$ test; }\label{fig:sim_SAR_Images_Ottawa}
\end{figure}
\begin{figure}[H]

{\centering \subfloat[ \label{fig:sim_SAR_Images_01_Ottawa-1}]{\includegraphics[width=40mm]{../Figures/PNG/Ottawa_512_pvalue7x7_H_01} }\subfloat[ \label{fig:sim_SAR_Images_01_Ottawa-2}]{\includegraphics[width=40mm]{../Figures/PNG/Ottawa_512_CV_pvalue7x7_CV} }\subfloat[ \label{fig:sim_SAR_Images_01_Ottawa-3}]{\includegraphics[width=40mm]{../Figures/PNG/Ottawa_512_mnad_7_0.1} }

}

\caption{Results of tests on simulated data with a threshold of $0.1$ of the $p$-value, Ottawa. (a) Entropy-based test; (b) CV test; (c) $\text{CV}_{\text{MnAD}}$ test.}\label{fig:sim_SAR_Images_01_Ottawa}
\end{figure}

\hypertarget{sec:conclusion}{%
\section{Conclusion}\label{sec:conclusion}}

In this article,\ldots{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\supplementary{This article is fully reproducible using RMarkdown. All
code and data are accessible at
\url{https://github.com/rjaneth/identifying-heterogeneity-in-sar-data-with-new-test-statistics}
(accessed on 5 April 2024).}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short
paragraph specifying their individual contributions must be provided.
The following statements should be used ``X.X. and Y.Y. conceive and
designed the experiments; X.X. performed the experiments; X.X. and Y.Y.
analyzed the data; W.W. contributed reagents/materials/analysis tools;
Y.Y. wrote the paper.'\,' Authorship must be limited to those who have
contributed substantially to the work reported.}

\funding{Please add: ``This research received no external funding'' or
``This research was funded by NAME OF FUNDER grant number XXX.'' and
``The APC was funded by XXX'\,'. Check carefully that the details given
are accurate and use the standard spelling of funding agency names at
\url{https://search.crossref.org/funding}, any errors may affect your
future funding.}

\institutionalreview{Not applicable.}

\dataavailability{Not applicable.}

\acknowledgments{This study was financed in part by the Coordenação de
Aperfeiçoamento de Pessoal de Nível Superior - Brasil (CAPES) - Finance
Code 001.}

\conflictsofinterest{The authors declare no conflict of interest.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional

%% Only for journal Encyclopedia

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{adjustwidth}{-\extralength}{0cm}

%\printendnotes[custom] % Un-comment to print a list of endnotes

\reftitle{References}
\bibliography{references.bib}

% If authors have biography, please use the format below
%\section*{Short Biography of Authors}
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
%{\textbf{Firstname Lastname} Biography of first author}
%
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
%{\textbf{Firstname Lastname} Biography of second author}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\PublishersNote{}
\end{adjustwidth}

\end{document}

### 2024-04-04 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
updated paper version

@@
 
-Figure 1a shows the phantom used for a simulated image with dimensions of $250\times 250$ pixels to illustrate the differences between heterogeneous (dark, $\alpha=-2$) and homogeneous (light, $\alpha=-10$) regions, with $L = 5$.
+Figure&nbsp;\ref{fig:sim_SAR_Images}(a) shows the phantom used for a simulated image with dimensions of $250\times 250$ pixels to illustrate the differences between heterogeneous (dark, $\alpha=-2$) and homogeneous (light, $\alpha=-10$) regions, with $L = 5$.
 The areas are formed by independent draws from the $G^0_I$ distribution.
@@
 
-We applied the proposed test statistics in actual SAR images acquired over cities, including Flevoland, Netherlands and Ottawa, Canada.   
-These images were captured by the Sentinel-1A satellite operating in the C band,  with  VV polarization, intensity format, and $L=5$ nominal looks.
-Both images have dimensions of $512 \times 512$ pixels and contain urban areas, water forest regions, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)-(b).
+We assessed the proposed test statistics using two real SAR images. For our analysis, we selected images of the city of Frankfurt, Germany, and Ottawa, Canada. 
+These images were acquired by the Sentinel-1A satellite operating in the C band,  with  VV polarization, intensity format, and $L=5$ nominal looks.
+
+Both images have dimensions of $512 \times 512$ pixels and contain urban areas, water and forest regions, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)-(b).
 
@@
 ```
-```{r sim_SAR_Images_Frankfurt, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics, Frankfurt.
-(a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\\text{CV}_{\\text{MnAD}}$ test; ',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+```{r sim_SAR_Images_Frankfurt, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics in Frankfurt image.
+(a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\\text{CV}_{\\text{MnAD}}$ test.
+',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 knitr::include_graphics("../Figures/PNG/Frankfurt_512_pvalue7x7_total_H.png")
@@
 ```
-```{r sim_SAR_Images_01Frankfurt, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of tests on simulated data with a threshold of $0.1$ of the $p$-value, Frankfurt.
+```{r sim_SAR_Images_01Frankfurt, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Test results with a threshold of $0.1$ of the $p$-value for the Frankfurt image.
 (a) Entropy-based test; (b) CV test; (c) $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
@@
 
-```{r sim_SAR_Images_Ottawa, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics, Ottawa.
-(a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\\text{CV}_{\\text{MnAD}}$ test; ',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+```{r sim_SAR_Images_Ottawa, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics in Ottawa image.
+(a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 knitr::include_graphics("../Figures/PNG/Ottawa_512_pvalue7x7_total_H.png")
@@
 ```
-```{r sim_SAR_Images_01_Ottawa, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of tests on simulated data with a threshold of $0.1$ of the $p$-value, Ottawa.
+```{r sim_SAR_Images_01_Ottawa, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Test results with a threshold of $0.1$ of the $p$-value for the Ottawa image.
 (a) Entropy-based test; (b) CV test; (c) $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}

### 2024-04-04 Text/Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics.tex
updated paper version

@@
 
-Figure 1a shows the phantom used for a simulated image with dimensions
-of \(250\times 250\) pixels to illustrate the differences between
-heterogeneous (dark, \(\alpha=-2\)) and homogeneous (light,
-\(\alpha=-10\)) regions, with \(L = 5\). The areas are formed by
-independent draws from the \(G^0_I\) distribution.
+Figure~\ref{fig:sim_SAR_Images}(a) shows the phantom used for a
+simulated image with dimensions of \(250\times 250\) pixels to
+illustrate the differences between heterogeneous (dark, \(\alpha=-2\))
+and homogeneous (light, \(\alpha=-10\)) regions, with \(L = 5\). The
+areas are formed by independent draws from the \(G^0_I\) distribution.
 
@@
 
-We applied the proposed test statistics in actual SAR images acquired
-over cities, including Flevoland, Netherlands and Ottawa, Canada.\\
-These images were captured by the Sentinel-1A satellite operating in the
-C band, with VV polarization, intensity format, and \(L=5\) nominal
-looks. Both images have dimensions of \(512 \times 512\) pixels and
-contain urban areas, water forest regions, as shown in
+We assessed the proposed test statistics using two real SAR images. For
+our analysis, we selected images of the city of Frankfurt, Germany, and
+Ottawa, Canada. These images were acquired by the Sentinel-1A satellite
+operating in the C band, with VV polarization, intensity format, and
+\(L=5\) nominal looks.
+
+Both images have dimensions of \(512 \times 512\) pixels and contain
+urban areas, water and forest regions, as shown in
 Figures~\ref{fig:real_SAR_Images_coe}(a)-(b).
@@
 
-\caption{Results of applying the test statistics, Frankfurt.
-(a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\text{CV}_{\text{MnAD}}$ test; }\label{fig:sim_SAR_Images_Frankfurt}
+\caption{Results of applying the test statistics in Frankfurt image.
+(a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\text{CV}_{\text{MnAD}}$ test.
+}\label{fig:sim_SAR_Images_Frankfurt}
 \end{figure}
@@
 
-\caption{Results of tests on simulated data with a threshold of $0.1$ of the $p$-value, Frankfurt.
+\caption{Test results with a threshold of $0.1$ of the $p$-value for the Frankfurt image.
 (a) Entropy-based test; (b) CV test; (c) $\text{CV}_{\text{MnAD}}$ test.}\label{fig:sim_SAR_Images_01Frankfurt}
@@
 
-\caption{Results of applying the test statistics, Ottawa.
-(a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\text{CV}_{\text{MnAD}}$ test; }\label{fig:sim_SAR_Images_Ottawa}
+\caption{Results of applying the test statistics in Ottawa image.
+(a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\text{CV}_{\text{MnAD}}$ test.}\label{fig:sim_SAR_Images_Ottawa}
 \end{figure}
@@
 
-\caption{Results of tests on simulated data with a threshold of $0.1$ of the $p$-value, Ottawa.
-(a) Entropy-based test; (b) CV test; (c) $\text{CV}_{\text{MnAD}}$ test.}\label{fig:sim_SAR_Images_01_Ottawa}
+\caption{Test results with a threshold of $0.1$ of the $p$-value for the Ottawa image. (a) Entropy-based test; (b) CV test; (c) $\text{CV}_{\text{MnAD}}$ test.}\label{fig:sim_SAR_Images_01_Ottawa}
 \end{figure}

### 2024-04-05 Text/Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics.tex
Review (part-1)

@@
 % Abstract (Do not insert blank lines, i.e. \\)
-\abstract{This paper presents a statistical approach to identify the
-underlying roughness characteristics in synthetic aperture radar (SAR)
-intensity data. The physical modeling of this kind of data allows to use
-the Gamma distribution in the presence of fully-developed speckle, i.e.,
-when there are infinitely many independent backscatterers per resolution
-cell. This situation is often called ``homogeneous'' or ``textureless''
-areas. The \(\mathcal{G}_I^0\) distribution is also a widely accepted
-law for heterogeneous and extremely heterogeneous areas. We propose
-three test statistics for discriminating between homogeneous and
-non-homogeneous areas, i.e., between Gamma and GI0 distributed data,
-both with a known number of looks. The first test statistic utilizes a
-bootstrapped non-parametric estimator of the Shannon entropy, offering a
-robust evaluation in the face of uncertain distributional assumptions.
-The second test uses the classic coefficient of variation. The third
-test employs an alternative form of estimating the CV based on the ratio
-of the mean absolute deviation from the median to the median. We apply
-our test statistic to produce maps of \(p\)-values for the hypothesis of
-homogeneity. These maps identify different types of targets. We show
-that our proposal outperforms its competitors using simulated and SAR
-data.}
+\abstract{
+This paper presents a statistical approach to identify the underlying roughness properties in synthetic aperture radar (SAR) intensity data. 
+The physical modeling of this type of data allows the use of the gamma distribution in the presence of fully developed speckle, i.e.
+when there are infinitely many independent backscatters per resolution cell.
+This situation is often referred to as ``homogeneous'' or ``textureless'' regions.
+The \(\mathcal{G}_I^0\) distribution is also a widely accepted law for heterogeneous and extremely heterogeneous regions. 
+We propose three test statistics to distinguish between homogeneous and inhomogeneous regions, i.e. between gamma and \(\mathcal{G}_I^0\) distributed data, both with a known number of looks. 
+The first test statistic uses a bootstrapped nonparametric estimator of Shannon entropy, which provides a robust assessment in the face of uncertain distributional assumptions.
+The second test uses the classical coefficient of variation. 
+The third test uses an alternative form of estimating the CV based on the ratio of the mean absolute deviation from the median to the median. 
+We apply our test statistic to create maps of \(p\) values for the hypothesis of homogeneity. These maps identify different types of targets. 
+We show that our proposal outperforms its competitors using simulated and SAR data.}
 
@@
 
-Synthetic Aperture Radar (SAR) technology has become an important tool
-for environmental monitoring and disaster management, providing valuable
-imagery in different conditions, including day or night and diverse
-weather situations~\cite{Moreira2013,Mu2019}. However, the effective
-utilization of SAR data depends on a thorough understanding of its
-statistical properties, especially the impact of speckle effects, which
-are inherent in SAR data due to the coherent nature of the imaging
-process~\cite{Argenti2013}.
+Synthetic Aperture Radar (SAR) technology has become an important tool for environmental monitoring and disaster management.
+It provides valuable images under various conditions, including day or night and different weather situations~\cite{Moreira2013,Mu2019}.
+However, the effective use of SAR data depends on a thorough understanding of its statistical properties, especially the impact of speckle effects inherent in SAR data due to the coherent nature of the imaging process~\cite{Argenti2013}.
 
-In the presence of non-Gaussian speckle interference, SAR data requires
-a reliable statistical model for accurate processing. The
-\(\mathcal{G}^0\) distribution, suitable for SAR data, includes the
-Gamma law as a limit case for fully developed
-speckle~\cite{Ferreira2020}, providing flexibility with fewer parameters
-for analysis.
+In the presence of non-Gaussian speckle interference, SAR data requires a reliable statistical model for accurate processing. The
+\(\mathcal{G}^0\) distribution, which is suitable for SAR data, includes the
+Gamma law as the limiting case for fully developed speckle~\cite{Ferreira2020} and provides flexibility with fewer parameters for analysis.
 
-Our work is motivated to improve the identification of potential
-roughness features in SAR intensity data. Physical modeling of SAR data
-allows to take advantage of the gamma distribution in the presence of
-fully developed speckle, creating a scenario with an infinite number of
-independent backscatterers per unit of resolution, often referred to as
-homogeneous areas.
+Our work aims to improve the identification of potential roughness features in SAR intensity data.
+Physical modeling of SAR data allows to take advantage of the gamma distribution in the presence of fully developed speckles and to create a scenario with an infinite number of independent backscatterers per resolution unit, often referred to as homogeneous regions.
 
-In this context, we present a set of three novel test statistics
-designed to discriminate between homogeneous and non-homogeneous areas,
-specifically aimed at differentiating between Gamma and
-\(\mathcal{G}^0\) distributed data, each with a known number of
-appearances. Hence, to understand the core ideas behind our approach, we
-explore into the use of properties such as entropy and coefficient of
-variation.
+In this context, we present a set of three novel test statistics that aim to distinguish between homogeneous and non-homogeneous domains, in particular between gamma and
+\(\mathcal{G}^0\) distributed data, each with a known number of looks. To understand the core ideas behind our approach, we explore the use of properties such as entropy and coefficient of variation.
 
-The entropy is a fundamental concept in information theory with broad
-applications to pattern recognition, statistical physics, stochastic
-dynamics, and statistics. Shannon introduced it for a random variable in
-1948~\cite{Shannon1948} as a measure of information and uncertainty.\\
-In statistics, Shannon entropy is a crucial descriptive parameter,
-particularly for assessing data dispersion and conducting tests for
-normality, exponentiality, and
-uniformity~\cite{Wieczorkowski1999,Zamanzade2012}. Entropy estimation
-involves several practical difficulties, especially when the model is
-unknown; in these cases, non-parametric methods are used.
+Entropy is a fundamental concept in information theory with far-reaching applications in pattern recognition, statistical physics, stochastic dynamics and statistics.
+Shannon introduced it in 1948~\cite{Shannon1948} for a random variable as a measure of information and uncertainty.\\
+In statistics, Shannon entropy is a crucial descriptive parameter, especially for evaluating data dispersion and performing tests for normality, exponentiality and uniformity~\cite{Wieczorkowski1999,Zamanzade2012}.
+Entropy estimation is associated with some practical difficulties, especially when the model is unknown.
+In these cases, non-parametric methods are used.
+Spacing methods have been discussed as a non-parametric approach in~\cite{AlizadehNoughabi2010,Subhash2021}.
+This strategy provides the flexibility to consider a wide range of models without enforcing certain parametric constraints.
 
-Spacing methods have been discussed as a non-parametric approach
-in~\cite{AlizadehNoughabi2010,Subhash2021}. This strategy offers
-flexibility to address a wide range of models without imposing specific
-parametric restrictions.
+The coefficient of variation (CV), introduced in 1896 by Pearson~\cite{Pearson1896}, is a relative dispersion measure widely used in various fields of applied statistics, including sampling, biostatistics, medical and biological research, climatology and other fields
+\cite{hendricks1936sampling, Tian2005,SubrahmanyaNairy2003,Chankham2024}.
+It facilitates the comparison of variability between different populations and is particularly valuable for comparing variables with different units.
+This is because when the main purpose is to compare the variations of several variables, the standard deviation can only serve as an adequate measure of variation if all variables are expressed in the same unit of measurement and have identical means.
+If these conditions are not met for the variables under investigation, the CV is the relative measure that is usually used in real applications.
+The variable with the highest CV value is the one with the largest relative dispersion around the mean value~\cite{Banik2011}.
 
-In our study, entropy serves as the fundamental parameter, providing a
-robust assessment by means of a bootstrapped non-parametric estimator of
+In our study, entropy serves as a fundamental parameter that allows a robust evaluation using a bootstrapped nonparametric estimator of the
 Shannon entropy.
-
-Simultaneously, we use the classic coefficient of variation (CV) and an
-alternative form based on the ratio between the median absolute
-deviation and the median. The CV is known as an efficient and robust
-index of textural information, measures the homogeneity of the
-image~\cite{Lopes1990}.
-
-The CV, introduced by Pearson~\cite{Pearson1896} in 1896, is a relative
-measure of dispersion widely used in various areas of applied statistics
-including sampling, biostatistics, medical and biological research,
-climatology, and other fields
-\cite{hendricks1936sampling, Tian2005,SubrahmanyaNairy2003,Chankham2024}.
-It facilitates the comparison of variability between different
-populations and is especially valuable for comparing variables with
-different units. This is because when the main purpose is to compare
-variations of several variables, the standard deviation cannot serve as
-an adequate measure of variation unless all variables are expressed in
-the same unit of measurement and have identical mean values. When these
-requirements are not hold for the variables under study, CV is the
-relative measure typically used in real applications. The variable with
-the highest CV value is the one with the highest relative dispersion
-around the mean~\cite{Banik2011}.
-
-Applying these test statistics to generate \(p\)-value maps facilitates
-testing of the homogeneity hypothesis, revealing diverse types of
-targets within the SAR data. Through extensive experimentation involving
-real and simulated SAR data, we demonstrate the superiority of our
-proposed methodology over existing approaches.
+At the same time, we use the classical CV and an alternative form based on the ratio between the median absolute deviation and the median. 
+The CV is known as an efficient and robust index for texture information and measures the homogeneity of the image~\cite{Lopes1990}.
+Applying these test statistics to generate maps of \(p\) values facilitates testing the homogeneity hypothesis and reveals different types of targets in the SAR data. 
+Through extensive experiments with real and simulated SAR data, we demonstrate the superiority of our proposed method over existing approaches.
 
 The article is structured as follows: Section~\ref{sec:Background}
-covers statistical modeling and entropy estimation for Intensity SAR
-data. Section~\ref{sec:test} outlines hypothesis testing based on
-non-parametric entropy estimators and and coefficient of variation. In
-Section~\ref{sec:Results}, we present experimental results. Finally, in
-Section~\ref{sec:conclusion} conclusions are exhibited.
+deals with statistical modeling and entropy estimation for intensity SAR
+data. Section~\ref{sec:test} outlines hypothesis tests based on nonparametric entropy estimators and coefficients of variation. In
+Section~\ref{sec:Results} we present experimental results. Finally, in
+Section~\ref{sec:conclusion} the conclusions are presented.
 
@@
 
-The primary models used for intensity SAR data include the Gamma and
-\(\mathcal{G}_I^0\) distributions~\citep{Frery1997}. The first is
-suitable for fully developed speckle and is a limiting case of the
-second, which is appealing due to its versatility in accurately
-representing regions with various roughness
-characteristics~\citep{Cassetti2022}. We denote
+The primary models used for SAR intensity data include the gamma and the
+\(\mathcal{G}_I^0\) distributions~\citep{Frery1997}.
+The first model is suitable for fully developed speckle and is a limiting case of the second model, which is interesting due to its versatility in accurately representing regions with different roughness properties~\citep{Cassetti2022}.
+We denote
 \(Z \sim \Gamma_{\text{SAR}}(L, \mu)\) and
@@
 distributions characterized by the respective probability density
-functions: \begin{align}
-    f_Z(z;L, \mu)&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gamma1}\\
+functions (pdfs): 
+\begin{align}
+    f_Z(z;L, \mu)&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z)\label{E:gamma1}\\
+    \intertext{ and }
     f_Z(z; \alpha, \gamma, L)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
-\end{align} where, in~\eqref{E:gamma1} \(\mu > 0\) is the mean;
-in~\eqref{E:gi01} \(\gamma > 0\) is the scale, \(\alpha < -1\) measures
+\end{align} 
+where \(\mu > 0\) is the mean, \(\gamma > 0\) is the scale, \(\alpha < -1\) measures
 the roughness, \(L \geq 1\) is the number of looks, \(\Gamma(\cdot)\) is
@@
 
-From \eqref{E:gi01}, the \(r\)th moment of \(Z\) is expressed as:
+If we take the law with the density~\eqref{E:gi01}, the \(r\)th non-central moment of \(Z\) is expressed as follows:
 \begin{align}
-    E_{G_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\gamma(L)}, \quad \alpha <-r. 
+    E_{G_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\Gamma(L)}, \quad \alpha <-r. 
     \label{E:rmom}
@@
 
-Even though the \(\mathcal{G}_I^0\) distribution is defined by the
-parameters \(\alpha\) and \(\gamma\), SAR literature commonly utilizes
-the texture \(\alpha\) and the mean \(\mu\)~\cite{Nascimento2010}. In
-this way, we compute the expected value \(\mu\) using the expression
-in~\eqref{E:rmom}, and we reparametrize~\eqref{E:gi01} using \(\mu\),
-\(\alpha\), and \(L\). Then \begin{align*}
+Although the \(\mathcal{G}_I^0\) distribution is defined by the parameters \(\alpha\) and \(\gamma\), in the SAR literature~\cite{Nascimento2010} the texture \(\alpha\) and the mean \(\mu\) are usually used.
+In this way, we calculate the expected value \(\mu\) using the expression in~\eqref{E:rmom}, and we reparametrize~\eqref{E:gi01} with \(\mu\),
+\(\alpha\), and \(L\).
+Then \begin{align*}
     \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
-\end{align*} Thus, the probability density function that characterize
-the \(G_I^0(\mu, \alpha, L)\) law is \begin{equation}
-        f_Z(z; \mu, \alpha, L)=\frac{L^L\Gamma(L-\alpha)}{\big(-\mu(\alpha+1)\big)^{\alpha}\Gamma(-\alpha)\Gamma(L)} \frac{z^{L-1}}{\big(-\mu(\alpha+1)+Lz\big)^{L-\alpha}}.\label{E:gi02}
+\end{align*} 
+The reparametrized pdf that characterizes the law \(G_I^0(\mu, \alpha, L)\) is thus
+\begin{equation}
+        f_Z(z; \mu, \alpha, L)=\frac{L^L\Gamma(L-\alpha)}{\big[-\mu(\alpha+1)\big]^{\alpha}\Gamma(-\alpha)\Gamma(L)} \frac{z^{L-1}}{\big[-\mu(\alpha+1)+Lz\big]^{L-\alpha}}.\label{E:gi02}
 \end{equation}
@@
 
-The parametric representation of Shannon entropy for a system described
-by a continuous random variable is: \begin{equation}
+The parametric representation of the Shannon entropy for a system described by a continuous random variable is:
+\begin{equation}
   \label{E:entropy2}
   H(Z)=-\int_{-\infty }^\infty \ f(z)\ln f(z)\, \mathrm{d}z,
-\end{equation} here, \(f(\cdot)\) is the probability density function
+\end{equation} 
+here, \(f(\cdot)\) is the pdf
 that characterizes the distribution of the real-valued random variable
@@
 \end{multline} where \(\psi^{(0)}(\cdot)\) is the digamma function.
-Figure~\ref{fig:Plot_GI0_to_gamma1}, shows the behaviour of the entropy
-of \(G_I^0\) when when
-\(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), observing its
-convergence towards the entropy of \(\Gamma_{\text{SAR}}\) as \(\alpha\)
-takes large negative values.
+Figure~\ref{fig:Plot_GI0_to_gamma1}, shows the behavior of the entropy of \(G_I^0\) when
+\(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), where the approximation to the entropy of \(\Gamma_{\text{SAR}}\) can be observed when \(\alpha\)
+assumes large negative values.
+In an interpretative sense, we can conclude that the more heterogeneous (high values of $\alpha$) the SAR region is, the higher the value of entropy (or degree of disorder).
+It is worth noting that this conclusion confirms what is written in the SAR literature.
 
@@
 
-The problem of non-parametric estimating of \(H(Z)\) has been considered
-by many authors
-including~\cite{vasicek1976test, Wieczorkowski1999,correa1995new,AlOmari2019},
-who proposed estimators based on spacings.
+The problem of non-parametric estimation of \(H(Z)\) has been considered by many authors, including~\cite{vasicek1976test, Wieczorkowski1999,correa1995new,AlOmari2019},
+who have proposed estimators based on spacings.
 
-One of the earliest non-parametric estimators relying on spacings was
-introduced by Vasicek~\cite{vasicek1976test}. Assuming that
-\(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) is a random sample from the
-distribution \(F(z)\), the estimator is defined as: \begin{equation*}
+One of the first non-parametric estimators based on spacings was introduced by Vasicek~\cite{vasicek1976test}. Under the assumption that
+\(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) is a random sample from the distribution \(F(z)\), the estimator is defined as:
+\begin{equation*}
 \label{E:Vas}
@@
 
-Several authors have explored adaptations to Vasicek's estimator. We
-consider three estimators known for their superior
-performance~\cite{Cassetti2022}:
-
-\begin{itemize}
-\item
-  Correa~\cite{correa1995new}: \(\widehat{H}_{\text{C}}\).
-\item
-  Ebrahimi et al~\cite{Ebrahimi1994}: \(\widehat{H}_{\mathrm{E}}\).
-\item
-  Al Omary~\cite{IbrahimAlOmari2014}: \(\widehat{H}_{\mathrm{AO}}\).
-\end{itemize}
+Several authors have explored adaptations to Vasicek's estimator. 
+We consider three estimators known for their superior performance~\cite{Cassetti2022}:
+Correa~\cite{correa1995new}, \(\widehat{H}_{\text{C}}\);
+Ebrahimi et al~\cite{Ebrahimi1994}, \(\widehat{H}_{\mathrm{E}}\);
+and Al Omary~\cite{IbrahimAlOmari2014}, \(\widehat{H}_{\mathrm{AO}}\).
 
@@
 
-We employ the bootstrap technique to refine the precision of existing
-non-parametric entropy estimators. This approach involves generating new
-datasets through resampling with repetition from an existing
-one~\cite{Michelucci2021}.
+We use the bootstrap technique to refine the accuracy of existing nonparametric entropy estimators.
+In this approach, new data sets are generated by replicate sampling from an existing data set~\cite{Michelucci2021}.
 
-Let's assume that non-parametric entropy estimators
-\(\widehat{H}=\widehat{\theta}(\bm{Z})\) are inherently biased, that is:
-\begin{equation}
+Let us assume that non-parametric entropy estimators
+\(\widehat{H}=\widehat{\theta}(\bm{Z})\) are inherently biased, i.e:\begin{equation}
 \label{Eq:bias1}
@@
 \widetilde{H} &= 2\widehat{\theta}(\bm{Z}) - \frac{1}{B}\sum_{b=1}^B \widehat{\theta}_b(\bm{Z}^{(b)}),
-\end{align*} where \(B\) is the number of replications in the bootstrap
-technique. Applying this methodology, the original estimators by Correa,
-Ebrahimi, and Al-Omari are now denoted as the proposed
-bootstrap-enhanced versions: \(\widetilde{H}_{\text{C}}\),
+\end{align*} 
+where \(B\) is the number of replications in the bootstrap
+technique. 
+Applying this methodology, the original estimators of Correa,
+Ebrahimi and Al-Omari are now referred to as the proposed bootstrap-enhanced versions:
+\(\widetilde{H}_{\text{C}}\),
 \(\widetilde{H}_{\text{E}}\), and \(\widetilde{H}_{\text{AO}}\),
@@
 
-We analyzed the performance of these estimators with a Monte Carlo
-study: \(500\) samples of \(G_I^0\) of size
-\(n\in\left\{9, 25, 49, 81, 121\right\}\) and several values of the
-mean, number of looks and roughness. We present the results with
-\(mu\in\left\{1, 10\right\}\), \(\alpha=-10\), and \(L=5\). The results
-are consistent for the other situations. In the case of the bootstrap
-technique, each sample is replicated \(100\) times with replacement. We
-choose to use the following heuristic formula for spacing,
+We analyzed the performance of these estimators with a Monte Carlo study: \(500\) samples of \(G_I^0\) of size
+\(n\in\left\{9, 25, 49, 81, 121\right\}\) and different values for mean, number of looks and roughness. We present the results with
+\(\mu\in\left\{1, 10\right\}\), \(\alpha=-10\) and \(L=5\).
+The results are also adherent for the other situations.
+In the bootstrap technique, each sample is replicated a hundred times with replacement.
+We use the following heuristic formula for spacing,
 \(m=\left[\sqrt{n}+0.5\right]\).
 
-In Figure~\ref{fig:Plot_bias_mse_gi0} we depict comparisons of bias and
-mean squared error (MSE) between the original non-parametric entropy
-estimators and their respective bootstrap-enhanced versions. The use of
-the bootstrap technique exhibits more precision, reduced bias and MSE,
-and improved convergence. The results of simulation are exhibited in
+In Figure~\ref{fig:Plot_bias_mse_gi0} we show comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions.
+The use of the bootstrap technique shows higher precision, lower bias and MSE, and improved convergence.
+The results of the simulation can be found in
 Table~\ref{tab:table2}.
 
-The precision of estimators, as evidenced by bias and MSE comparisons,
-benefits significantly from the bootstrap technique, particularly for
-sample sizes below 81.
+The precision of the estimators resulting from the comparison of bias and MSE benefits significantly from the bootstrap technique, especially for sample sizes below 81.
 
@@
 
-The population CV is defined as a ratio of the population standard
-deviation \((\sigma)\) to the population mean \((\mu)\):
+The population CV is defined as the ratio of the population standard deviation \((\sigma)\) to the population mean \((\mu)\):
 
 \begin{align}
-    \text{CV}=\frac{\sigma}{\mu}, \quad \mu \neq 0.
+    \text{CV}=\frac{\sigma}{\mu}, \quad \text{ for }\mu \neq 0.
 \end{align}
 
-We explore a robust alternative to the CV as discussed in
-\cite{Ospina2019}, involving the ratio of the mean absolute deviation
-from the median (MnAD) to the median, two well-known robust measures of
-scale and location, respectively. The MnAD is defined as
+We explore a robust alternative to CV, as described in
+\cite{Ospina2019}, which incorporates the ratio between the mean absolute deviation from the median (MnAD) and the median, two well-known robust measures of
+scale and location, respectively. The sample version for the MnAD is defined as
 \(n^{-1}\sum_{i=1}^n|x_i-\widehat{Q}_2|\), where \(\widehat{Q}_2\)
-represents an estimate of the population median, which can be
-approximated by the sample median.
+is an estimate for the median of the population, which can be approximated by the median of the sample.
 
@@
 We aim at testing the following hypotheses:
-
 \[
@@
   \mathcal{H}_1:\text{ The data comes from the } G_I^0.\end{cases}
-\] In other words, we verify the hypothesis that the data are
-fully-developed speckle. The proposed tests are described below.
+\] 
+In the physical sense, we are testing the hypothesis that the data are fully developed speckle.
+As for the parametric problem, once it is not possible to define the hypothesis $\mathcal{H}_0=\alpha=-\infty$, it is impossible to solve this problem with the parametric statistical inference alternatives (such as likelihood ratio, score, grandient and Wald hypothesis test).
+The proposed tests to solve this physical problem in SAR systems are described below.
 
@@
 
-The first test statistic assess the behavior of the data under the null
-hypothesis, through the empirical distribution. \begin{equation}
-\label{Eq:test_e}
+The first test statistic evaluates the behavior of the data under the null hypothesis using the empirical distribution: 
+\begin{equation}\label{Eq:test_e}
 S_H= \widetilde{H}-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \overline{Z}\right].
-\end{equation} The values should be around zero under the null
-hypothesis and far otherwise.
+\end{equation} 
+The values should be zero under the null hypothesis and otherwise far from it.
 
-Figure~\ref{fig:Plot_density} depicts empirical test statistic densities
-for various sample sizes, and Table~\ref{tab:table_stat_combined}
-summarizes key statistics, including mean, SD, variance (Var), skewness
-(SK), excess kurtosis (EK), and Anderson--Darling \(p\)-values for
-normality. Results with \(p\)-values larger than \(0.05\) indicate no
-evidence against normality. Small variance and near-zero skewness and
-excess kurtosis suggest limited spread, symmetry, and light tails.\\
-Normal QQ-plots, confirm that there is no evidence to reject the normal
-distribution.
+Figure~\ref{fig:Plot_density} shows the empirical test statistic densities for different sample sizes, and Table~\ref{tab:table_stat_combined}
+summarizes the main descriptive statistics, including mean, SD, variance (Var), skewness
+(SK), excessive kurtosis (EK) and Anderson--Darling \(p\) values for normality.
+Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption.
+A low variance as well as a skewness and an excessive kurtosis of almost zero indicate limited dispersion, symmetry and a slight tail.\\
+Normal QQ plots confirm that there is no evidence against a normal distribution.
 
@@
 
-After verifying the normality of the data, we proceeded to explore the
-capabilities of the proposed test in terms of size and power. Under
-\(\mathcal{H}_0\), the distribution of test statistic is asymptotically
-normal. Therefore, the \(p\)-value is calculated as
+After checking the normality of the data, we examined the possibilities of the proposed test in terms of size and power.
+Under \(\mathcal{H}_0\), the distribution of the test statistic is asymptotically normal.
+Therefore, the \(p\) value is calculated as
 \(2\Phi(-\mid \varepsilon\mid)\), where \(\Phi\) is the standard
-Gaussian cumulative distribution and \(\varepsilon\) is the standardized
-test statistic given by: \[
+Gaussian cumulative distribution and \(\varepsilon\) is the standardized test statistic given by :
+\[
 \varepsilon=\frac{\tilde{H}-H_{\Gamma_{\text{SAR}}}}{\hat\sigma}.
@@
 
-We considered nominal levels of \SI{1}{\percent}, \SI{5}{\percent}, and
-\SI{10}{\percent}. In reference to the size, \(1000\) simulations have
-been used for various sample sizes with satisfactory results. In all
-cases, the nominal level has been achieved. The power, in general,
-improves with the increase in the sample size and the number of looks.
-The results are presented in Table~\ref{tab:table_size_power}.
+We have nominal levels of \SI{1}{\ percent}, \SI{5}{\ percent}, and
+\SI{10}{\percent}. 
+In terms of size, \(1000\) simulations were used for different sample sizes with satisfactory results. 
+In all cases, the nominal level was achieved. 
+The power generally improves with increasing sample size and number of looks.
+The results are shown in Table~\ref{tab:table_size_power}.
 
@@
 In addition to the entropy-based test, we also propose a test statistic
-based on the classical CV. This test statistic is defined as follows:
+based on the classical CV. 
+This test statistic is defined as follows:
 \begin{align}
     T_{\text{CV}}=\frac{S}{\overline{Z}},
-\end{align} where \(S\) and \(\overline{Z}\) are the sample standard
-deviation and the sample mean, respectively.
+\end{align} 
+where \(S\) and \(\overline{Z}\) are the sample standard deviation and the sample mean, respectively.
 
-Similarly, we use another test statistic based on the ratio of the MnAD
-to the median. This statistic is given by: \begin{align}
+Similarly, we use another test statistic based on the ratio between the MnAD and the median.
+This statistic is given by:
+\begin{align}
     T_{\text{CV}_{\text{MnAD}}}=\frac{\text{MnAD}}{\text{Median}}.
@@
 
-The situations where the use of CV and \(\text{CV}_{\text{MnAD}}\) may
-be appropriate, i.e.~where the observations are positive, the log-normal
-(LN) and inverse Gaussian (IG) distribution are often more justified
-compared to Gamma and Weibull distributions
+The situations in which the use of CV and \(\text{CV}_{\text{MnAD}}\) may be appropriate, i.e.~when the observations are positive, the log-normal
+(LN) and the inverse Gaussian distribution (IG) are often more appropriate than the Gamma and Weibull distributions
 \cite{Chaubey2017,takagi1997application}.
 
-The inverse Gaussian distribution is shown to be well approximated by
-the log-normal distribution \cite{whitmore1978} which implies that the
-IG distribution also does not share the problem of non-existence of
-fixed width confidence interval with the Gaussian case.
+It is shown that the IG distribution is well approximated by the log-normal distribution, which means that the
+IG distribution also does not share the problem of the non-existence of a fixed-width confidence interval with the Gaussian case \cite{whitmore1978}.
 
 The LN distribution in two parameters has the following density
-function. \begin{align}
-    f_Z(z;\mu, \sigma )=\frac{1}{\sigma z\sqrt{2\pi}}\exp\left\{-\frac{(\ln z- \mu)^2}{2\sigma^2}\right\}, \quad z>0, \sigma>0, -\infty < \mu < \infty,
-\end{align} here, \(\mu\) is the log-scale parameter and \(\sigma\) is
+function. 
+\begin{align}
+    f_Z(z;\mu_{\text{LN}}, \sigma )=\frac{1}{\sigma z\sqrt{2\pi}}\exp\left\{-\frac{(\ln z- \mu_{\text{LN}})^2}{2\sigma^2}\right\}\mathbbm 1_{\mathbbm R_+}(z),
+\end{align} here, $\sigma>0$, $-\infty < \mu_{\text{LN}} < \infty$, \(\mu\) is the log-scale parameter and \(\sigma\) is
 the shape parameter.
+
+\vskip+1ex
+{\color{red} ADCN: Fiz uma diferen\c{c}a entre as nota\c{c}\~oes para m\'edia da G0I e da LN. Por favor, verifique se faz sentido, isto \'e se ela n\~ao \'e encaixada a G0I neste contexto.}
+\vskip+1ex
 
@@
 Tables~\ref{tab:table_aic_gamma}-\ref{tab:table_aic_gio_MnADmedian}
-indicate that the CV and \(\text{CV}_{\text{MnAD}}\) data from different
-synthetic sample sizes, extracted from the Gamma SAR and \(G_I^0\)
-distributions, respectively, adhere to the characteristics of an LN
-distribution. The AIC and BIC values of the IG distribution and the LN
-distribution are not significantly different because both distributions
-are based on the right-skewed characteristic. In this situation, the
-model for the LN distribution was considered to be the best due to it
-providing the lowest AIC and BIC values.
+indicate that the CV and \(\text{CV}_{\text{MnAD}}\) data from different distributed gamma and \(G_I^0\) synthetic sample sizes match the properties of an LN distribution.
+{\color{green}
+It is important to note that this conclusion was drawn empirically based on a dictionary of distributions that are anlaytically tractable and well-defined under biparametric, unimodal, asymmetric, and positive distributions.
+}
+\vskip+1ex
+{\color{red} ADCN: 
+Caros, esse \'e o ponto mais delicado da excelente ideia desse paper em minha opini\~ao.
+N\~ao me oponho a colocarmos a lognormal como uma possibilidade, mas \'e preciso deixar claro que \'e uma possibilidade emp\'irica.
+Uma alternativa empirica para uma solu\c{c}\~ao do momento usando distribui\c{c}\~oes mais densenvolvidas na literatura e que sejam analiticamente trat\'aveis.
+Estou pensando corretamente?
+Se sim, por que n\~ao log-t-student, log-Laplace, power exponential, Log-hyperbolic,....
+(e a lista segue).
+Sugiro talvez indicar (i) a dedu\c{c}\~ao da distribui\c{c}\~ao assint\'otica das estat\'isticas em fun\c{c}\~ao de CV e MNAD dando com entrada G0I ($\mathcal{H}_1$) e a Gamma ($\mathcal{H}_0$) como trabalho futuro.
+Do que eu entendi, a suposi\c{c}\~ao da normal assint\'otica para entropia vem de uma cole\c{c}\~ao de trabalhos te\'oricos.
+J\'a a LN, do que percebi, n\~ao.
+Coloquei um coment\'ario em verde. Vejam se est\~ao de acordo.
+}
+\vskip+1ex
+The AIC and BIC values of the IG distribution and the LN distribution are not significantly different, as both distributions are based on the right-skewed characteristic.
+In this situation, the model for the LN distribution was considered the best, as it has the lowest AIC and BIC values.
 
-Figures~\ref{fig:Plot_cv}-\ref{fig:Plot_madmed_gi0_MnADmedian} present
-density plots, Q-Q plots, P-P plots, and Cumulative Distribution
-Function plots, which offer an additional measure of goodness-of-fit and
-confirm that the most suitable distribution to be considered is the LN
-distribution.
+Figures~\ref{fig:Plot_cv}-\ref{fig:Plot_madmed_gi0_MnADmedian} show empirical and fitted density plots, Q-Q plots, P-P plots as well as empirical and fitted cumulative distribution functions.
+They provide qualitative sources that confirm that the LN distribution is the most appropriate distribution.
 
@@
 
-This section presents simulations performed to obtain an assessment of
-the performances of the proposed test statistics.
+This section presents simulations that were performed to obtain an evaluation of the performance of the proposed test statistics.
 
@@
 
-Figure~\ref{fig:sim_SAR_Images}(a) shows the phantom used for a
-simulated image with dimensions of \(250\times 250\) pixels to
-illustrate the differences between heterogeneous (dark, \(\alpha=-2\))
-and homogeneous (light, \(\alpha=-10\)) regions, with \(L = 5\). The
-areas are formed by independent draws from the \(G^0_I\) distribution.
+Figure~\ref{fig:sim_SAR_Images}(a) shows the phantom used for a simulated image with dimensions of \(250\times 250\) pixels to show the differences between heterogeneous (dark, \(\alpha=-2\))
+and homogeneous (light, \(\alpha=-10\)) regions, with \(L = 5\). 
+The regions are formed by independent draws from the \(G^0_I\) distribution.
 
@@
 Figures~\ref{fig:sim_SAR_Images}(b)-(d) and
-Figures~\ref{fig:sim_SAR_Images_p05}(a)-(c), respectively. The new
-images reveal that a darker background indicates homogeneity, while
-lighter backgrounds represent heterogeneous areas.
+Figures~\ref{fig:sim_SAR_Images_p05}(a)-(c), respectively. 
+The new images reveal that a darker background indicates homogeneity, while lighter backgrounds represent heterogeneous areas.
 
@@
 
-We assessed the proposed test statistics using two real SAR images. For
-our analysis, we selected images of the city of Frankfurt, Germany, and
-Ottawa, Canada. These images were acquired by the Sentinel-1A satellite
-operating in the C band, with VV polarization, intensity format, and
+We evaluated the proposed test statistic using two real SAR images. 
+For our analysis, we used images of the city of Frankfurt, Germany, and of
+Ottawa, Canada. 
+These images were acquired by the Sentinel-1A satellite operating in C-band, with VV polarization, intensity format and
 \(L=5\) nominal looks.
-
-Both images have dimensions of \(512 \times 512\) pixels and contain
-urban areas, water and forest regions, as shown in
+Both images have a size of \(512 \times 512\) pixels and contain urban areas, water and forest regions, as shown in
 Figures~\ref{fig:real_SAR_Images_coe}(a)-(b).
@@
 respectively.
+
+In general, using the original and robust CV is more meaningful than using Shannon entropy to capture texturelessness.
+It is justified that the dark areas of the maps based on the $\text{CV}$ and $\text{CV}_{\text{MnAD}}$ tests cover the areas reported for the Shannon entropy-based map.
+Both CV-based tools predicted textureless regions as well as boundaries where the statistical properties of texture vary.
+Assuming $10\%$ as the threshold for the $p$ values, the dark region produced by the $\text{CV}$ test was higher than that produced by the $\text{CV}_{\text{MnAD}}$ and entropy test.
+The latter observation is to be expected as the latter tests are robust alternatives to the former test, which is essentially based on the expected value operator that reacts to outliers.
 
@@
 
-In this article,\ldots{}
+In this article, we have provided a practical and theoretical answer to the following physical question: How to detect texturelessness in SAR images, assuming that the SAR intensity follows the $\mathcal{G}^0_I$ distribution.
+Solving this problem is not easy, considering that the texturelessness in the parametric space of $\mathcal{G}^0_I$ means the infinity value, which is neither analitically tractable nor practically provable.
+To this end, we have proposed three novel hypothesis tests, one from the Shannon entropy and two others from the variation coefficient variants.
 

### 2024-04-11 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Changes added in Rmd file

@@
   The physical modeling of this kind of data allows to use the Gamma distribution in the presence of fully-developed speckle, i.e., when there are infinitely many independent backscatterers per resolution cell.
-This situation is often called "homogeneous" or
-  "textureless" areas.
-The $\mathcal{G}_I^0$ distribution is also a widely accepted law for heterogeneous and extremely heterogeneous areas.
-We propose three test statistics for discriminating between homogeneous and non-homogeneous areas, i.e., between Gamma and GI0 distributed data, both with a known number of looks.
-The first test statistic utilizes a bootstrapped non-parametric estimator of the Shannon entropy, offering a robust evaluation in the face of uncertain distributional assumptions.
-The second test uses the classic coefficient of variation.
-The third test employs an alternative form of estimating the CV based on the ratio of the mean absolute deviation from the median to the median.
-We apply our test statistic to produce maps of $p$-values for the hypothesis of homogeneity.
-These maps identify different types of targets.
+This situation is often called "homogeneous" or  "textureless" regions.
+  The $\mathcal{G}_I^0$ distribution is also a widely accepted law for heterogeneous and extremely heterogeneous regions.
+We propose three test statistics to distinguish between homogeneous and inhomogeneous regions, i.e.
+between gamma and \(\mathcal{G}_I^0\) distributed data, both with a known number of looks.
+  The first test statistic uses a bootstrapped nonparametric estimator of Shannon entropy, which provides a robust assessment in the face of uncertain distributional assumptions.
+  The second test uses the classical coefficient of variation. 
+  The third test uses an alternative form of estimating the CV based on the ratio of the mean absolute deviation from the median to the median. 
+  We apply our test statistic to create maps of \(p\) values for the hypothesis of homogeneity. These maps identify different types of targets. 
   We show that our proposal outperforms its competitors using simulated and SAR data.
-# back matter
 keywords: |
@@
  This article is fully reproducible using RMarkdown. All code and data are accessible at
- \url{https://github.com/rjaneth/identifying-heterogeneity-in-sar-data-with-new-test-statistics} (accessed on 5 April 2024).
+ \url{https://github.com/rjaneth/identifying-heterogeneity-in-sar-data-with-new-test-statistics} (accessed on 12 April 2024).
 # abbreviations:
@@
    - \usepackage{color}
+   - \usepackage{xcolor}
    - \usepackage{amsmath}
@@
 #appendix: appendix.tex
-endnotes: false
+#endnotes: false
 output:
@@
 #knitr::opts_chunk$set(echo = FALSE)
+library(fitdistrplus)
 library(ggplot2)
@@
 library(nortest)# AD
-library(MASS)#
-library(fitdistrplus)# model selection AIC and BIC
+#library(MASS)#
+# model selection AIC and BIC
 
@@
 )
-
-# if(!require("rstudioapi")) install("rstudioapi")
-# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
-
-# opts_chunk$set(comment="",
-#                message=FALSE,
-#                tidy.opts=list(keep.blank.line=TRUE, width.cutoff=120),
-#                options(width=100), 
-#                # cache=TRUE,
-#                fig.align='center',
-#                fig.height=6, fig.width=10,
-#                fig.show='hold',
-#                cache=TRUE)
 
@@
 
-```{r DefinitionSimulationRoutines, echo=FALSE}
-#set.seed(1234567890, kind="Mersenne-Twister")
-```
-\setlength{\tabcolsep}{6pt} 
 \newcommand{\bias}{\operatorname{Bias}}
@@
 
-Synthetic Aperture Radar (SAR) technology has become an important tool for environmental monitoring and disaster management, providing valuable imagery in different conditions, including day or night and diverse weather situations&nbsp;\cite{Moreira2013,Mu2019}.
-However, the effective utilization of SAR data depends on a thorough understanding of its statistical properties, especially the impact of speckle effects, which are inherent in SAR data due to the coherent nature of the imaging process&nbsp;\cite{Argenti2013}.
+Synthetic Aperture Radar (SAR) technology has become an important tool for environmental monitoring and disaster management.
+It provides valuable images under various conditions, including day or night and different weather situations&nbsp;\cite{Moreira2013,Mu2019}.
+However, the effective use of SAR data depends on a thorough understanding of its statistical properties, especially the impact of speckle effects inherent in SAR data due to the coherent nature of the imaging process&nbsp;\cite{Argenti2013}.
 
 In the presence of non-Gaussian speckle interference, SAR data requires a reliable statistical model for accurate processing. 
-The $\mathcal{G}^0$ distribution, suitable for SAR data, includes the Gamma law as a limit case for fully developed speckle&nbsp;\cite{Ferreira2020}, providing flexibility with fewer parameters for analysis.
-
-Our work is motivated to improve the identification of potential roughness features in SAR intensity data. 
-Physical modeling of SAR data allows to take advantage of the gamma distribution in the presence of fully developed speckle, creating a scenario with an infinite number of independent backscatterers per unit of resolution, often referred to as homogeneous areas.
-
-In this context, we present a set of three novel test statistics designed to discriminate between homogeneous and non-homogeneous areas, specifically aimed at differentiating between Gamma and $\mathcal{G}^0$ distributed data, each with a known number of appearances.
-Hence, to understand the core ideas behind our approach, we explore into the use of properties such as entropy and coefficient of variation.
-
-The entropy is a fundamental concept in information theory with broad applications to pattern recognition, statistical physics, stochastic dynamics, and statistics. 
-Shannon introduced it for a random variable in 1948&nbsp;\cite{Shannon1948} as a measure of information and uncertainty.  
-In statistics, Shannon entropy is a crucial descriptive parameter, particularly for assessing data dispersion and conducting tests for normality, exponentiality, and uniformity&nbsp;\cite{Wieczorkowski1999,Zamanzade2012}.
-Entropy estimation involves several practical difficulties, especially when the model is unknown; in these cases, non-parametric methods are used.
-
+The $\mathcal{G}^0$ distribution, which is suitable for SAR data, includes the
+Gamma law as the limiting case for fully developed speckle&nbsp;\cite{Ferreira2020} and provides flexibility with fewer parameters for analysis.
+
+Our work aims to improve the identification of potential roughness features in SAR intensity data. 
+Physical modeling of SAR data allows to take advantage of the gamma distribution in the presence of fully developed speckles and to create a scenario with an infinite number of independent backscatterers per resolution unit, often referred to as homogeneous regions.
+
+In this context, we present a set of three novel test statistics that aim to distinguish between homogeneous and non-homogeneous domains, in particular between gamma and \(\mathcal{G}^0\) distributed data, each with a known number of looks.
+To understand the core ideas behind our approach, we explore the use of properties such as entropy and coefficient of variation.
+
+Entropy is a fundamental concept in information theory with far-reaching applications in pattern recognition, statistical physics, image processing, edge detection and SAR image analysis&nbsp;\cite{Presse2013,MohammadDjafari2015,Avval2021, Nascimento2014,Nascimento2019}.
+Shannon introduced it in 1948&nbsp;\cite{Shannon1948} for a random variable as a measure of information and uncertainty.
+In statistics, Shannon entropy is a crucial descriptive parameter, especially for evaluating data dispersion and performing tests for normality, exponentiality and uniformity&nbsp;\cite{Wieczorkowski1999,Zamanzade2012}.
+Entropy estimation is associated with some practical difficulties, especially when the model is unknown. In these cases, non-parametric methods are used.
 Spacing methods have been discussed as a non-parametric approach in&nbsp;\cite{AlizadehNoughabi2010,Subhash2021}.
-This strategy offers flexibility to address a wide range of models without imposing specific parametric restrictions.
-
-In our study, entropy serves as the fundamental parameter, providing a robust assessment by means of a bootstrapped non-parametric estimator of Shannon entropy.
-
-Simultaneously, we use the classic coefficient of variation (CV) and an alternative form based on the ratio between the median absolute deviation and the median. 
-The CV is known as an efficient and robust index of textural information, measures the homogeneity of the image&nbsp;\cite{Lopes1990}.
-
-The CV, introduced by Pearson&nbsp;\cite{Pearson1896} in 1896, is a relative measure of dispersion widely used in various areas of applied statistics including sampling, biostatistics, medical and biological research, climatology, and other fields \cite{hendricks1936sampling, Tian2005,SubrahmanyaNairy2003,Chankham2024}.
-It facilitates the comparison of variability between different populations and is especially valuable for comparing variables with different units. 
-This is because when the main purpose is to compare variations of several variables, the standard deviation cannot serve as an adequate measure of variation unless all variables are expressed in the same unit of measurement and have identical mean values.
-When these requirements are not hold for the variables under study, CV is the relative measure typically used in real applications. 
-The variable with the highest CV value is the one with the highest relative dispersion around the mean&nbsp;\cite{Banik2011}.
+This strategy provides the flexibility to consider a wide range of models without enforcing certain parametric constraints.
+
+The coefficient of variation (CV), introduced in 1896 by Pearson&nbsp;\cite{Pearson1896}, is a relative dispersion measure widely used in various fields of applied statistics, including sampling, biostatistics, medical and biological research, climatology and other fields&nbsp;\cite{hendricks1936sampling,Tian2005,SubrahmanyaNairy2003,Chankham2024}.
+It facilitates the comparison of variability between different populations and is particularly valuable for comparing variables with different units. 
+This is because when the main purpose is to compare the variations of several variables, the standard deviation can only serve as an adequate measure of variation if all variables are expressed in the same unit of measurement and have identical means.
+If these conditions are not met for the variables under investigation, the CV is the relative measure that is usually used in real applications.
+The variable with the highest CV value is the one with the largest relative dispersion around the mean value&nbsp;\cite{Banik2011}.
+
+In our study, entropy serves as a fundamental parameter that allows a robust evaluation using a bootstrapped nonparametric estimator of the Shannon entropy.
+At the same time, we use the classical CV and an alternative form based on the ratio between the median absolute deviation and the median. 
+The CV is known as an efficient and robust index for texture information and measures the homogeneity of the image&nbsp;\cite{Lopes1990}.
+Applying these test statistics to generate maps of \(p\) values facilitates testing the homogeneity hypothesis and reveals different types of targets in the SAR data. 
+Through extensive experiments with real and simulated SAR data, we demonstrate the superiority of our proposed method over existing approaches.
 
@@
 
-The article is structured as follows: 
-Section&nbsp;\ref{sec:Background} covers statistical modeling and entropy estimation for Intensity SAR data.
-Section&nbsp;\ref{sec:test} outlines hypothesis testing based on non-parametric entropy estimators and and coefficient of variation.
-In Section&nbsp;\ref{sec:Results}, we present experimental results. 
-Finally, in Section&nbsp;\ref{sec:conclusion} conclusions are exhibited.
+The article is structured as follows: Section&nbsp;\ref{sec:Background}
+deals with statistical modeling and entropy estimation for intensity SAR
+data. 
+Section&nbsp;\ref{sec:test} outlines hypothesis tests based on nonparametric entropy estimators and coefficients of variation. 
+In Section&nbsp;\ref{sec:Results} we present experimental results. 
+Finally, in Section&nbsp;\ref{sec:conclusion} the conclusions are presented.
 
@@
 The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$  distributions&nbsp;[@Frery1997]. 
-The first is suitable for fully developed speckle and is a limiting case of the second, which is appealing due to its versatility in accurately representing regions with various roughness characteristics&nbsp;[@Cassetti2022].
-We denote $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and $Z \sim G_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the respective probability density functions:
+The first is suitable for fully developed speckle and is a limiting case of the second model, which is interesting due to its versatility in accurately representing regions with different roughness properties&nbsp;[@Cassetti2022].
+We denote $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and $Z \sim \mathcal{G}_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the respective probability density
+functions (pdfs): 
 \begin{align}
-	f_Z(z;L, \mu)&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gamma1}\\
+    f_Z(z;L, \mu)&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z)\label{E:gamma1}\\
+    \intertext{ and }
     f_Z(z; \alpha, \gamma, L)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
 \end{align} 
-where, in&nbsp;\eqref{E:gamma1} $\mu > 0$ is the mean; in&nbsp;\eqref{E:gi01}  $\gamma > 0$ is the scale, $\alpha < -1$ measures the roughness,  $L \geq 1$ is the number of looks, $\Gamma(\cdot)$ is the gamma function, and $\mathbbm 1_{A}(z)$ is the indicator function of the set $A$.
-
-From \eqref{E:gi01}, the $r$th moment of $Z$ is expressed as:
+where \(\mu > 0\) is the mean, \(\gamma > 0\) is the scale, \(\alpha < -1\) measures
+the roughness, \(L \geq 1\) is the number of looks, \(\Gamma(\cdot)\) is
+the gamma function, and \(\mathbbm 1_{A}(z)\) is the indicator function
+of the set \(A\).
+
+If we take the law with the density&nbsp;\eqref{E:gi01}, the \(r\)th non-central moment of \(Z\) is expressed as follows:
 \begin{align}
-	E_{G_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\gamma(L)}, \quad \alpha <-r. 
+    E_{G_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\Gamma(L)}, \quad \alpha <-r. 
     \label{E:rmom}
@@
 
-Even though the $\mathcal{G}_I^0$  distribution is defined by the parameters $\alpha$ and $\gamma$, SAR literature commonly utilizes the texture $\alpha$ and the mean $\mu$&nbsp;\cite{Nascimento2010}.
-In this way, we compute the expected value $\mu$ using the expression in&nbsp;\eqref{E:rmom}, and we reparametrize&nbsp;\eqref{E:gi01} using $\mu$, $\alpha$, and $L$. Then
-\begin{align*}
+Although the \(\mathcal{G}_I^0\) distribution is defined by the parameters \(\alpha\) and \(\gamma\), in the SAR literature&nbsp;\cite{Nascimento2010} the texture \(\alpha\) and the mean \(\mu\) are usually used.
+In this way, we calculate the expected value \(\mu\) using the expression in&nbsp;\eqref{E:rmom}, and we reparametrize&nbsp;\eqref{E:gi01} with \(\mu\),
+\(\alpha\), and \(L\).
+Then \begin{align*}
     \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
 \end{align*} 
-Thus, the probability density function that characterize the $G_I^0(\mu, \alpha, L)$ law is
+The reparametrized pdf that characterizes the law \(G_I^0(\mu, \alpha, L)\) is thus
 \begin{equation}
-		f_Z(z; \mu, \alpha, L)=\frac{L^L\Gamma(L-\alpha)}{\big(-\mu(\alpha+1)\big)^{\alpha}\Gamma(-\alpha)\Gamma(L)} \frac{z^{L-1}}{\big(-\mu(\alpha+1)+Lz\big)^{L-\alpha}}.\label{E:gi02}
+        f_Z(z; \mu, \alpha, L)=\frac{L^L\Gamma(L-\alpha)}{\big[-\mu(\alpha+1)\big]^{\alpha}\Gamma(-\alpha)\Gamma(L)} \frac{z^{L-1}}{\big[-\mu(\alpha+1)+Lz\big]^{L-\alpha}}.\label{E:gi02}
 \end{equation}
@@
 \end{equation}
-here, $f(\cdot)$ is the probability density function that characterizes the distribution of the real-valued random variable $Z$.
+here, \(f(\cdot)\) is the pdf that characterizes the distribution of the real-valued random variable \(Z\).
 
@@
 where $\psi^{(0)}(\cdot)$ is the digamma function.
-Figure&nbsp;\ref{fig:Plot_GI0_to_gamma1}, shows the behaviour of the entropy of \(G_I^0\) when when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), observing its convergence towards the entropy of \(\Gamma_{\text{SAR}}\) as \(\alpha\) takes large negative values.
+Figure&nbsp;\ref{fig:Plot_GI0_to_gamma1}, shows the behavior of the entropy of \(G_I^0\) when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), where the approximation to the entropy of \(\Gamma_{\text{SAR}}\) can be observed when \(\alpha\) assumes large negative values.
+In an interpretative sense, we can conclude that the more heterogeneous (high values of $\alpha$) the SAR region is, the higher the value of entropy (or degree of disorder).
+It is worth noting that this conclusion confirms what is written in the SAR literature.
 
@@
 
-The problem of non-parametric estimating of $H(Z)$ has been considered by many authors including&nbsp;\cite{vasicek1976test, Wieczorkowski1999,correa1995new,AlOmari2019}, who proposed estimators based on spacings.
-
-One of the earliest non-parametric estimators relying on spacings was introduced by Vasicek&nbsp;\cite{vasicek1976test}. 
-Assuming that $\bm{Z}=(Z_1, Z_2,\ldots,Z_n)$ is a random sample from the distribution $F(z)$, the estimator is defined as:
+The problem of non-parametric estimating of $H(Z)$ has been considered by many authors including&nbsp;\cite{vasicek1976test, Wieczorkowski1999,correa1995new,AlOmari2019}, who have proposed estimators based on spacings.
+
+One of the first non-parametric estimators based on spacings was introduced by Vasicek&nbsp;\cite{vasicek1976test}. 
+Under the assumption that \(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) is a random sample from the distribution \(F(z)\), the estimator is defined as:
 \begin{equation*}
@@
 We consider three estimators known for their superior performance&nbsp;\cite{Cassetti2022}:
-
-* Correa&nbsp;\cite{correa1995new}: $\widehat{H}_{\text{C}}$.
-
-* Ebrahimi et al&nbsp;\cite{Ebrahimi1994}: $\widehat{H}_{\mathrm{E}}$.
-
-* Al Omary&nbsp;\cite{IbrahimAlOmari2014}: $\widehat{H}_{\mathrm{AO}}$.
+Correa&nbsp;\cite{correa1995new}, \(\widehat{H}_{\text{C}}\);
+Ebrahimi et al&nbsp;\cite{Ebrahimi1994}, \(\widehat{H}_{\mathrm{E}}\);
+and Al Omary&nbsp;\cite{IbrahimAlOmari2014}, \(\widehat{H}_{\mathrm{AO}}\).
 
@@
 
-We employ the bootstrap technique to refine the precision of existing non-parametric entropy estimators. 
-This approach involves generating new datasets through resampling with repetition from an existing one&nbsp;\cite{Michelucci2021}.
-
-<!-- This approach involves generating new datasets through resampling with repetition from an existing one. -->
-
-Let's assume that non-parametric entropy estimators \(\widehat{H}=\widehat{\theta}(\bm{Z})\) are inherently biased, that is:
-\begin{equation}
+We use the bootstrap technique to refine the accuracy of existing nonparametric entropy estimators.
+In this approach, new data sets are generated by replicate sampling from an existing data set&nbsp;\cite{Michelucci2021}.
+
+Let us assume that non-parametric entropy estimators
+\(\widehat{H}=\widehat{\theta}(\bm{Z})\) are inherently biased, i.e:\begin{equation}
 \label{Eq:bias1}
-\bias\big(\widehat{\theta}(\bm{Z})\big) = E\big[\widehat{\theta}(\bm{Z})\big] - \theta \neq 0.
-\end{equation}
-Our bootstrap-improved estimators are of the form:
-<!-- introducing an "ideal unbiased estimator" \(\check{\theta}(\bm{Z})\): -->
-<!-- \begin{equation} -->
-<!-- \label{Eq:bias2} -->
-<!-- \widecheck{\theta}(\bm{Z}) = \widehat{\theta}(\bm{Z}) - \bias\big(\widehat{\theta}(\bm{Z})\big). -->
-<!-- \end{equation} -->
-<!-- However, \(\check{\theta}(\bm{Z})\) is not an estimator, because it depends on the true parameter \(\theta\), prompting the formulation of a new estimator \(\widetilde{H}\).  -->
-<!-- From&nbsp;\eqref{Eq:bias1} and&nbsp;\eqref{Eq:bias2} we have: -->
+\operatorname{Bias}\big(\widehat{\theta}(\bm{Z})\big) = E\big[\widehat{\theta}(\bm{Z})\big] - \theta \neq 0.
+\end{equation} Our bootstrap-improved estimators are of the form:
 \begin{align*}
@@
 \end{align*} 
-where $B$ is the number of replications in the bootstrap technique.
-Applying this methodology, the original estimators by Correa, Ebrahimi, and Al-Omari are now denoted as the proposed bootstrap-enhanced versions: $\widetilde{H}_{\text{C}}$, $\widetilde{H}_{\text{E}}$, and $\widetilde{H}_{\text{AO}}$, respectively.
-
-We analyzed the performance of these estimators with a Monte Carlo study:
-$500$ samples of $G_I^0$ of size \(n\in\left\{9, 25, 49, 81, 121\right\}\) and several values of the mean, number of looks and roughness.
-We present the results with \(mu\in\left\{1, 10\right\}\), \(\alpha=-10\), and \(L=5\). 
-The results are consistent for the other situations. 
-In the case of the bootstrap technique, each sample is replicated $100$ times with replacement.
-We choose to use the following heuristic formula for spacing, $m=\left[\sqrt{n}+0.5\right]$.
-
-In Figure&nbsp;\ref{fig:Plot_bias_mse_gi0} we depict comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions.
-The use of the bootstrap technique exhibits more precision, reduced bias and MSE, and improved convergence.
-The results of simulation are exhibited in Table&nbsp;\ref{tab:table2}.
-
-The precision of estimators, as evidenced by bias and MSE comparisons, benefits significantly from the bootstrap technique, particularly for sample sizes below 81.
+where \(B\) is the number of replications in the bootstrap
+technique. 
+Applying this methodology, the original estimators of Correa,
+Ebrahimi and Al-Omari are now referred to as the proposed bootstrap-enhanced versions:
+\(\widetilde{H}_{\text{C}}\),
+\(\widetilde{H}_{\text{E}}\), and \(\widetilde{H}_{\text{AO}}\),
+respectively.
+
+We analyzed the performance of these estimators with a Monte Carlo study: \(500\) samples of \(G_I^0\) of size
+\(n\in\left\{9, 25, 49, 81, 121\right\}\) and different values for mean, number of looks and roughness. We present the results with
+\(\mu\in\left\{1, 10\right\}\), \(\alpha=-10\) and \(L=5\).
+The results are also adherent for the other situations.
+In the bootstrap technique, each sample is replicated a hundred times with replacement.
+We use the following heuristic formula for spacing,
+\(m=\left[\sqrt{n}+0.5\right]\).
+
+In Figure&nbsp;\ref{fig:Plot_bias_mse_gi0} we show comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions.
+The use of the bootstrap technique shows higher precision, lower bias and MSE, and improved convergence.
+The results of the simulation can be found in
+Table&nbsp;\ref{tab:table2}.
+
+The precision of the estimators resulting from the comparison of bias and MSE benefits significantly from the bootstrap technique, especially for sample sizes below 81.
 
@@
 # Number of replications
-R <-200
+R <-300
 
 # Number of bootstrap replications
-B1 <- 5
+B1 <- 20
 mu_values <- c(1, 10)
@@
 The population CV is defined as a ratio of the population standard deviation $(\sigma)$ to the population mean $(\mu)$:
-
 \begin{align}
@@
 
-<!-- In practice, the population CV is unknown and needs to be estimated.  -->
-<!-- The typical sample estimate of the population CV is given as: -->
-<!-- \begin{align} -->
-<!-- 	\text{CV}=\frac{S}{\bar{X}},  -->
-<!-- \end{align} -->
-<!-- where $S$ and $\bar{X}$ are the sample standard deviation and the sample mean, respectively. -->
-
-We explore a robust alternative to the CV as discussed in \cite{Ospina2019}, involving the ratio of the mean absolute deviation from the median (MnAD) to the median, two well-known robust measures of scale and location, respectively.
-The MnAD is defined as $n^{-1}\sum_{i=1}^n|x_i-\widehat{Q}_2|$, where $\widehat{Q}_2$ represents an estimate of the population median, which can be approximated by the sample median.
+We explore a robust alternative to CV, as described in&nbsp;\cite{Ospina2019}, which incorporates the ratio between the mean absolute deviation from the median (MnAD) and the median, two well-known robust measures of
+scale and location, respectively. The sample version for the MnAD is defined as
+\(n^{-1}\sum_{i=1}^n|x_i-\widehat{Q}_2|\), where \(\widehat{Q}_2\)
+is an estimate for the median of the population, which can be approximated by the median of the sample.
 
@@
 $$
-In other words, we verify the hypothesis that the data are fully-developed speckle.
-The proposed tests are described below.
+In the physical sense, we are testing the hypothesis that the data are fully developed speckle.
+As for the parametric problem, once it is not possible to define the hypothesis $\mathcal{H}_0=\alpha=-\infty$, it is impossible to solve this problem with the parametric statistical inference alternatives (such as likelihood ratio, score, grandient and Wald hypothesis test).
+The proposed tests to solve this physical problem in SAR systems are described below.
 
@@
 
-The first test statistic assess the behavior of the data under the null hypothesis, through the empirical distribution.
+The first test statistic evaluates the behavior of the data under the null hypothesis using the empirical distribution: 
 \begin{equation}
@@
 <!-- This suggests significant differences and implies the presence of heterogeneous clutter. -->
-
-Figure&nbsp;\ref{fig:Plot_density} depicts empirical test statistic densities for various sample sizes, and Table&nbsp;\ref{tab:table_stat_combined} summarizes key statistics, including mean, SD, variance (Var), skewness (SK), excess kurtosis (EK), and Anderson–Darling $p$-values for normality.
-<!-- ACF Only show L=2 and L=8 -->
-Results with $p$-values larger than $0.05$  indicate no evidence against normality. 
-Small variance and near-zero skewness and excess kurtosis suggest limited spread, symmetry, and light tails.  
-Normal QQ-plots, confirm that there is no evidence to reject the normal distribution.
-
-<!-- In Fig.&nbsp;\ref{fig:Plot_normality_qq}, normal QQ-plots visually affirm distributional similarity with the expected normal line. -->
+Figure&nbsp;\ref{fig:Plot_density} shows the empirical test statistic densities for different sample sizes, and Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean, SD, variance (Var), skewness (SK), excessive kurtosis (EK) and Anderson--Darling \(p\) values for normality.
+Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption.
+A low variance as well as a skewness and an excessive kurtosis of almost zero indicate limited dispersion, symmetry and a slight tail.
+Normal QQ plots confirm that there is no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.
 
@@
 
-R <- 500
+R <- 2000
 mu <- 1
-B <- 1
+B <- 2
 
@@
 )
-colnames(combined_summary_stats) <- c("$L$", "$n$", "Mean", "SD", "Var", "SK", "EK", "$p$-value")
+colnames(combined_summary_stats) <- c("$\\bm{L}$", "$\\bm{n}$", "\\textbf{Mean}", "\\textbf{SD}", "\\textbf{Var}", "\\textbf{SK}", "\\textbf{EK}", "$p$-\\textbf{value}")
 
@@
 
-After verifying the normality of the data, we proceeded to explore the capabilities of the proposed test in terms of size and power.
-Under $\mathcal{H}_0$, the distribution of test statistic is asymptotically normal.
-Therefore, the $p$-value  is calculated as $2\Phi(-\mid \varepsilon\mid)$, where  $\Phi$ is the standard Gaussian cumulative distribution and $\varepsilon$ is the standardized test statistic given by:
-$$
-\varepsilon=\frac{\tilde{H}-H_{\Gamma_{\text{SAR}}}}{\hat\sigma}.
-$$
-
-We considered nominal levels of \SI{1}{\percent}, \SI{5}{\percent}, and \SI{10}{\percent}. 
-In reference to the size, $1000$ simulations have been used for various sample sizes with  satisfactory results. In all cases, the nominal level has been achieved. 
-The power, in general, improves with the increase in the sample size and the number of looks. 
-The results are presented in Table&nbsp;\ref{tab:table_size_power}.
+After checking the normality of the data, we examined the possibilities of the proposed test in terms of size and power.
+Under \(\mathcal{H}_0\), the distribution of the test statistic is asymptotically normal.
+Therefore, the \(p\) value is calculated as
+\(2\Phi(-\mid \varepsilon\mid)\), where \(\Phi\) is the standard
+Gaussian cumulative distribution and \(\varepsilon\) is the standardized test statistic given by :
+\[
+\varepsilon=\frac{\widetilde{H}-H_{\Gamma_{\text{SAR}}}}{\hat\sigma}.
+\]
+
+We have nominal levels of \SI{1}{\ percent}, \SI{5}{\ percent}, and
+\SI{10}{\percent}. 
+In terms of size, \(1000\) simulations were used for different sample sizes with satisfactory results. 
+In all cases, the nominal level was achieved. 
+The power generally improves with increasing sample size and number of looks.
+The results are shown in Table&nbsp;\ref{tab:table_size_power}.
 
@@
 set.seed(1234567890, kind = "Mersenne-Twister")
-
 # 
@@
 }
-
-R <- 100
+R <- 1000
 mu <- 1
@@
 alpha_nominals <- c(0.01, 0.05, 0.1)
-
 results <- data.frame()
-
 for (L in L_values) {
@@
 }
-
-save(results, file = "./Data/type_I_results1.Rdata")
-
+save(results, file = "./Data/type_I_results.Rdata")
 ```
@@
 ```{r Simulated_power, echo=FALSE, message=FALSE}
-
 set.seed(1234567890, kind = "Mersenne-Twister")
-
 calculate_p_value <- function(test_statistic, mu_W, sigma_W) {
@@
 }
-
 calculate_type_II_error_rate <- function(p_values, alpha_nominal) {
@@
 }
-
 # Function to calculate power for different L values and alpha_nominals
@@
 alpha_nominals <- c(0.01, 0.05, 0.1)
-
 results_power <- calculate_power(R, mu, L_values, B, sample_sizes, alpha_nominals)
-save(results_power, file = "./Data/results_power1.Rdata")
-
+save(results_power, file = "./Data/results_power.Rdata")
+```
+
+```{r Table_size_and_power, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+#cat("\\setlength{\\tabcolsep}{4pt}\n")
+load("./Data/type_I_results.Rdata")
+type_I_error_rates <- tapply(results$P_Value, INDEX = list(results$L, results$Sample_Size, results$Alpha_Nominal), FUN = function(p_values) {
+  sum(p_values) / length(p_values)  
+})
+type_I_error_results <- as.data.frame(as.table(type_I_error_rates))
+colnames(type_I_error_results) <- c("L", "Sample_Size", "Alpha_Nominal", "Type_I_Error_Rate")
+spread_results <- spread(type_I_error_results, key = Alpha_Nominal, value = Type_I_Error_Rate)
+spread_results <- spread_results %>% 
+  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)
+load("./Data/results_power.Rdata")
+summary_stats <- results_power %>%
+  spread(key = alpha_nominal, value = power) %>%
+  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)
+combined_results <- merge(spread_results, summary_stats, by = c("L", "Sample_Size"))
+combined_results <- combined_results %>% 
+  arrange(L, Sample_Size)
+combined_results <- combined_results %>% 
+  select(L, Sample_Size, `0.01.x`, `0.05.x`, `0.1.x`, `0.01.y`, `0.05.y`, `0.1.y`)
+colnames(combined_results) <- c("$L$", "$n$", "$1\\%$", "$5\\%$", "$10\\%$", "$1\\%$", "$5\\%$", "$10\\%$")
+# LaTeX notation 
+combined_results[] <- lapply(combined_results, function(x) {
+  if (is.numeric(x)) {
+    if (all(x %% 1 == 0)) {
+      formatted_numbers <- sprintf("$%d$", x)
+    } else {
+      formatted_numbers <- ifelse(x < 0, sprintf("$%.4f$", x), sprintf("$\\phantom{-}%.4f$", x))
+    }
+    return(formatted_numbers)
+  } else {
+    return(x)
+  }
+})
+table_combined_result <- knitr::kable(
+  combined_results,
+  caption = "Size and Power of the entropy-based test.",
+  format = "latex",
+  booktabs = TRUE,
+  align = "lcccccccc",
+  escape = FALSE,
+  digits = 4,
+  label = "table_size_power",
+  centering = FALSE,
+  #linesep = "",
+  table.envir = "table", position = "H")%>%
+  add_header_above(c(" ", " ", "Size" = 3,  "Power" = 3)) %>%
+  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
+  row_spec(0,  align = "c")
+print(table_combined_result)
 ```
@@
 
-The situations where the use of CV and $\text{CV}_{\text{MnAD}}$ may be appropriate, i.e.
-where the observations are positive, the log-normal (LN) and inverse Gaussian (IG) distribution are often more justified compared to Gamma and Weibull distributions \cite{Chaubey2017,takagi1997application}.
-
-The inverse Gaussian distribution is shown to be well approximated by the log-normal distribution \cite{whitmore1978} which implies that the IG distribution also does not share the problem of non-existence of fixed width confidence interval with the Gaussian case.
+The situations in which the use of CV and \(\text{CV}_{\text{MnAD}}\) may be appropriate, i.e. when the observations are positive, the log-normal
+(LN) and the inverse Gaussian distribution (IG) are often more appropriate than the Gamma and Weibull distributions&nbsp;\cite{Chaubey2017,takagi1997application}.
+
+It is shown that the IG distribution is well approximated by the log-normal distribution, which means that the
+IG distribution also does not share the problem of the non-existence of a fixed-width confidence interval with the Gaussian case&nbsp;\cite{whitmore1978}.
 
 The LN distribution in two parameters has the following density function.
+
 \begin{align}
-	f_Z(z;\mu, \sigma )=\frac{1}{\sigma z\sqrt{2\pi}}\exp\left\{-\frac{(\ln z- \mu)^2}{2\sigma^2}\right\}, \quad z>0, \sigma>0, -\infty < \mu < \infty,
+    f_Z(z;\mu_{\text{LN}}, \sigma_{\text{LN}} )=\frac{1}{\sigma_{\text{LN}} z\sqrt{2\pi}}\exp\left\{-\frac{(\ln z- \mu_{\text{LN}})^2}{2\sigma_{\text{LN}}^2}\right\}\mathbbm 1_{\mathbbm R_+}(z),
 \end{align}  
-here, $\mu$ is the log-scale parameter and $\sigma$ is the shape parameter.
+here, $\mu_{\text{LN}}$ and $\sigma_{\text{LN}}$ are the mean and standard deviation of the logarithm.
 
@@
 
-The AIC and BIC results in Tables&nbsp;\ref{tab:table_aic_gamma}-\ref{tab:table_aic_gio_MnADmedian} indicate that the CV and $\text{CV}_{\text{MnAD}}$ data from different synthetic sample sizes, extracted from the Gamma SAR and $G_I^0$ distributions, respectively, adhere to the characteristics of an LN distribution.
-The AIC and BIC values of the IG distribution and the LN distribution are not significantly different because both distributions are based on the right-skewed characteristic.
-In this situation, the model for the LN distribution was considered to be the best due to it providing the lowest AIC and BIC values.
-
-Figures&nbsp;\ref{fig:Plot_cv}-\ref{fig:Plot_madmed_gi0_MnADmedian} present density plots, Q-Q plots, P-P plots, and Cumulative Distribution Function plots, which offer an additional measure of goodness-of-fit and confirm that the most suitable distribution to be considered is the LN distribution.
+The AIC and BIC results in Tables&nbsp;\ref{tab:table_aic_gamma}--\ref{tab:table_aic_gio_MnADmedian} indicate that the CV and \(\text{CV}_{\text{MnAD}}\) data from different distributed gamma and \(G_I^0\) synthetic sample sizes match the properties of an LN distribution.
+\textcolor{green}{%
+It is important to note that this conclusion was drawn empirically based on a dictionary of distributions that are analytically tractable and well-defined under biparametric, unimodal, asymmetric, and positive distributions.
+}
+
+\textcolor{red}{%
+ADCN: Caros, esse é o ponto mais delicado da excelente ideia desse paper em minha opinião.
+Não me oponho a colocarmos a lognormal como uma possibilidade, mas é preciso deixar claro que é uma possibilidade empírica.
+Uma alternativa empírica para uma solução do momento usando distribuições mais desenvolvidas na literatura e que sejam analiticamente tratáveis.
+Estou pensando corretamente?
+Se sim, por que não log-t-student, log-Laplace, power exponential, Log-hyperbolic,....
+(e a lista segue).
+Sugiro talvez indicar (i) a dedução da distribuição assintótica das estatísticas em função de CV e MNAD dando com entrada G0I ($\mathcal{H}_1$) e a Gamma ($\mathcal{H}_0$) como trabalho futuro.
+Do que eu entendi, a suposição da normal assintótica para entropia vem de uma coleção de trabalhos teóricos.
+Já a LN, do que percebi, não.
+Coloquei um comentário em verde.
+Vejam se estão de acordo.
+}
+
+Figures&nbsp;\ref{fig:Plot_cv}--\ref{fig:Plot_madmed_gi0_MnADmedian} show empirical and fitted density plots, Q-Q plots, P-P plots as well as empirical and fitted cumulative distribution functions.
+They provide qualitative sources that confirm that the LN distribution is the most appropriate distribution
 
@@
 
-This section presents simulations performed to obtain an assessment of the performances of the proposed test statistics.
+This section presents simulations that were performed to obtain an evaluation of the performance of the proposed test statistics.
 
@@
 
-Figure&nbsp;\ref{fig:sim_SAR_Images}(a) shows the phantom used for a simulated image with dimensions of $250\times 250$ pixels to illustrate the differences between heterogeneous (dark, $\alpha=-2$) and homogeneous (light, $\alpha=-10$) regions, with $L = 5$.
-The areas are formed by independent draws from the $G^0_I$ distribution.
+Figure&nbsp;\ref{fig:sim_SAR_Images}(a) shows the phantom used for a simulated image with dimensions of $250\times 250$ pixels to show the differences between heterogeneous (dark, $\alpha=-2$) and homogeneous (light, $\alpha=-10$) regions, with $L = 5$.
+The regions are formed by independent draws from the $G^0_I$ distribution.
 
@@
 
-The resulting $p$-values for the tests $S_H$, $T_{\text{CV}}$, and $T_{\text{CV}_{\text{MnAD}}}$ are shown in Figures&nbsp;\ref{fig:sim_SAR_Images}(b)-(d) and Figures&nbsp;\ref{fig:sim_SAR_Images_p05}(a)-(c), respectively.
+The resulting $p$-values for the tests $S_H$, $T_{\text{CV}}$, and $T_{\text{CV}_{\text{MnAD}}}$ are shown in Figures&nbsp;\ref{fig:sim_SAR_Images}(b)--(d) and Figures&nbsp;\ref{fig:sim_SAR_Images_p05}(a)--(c), respectively.
 The new images reveal that a darker background indicates homogeneity, while lighter backgrounds represent heterogeneous areas.
@@
 
-We assessed the proposed test statistics using two real SAR images. For our analysis, we selected images of the city of Frankfurt, Germany, and Ottawa, Canada. 
-These images were acquired by the Sentinel-1A satellite operating in the C band,  with  VV polarization, intensity format, and $L=5$ nominal looks.
-
-Both images have dimensions of $512 \times 512$ pixels and contain urban areas, water and forest regions, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)-(b).
-
-  The $p$-values obtained for the $S_H$, $T_{\text{CV}}$, and $T_{\text{CV}_{\text{MnAD}}}$ tests are presented in Figures&nbsp;\ref{fig:sim_SAR_Images_Frankfurt}-\ref{fig:sim_SAR_Images_01_Ottawa}, respectively.
+We evaluated the proposed test statistic using two real SAR images. 
+For our analysis, we used images of the city of Frankfurt, Germany, and of Ottawa, Canada. 
+These images were acquired by the Sentinel-1A satellite operating in C-band, with VV polarization, intensity format and
+\(L=5\) nominal looks.
+Both images have a size of \(512 \times 512\) pixels and contain urban areas, water and forest regions, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)--(b).
+
+  The $p$-values obtained for the $S_H$, $T_{\text{CV}}$, and $T_{\text{CV}_{\text{MnAD}}}$ tests are presented in Figures&nbsp;\ref{fig:sim_SAR_Images_Frankfurt}--\ref{fig:sim_SAR_Images_01_Ottawa}, respectively.
+
+In general, using the original and robust CV is more meaningful than using Shannon entropy to capture texturelessness.
+It is justified that the dark areas of the maps based on the $\text{CV}$ and $\text{CV}_{\text{MnAD}}$ tests cover the areas reported for the Shannon entropy-based map.
+Both CV-based tools predicted textureless regions as well as boundaries where the statistical properties of texture vary.
+Assuming $10\%$ as the threshold for the $p$ values, the dark region produced by the $\text{CV}$ test was higher than that produced by the $\text{CV}_{\text{MnAD}}$ and entropy test.
+The latter observation is to be expected as the latter tests are robust alternatives to the former test, which is essentially based on the expected value operator that reacts to outliers.
 
@@
 
-In this article,...
+In this article, we have provided a practical and theoretical answer to the following physical question: How to detect texturelessness in SAR images, assuming that the SAR intensity follows the $\mathcal{G}^0_I$ distribution.
+Solving this problem is not easy, considering that the texturelessness in the parametric space of $\mathcal{G}^0_I$ means the infinity value, which is neither analytically tractable nor practically provable.
+To this end, we proposed three novel hypothesis tests, one from the Shannon entropy and two others from the variation coefficient variants.
+The performance of our proposals was evaluated using a Monte Carlo study. 
+The results showed that they were conservative in estimating the probability of a type I error (false alarm rate) and the test power (probability of detection), which increases with sample size.
+An application to two recent SAR images was performed. 
+The results showed that the $\text{CV}_{\text{MnAD}}$ and Shannon entropy-based tests were more robust than the CV-based tests. 
+In addition, the CV-based tests were able to recognize both images without texture and those where the type of texture changes.

### 2024-04-11 Text/Review-and-suggestions-Prof.-Abraao-R1.tex
Changes added in Rmd file

--- 2024-04-05 Text/Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics.tex
@@
 Solving this problem is not easy, considering that the texturelessness in the parametric space of $\mathcal{G}^0_I$ means the infinity value, which is neither analitically tractable nor practically provable.
-To this end, we have proposed three novel hypothesis tests, one from the Shannon entropy and two others from the variation coefficient variants.
+To this end, we proposed three novel hypothesis tests, one from the Shannon entropy and two others from the variation coefficient variants.
+The performance of our proposals was evaluated using a Monte Carlo study.
+The results showed that they were conservative in estimating the probability of a type I error (false alarm rate) and the test power (probability of detection), which increases with sample size.
+An application to two recent SAR images was performed.
+The results showed that the $\text{CV}_{\text{MnAD}}$ and Shannon entropy-based tests were more robust than the CV-based tests.
+In addition, the CV-based tests were able to recognize both images without texture and those where the type of texture changes.
 

### 2024-04-14 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Starting the review

@@
   This paper presents a statistical approach to identify the underlying roughness characteristics in synthetic aperture radar (SAR) intensity data. 
-  The physical modeling of this kind of data allows to use the Gamma distribution in the presence of fully-developed speckle, i.e., when there are infinitely many independent backscatterers per resolution cell.
+  The physical modeling of this kind of data allows to use the Gamma distribution in the presence of fully-developed speckle, i.e., when there are infinitely many independent backscatterers per resolution cell, and none dominates the return.
 This situation is often called "homogeneous" or  "textureless" regions.
-  The $\mathcal{G}_I^0$ distribution is also a widely accepted law for heterogeneous and extremely heterogeneous regions.
-We propose three test statistics to distinguish between homogeneous and inhomogeneous regions, i.e.
-between gamma and \(\mathcal{G}_I^0\) distributed data, both with a known number of looks.
+  The $\mathcal{G}_I^0$ distribution is also a widely accepted law for heterogeneous and extremely heterogeneous regions, i.e., areas in which the fully-developed speckle hypotheses do not hold. 
+  We propose three test statistics to distinguish between homogeneous and inhomogeneous regions, i.e. between gamma and \(\mathcal{G}_I^0\) distributed data, both with a known number of looks. 
   The first test statistic uses a bootstrapped nonparametric estimator of Shannon entropy, which provides a robust assessment in the face of uncertain distributional assumptions.
@@
   The third test uses an alternative form of estimating the CV based on the ratio of the mean absolute deviation from the median to the median. 
-  We apply our test statistic to create maps of \(p\) values for the hypothesis of homogeneity. These maps identify different types of targets. 
+  We apply our test statistic to create maps of \(p\) values for the homogeneity hypothesis.
+  These maps identify different types of targets. 
   We show that our proposal outperforms its competitors using simulated and SAR data.
+# ACF Which is "our proposal" and which are the "competitors"?
 keywords: |
@@
 It provides valuable images under various conditions, including day or night and different weather situations&nbsp;\cite{Moreira2013,Mu2019}.
-However, the effective use of SAR data depends on a thorough understanding of its statistical properties, especially the impact of speckle effects inherent in SAR data due to the coherent nature of the imaging process&nbsp;\cite{Argenti2013}.
-
-In the presence of non-Gaussian speckle interference, SAR data requires a reliable statistical model for accurate processing. 
+However, the effective use of SAR data depends on a thorough understanding of their statistical properties because they are corrupted by speckle.
+This noise-like interference effect is inherent in SAR data due to the coherent nature of the imaging process&nbsp;\cite{Argenti2013}.
+
+Speckle is non-Gaussian speckle, thus SAR data require reliable statistical models for accurate processing. 
 The $\mathcal{G}^0$ distribution, which is suitable for SAR data, includes the
-Gamma law as the limiting case for fully developed speckle&nbsp;\cite{Ferreira2020} and provides flexibility with fewer parameters for analysis.
+Gamma law as the limiting case for fully-developed speckle&nbsp;\cite{Ferreira2020} and provides flexibility with fewer parameters for analysis.
 
 Our work aims to improve the identification of potential roughness features in SAR intensity data.
-Physical modeling of SAR data allows to take advantage of the gamma distribution in the presence of fully developed speckles and to create a scenario with an infinite number of independent backscatterers per resolution unit, often referred to as homogeneous regions.
+<!-- ACF The following sentence is misleading: the gamma law is a consequence of infinitely many backscatterers with none dominating the return, not the other way aroud. Rephrase. -->
+Physical modeling of SAR data allows to take advantage of the gamma distribution in the presence of fully-developed speckle and to create a scenario with an infinite number of independent backscatterers per resolution unit, often referred to as homogeneous regions.
 
@@
 The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$  distributions&nbsp;[@Frery1997]. 
-The first is suitable for fully developed speckle and is a limiting case of the second model, which is interesting due to its versatility in accurately representing regions with different roughness properties&nbsp;[@Cassetti2022].
+The first is suitable for fully-developed speckle and is a limiting case of the second model, which is interesting due to its versatility in accurately representing regions with different roughness properties&nbsp;[@Cassetti2022].
 We denote $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and $Z \sim \mathcal{G}_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the respective probability density
@@
 $$
-In the physical sense, we are testing the hypothesis that the data are fully developed speckle.
+In the physical sense, we are testing the hypothesis that the data are fully-developed speckle.
 As for the parametric problem, once it is not possible to define the hypothesis $\mathcal{H}_0=\alpha=-\infty$, it is impossible to solve this problem with the parametric statistical inference alternatives (such as likelihood ratio, score, grandient and Wald hypothesis test).

### 2024-04-14 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
One more line

@@
 
-In this context, we present a set of three novel test statistics that aim to distinguish between homogeneous and non-homogeneous domains, in particular between gamma and \(\mathcal{G}^0\) distributed data, each with a known number of looks.
-To understand the core ideas behind our approach, we explore the use of properties such as entropy and coefficient of variation.
+In this context, we present a set of three novel test statistics that aim to distinguish between homogeneous and non-homogeneous return, in particular between gamma and \(\mathcal{G}^0\) distributed data, assuming the number of looks is known.
+We use properties such as entropy and coefficient of variation.
 

### 2024-04-16 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Entering the size and power

@@
   We propose three test statistics to distinguish between homogeneous and inhomogeneous regions, i.e. between gamma and \(\mathcal{G}_I^0\) distributed data, both with a known number of looks. 
-  The first test statistic uses a bootstrapped nonparametric estimator of Shannon entropy, which provides a robust assessment in the face of uncertain distributional assumptions.
+  The first test statistic uses a bootstrapped non-parametric estimator of Shannon entropy, which provides a robust assessment in the face of uncertain distributional assumptions.
   The second test uses the classical coefficient of variation. 
@@
 The variable with the highest CV value is the one with the largest relative dispersion around the mean value&nbsp;\cite{Banik2011}.
-
-In our study, entropy serves as a fundamental parameter that allows a robust evaluation using a bootstrapped nonparametric estimator of the Shannon entropy.
-At the same time, we use the classical CV and an alternative form based on the ratio between the median absolute deviation and the median. 
-The CV is known as an efficient and robust index for texture information and measures the homogeneity of the image&nbsp;\cite{Lopes1990}.
-Applying these test statistics to generate maps of \(p\) values facilitates testing the homogeneity hypothesis and reveals different types of targets in the SAR data. 
-Through extensive experiments with real and simulated SAR data, we demonstrate the superiority of our proposed method over existing approaches.
-
-Applying these test statistics to generate $p$-value maps facilitates testing of the homogeneity hypothesis, revealing diverse types of targets within the SAR data. 
-Through extensive experimentation involving real and simulated SAR data, we demonstrate the superiority of our proposed methodology over existing approaches.
+The coefficient of variation is the basic measure of heterogeneity in SAR data&nbsp;\cite{oliverquegan98}.
+We study two ways of estimating the coefficient of variation.
+
+The other parameter we study is the Shannon entropy.
+Different models for SAR data have different entropy values, but this fundamental quantity can be also estimated in a model-agnostic way.
+We exploit this property and design a bootstrap-improved non-parametric estimator for the Shannon entropy.
+
+We devise test statistics based on these three estimators: the classical coefficient of variation, a robust version, and the Shannon entropy estimator.
+We apply these test statistics to generate maps of evidence of homogeneity
+that reveal different types of targets in the SAR data. 
+Through extensive experiments with simulated and SAR data, we demonstrate the superiority of our proposed method over existing approaches.
 
@@
 data. 
-Section&nbsp;\ref{sec:test} outlines hypothesis tests based on nonparametric entropy estimators and coefficients of variation. 
+Section&nbsp;\ref{sec:test} outlines hypothesis tests based on non-parametric entropy and coefficients of variation estimators. 
 In Section&nbsp;\ref{sec:Results} we present experimental results. 
-Finally, in Section&nbsp;\ref{sec:conclusion} the conclusions are presented.
+Finally, we draw our conclusions in Section&nbsp;\ref{sec:conclusion}.
 
@@
 \begin{align}
-    E_{G_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\Gamma(L)}, \quad \alpha <-r. 
+    E_{\mathcal{G}_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\Gamma(L)}, \quad \alpha <-r. 
     \label{E:rmom}
@@
 Although the \(\mathcal{G}_I^0\) distribution is defined by the parameters \(\alpha\) and \(\gamma\), in the SAR literature&nbsp;\cite{Nascimento2010} the texture \(\alpha\) and the mean \(\mu\) are usually used.
-In this way, we calculate the expected value \(\mu\) using the expression in&nbsp;\eqref{E:rmom}, and we reparametrize&nbsp;\eqref{E:gi01} with \(\mu\),
-\(\alpha\), and \(L\).
-Then \begin{align*}
-    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
-\end{align*} 
-The reparametrized pdf that characterizes the law \(G_I^0(\mu, \alpha, L)\) is thus
+The expected value \(\mu\) using the expression in&nbsp;\eqref{E:rmom} is
+\begin{equation}
+    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1},
+\end{equation} 
+and we reparametrize&nbsp;\eqref{E:gi01} with \(\mu\) obtaining:
 \begin{equation}
@@
 
-Using&nbsp;\eqref{E:entropy2}, we can express the Shannon entropy of $\Gamma_{\text{SAR}}$in&nbsp;\eqref{E:gamma1} and $G_I^0$ in&nbsp;\eqref{E:gi02} based on&nbsp;\cite{Cassetti2022} and&nbsp;\cite{Ferreira2020}:
+Using&nbsp;\eqref{E:entropy2}, we obtain the Shannon entropy of $\Gamma_{\text{SAR}}$ in&nbsp;\eqref{E:gamma1} and $G_I^0$ in&nbsp;\eqref{E:gi02}:
 \begin{equation}
@@
 where $\psi^{(0)}(\cdot)$ is the digamma function.
-Figure&nbsp;\ref{fig:Plot_GI0_to_gamma1}, shows the behavior of the entropy of \(G_I^0\) when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), where the approximation to the entropy of \(\Gamma_{\text{SAR}}\) can be observed when \(\alpha\) assumes large negative values.
-In an interpretative sense, we can conclude that the more heterogeneous (high values of $\alpha$) the SAR region is, the higher the value of entropy (or degree of disorder).
-It is worth noting that this conclusion confirms what is written in the SAR literature.
+Figure&nbsp;\ref{fig:Plot_GI0_to_gamma1}, shows the entropy of \(G_I^0\) as a function of $\mu$ when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\).
+Notice that it converges to the entropy of \(\Gamma_{\text{SAR}}\) when \(\alpha\to-\infty\), as expected.
+The more heterogeneous (large $\alpha$ values) the SAR region is, the larger the entropy (or degree of disorder) is.
 
@@
 
-The problem of non-parametric estimating of $H(Z)$ has been considered by many authors including&nbsp;\cite{vasicek1976test, Wieczorkowski1999,correa1995new,AlOmari2019}, who have proposed estimators based on spacings.
+Several authors&nbsp;\cite{vasicek1976test, Wieczorkowski1999,correa1995new,AlOmari2019} have studied the problem of the non-parametric estimation of $H(Z)$.
+Their proposals use estimators based on differences between order statistics: spacings.
 
@@
 	\end{equation*}
-where $m<n/2$ is a positive integer, $Z_{(i+m)}-Z_{(i-m)}$ is the $m$-spacing and $Z_{(1)}\leq Z_{(2)}\leq\ldots\leq Z_{(n)}$ are the order statistics and $Z_{(i)}= Z_{(1)}$ if $i<1$, $Z_{(i)}= Z_{(n)}$ if $i>n$.
+where $m<n/2$ is a positive integer, $Z_{(i+m)}-Z_{(i-m)}$ is the $m$-spacing and $Z_{(1)}\leq Z_{(2)}\leq\ldots\leq Z_{(n)}$ are the order statistics, $Z_{(i)}= Z_{(1)}$ if $i<1$, $Z_{(i)}= Z_{(n)}$ if $i>n$.
 
@@
 and Al Omary&nbsp;\cite{IbrahimAlOmari2014}, \(\widehat{H}_{\mathrm{AO}}\).
-
-## Enhanced Bootstrap Technique
-
-We use the bootstrap technique to refine the accuracy of existing nonparametric entropy estimators.
+<!-- ACF Define the estimators and state their main properties -->
+
+These estimators are asymptotically consistent, 
+but we will use improved bootstrap-improved versions because we need them to perform well with small samples.
+
+## Enhanced estimators with Bootstrap
+
+We use the bootstrap technique to refine the accuracy of non-parametric entropy estimators. 
 In this approach, new data sets are generated by replicate sampling from an existing data set&nbsp;\cite{Michelucci2021}.
@@
 \end{align*} 
-where \(B\) is the number of replications in the bootstrap
-technique. 
+where \(B\) is the number of observations obtained by resampling from $\bm Z$ with replacement. 
 Applying this methodology, the original estimators of Correa,
@@
 
-We analyzed the performance of these estimators with a Monte Carlo study: \(500\) samples of \(G_I^0\) of size
-\(n\in\left\{9, 25, 49, 81, 121\right\}\) and different values for mean, number of looks and roughness. We present the results with
+We analyzed the performance of these estimators with a Monte Carlo study: \(500\) samples from the \(G_I^0\) law of size
+\(n\in\left\{9, 25, 49, 81, 121\right\}\) and different mean, number of looks and roughness. 
+We present the results with
 \(\mu\in\left\{1, 10\right\}\), \(\alpha=-10\) and \(L=5\). 
-The results are also adherent for the other situations.
-In the bootstrap technique, each sample is replicated a hundred times with replacement.
-We use the following heuristic formula for spacing,
-\(m=\left[\sqrt{n}+0.5\right]\).
-
-In Figure&nbsp;\ref{fig:Plot_bias_mse_gi0} we show comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions.
-The use of the bootstrap technique shows higher precision, lower bias and MSE, and improved convergence.
+The results are consistent with the other situations. 
+We used $B=100$ bootstrap samples and the heuristic spacing
+\(m=\left[\sqrt{n}+0.5\right]\), as recommended in the literature.
+
+In Figure&nbsp;\ref{fig:Plot_bias_mse_gi0} we show the bias and mean squared error (MSE) of the original non-parametric entropy estimators and their respective bootstrap-enhanced versions. 
+Bootstrap-enhanced estimators have smaller bias and MSE, especially for sample sizes below $81$.
 The results of the simulation can be found in
 Table&nbsp;\ref{tab:table2}.
-
-The precision of the estimators resulting from the comparison of bias and MSE benefits significantly from the bootstrap technique, especially for sample sizes below 81.
 
@@
 
-We explore a robust alternative to CV, as described in&nbsp;\cite{Ospina2019}, which incorporates the ratio between the mean absolute deviation from the median (MnAD) and the median, two well-known robust measures of
+We explore a robust alternative to CV, as described by \citet{Ospina2019}, which incorporates the ratio between the mean absolute deviation from the median (MnAD) and the median, two well-known robust measures of
 scale and location, respectively. The sample version for the MnAD is defined as
@@
 We aim at testing the following hypotheses: 
-
 $$
- \begin{cases}\mathcal{H}_0: \text{ The data comes from the } \Gamma_{\text{SAR}}\\ 
-  \mathcal{H}_1:\text{ The data comes from the } G_I^0.\end{cases}
+\begin{cases}
+  \mathcal{H}_0: \text{ The data come from the } \Gamma_{\text{SAR}}\text{ law},\\ 
+  \mathcal{H}_1:\text{ The data come from the } G_I^0 \text{ distribution}.
+\end{cases}
 $$
-In the physical sense, we are testing the hypothesis that the data are fully-developed speckle.
-As for the parametric problem, once it is not possible to define the hypothesis $\mathcal{H}_0=\alpha=-\infty$, it is impossible to solve this problem with the parametric statistical inference alternatives (such as likelihood ratio, score, grandient and Wald hypothesis test).
+We are testing the hypothesis that the data are fully-developed speckle versus the alternative of data with roughness.
+As for the parametric problem, once it is not possible to define the hypothesis $\mathcal{H}_0=\alpha=-\infty$, it is impossible to solve this problem with parametric  inference alternatives (such as likelihood ratio, score, gradient and Wald hypothesis test).
 The proposed tests to solve this physical problem in SAR systems are described below.
@@
 Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption.
-A low variance as well as a skewness and an excessive kurtosis of almost zero indicate limited dispersion, symmetry and a slight tail.
+A low variance as well as a skewness and an excessive kurtosis of almost zero indicate limited dispersion, symmetry and a light tail.
 Normal QQ plots confirm that there is no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.
@@
 
-After checking the normality of the data, we examined the possibilities of the proposed test in terms of size and power.
+After checking the normality of the test statistics, we examined the possibilities of the proposed test in terms of size and power.
 Under \(\mathcal{H}_0\), the distribution of the test statistic is asymptotically normal.
 Therefore, the \(p\) value is calculated as
-\(2\Phi(-\mid \varepsilon\mid)\), where \(\Phi\) is the standard
-Gaussian cumulative distribution and \(\varepsilon\) is the standardized test statistic given by :
+\(2\Phi(-|\varepsilon|)\), where \(\Phi\) is the standard
+Gaussian cumulative distribution function, and \(\varepsilon\) is the standardized test statistic given by :
 \[
@@
 
-## Real Data
+## SAR Data
 

### 2024-04-16 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Clarify the power study
Clarification before meeting

@@
 The first test statistic evaluates the behavior of the data under the null hypothesis using the empirical distribution: 
+<!-- ACF This is an important contribution.
+Highlight the rationale: under H0, \widetilde{H} (estimated) and H_{\Gamma_{\text{SAR}}}(L) (fixed) should be close.
+Therefore, their difference should be small.
+Explain why you need \widebar{Z} -->
 \begin{equation}
@@
 The results are shown in Table&nbsp;\ref{tab:table_size_power}.
+<!-- ACF Please clarify which alternatives you used for the power -->
 

### 2024-04-24 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Made corrections and added new images

@@
   The first test statistic uses a bootstrapped non-parametric estimator of Shannon entropy, which provides a robust assessment in the face of uncertain distributional assumptions.
-  The second test uses the classical coefficient of variation. 
+  The second test uses the classical coefficient of variation (CV). 
   The third test uses an alternative form of estimating the CV based on the ratio of the mean absolute deviation from the median to the median. 
   We apply our test statistic to create maps of \(p\) values for the homogeneity hypothesis.
-  These maps identify different types of targets. 
-  We show that our proposal outperforms its competitors using simulated and SAR data.
-# ACF Which is "our proposal" and which are the "competitors"?
+  Finally, we show that our proposal, the entropy-based test, outperforms existing methods such as the classical CV and its alternative variant, in identifying heterogeneity when applied to both simulated and actual data.
+#These maps identify different types of targets.
+# We show that our proposal outperforms its competitors using simulated and SAR data.
+# ACF Which is "our proposal" and which are the "competitors"? # ok
 keywords: |
@@
 acknowledgement: |
-  This study was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior - Brasil (CAPES) - Finance Code 001.
+  The author J.A.
+would like to thank the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) and the Fundação de Amparo à Ciência e Tecnologia de Pernambuco (FACEPE) for their support.
 authorcontributions: |
-  For research articles with several authors, a short paragraph specifying their 
-  individual contributions must be provided. The following statements should be 
-  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
-  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
-  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
-  limited to those who have contributed substantially to the work reported.
+  All authors (A.C.F., J.A, and A.D.C.N.) discussed the results and contributed to the research. All authors have read and agreed to the published version of the manuscript.
+
 funding: |
@@
 dataavailability: |
-  Not applicable.
+  The Sentinel-1  images are made publicly available by European Space Agency via Copernicus Data Space Ecosystem at \url{https://dataspace.copernicus.eu/} (accessed on 24 April 2024).
 conflictsofinterest: |
@@
 supplementary: |
- This article is fully reproducible using RMarkdown. All code and data are accessible at
- \url{https://github.com/rjaneth/identifying-heterogeneity-in-sar-data-with-new-test-statistics} (accessed on 12 April 2024).
+ This article was written in Rmarkdown and is fully reproducible. The code and data are accessible at
+ \url{https://github.com/rjaneth/identifying-heterogeneity-in-sar-data-with-new-test-statistics} (accessed on 24 April 2024).
 # abbreviations:
@@
 source("../Code/R/MainFunctions/ebrahimi_estimator.R")
-source("../Code/R/MainFunctions/noughabi_arghami_estimator.R")
+#source("../Code/R/MainFunctions/noughabi_arghami_estimator.R")
 source("../Code/R/MainFunctions/vasicek_estimator.R")
@@
 source("../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
-source("../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.R")
+#source("../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.R")
 source("../Code/R/MainFunctions/bootstrap_vasicek_estimator.R")
@@
 <!-- ACF The following sentence is misleading: the gamma law is a consequence of infinitely many backscatterers with none dominating the return, not the other way aroud. Rephrase. -->
-Physical modeling of SAR data allows to take advantage of the gamma distribution in the presence of fully-developed speckle and to create a scenario with an infinite number of independent backscatterers per resolution unit, often referred to as homogeneous regions.
+<!-- JA Corrected -->
+Physical modeling of SAR data allows the use of the Gamma distribution in the presence of fully-developed speckle, where an infinite number of independent backscatterers per resolution unit is assumed, commonly referred to as homogeneous regions
 
@@
 
-The coefficient of variation (CV), introduced in 1896 by Pearson&nbsp;\cite{Pearson1896}, is a relative dispersion measure widely used in various fields of applied statistics, including sampling, biostatistics, medical and biological research, climatology and other fields&nbsp;\cite{hendricks1936sampling,Tian2005,SubrahmanyaNairy2003,Chankham2024}.
+The CV, introduced in 1896 by Pearson&nbsp;\cite{Pearson1896}, is a relative dispersion measure widely used in various fields of applied statistics, including sampling, biostatistics, medical and biological research, climatology and other fields&nbsp;\cite{hendricks1936sampling,Tian2005,SubrahmanyaNairy2003,Chankham2024}.
 It facilitates the comparison of variability between different populations and is particularly valuable for comparing variables with different units. 
@@
 Several authors have explored adaptations to Vasicek's estimator. 
-We consider three estimators known for their superior performance&nbsp;\cite{Cassetti2022}:
-Correa&nbsp;\cite{correa1995new}, \(\widehat{H}_{\text{C}}\);
-Ebrahimi et al&nbsp;\cite{Ebrahimi1994}, \(\widehat{H}_{\mathrm{E}}\);
-and Al Omary&nbsp;\cite{IbrahimAlOmari2014}, \(\widehat{H}_{\mathrm{AO}}\).
-<!-- ACF Define the estimators and state their main properties -->
+We consider three estimators known for their superior performance&nbsp;\cite{Cassetti2022}.
+
+* Correa&nbsp;\cite{correa1995new}:
+\begin{equation}
+\widehat{H}_{\text{C}}(\bm{Z})=-\frac{1}{n} \sum_{i=1}^n \log \frac{\sum_{j=i-m}^{i+m}(j-i)\left(Z_{(j)}-\widebar{Z}_{(i)}\right)}{n\sum_{j=i-m}^{i+m}\left(Z_{(j)}-\widebar{Z}_{(i)}\right)^2},
+\end{equation}
+where  $\widebar{Z}_{(i)}=(2 m+1)^{-1} \sum_{j=i-m}^{i+m} Z_{(j)}$, $m< \frac{n}{2}$, $Z_{(i)}=Z_{(1)}$ for $i<1$ and $Z_{(i)}=Z_{(n)}$ for $i>n$.
+Based on simulation, he showed that his estimator has a smaller mean square error in comparison with Vasicek's approach.
+
+* Ebrahimi et al.&nbsp;\cite{Ebrahimi1994}:
+\begin{equation}
+\widehat{H}_{\text{E}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{c_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
+\end{equation}
+where
+$$
+c_i=\begin{cases}1+(i-1) / m & \text { if } \quad 1 \leq i \leq m, \\ 2 & \text { if }\quad m+1 \leq i \leq n-m,\\ 1+(n-i) / m & \text { if }\quad n-m+1 \leq i \leq n.\end{cases}
+$$
+The authors proved that $\widehat{H}_{\text{E}}(\bm{Z})\xrightarrow{p}H[Z]$, when $m,n\rightarrow\infty$ and  $m/n\rightarrow0$.
+
+* Al-Omari&nbsp;\cite{IbrahimAlOmari2014}:
+$$
+\widehat{H}_{\text{AO}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{\omega_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right]
+$$
+where
+$$
+\omega_i= \begin{cases}3/2 & \text { if }\quad 1 \leq i \leq m, \\ 2 & \text { if }\quad m+1 \leq i \leq n-m, \\ 3/2 & \text { if } \quad n-m+1 \leq i \leq n,\end{cases}
+$$
+in which $Z_{(i-m)}=Z_{(1)}$ for $i \leq m$, and $Z_{(i+m)}=Z_{(n)}$ for $i \geq n-m$.
 
@@
 
-We analyzed the performance of these estimators with a Monte Carlo study: \(500\) samples from the \(G_I^0\) law of size
-\(n\in\left\{9, 25, 49, 81, 121\right\}\) and different mean, number of looks and roughness. 
-We present the results with
-\(\mu\in\left\{1, 10\right\}\), \(\alpha=-10\) and \(L=5\). 
+We analyzed the performance of these estimators with a Monte Carlo study: \(1000\) samples from the \(\Gamma_{\text{SAR}}\) distribution of size
+\(n\in\left\{9, 25, 49, 81, 121\right\}\), with
+\(\mu\in\left\{1, 10\right\}\) and \(L=5\). 
 The results are consistent with the other situations. 
-We used $B=100$ bootstrap samples and the heuristic spacing
+We used $B=200$ bootstrap samples and the heuristic spacing
 \(m=\left[\sqrt{n}+0.5\right]\), as recommended in the literature.
@@
 # Number of replications
-R <-300
+R <-500
 
 # Number of bootstrap replications
-B1 <- 20
+B1 <- 30
 mu_values <- c(1, 10)
-alpha <- -20
+alpha <- -50
 L <- 5
@@
 # Define estimators
-estimators_to_table <- c( "Al Omari","Correa", "Ebrahimi", "Al Omari Bootstrap",  "Correa Bootstrap","Ebrahimi Bootstrap")
+estimators_to_table <- c( "Correa", "Ebrahimi", "Al Omari", "Correa Bootstrap","Ebrahimi Bootstrap","Al Omari Bootstrap")
 
@@
 
-colnames(reshaped_results) <- c("$\\mu$", "$n$", "$\\widehat{H}_{\\text{AO}}$", "$\\widehat{H}_{\\text{C}}$", "$\\widehat{H}_{\\text{E}}$", "$\\widetilde{H}_{\\text{AO}}$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$",  "$\\widehat{H}_{\\text{AO}}$", "$\\widehat{H}_{\\text{C}}$", "$\\widehat{H}_{\\text{E}}$","$\\widetilde{H}_{\\text{AO}}$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$")
+colnames(reshaped_results) <- c("$\\mu$", "$n$",  "$\\widehat{H}_{\\text{C}}$", "$\\widehat{H}_{\\text{E}}$","$\\widehat{H}_{\\text{AO}}$",  "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$","$\\widetilde{H}_{\\text{AO}}$",   "$\\widehat{H}_{\\text{C}}$", "$\\widehat{H}_{\\text{E}}$","$\\widehat{H}_{\\text{AO}}$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$","$\\widetilde{H}_{\\text{AO}}$")
 
@@
 
-We explore a robust alternative to CV, as described by \citet{Ospina2019}, which incorporates the ratio between the mean absolute deviation from the median (MnAD) and the median, two well-known robust measures of
-scale and location, respectively. The sample version for the MnAD is defined as
+We explore a robust alternative to CV, as describedby&nbsp;\cite{Ospina2019}, which incorporates the ratio between the mean absolute deviation from the median (MnAD) and the median, two well-known robust measures of
+scale and location, respectively. 
+The sample version for the MnAD is defined as
 \(n^{-1}\sum_{i=1}^n|x_i-\widehat{Q}_2|\), where \(\widehat{Q}_2\)
@@
 
-The first test statistic evaluates the behavior of the data under the null hypothesis using the empirical distribution: 
+For a random sample \(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) from a distribution $\mathcal{D}$, a test statistic is proposed.
+It is based on an  empirical distribution that arises  from the difference between non-parametrically estimated entropies $\widetilde{H}(\bm{Z})$ and the analytical entropy of Gamma SAR&nbsp;\eqref{E:E-gamma} evaluated at the logarithm of the sample mean, where $L_0\geq 1$ is known.
+
+Hence, the entropy-based test statistic is defined as:
+\begin{equation}
+\label{Eq:test_e}
+S(\bm{Z};L_0)= \widetilde{H}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L_0)+\ln \widebar{\bm{Z}}\right].
+\end{equation}
+
+This test statistic  aims to assess the behavior of the data under the null hypothesis using the empirical distribution.
+If the data represent fully-developed speckle, the density should center around zero, i.e., $S(\bm{Z};L_0)\approx 0$.
+Otherwise, under the alternative hypothesis, the empirical distribution would shift from zero, suggesting significant differences and implying the presence of heterogeneous clutter.
+
 <!-- ACF This is an important contribution.
@@
 Explain why you need \widebar{Z} -->
-\begin{equation}
-\label{Eq:test_e}
-S_H= \widetilde{H}-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{Z}\right].
-\end{equation}
-The values should be around zero under the null hypothesis and far otherwise. 
-<!-- This suggests significant differences and implies the presence of heterogeneous clutter. -->
-Figure&nbsp;\ref{fig:Plot_density} shows the empirical test statistic densities for different sample sizes, and Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean, SD, variance (Var), skewness (SK), excessive kurtosis (EK) and Anderson--Darling \(p\) values for normality.
+<!-- JA Corrected -->
+
+Figure&nbsp;\ref{fig:Plot_density} shows the empirical test statistic densities for different sample sizes using \(\widetilde{H}_{\text{AO}}\) estimator, and Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean, SD, variance (Var), skewness (SK), excessive kurtosis (EK) and Anderson--Darling \(p\) values for normality.
 Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption.
@@
 mu <- 1
-B <- 2
+B <- 50
 
@@
       #z <- gi0_sample(mu, alpha1, L, s)
-      TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
+      TestStat1[r] <-bootstrap_al_omari_1_estimator(z,B) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+      #TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
     }
@@
   combined_summary_stats,
-  caption = "Descriptive analysis of $S_H$ with $L\\in\\left\\{3,5, 8,11\\right\\}$ and $\\mu=1$.",
+  caption = "Descriptive analysis of $S(\\bm Z; L)$ with $L\\in\\left\\{3,5, 8,11\\right\\}$ and $\\mu=1$.",
   format = "latex",
@@
 
-We have nominal levels of \SI{1}{\ percent}, \SI{5}{\ percent}, and
+We have nominal levels of \SI{1}{\percent}, \SI{5}{\percent}, and
 \SI{10}{\percent}. 
-In terms of size, \(1000\) simulations were used for different sample sizes with satisfactory results. 
+In terms of size, \(1000\) simulations were used for different sample sizes from the $\Gamma_{\text{SAR}}$ distribution, with different values of $L$,  $\mu=1$ and \(\widetilde{H}_{\text{AO}}\) estimator.
 In all cases, the nominal level was achieved. 
+We assessed the test power using \(1000\) simulations for different sample sizes from the $G_I^0$ distribution, with  $\mu=1$, $\alpha=-2$, and \(\widetilde{H}_{\text{AO}}\) estimator.
 The power generally improves with increasing sample size and number of looks.
@@
 <!-- ACF Please clarify which alternatives you used for the power -->
+<!-- JA Corrected -->
 
@@
 mu <- 1
-B <- 1
+B <- 100
 L_values <- c( 3, 5, 8, 11)
@@
         z <- gamma_sar_sample(L, mu, s)
-        TestStat[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
+        TestStat[r] <-bootstrap_al_omari_1_estimator(z,B) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+        #TestStat[r] <- bootstrap_correa_estimator(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
       }
@@
         for (r in 1:R) {
-          z <- gi0_sample(mu, -5, L, s)
-          TestStat[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
+          z <- gi0_sample(mu, -2, L, s)
+          TestStat[r] <-bootstrap_al_omari_1_estimator(z,B) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+          #TestStat[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
         }
@@
 L_values <- c(3, 5,  8, 11)
-B <- 1
+B <- 100
 sample_sizes <- c(25, 49, 81, 121)
@@
 
-The AIC and BIC results in Tables&nbsp;\ref{tab:table_aic_gamma}--\ref{tab:table_aic_gio_MnADmedian} indicate that the CV and \(\text{CV}_{\text{MnAD}}\) data from different distributed gamma and \(G_I^0\) synthetic sample sizes match the properties of an LN distribution.
-\textcolor{green}{%
+The AIC and BIC results in Tables&nbsp;\ref{tab:table_aic_gamma}--\ref{tab:table_aic_gio_MnADmedian} indicate that the CV and \(\text{CV}_{\text{MnAD}}\) data from different distributed Gamma and \(G_I^0\) synthetic sample sizes match the properties of an LN distribution.
 It is important to note that this conclusion was drawn empirically based on a dictionary of distributions that are analytically tractable and well-defined under biparametric, unimodal, asymmetric, and positive distributions.
-}
-
-\textcolor{red}{%
-ADCN: Caros, esse é o ponto mais delicado da excelente ideia desse paper em minha opinião.
+
+<!-- \textcolor{red}{% -->
+<!-- ADCN: Caros, esse é o ponto mais delicado da excelente ideia desse paper em minha opinião.
 Não me oponho a colocarmos a lognormal como uma possibilidade, mas é preciso deixar claro que é uma possibilidade empírica.
@@
 Vejam se estão de acordo.
-}
+-->
+<!-- } -->
 
@@
 plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
-denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlab = "CV")
-qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
-cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlab = "CV")
-ppcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
+denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV")
+qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
+cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV")
+ppcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
 
@@
 
-Figure&nbsp;\ref{fig:sim_SAR_Images}(a) shows the phantom used for a simulated image with dimensions of $250\times 250$ pixels to show the differences between heterogeneous (dark, $\alpha=-2$) and homogeneous (light, $\alpha=-10$) regions, with $L = 5$.
-The regions are formed by independent draws from the $G^0_I$ distribution.
-
-The three test statistics are applied to the simulated image using local sliding windows of size $7\times 7$.
-
-The resulting $p$-values for the tests $S_H$, $T_{\text{CV}}$, and $T_{\text{CV}_{\text{MnAD}}}$ are shown in Figures&nbsp;\ref{fig:sim_SAR_Images}(b)--(d) and Figures&nbsp;\ref{fig:sim_SAR_Images_p05}(a)--(c), respectively.
-The new images reveal that a darker background indicates homogeneity, while lighter backgrounds represent heterogeneous areas.
-
-```{r sim_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics.
-(a) Simulated image; $P$-values from the entropy-based test; (c) $P$-values from the CV test; (d) $P$-values from the   $\\text{CV}_{\\text{MnAD}}$ test; ',  fig.subcap=c('', '', '', ''), out.width = c("40mm", "40mm","40mm", "40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
-knitr::include_graphics("../Figures/PNG/simulated7x7.png")
-knitr::include_graphics("../Figures/PNG/sim_pvalue7x7_total_H.png")
-knitr::include_graphics("../Figures/PNG/sim_pvalue7x7_total_cv.png")
-knitr::include_graphics("../Figures/PNG/sim_pvalue7x7_total_mnad.png")
-```
-```{r sim_SAR_Images_p05, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of tests on simulated data with a threshold of $0.1$ of the $p$-value.
+Figure&nbsp;\ref{fig:sim_Phantom} shows the phantom used for a simulated image with dimensions of $500\times 500$ pixels that consists of four smaller phantoms, each of which exhibits differences between homogeneous and heterogeneous regions.
+The regions are formed by independent draws from the $G^0_I$ distribution, with $L = 5$ and varying $\alpha$.
+
+The $\alpha$ parameter of the $G_I^0$ distribution is essential for interpreting texture characteristics. 
+Values close to zero greater than $-3$ suggest extremely textured targets, such as urban zones&nbsp;\cite{Frery2019a}. 
+As the value decreases, it indicates regions with moderate texture (in $\left[-6,-3\right]$), related to forest zones, while values below $-6$ correspond to textureless regions, such as pasture, agricultural fields, and water bodies&nbsp;\cite{Neto2023}.
+
+```{r sim_Phantom, echo=FALSE, message=FALSE, warning=FALSE, out.width="40%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Simulated image: Light regions in upper/lower left phantoms show homogeneity ($\\alpha=-10$), while dark ones suggest heterogeneity ($\\alpha=-2$).
+Conversely, in upper/lower right phantoms, dark regions mean homogeneity ($\\alpha=-9$), light ones mean heterogeneity ($\\alpha=-3$).
+', fig.width = 4, fig.height = 4}
+knitr::include_graphics("../Figures/PNG/Phantom.png")
+
+```
+
+The three test statistics (entropy-based, ${\text{CV}}$, and ${\text{CV}_{\text{MnAD}}}$) are applied to the simulated image using local sliding windows of size $7\times 7$, as shown in Figures&nbsp;\ref{fig:sim_results}(a)--(c).
+For the first test we considered the \(\widetilde{H}_{\text{AO}}\)  estimator due to its superior performance in simulations and shorter processing time compared to other entropy estimators.
+
+```{r sim_results, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics: (a)  Entropy-based test; (b)  CV test; (c)   $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c('', '', ''), out.width = c( "40mm","40mm", "40mm"),  fig.ncol=3, fig.width = 40, fig.height = 30}
+
+knitr::include_graphics("../Figures/PNG/test-entropy-Phantom_AO_7W_L5_100b.png")
+knitr::include_graphics("../Figures/PNG/cv_values_Phantom.png")
+knitr::include_graphics("../Figures/PNG/mnad_Phantom.png")
+```
+
+The resulting $p$-values for each test  are shown in Figures&nbsp;\ref{fig:sim_SAR_Images}(a)--(c) and Figures&nbsp;\ref{fig:sim_SAR_Images_p05}(a)--(c), respectively. 
+The new images reveal that a lighter  background indicates homogeneity, while darker backgrounds represent heterogeneous areas.
+
+```{r sim_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Map of $p$-values: (a) Entropy-based test; (b)  CV test; (c)  $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c('', '', ''), out.width = c( "40mm","40mm", "40mm"),  fig.ncol=3, fig.width = 40, fig.height = 30}
+
+knitr::include_graphics("../Figures/PNG/H_pvalue_Phantom_AO_7x7_L5_100b.png")
+knitr::include_graphics("../Figures/PNG/cv_p_values_Phantom.png")
+knitr::include_graphics("../Figures/PNG/mnad_p_values_Phantom.png")
+```
+```{r sim_SAR_Images_p05, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value: (a) Entropy-based test; (b) CV test; (c) $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/H_005_pvalues_Phantom_AO_7x7.png")
+knitr::include_graphics("../Figures/PNG/nominal_level_005_pvalues-Phantom.png")
+knitr::include_graphics("../Figures/PNG/mnad_005_pvalues-Phantom.png")
+
+```
+
+## Real SAR Data
+
+We evaluated the proposed test statistics using three real SAR images. 
+For our analysis, we used images of the coast of Jalisco, Mexico, and of Illinois, USA. 
+These images were acquired by the Sentinel-1B satellite operating in C-band, with VV polarization, intensity format, \(L=18\) and \(L=36\)  nominal looks.
+
+The first two images have a size of \(512 \times 512\) pixels, while the third has \(1024 \times 1024\) pixels  and they contain mountainous areas, agricultural regions, water bodies and  urban areas, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)--(c).
+
+The three statistical tests are applied to the SAR images using $7\times 7$ local sliding windows, as illustrated in Figures&nbsp;\ref{fig:real_images_test_Mexico}, \ref{fig:test_lake} and&nbsp;\ref{fig:real_images_test_Illinois}.
+
+ The $p$-values obtained for each test are presented in Figures&nbsp;\ref{fig:Mexico_pvalue}, \ref{fig:lake_pvalue} and&nbsp;\ref{fig:Illinois_crops_pvalue}, respectively.
+
+In Figures &nbsp;\ref{fig:Mexico_crops_0.05}, \ref{fig:lake_0.05} and&nbsp;\ref{fig:Illinois_crops_0.05}, the maps of $p$-values represent the decisions at a $5\%$ significance level. 
+Values below  $0.05$  are represented by dark areas, indicating evidence to reject the null hypothesis and suggesting heterogeneity in these regions. 
+In contrast, values above 0.05 are represented as white areas, indicating no evidence to reject the fully-developed speckle hypothesis.
+
+```{r real_SAR_Images_coe, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Real SAR images: (a) Coast of Jalisco; (b) Illinois-Region 1; (c) Illinois-Region 2.
+',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm", "40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/Mexico_512.png")
+knitr::include_graphics("../Figures/PNG/lake_512.png")
+knitr::include_graphics("../Figures/PNG/Illinois_1024_36L.png")
+
+```
+
+```{r real_images_test_Mexico, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics, Coast of Jalisco: (a)  Entropy-based test using $\\widetilde{H}_{\\text{AO}}$ estimator; (b)  CV test; (c)   $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c('', '', ''), out.width = c( "40mm","40mm", "40mm"),  fig.ncol=3, fig.width = 40, fig.height = 30}
+
+knitr::include_graphics("../Figures/PNG/Entropy_Mexico_512_18L_AO_200b.png")
+knitr::include_graphics("../Figures/PNG/cv_mexico_512.png")
+knitr::include_graphics("../Figures/PNG/mnad_mexico_512.png")
+```
+
+```{r Mexico_pvalue, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Map of $p$-values, Coast of Jalisco: (a) Entropy-based test; (b)  CV test; (c)  $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/H_pvalue_Mexico_512_18L_AO_200b.png")
+knitr::include_graphics("../Figures/PNG/cv_pvalues_mexico_512.png")
+knitr::include_graphics("../Figures/PNG/mnad_p_values_mexico_512.png")
+
+```
+
+```{r Mexico_crops_0.05, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value for the Coast of Jalisco.
 (a) Entropy-based test; (b) CV test; (c) $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
-knitr::include_graphics("../Figures/PNG/sim_pvalue7x7_H.png")
-knitr::include_graphics("../Figures/PNG/sim_pvalue7x7_cv.png")
-knitr::include_graphics("../Figures/PNG/sim_pvalue7x7_mnad.png")
-
-```
-
-## SAR Data
-
-We evaluated the proposed test statistic using two real SAR images. 
-For our analysis, we used images of the city of Frankfurt, Germany, and of Ottawa, Canada. 
-These images were acquired by the Sentinel-1A satellite operating in C-band, with VV polarization, intensity format and
-\(L=5\) nominal looks.
-Both images have a size of \(512 \times 512\) pixels and contain urban areas, water and forest regions, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)--(b).
-
-  The $p$-values obtained for the $S_H$, $T_{\text{CV}}$, and $T_{\text{CV}_{\text{MnAD}}}$ tests are presented in Figures&nbsp;\ref{fig:sim_SAR_Images_Frankfurt}--\ref{fig:sim_SAR_Images_01_Ottawa}, respectively.
-
-In general, using the original and robust CV is more meaningful than using Shannon entropy to capture texturelessness.
+knitr::include_graphics("../Figures/PNG/H_005__Mexico_512_18L_AO_200b.png")
+knitr::include_graphics("../Figures/PNG/cv_005_pvalues_mexico_512.png")
+knitr::include_graphics("../Figures/PNG/mnad_005_mexico_512.png")
+
+```
+
+```{r test_lake, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics, Illinois-Region 1: (a)  Entropy-based test using $\\widetilde{H}_{\\text{AO}}$ estimator; (b)  CV test; (c)   $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c('', '', ''), out.width = c( "40mm","40mm", "40mm"),  fig.ncol=3, fig.width = 40, fig.height = 30}
+
+knitr::include_graphics("../Figures/PNG/Entropy_lake_512_36L_AO_100b.png")
+knitr::include_graphics("../Figures/PNG/cv_lake_512.png")
+knitr::include_graphics("../Figures/PNG/mnad_lake_512.png")
+```
+
+```{r lake_pvalue, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Map of $p$-values, Illinois-Region 1: (a) Entropy-based test; (b)  CV test; (c)  $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/H_pvalue_lake_512_36L_AO_100b.png")
+knitr::include_graphics("../Figures/PNG/cv_pvalues_lake_512.png")
+knitr::include_graphics("../Figures/PNG/mnad_p_values_lake_512.png")
+
+```
+
+```{r lake_0.05, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Illinois-Region 1.
+(a) Entropy-based test; (b) CV test; (c) $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/H_005_lake_512_36L_AO_100b.png")
+knitr::include_graphics("../Figures/PNG/cv_005_pvalues_lake_512.png")
+knitr::include_graphics("../Figures/PNG/mnad_005_lake_512.png")
+
+```
+
+```{r real_images_test_Illinois, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics, Illinois-Region 2: (a)  Entropy-based test using $\\widetilde{H}_{\\text{AO}}$ estimator; (b)  CV test; (c)   $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c('', '', ''), out.width = c( "40mm","40mm", "40mm"),  fig.ncol=3, fig.width = 40, fig.height = 30}
+
+knitr::include_graphics("../Figures/PNG/Entropy_Illinois_1024_36L_AO_200b.png")
+knitr::include_graphics("../Figures/PNG/cv_Illinois_crops_1024.png")
+knitr::include_graphics("../Figures/PNG/mnad_Illinois_crops_1024.png")
+```
+
+```{r Illinois_crops_pvalue, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Map of $p$-values, Illinois-Region 2: (a) Entropy-based test; (b)  CV test; (c)  $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/H_pvalue_Illinois_1024_36L_AO_200b.png")
+knitr::include_graphics("../Figures/PNG/cv_pvalues_Illinois_crops_1024.png")
+knitr::include_graphics("../Figures/PNG/mnad_p_values_Illinois_crops_1024.png")
+
+```
+```{r Illinois_crops_0.05, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Illinois-Region 2.
+(a) Entropy-based test; (b) CV test; (c) $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/H_005_pvalues_Illinois_1024_36L_AO_200b.png")
+knitr::include_graphics("../Figures/PNG/cv_005_pvalues_Illinois_crops_1024.png")
+knitr::include_graphics("../Figures/PNG/mnad_005_Illinois_crops_1024.png")
+
+```
+
+In general, using Shannon entropy is more meaningful than using the original and robust CV  to capture heterogeneity.
+
 It is justified that the dark areas of the maps based on the $\text{CV}$ and $\text{CV}_{\text{MnAD}}$ tests cover the areas reported for the Shannon entropy-based map.
-Both CV-based tools predicted textureless regions as well as boundaries where the statistical properties of texture vary.
-Assuming $10\%$ as the threshold for the $p$ values, the dark region produced by the $\text{CV}$ test was higher than that produced by the $\text{CV}_{\text{MnAD}}$ and entropy test.
+
+It is noticeable that the entropy and CV-based tools predicted heterogeneity regions as well as boundaries where the statistical properties of texture vary. 
+Considering a higher significance level may increase the sensitivity to edge detection, but it may also increase the risk of detecting false heterogeneous regions.
+
+Moreover, assuming $5\%$ as the threshold for the $p$ values, the dark region produced by the $\text{CV}$ test was lower than produced by the $\text{CV}_{\text{MnAD}}$ and entropy test.
+
 The latter observation is to be expected as the latter tests are robust alternatives to the former test, which is essentially based on the expected value operator that reacts to outliers.
 
-```{r real_SAR_Images_coe, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='SAR images.
-(a) Frankfurt; (b) Ottawa.
-',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm"),  fig.ncol=2, fig.width = 20, fig.height = 10}
-knitr::include_graphics("../Figures/PNG/Intensity_Frankfurt_512_n.png")
-knitr::include_graphics("../Figures/PNG/Intensity_Ottawa_512_n.png")
-#knitr::include_graphics("../Figures/PNG/sim_pvalue7x7_mnad.png")
-
-```
-```{r sim_SAR_Images_Frankfurt, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics in Frankfurt image.
-(a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\\text{CV}_{\\text{MnAD}}$ test.
-',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
-knitr::include_graphics("../Figures/PNG/Frankfurt_512_pvalue7x7_total_H.png")
-knitr::include_graphics("../Figures/PNG/Frankfurt_512_pvalue7x7_total_CV.png")
-knitr::include_graphics("../Figures/PNG/Frankfurt_512_mnad_7_total.png")
-
-```
-```{r sim_SAR_Images_01Frankfurt, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Test results with a threshold of $0.1$ of the $p$-value for the Frankfurt image.
-(a) Entropy-based test; (b) CV test; (c) $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
-knitr::include_graphics("../Figures/PNG/Frankfurt_512_pvalue7x7_H_01.png")
-knitr::include_graphics("../Figures/PNG/Frankfurt_512_pvalue7x7_CV.png")
-knitr::include_graphics("../Figures/PNG/Frankfurt_512_mnad_7_0.1.png")
-
-```
-
-```{r sim_SAR_Images_Ottawa, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics in Ottawa image.
-(a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
-knitr::include_graphics("../Figures/PNG/Ottawa_512_pvalue7x7_total_H.png")
-knitr::include_graphics("../Figures/PNG/Ottawa_512_CV_pvalue7x7_total_CV.png")
-knitr::include_graphics("../Figures/PNG/Ottawa_512_mnad_7_total.png")
-
-```
-```{r sim_SAR_Images_01_Ottawa, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Test results with a threshold of $0.1$ of the $p$-value for the Ottawa image.
-(a) Entropy-based test; (b) CV test; (c) $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
-knitr::include_graphics("../Figures/PNG/Ottawa_512_pvalue7x7_H_01.png")
-knitr::include_graphics("../Figures/PNG/Ottawa_512_CV_pvalue7x7_CV.png")
-knitr::include_graphics("../Figures/PNG/Ottawa_512_mnad_7_0.1.png")
-
-```
-
 # Conclusion {#sec:conclusion}
 
-In this article, we have provided a practical and theoretical answer to the following physical question: How to detect texturelessness in SAR images, assuming that the SAR intensity follows the $\mathcal{G}^0_I$ distribution.
-Solving this problem is not easy, considering that the texturelessness in the parametric space of $\mathcal{G}^0_I$ means the infinity value, which is neither analytically tractable nor practically provable.
+In this article, we have provided a practical and theoretical answer to the following physical question: How to detect heterogeneity in SAR images, assuming that the SAR intensity follows the $\Gamma_{\text{SAR}}$ model.
+<!-- Solving this problem is not easy, considering that the texturelessness in the parametric space of $\mathcal{G}^0_I$ means the infinity value, which is neither analytically tractable nor practically provable.
+-->
 To this end, we proposed three novel hypothesis tests, one from the Shannon entropy and two others from the variation coefficient variants.
@@
 The results showed that they were conservative in estimating the probability of a type I error (false alarm rate) and the test power (probability of detection), which increases with sample size.
-An application to two recent SAR images was performed. 
-The results showed that the $\text{CV}_{\text{MnAD}}$ and Shannon entropy-based tests were more robust than the CV-based tests. 
-In addition, the CV-based tests were able to recognize both images without texture and those where the type of texture changes.
+An application to three recent SAR images was performed. 
+The results showed that the Shannon entropy-based test was more robust than the CV-based tests. 
+In addition, all tests were able to recognize images with different textures and identified edges where the texture type changes.

### 2024-04-24 Code/R/MainFunctions/adaptive_al_omari_1_estimator.R

@@ -1,108 +1,0 @@
-# adaptive_al_omari_1_estimator <- function(data) {
-#   n <- length(data)
-#   data_sorted <- sort(data)
-#   sum_term <- numeric(n-1)
-#   
-#   for (m in 1:(n-1)) {
-#     #sum_term <- 0
-#     
-#     for (i in 1:n) {
-#       if (i <= m) {
-#         omega_i <- 3/2
-#         diff_term <- data_sorted[i + m] - data_sorted[1]
-#       } else if (i >= n - m + 1) {
-#         omega_i <- 3/2
-#         diff_term <- data_sorted[n] - data_sorted[i - m]
-#       } else {
-#         omega_i <- 2
-#         diff_term <- data_sorted[i + m] - data_sorted[i - m]
-#       }
-#       
-#       sum_term <- sum_term + log((n / (omega_i * m)) * diff_term)
-#     }
-#     
-#     sum_term <- sum_term / n
-#   }
-#   
-#   estimated_entropy <-  (1/(n-1)) * sum_term
-#   
-#   #cat("Debug info: sum_term =", sum_term, "\n")
-#   
-#   return(estimated_entropy)
-# }
-
-adaptive_al_omari_1_estimator <- function(data) {
-  n <- length(data)
-  data_sorted <- sort(data)
-  sum_term <- numeric(n-1)
-
-  for (m in 1:(n-1)) {
-    sum_term[m] <- 0
-
-    for (i in 1:n) {
-      if (i <= m) {
-        omega_i <- 3/2
-        diff_term <- data_sorted[i + m] - data_sorted[1]
-      } else if (i >= n - m + 1) {
-        omega_i <- 3/2
-        diff_term <- data_sorted[n] - data_sorted[i - m]
-      } else {
-        omega_i <- 2
-        diff_term <- data_sorted[i + m] - data_sorted[i - m]
-      }
-
-      if (!is.na(diff_term) && diff_term != 0) {
-        sum_term[m] <- sum_term[m] + log((n / (omega_i * m)) * diff_term)
-      }
-    }
-
-    sum_term[m] <- sum_term[m] / n
-  }
-
-  estimated_entropy <- mean(sum_term, na.rm = TRUE)
-
-  #cat("Debug info: sum_term =", sum_term, "\n")
-
-  return(estimated_entropy)
-}
-
-# al_omari_estimator <- function(X) {
-#   n <- length(X)
[…]

### 2024-04-24 Code/R/MainFunctions/adaptive_correa_estimator.R

@@ -1,32 +1,0 @@
-adaptive_correa_estimator <- function(data) {
-  n <- length(data)
-  X_sorted <- sort(data)
-  C_mn <- numeric(n-1)
-  
-  for (m in 1:(n-1)) {
-    C_mn[m] <- 0
-    
-    for (i in 1:n) {
-      i_minus_m <- max(1, i - m)
-      i_plus_m <- min(n, i + m)
-      
-      X_i <- X_sorted[i]
-      X_window <- X_sorted[i_minus_m:i_plus_m]
-      X_bar_i <- mean(X_window)
-      
-      differences <- X_window - X_bar_i
-      num <- sum(differences * (i_minus_m:i_plus_m - i))
-      den <- n * sum(differences^2)
-      
-      b_i <- ifelse(den == 0, 0, num / den)
-      
-      C_mn[m] <- C_mn[m] - log(pmax(b_i, 0))
-    }
-    
-    C_mn[m] <- C_mn[m] / n
-  }
-  
-  estimated_entropy <- mean(C_mn)
-  
-  return(estimated_entropy)
-}

### 2024-04-24 Code/R/MainFunctions/bootstrap_correa_estimator_opt.R

@@ -1,30 +1,0 @@
-bootstrap_correa_estimator_opt <- function(x, B) {
-  v.Bootstrap <- numeric(B)
-  
-  for (b in seq_len(B)) {
-    same_values <- TRUE
-    while (same_values) {
-      bx <- sample(x, replace = TRUE)
-      if (!all(bx == bx[1])) {
-        same_values <- FALSE
-        entropy_result <- adaptive_correa_estimator(bx)
-        if (is.finite(entropy_result)) {
-          v.Bootstrap[b] <- entropy_result
-          #cat("Entropy for Bootstrap Sample", b, ": ", v.Bootstrap[b], "\n")
-        }
-      }
-    }
-  }
-  
-  t <- adaptive_correa_estimator(x)
-  estimated_mean <- mean(v.Bootstrap[!is.na(v.Bootstrap)])
-  
-  return(2 * t - estimated_mean)
-}
-
-# # Ejemplo de uso
-# set.seed(123)  # Para reproducibilidad
-# X <- rnorm(1000)  # Reemplaza esto con tu conjunto de datos
-# B <- 1000
-# system.time(result <- bootstrap_yee_estimator_optimized(X, B))
-# print(paste("Resultado:", result))

### 2024-04-24 Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.R

@@ -1,33 +1,0 @@
-
-
-
-
-#source("../MainFunctions/noughabi_arghami_estimator.r")
-
-
-bootstrap_noughabi_arghami_estimator <- function(x, B){
-  
-  v.Bootstrap <- rep(0, B)
-  
-  for(b in 1:B) {
-    same_values <- TRUE
-    while (same_values) {
-      bx <- sample(x, replace = TRUE)
-      if (!all(bx == bx[1])) {
-        same_values <- FALSE
-        entropy_result <- noughabi_arghami_estimator(bx)
-        if (is.finite(entropy_result)) {
-          v.Bootstrap[b] <- entropy_result
-          #cat("Entropy for Bootstrap Sample", b, ": ", v.Bootstrap[b], "\n")
-        }
-      }
-    }
-  }
-  
-  
-  t <- noughabi_arghami_estimator(x)
-  estimated_mean <- mean(v.Bootstrap[!is.na(v.Bootstrap)])
-  
-  return(2*t - estimated_mean)
-  
-}

### 2024-04-24 Code/R/MainFunctions/bootstrap_yee_estimator.R

@@ -1,29 +1,0 @@
-
-
-
-bootstrap_yee_estimator <- function(x, B){
-  
-  v.Bootstrap <- rep(0, B)
-  
-  for(b in 1:B) {
-    same_values <- TRUE
-    while (same_values) {
-      bx <- sample(x, replace = TRUE)
-      if (!all(bx == bx[1])) {
-        same_values <- FALSE
-        entropy_result <- yee_estimator(bx)
-        if (is.finite(entropy_result)) {
-          v.Bootstrap[b] <- entropy_result
-          #cat("Entropy for Bootstrap Sample", b, ": ", v.Bootstrap[b], "\n")
-        }
-      }
-    }
-  }
-  
-  
-  t <- yee_estimator(x)
-  estimated_mean <- mean(v.Bootstrap[!is.na(v.Bootstrap)])
-  
-  return(2*t - estimated_mean)
-  
-}

### 2024-04-24 Code/R/MainFunctions/noughabi_arghami_estimator.R

@@ -1,28 +1,0 @@
-  noughabi_arghami_estimator <- function(data) {
-    n <- length(data)
-    m <- round(sqrt(n) + 0.5)  # m-spacing
-    data_sorted <- sort(data)
-    sum_term <- 0
-    
-    for (i in 1:n) {
-      if (i <= m) {
-        ai <- 1
-        diff_term <- data_sorted[i + m] - data_sorted[1]
-      } else if (i >= n - m + 1) {
-        ai <- 1
-        diff_term <- data_sorted[n] - data_sorted[i - m]
-      } else {
-        ai <- 2
-        diff_term <- data_sorted[i + m] - data_sorted[i - m]
-      }
-      
-      sum_term <- sum_term + log((n / (ai * m)) * diff_term)
-    }
-    
-    return(sum_term / n)
-  }
-  
-  # # Example usage:
-  # data <- c(1.2, 1.5,3.6, 2.0, 2.1, 2.5, 2.6, 3.0, 3.1, 3.5 )
-  # result <- noughabi_arghami_estimator(data)
-  # cat("noughabi_arghami:", result, "\n")

### 2024-04-24 Code/R/MainFunctions/yee_estimator.R

@@ -1,67 +1,0 @@
-
-
-yee_estimator<- function(X) {
-  n <- length(X)
-  H_Y <- numeric(n-1)
-  
-  sorted_X <- sort(X)
-  
-  for (m in 1:(n-1)) {
-    differences <- sorted_X[(m+1):n] - sorted_X[1:(n-m)]
-    term_sum <- sum(log((n/m) * differences))
-    
-    H_Y[m] <- (1/(n-m)) * term_sum - digamma(m) + log(m)
-  }
-  
-  estimated_entropy <- (1/(n-1)) * sum(H_Y)
-  
-  return(estimated_entropy)
-}
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-# yee_estimator<- function(X) {
-#   n <- length(X)
-#   H_Y <- numeric(n-1)
-#   
-#   sorted_X <- sort(X)
-#   
-#   for (m in 1:(n-1)) {
-#     differences <- sorted_X[(m+1):n] - sorted_X[1:(n-m)]
-#     term_sum <- sum(log((n/m) * differences))
-#     
-#     H_Y[m] <- (1/(n-m)) * term_sum - digamma(m) + log(m)
-#   }
-#   
-#   estimated_entropy <- (1/(n-1)) * sum(H_Y)
-#   
-#   return(estimated_entropy)
-# }
-
-
-# set.seed(123)  # Para reproducibilidad
-# X_large <- rnorm(1000)  # Reemplaza esto con tu conjunto de datos
-# system.time(entropy_estimate_large <- yee_entropy_estimator_optimized(X_large))
-# print(paste("Estimación de entropía:", entropy_estimate_large))

### 2024-04-24 Code/R/PlottingFunctions/best_estimators.R

@@ -1,118 +1,0 @@
-rm(list = ls())
-library(ggplot2)
-library(tidyr)
-library(gtools)
-library(stats4)
-library(rmutil)
-library(invgamma)
-library(ggplot2)
-library(tidyverse)
-library(scales)
-library(RColorBrewer)
-library(ggsci)
-library(wesanderson)
-library(ggpubr)
-
-# Load the source files (make sure you have the correct file paths)
-source("../MainFunctions/gamma_sar_sample.r")
-source("../MainFunctions/entropy_gamma_sar.r")
-source("../MainFunctions/van_es_estimator.r")
-source("../MainFunctions/correa_estimator.r")
-source("../MainFunctions/ebrahimi_estimator.r")
-source("../MainFunctions/noughabi_arghami_estimator.r")
-source("../MainFunctions/vasicek_estimator.r")
-source("../MainFunctions/al_omari_1_estimator.r")
-source("../MainFunctions/al_omari_2_estimator.r")
-source("../MainFunctions/bootstrap_van_es_estimator.r")
-source("../MainFunctions/bootstrap_correa_estimator.r")
-source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
-source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
-source("../MainFunctions/bootstrap_vasicek_estimator.r")
-source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
-source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
-
-set.seed(1234567890, kind = "Mersenne-Twister")
-
-sample_sizes <- c( 9, 25, 49, 81, 121, 225)
-R <- 100
-mu <- 1
-L <- 1
-
-# Function to calculate Bias and MSE for both non-parametric and bootstrap estimators
-calculate_bias_mse <- function(sample_sizes, R, mu, L) {
-  true_entropy <- entropy_gamma_sar(L, mu)
-  
-  # Define a list of estimators
-  estimators <- list(
-    "Van Es" = van_es_estimator,
-    "Correa" = correa_estimator,
-    "Ebrahimi" = ebrahimi_estimator,
-    "Noughabi Arghami" = noughabi_arghami_estimator,
-    "Vasicek" = vasicek_estimator,
-    "Al Omari 1" = al_omari_1_estimator,
-    "Al Omari 2" = al_omari_2_estimator,
[…]

### 2024-04-24 Code/R/PlottingFunctions/bias_mse_al_omari_1.R

@@ -1,101 +1,0 @@
-rm(list = ls())
-library(ggplot2)
-library(gtools)
-library(stats4)
-library(rmutil)
-#library(gsl)
-library(invgamma)
-
-library(ggthemes)
-library(grid)
-library(gridExtra)
-library(gtable)
-#install.packages("cowplot")
-library(cowplot)
-library(ggpubr)
-theme_set(theme_bw()  +
-            theme(text=element_text(family="serif"),
-                  legend.position = "top")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
-)
-source("../MainFunctions/gamma_sar_sample.r")
-source("../MainFunctions/entropy_gamma_sar.r")
-
-source("../MainFunctions/van_es_estimator.r")
-source("../MainFunctions/correa_estimator.r")
-source("../MainFunctions/ebrahimi_estimator.r")
-source("../MainFunctions/noughabi_arghami_estimator.r")
-source("../MainFunctions/vasicek_estimator.r")
-source("../MainFunctions/al_omari_1_estimator.r")
-source("../MainFunctions/al_omari_2_estimator.r")
-
-source("../MainFunctions/bootstrap_van_es_estimator.r")
-source("../MainFunctions/bootstrap_correa_estimator.r")
-source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
-source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
-source("../MainFunctions/bootstrap_vasicek_estimator.r")
-source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
-source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
-
-set.seed(1234567890, kind="Mersenne-Twister")
-
-sample_sizes <- c(9, 25, 49, 81, 121)
-R <- 100
-mu <- 1
-L <- 1
-
-# 
-results <- data.frame()
-
-for (n in sample_sizes) {
-  true_entropy <- entropy_gamma_sar(L, mu)
-  bias_est <- rep(0, R)
-  mse_est <- rep(0, R)
-  bias_bootstrap <- rep(0, R)
-  mse_bootstrap <- rep(0, R)
-  
-  for (r in 1:R) {
-    # Samples
-    data <- gamma_sar_sample(L, mu, n)
-    
-    # Entropy estimations
-    est <- al_omari_1_estimator(data)
[…]

### 2024-04-24 Code/R/PlottingFunctions/bias_mse_al_omari_2.R

@@ -1,101 +1,0 @@
-rm(list = ls())
-library(ggplot2)
-library(gtools)
-library(stats4)
-library(rmutil)
-#library(gsl)
-library(invgamma)
-
-library(ggthemes)
-library(grid)
-library(gridExtra)
-library(gtable)
-#install.packages("cowplot")
-library(cowplot)
-library(ggpubr)
-theme_set(theme_bw()  +
-            theme(text=element_text(family="serif"),
-                  legend.position = "top")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
-)
-source("../MainFunctions/gamma_sar_sample.r")
-source("../MainFunctions/entropy_gamma_sar.r")
-
-source("../MainFunctions/van_es_estimator.r")
-source("../MainFunctions/correa_estimator.r")
-source("../MainFunctions/ebrahimi_estimator.r")
-source("../MainFunctions/noughabi_arghami_estimator.r")
-source("../MainFunctions/vasicek_estimator.r")
-source("../MainFunctions/al_omari_1_estimator.r")
-source("../MainFunctions/al_omari_2_estimator.r")
-
-source("../MainFunctions/bootstrap_van_es_estimator.r")
-source("../MainFunctions/bootstrap_correa_estimator.r")
-source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
-source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
-source("../MainFunctions/bootstrap_vasicek_estimator.r")
-source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
-source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
-
-set.seed(1234567890, kind="Mersenne-Twister")
-
-sample_sizes <- c(9, 25, 49, 81, 121)
-R <- 10
-mu <- 1
-L <- 1
-
-# 
-results <- data.frame()
-
-for (n in sample_sizes) {
-  true_entropy <- entropy_gamma_sar(L, mu)
-  bias_est <- rep(0, R)
-  mse_est <- rep(0, R)
-  bias_bootstrap <- rep(0, R)
-  mse_bootstrap <- rep(0, R)
-  
-  for (r in 1:R) {
-    # Samples
-    data <- gamma_sar_sample(L, mu, n)
-    
-    # Entropy estimations
-    est <- al_omari_2_estimator(data)
[…]

### 2024-04-24 Code/R/PlottingFunctions/bias_mse_correa.R

@@ -1,101 +1,0 @@
-rm(list = ls())
-library(ggplot2)
-library(gtools)
-library(stats4)
-library(rmutil)
-#library(gsl)
-library(invgamma)
-
-library(ggthemes)
-library(grid)
-library(gridExtra)
-library(gtable)
-#install.packages("cowplot")
-library(cowplot)
-library(ggpubr)
-theme_set(theme_bw()  +
-            theme(text=element_text(family="serif"),
-                  legend.position = "top")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
-)
-source("../MainFunctions/gamma_sar_sample.r")
-source("../MainFunctions/entropy_gamma_sar.r")
-
-source("../MainFunctions/van_es_estimator.r")
-source("../MainFunctions/correa_estimator.r")
-source("../MainFunctions/ebrahimi_estimator.r")
-source("../MainFunctions/noughabi_arghami_estimator.r")
-source("../MainFunctions/vasicek_estimator.r")
-source("../MainFunctions/al_omari_1_estimator.r")
-source("../MainFunctions/al_omari_2_estimator.r")
-
-source("../MainFunctions/bootstrap_van_es_estimator.r")
-source("../MainFunctions/bootstrap_correa_estimator.r")
-source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
-source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
-source("../MainFunctions/bootstrap_vasicek_estimator.r")
-source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
-source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
-
-set.seed(1234567890, kind="Mersenne-Twister")
-
-sample_sizes <- c(9, 25, 49, 81, 121)
-R <- 10
-mu <- 1
-L <- 1
-
-# 
-results <- data.frame()
-
-for (n in sample_sizes) {
-  true_entropy <- entropy_gamma_sar(L, mu)
-  bias_est <- rep(0, R)
-  mse_est <- rep(0, R)
-  bias_bootstrap <- rep(0, R)
-  mse_bootstrap <- rep(0, R)
-  
-  for (r in 1:R) {
-    # Samples
-    data <- gamma_sar_sample(L, mu, n)
-    
-    # Entropy estimations
-    est <- correa_estimator(data)
[…]

### 2024-04-24 Code/R/PlottingFunctions/bias_mse_ebrahimi.R

@@ -1,101 +1,0 @@
-rm(list = ls())
-library(ggplot2)
-library(gtools)
-library(stats4)
-library(rmutil)
-#library(gsl)
-library(invgamma)
-
-library(ggthemes)
-library(grid)
-library(gridExtra)
-library(gtable)
-#install.packages("cowplot")
-library(cowplot)
-library(ggpubr)
-theme_set(theme_bw()  +
-            theme(text=element_text(family="serif"),
-                  legend.position = "top")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
-)
-source("../MainFunctions/gamma_sar_sample.r")
-source("../MainFunctions/entropy_gamma_sar.r")
-
-source("../MainFunctions/van_es_estimator.r")
-source("../MainFunctions/correa_estimator.r")
-source("../MainFunctions/ebrahimi_estimator.r")
-source("../MainFunctions/noughabi_arghami_estimator.r")
-source("../MainFunctions/vasicek_estimator.r")
-source("../MainFunctions/al_omari_1_estimator.r")
-source("../MainFunctions/al_omari_2_estimator.r")
-
-source("../MainFunctions/bootstrap_van_es_estimator.r")
-source("../MainFunctions/bootstrap_correa_estimator.r")
-source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
-source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
-source("../MainFunctions/bootstrap_vasicek_estimator.r")
-source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
-source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
-
-set.seed(1234567890, kind="Mersenne-Twister")
-
-sample_sizes <- c(9, 25, 49, 81, 121)
-R <- 10
-mu <- 1
-L <- 1
-
-# 
-results <- data.frame()
-
-for (n in sample_sizes) {
-  true_entropy <- entropy_gamma_sar(L, mu)
-  bias_est <- rep(0, R)
-  mse_est <- rep(0, R)
-  bias_bootstrap <- rep(0, R)
-  mse_bootstrap <- rep(0, R)
-  
-  for (r in 1:R) {
-    # Samples
-    data <- gamma_sar_sample(L, mu, n)
-    
-    # Entropy estimations
-    est <- ebrahimi_estimator(data)
[…]

### 2024-04-24 Code/R/PlottingFunctions/bias_plot.R

@@ -1,80 +1,0 @@
-rm(list = ls())
-library(ggplot2)
-library(gtools)
-library(stats4)
-library(rmutil)
-#library(gsl)
-library(invgamma)
-library(ggplot2)
-library(ggthemes)
-theme_set(theme_pander() +
-            theme(text=element_text(family="serif"),
-                  legend.position = "top")
-)
-source("../MainFunctions/gamma_sar_sample.r")
-source("../MainFunctions/entropy_gamma_sar.r")
-
-source("../MainFunctions/van_es_estimator.r")
-source("../MainFunctions/correa_estimator.r")
-source("../MainFunctions/ebrahimi_estimator.r")
-source("../MainFunctions/noughabi_arghami_estimator.r")
-source("../MainFunctions/vasicek_estimator.r")
-source("../MainFunctions/al_omari_1_estimator.r")
-source("../MainFunctions/al_omari_2_estimator.r")
-
-set.seed(1234567890, kind="Mersenne-Twister")
-
-sample_sizes <- c( 9, 25, 49, 81, 121, 1000)
-R <- 100
-mu <- 1
-L <- 1
-
-#  True entropy value for the gamma SAR distribution
-true_entropy <- entropy_gamma_sar(L, mu)
-
-
-output <- data.frame(SampleSize = integer(0), Estimator = character(0), Bias = numeric(0))
-
-#List of estimator
-estimators <- list(
-  list(func = van_es_estimator, label = "Van Es"),
-  list(func = correa_estimator, label = "Correa"),
-  list(func = ebrahimi_estimator, label = "Ebrahimi"),
-  list(func = noughabi_arghami_estimator, label = "Noughabi Arghami"),
-  list(func = vasicek_estimator, label = "Vasicek"),
-  list(func = al_omari_1_estimator, label = "Al Omari 1"),
-  list(func = al_omari_2_estimator, label = "Al Omari 2")
-)
-
-
-
-
-for (estimator in estimators) {
-  for (ssize in sample_sizes) {
-    v.nonparametric.entropy <- numeric(R)
-   
-    for (r in 1:R) {
-      sample <- gamma_sar_sample(L, mu, ssize)
-      #cat("sample:", estimator$label, sample, "\n")
-      v.nonparametric.entropy[r] <- estimator$func(sample)
-      #cat("non:", v.nonparametric.entropy, "\n")
-      
-     
-    }
[…]

### 2024-04-24 Code/R/PlottingFunctions/bias_plot_bootstrap.R

@@ -1,86 +1,0 @@
-rm(list = ls())
-library(ggplot2)
-library(gtools)
-library(stats4)
-library(rmutil)
-#library(gsl)
-library(invgamma)
-library(ggplot2)
-library(ggthemes)
-theme_set(theme_pander() +
-            theme(text=element_text(family="serif"),
-                  legend.position = "top")
-)
-source("../MainFunctions/gamma_sar_sample.r")
-source("../MainFunctions/entropy_gamma_sar.r")
-
-source("../MainFunctions/van_es_estimator.r")
-source("../MainFunctions/correa_estimator.r")
-source("../MainFunctions/ebrahimi_estimator.r")
-source("../MainFunctions/noughabi_arghami_estimator.r")
-source("../MainFunctions/vasicek_estimator.r")
-source("../MainFunctions/al_omari_1_estimator.r")
-source("../MainFunctions/al_omari_2_estimator.r")
-
-source("../MainFunctions/bootstrap_van_es_estimator.r")
-source("../MainFunctions/bootstrap_correa_estimator.r")
-source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
-source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
-source("../MainFunctions/bootstrap_vasicek_estimator.r")
-source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
-source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
-
-set.seed(1234567890, kind="Mersenne-Twister")
-
-sample_sizes <- c( 9, 25)
-R <- 5
-mu <- 1
-L <- 1
-
-#  True entropy value for the gamma SAR distribution
-true_entropy <- entropy_gamma_sar(L, mu)
-
-
-output <- data.frame(SampleSize = integer(0), Estimator = character(0), Bias = numeric(0))
-
-#List of estimator
-estimators <- list(
-  list(func = bootstrap_van_es_estimator, label = " bootstrap Van Es"),
-  list(func = bootstrap_correa_estimator, label = " bootstrap Correa"),
-  # list(func = bootstrap_ebrahimi_estimator, label = "bootstrap Ebrahimi"),
-  # list(func = bootstrap_noughabi_arghami_estimator, label = "bootstrap Noughabi Arghami"),
-  # list(func = bootstrap_vasicek_estimator, label = "bootstrap Vasicek"),
[…]

### 2024-04-24 Code/R/PlottingFunctions/bias_plot_one_estimator.R

@@ -1,67 +1,0 @@
-rm(list = ls())
-library(ggplot2)
-library(gtools)
-#library(stats4)
-#library(rmutil)
-#library(gsl)
-library(invgamma)
-library(ggplot2)
-library(ggthemes)
-theme_set(theme_pander() +
-            theme(text=element_text(family="serif"),
-                  legend.position = "top")
-)
-source("../MainFunctions/gamma_sar_sample.r")
-source("../MainFunctions/entropy_gamma_sar.r")
-
-source("../MainFunctions/van_es_estimator.r")
-source("../MainFunctions/correa_estimator.r")
-source("../MainFunctions/ebrahimi_estimator.r") 
-source("../MainFunctions/noughabi_arghami_estimator.r") 
-source("../MainFunctions/vasicek_estimator.r") 
-source("../MainFunctions/al_omari_1_estimator.r") 
-source("../MainFunctions/al_omari_2_estimator.r") 
-
-
-set.seed(1234567890, kind = "Mersenne-Twister")
-
-
-
-# Set sample sizes, the number of repetitions, and parameters
-sample_sizes <- c(9, 25, 49, 81, 121, 225)
-R <- 1000
-mu <- 1
-L <- 1
-
-
-# Define the true entropy value for the gamma SAR distribution
-true_entropy <- entropy_gamma_sar(L, mu)  # Replace with the true entropy value
-# Initialize the output data frame
-output <- NULL
-
-# Perform non-parametric entropy estimation for different sample sizes
-for (ssize in sample_sizes) {
-  v.nonparametric.entropy <- NULL
-  for (r in 1:R) {
-    sample <- gamma_sar_sample(L, mu, ssize)
-    v.nonparametric.entropy[r] <- van_es_estimator(sample)
-  }
-  
-  # Calculate the bias by subtracting the true entropy value
-  bias <- mean(v.nonparametric.entropy) - true_entropy
-  
-  # Store the bias in the output data frame
-  output <- rbind(output, c(bias, ssize))
-}
-
-# Create a data frame with results
-output <- data.frame(output)
-names(output) <- c("Bias")
-output$SampleSize <- sample_sizes
-
-# Plot the bias as a function of the sample size
-ggplot(output, aes(x=SampleSize, y=Bias)) +
-  geom_line() +
-  geom_point() +
-  xlab("Sample Size") +
-  ylab("Bias of Non-parametric Entropy Estimator")

### 2024-04-24 Code/R/PlottingFunctions/gamma_sar_L1.R

@@ -1,56 +1,0 @@
-
-# This code demonstrates non-parametric entropy estimation for Gamma SAR data.
-# It uses non-parametric estimators to calculate the sample mean and standard deviation 
-# of the entropy for various sample sizes.
-# The code also includes error bars based on the standard deviation for visualization.
-
-
-rm(list = ls())
-library(ggplot2)
-
-source("../MainFunctions/gamma_sar_sample.r")
-source("../MainFunctions/van_es_estimator.r")
-source("../MainFunctions/entropy_gamma_sar.r")
-set.seed(1234567890, kind="Mersenne-Twister")
-
-# Define sample sizes, the number of repetitions, and parameters
-sample_sizes <- c(9, 25, 49, 81, 121, 225)
-R <- 100
-mu <- 1
-L <- 1
-true_entropy <- entropy_gamma_sar(2, 2)
-#cat( "True entropy:", tru2_entropy)
-# Initialize the output data frame
-output <- NULL
-
-# Perform non-parametric entropy estimation for different sample sizes
-for(ssize in sample_sizes) {
-  v.nonparametric.entropy <- NULL
-  for(r in 1:R) {
-    sample <- gamma_sar_sample(L, mu, ssize)
-    v.nonparametric.entropy[r] <- van_es_estimator(sample)
-  }
-  output <- rbind(output, c(mean(v.nonparametric.entropy), sd(v.nonparametric.entropy)))
-  cat( "Sample Size:", ssize, "entropy:", mean(v.nonparametric.entropy),"True entropy:", true_entropy, "\n")
-}
-
-# Create a data frame with results
-output <- data.frame(output)
-names(output) <- c("Mean", "Std")
-output$SampleSize <- sample_sizes
-
-#cat( "True entropy:", tru2_entropy)
-#Plot
-ggplot(output, aes(x=SampleSize, y=Mean)) +
-  geom_hline(yintercept = entropy_gamma_sar(1, 1)) +
-  geom_line() +
-  geom_point() +
-  #geom_errorbar(aes(ymin = Mean - Std, ymax = Mean + Std), width = 0.1) +
-  xlab("Sample Size") +
-  #scale_x_log10(breaks=output$SampleSize) +
-  ylab("Mean Non-parametric Entropy")
-
-# Save the plot as a PDF file
-#ggsave("myplot.pdf")
-
-

### 2024-04-24 Code/R/PlottingFunctions/main_plots.R

@@ -1,92 +1,0 @@
-rm(list = ls())
-
-#options(digits = 5)
-
-# Resto de tu código aquí
-
-# Restaurar la opción digits a su valor original si es necesario
-#on.exit(options(digits = getOption("digits")))
-library(ggplot2)
-library(tidyr)
-library(gtools)
-library(stats4)
-library(rmutil)
-library(invgamma)
-library(tidyverse)
-library(scales)
-library(RColorBrewer)
-library(ggsci)
-library(wesanderson)
-library(ggpubr)
-library(patchwork)
-theme_set(theme_bw()  +
-            theme(text=element_text(family="serif"),
-                  legend.position = "top", panel.grid = element_blank())# Gridtop , right , bottom , or left#, panel.grid = element_blank()
-)
-
-
-# Load the source files (make sure you have the correct file paths)
-source("../MainFunctions/gamma_sar_sample.r")
-source("../MainFunctions/entropy_gamma_sar.r")
-source("../MainFunctions/van_es_estimator.r")
-source("../MainFunctions/correa_estimator.r")
-source("../MainFunctions/ebrahimi_estimator.r")
-source("../MainFunctions/noughabi_arghami_estimator.r")
-source("../MainFunctions/vasicek_estimator.r")
-source("../MainFunctions/al_omari_1_estimator.r")
-source("../MainFunctions/al_omari_2_estimator.r")
-source("../MainFunctions/bootstrap_van_es_estimator.r")
-source("../MainFunctions/bootstrap_correa_estimator.r")
-source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
-source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
-source("../MainFunctions/bootstrap_vasicek_estimator.r")
-source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
-source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
-
-#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
-source("../Programs/functions_sample_bias_mse.R")# 
-
-set.seed(1234567890, kind = "Mersenne-Twister")
-
-
-# Define sample sizes for analysis
-sample_sizes <- c(9, 25, 49, 81, 121, 225)
-
-# Number of replications
[…]

### 2024-04-24 Code/R/PlottingFunctions/plot_3d_entropy_with_labels_but_no_rotation.R

@@ -1,88 +1,0 @@
-library(plotly)
-library(latex2exp)
-
-# Define la función de entropía
-entropy_gI0 <- function(mu, alpha, L) {
-  term1 <- L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu)   
-  term2 <- -L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha))
-  entropy <- term1 + term2 
-  return(entropy)
-}
-
-mu <- seq(1, 20, length.out = 200)
-alpha <- seq(-20, -2, length.out = 200)
-# entropyL1 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=1))
-# entropyL3 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=3))
-# entropyL8 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=8))
-# entropyL12 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=12))
-# entropyL100 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=100))
-
-entropyL1 <- outer(alpha, mu, function(alpha, mu) entropy_gI0(mu, alpha, L = 1))
-entropyL3 <- outer(alpha, mu, function(alpha, mu) entropy_gI0(mu, alpha, L = 3))
-entropyL8 <- outer(alpha, mu, function(alpha, mu) entropy_gI0(mu, alpha, L = 8))
-entropyL12 <- outer(alpha, mu, function(alpha, mu) entropy_gI0(mu, alpha, L = 12))
-entropyL100 <- outer(alpha, mu, function(alpha, mu) entropy_gI0(mu, alpha, L = 100))
-
-fig <- plot_ly(x = mu, y = alpha, showscale = FALSE)
-
-fig <- fig %>% add_surface(z = ~entropyL1, colorscale = list(c(0, 1), c("rgb(255,107,184)", "rgb(128,0,64)")), name = "L=1")
-fig <- fig %>% add_surface(z = ~entropyL3, colorscale = list(c(0, 1), c("rgb(247,226,157)", "rgb(255,192,7)")), name = "L=3")
[…]

### 2024-04-24 Code/R/PlottingFunctions/plot_3d_entropy_with_orca.R

@@ -1,45 +1,0 @@
-library(plotly)
-library(latex2exp)
-
-# Entropy
-entropy_gI0 <- function(mu, alpha, L) {
-  term1 <- L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu)   
-  term2 <- -L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha))
-  entropy <- term1 + term2 
-  return(entropy)
-}
-
-mu <- seq(1, 10, length.out = 200)
-alpha <- seq(-20, -2, length.out = 200)
-
-entropyL1 <- outer(alpha, mu, function(alpha, mu) entropy_gI0(mu, alpha, L = 1))
-entropyL3 <- outer(alpha, mu, function(alpha, mu) entropy_gI0(mu, alpha, L = 3))
-entropyL8 <- outer(alpha, mu, function(alpha, mu) entropy_gI0(mu, alpha, L = 8))
-entropyL12 <- outer(alpha, mu, function(alpha, mu) entropy_gI0(mu, alpha, L = 12))
-entropyL100 <- outer(alpha, mu, function(alpha, mu) entropy_gI0(mu, alpha, L = 100))
-
-fig <- plot_ly(x = mu, y = alpha, showscale = FALSE)
-
-fig <- fig %>% add_surface(z = ~entropyL1, colorscale = list(c(0, 1), c("rgb(255,107,184)", "rgb(128,0,64)")), name = "L=1")
-fig <- fig %>% add_surface(z = ~entropyL3, colorscale = list(c(0, 1), c("rgb(247,226,157)", "rgb(255,192,7)")), name = "L=3")
-fig <- fig %>% add_surface(z = ~entropyL8,colorscale = list(c(0, 1), c("rgb(107,255,184)", "rgb(0,124,90)")),  name = "L=8")
-fig <- fig %>% add_surface(z = ~entropyL12,colorscale = list(c(0,1),c("rgb(129,212,247)","rgb(12,177,247)")),  name = "L=12")
-fig <- fig %>% add_surface(z = ~entropyL100, colorscale = list(c(0, 1), c("rgb(182,142,242)", "rgb(104,3,255)")), name = "L=100")
-
-# 
-fig <- fig %>% layout(
-  scene = list(
-    camera = list(
[…]

### 2024-04-24 Code/R/Programs/CV-test.R

@@ -1,0 +1,57 @@
+#rm(list = ls())
+
+# if(!require("rstudioapi")) install("rstudioapi")
+# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+
+# source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
+# source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+ source("../../../Code/R/Programs/read_ENVI_images.R")
+# source("../../../Code/R/MainFunctions/correa_estimator.R")
+
+
+x <- myread.ENVI(file='../../../Data/SAR/chicago_1024/Intensity_HH.img', 
+                  headerfile='../../../Data/SAR/chicago_1024/Intensity_HH.hdr')
+
+#L <- 5
+#B <- 100
+
+
+window_size <- 9
+
+
+rows <- nrow(x)
+cols <- ncol(x)
+
+
+cv_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+
+
+# 
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Seleccionar ventana local
+    window_data <- x[i:(i + window_size - 1), j:(j + window_size - 1)]
+    
+    
+    x_values <- window_data
+    
+    
+    # 
+    mean_values <- mean(window_data)
+    sd_values <- sd(window_data)
+    
+    # 
+    cv_values[i, j] <- sd_values / mean_values
+    
+    
+    
+  }
+}
+
+
+
+save( cv_values, x, file = "./Data/CV_results_data_Illinois_crops_1024.Rdata")
+#save(cv_values, Z,  file = "./Data/results_data_simulated_Phantom_7.Rdata")
+
+

### 2024-04-24 Code/R/Programs/Goodness-of-fit tests.R

@@ -1,0 +1,83 @@
+
+rm(list = ls())
+
+library(ggplot2)
+library(ggsci)
+library(univariateML)
+library(compiler)
+library(MASS)
+library(fitdistrplus)
+library(invgamma)
+
+# source("../MainFunctions/ebrahimi_estimator.R")
+# source("../MainFunctions/gamma_sar_sample.R")
+# source("../MainFunctions/correa_estimator.R")
+# source("../MainFunctions/bootstrap_correa_estimator.R")
+# source("../MainFunctions/bootstrap_correa_estimator_log_mean.R")
+# source("../MainFunctions/entropy_gI0.R")
+# source("../MainFunctions/gi0_sample.R")
+
+
+
+#load("../Programs/Data/results_data_simulated_Phantom_7.Rdata")
+#save(cd_values_mnad, Z, file = "./Data/results_Phantom_mnad_7.Rdata")
+#load("../Programs/Data/results_Phantom_mnad_7.Rdata")
+
+#save( cv_values, x, file = "./Data/CV_results_data_Illinois_crops_1024.Rdata")
+#load("../Programs/Data/CV_results_data_Illinois_crops_1024.Rdata")
+
+#save( cd_values_mnad, x, file = "./Data/MnAD_results_data_Illinois_crops_1024.Rdata")
+#load("../Programs/Data/MnAD_results_data_Illinois_crops_1024.Rdata")
+
+#save( cv_values, x, file = "./Data/CV_results_data_Mexixo_512.Rdata")
+#load("../Programs/Data/CV_results_data_Mexixo_512.Rdata")
+
+#save( cd_values_mnad, x, file = "./Data/MnAD_results_data_mexico_512.Rdata")
+#load("../Programs/Data/MnAD_results_data_mexico_512.Rdata")
+
+#save( cv_values, x, file = "./Data/CV_results_data_lake_512.Rdata")
+#load("../Programs/Data/CV_results_data_lake_512.Rdata")
+
+#save( cd_values_mnad, x, file = "./Data/MnAD_results_data_lake_512.Rdata")
+load("../Programs/Data/MnAD_results_data_lake_512.Rdata")
+#cv_values_vector <- as.vector(cv_values)
+
+
+cv_values_vector <- as.vector(cd_values_mnad)
+
+
+
+fln <- fitdist(cv_values_vector, "lnorm")
[…]

### 2024-04-24 Code/R/Programs/MnAD-test.R

@@ -1,0 +1,41 @@
+#rm(list = ls())
+
+# if(!require("rstudioapi")) install("rstudioapi")
+# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+source("../../../Code/R/Programs/read_ENVI_images.R")
+source("../../../Code/R/MainFunctions/correa_estimator.R")
+
+x <- myread.ENVI(file='../../../Data/SAR/chicago_1024/Intensity_HH.img', 
+                 headerfile='../../../Data/SAR/chicago_1024/Intensity_HH.hdr')
+
+
+rows <- nrow(x)
+cols <- ncol(x)
+
+window_size <- 9
+
+
+MnADmedian <- function(mat){
+  mdn <- median(mat)
+  MnAD <- mean(abs(mat - mdn))
+  MnAD/mdn
+}
+
+cd_values_mnad <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Seleccionar ventana local
+    window_data <- x[i:(i + window_size - 1), j:(j + window_size - 1)]
+    
+    # Calcular el CD basado en MnAD para la ventana local (matriz)
+    cd_values_mnad[i, j] <- MnADmedian(window_data)
+  }
+}
+
+# Guardar el resultado en un archivo
+save( cd_values_mnad, x, file = "./Data/MnAD_results_data_Illinois_crops_1024.Rdata")
+#save(cd_values_mnad, x, file = "./Data/results_data_Ottawa_512_mnad_7.Rdata")

### 2024-04-24 Code/R/Programs/Phantom_code.R

@@ -11,7 +11,7 @@ rGI0 <- function(n, p_alpha, p_mu, p_Looks) {
 
 Z <- Phantom1 <- readPNG("../../../Figures/PNG/Phantom1.png")[,,1]
 dim(Phantom1)
-plot(imagematrix(Phantom1))
+#plot(imagematrix(Phantom1))
 
 E <- function(a, g) {-g/(a+1)}
 H <- function(a, g) {(a-1)/a - log(-a/g, base=exp(1))}
@@ -38,55 +38,57 @@ p.bo.ri <- Phantom1[251:500,251:500]
 
 ### Upper Left (means 1 and 1)
 z.up.le.b <- rGI0(n=sum(1-p.up.le), 
-                  p_alpha=-2, p_mu=1, p_Looks=2)
+                  p_alpha=-2, p_mu=1, p_Looks=5)
 mean(z.up.le.b)
 
 z.up.le.w <- rGI0(n=sum(p.up.le), 
-                  p_alpha=-10, p_mu=9, p_Looks=2)
+                  p_alpha=-10, p_mu=9, p_Looks=5)
 mean(z.up.le.w)
 z.up.le <- p.up.le
 z.up.le[p.up.le==0] <- z.up.le.b
 z.up.le[p.up.le==1] <- z.up.le.w
-#plot(imagematrix(equalize(z.up.le)))
+plot(imagematrix(equalize(z.up.le)))
 
 ### Upper Right (means 50 and 5)
 z.up.ri.b <- rGI0(n=sum(1-p.up.ri), 
-                  p_alpha=-2, p_mu=50, p_Looks=2)
+                  p_alpha=-10, p_mu=1, p_Looks=5)
 mean(z.up.ri.b)
+
 z.up.ri.w <- rGI0(n=sum(p.up.ri), 
-                  p_alpha=-2, p_mu=5, p_Looks=2)
+                  p_alpha=-2, p_mu=9, p_Looks=5)
 mean(z.up.ri.w)
 z.up.ri <- p.up.ri
 z.up.ri[p.up.ri==0] <- z.up.ri.b
 z.up.ri[p.up.ri==1] <- z.up.ri.w
-#plot(imagematrix(equalize(z.up.ri)))
+plot(imagematrix(equalize(z.up.ri)))
 
 
 ### Bottom Right (means 10 and 10)
 
[…]

### 2024-04-24 Code/R/Programs/data_gamma.R

@@ -1,107 +1,0 @@
-rm(list = ls())
-
-library(ggplot2)
-library(ggsci)
-library(invgamma)
-library(latex2exp)
-if(!require("rstudioapi")) install("rstudioapi")
-setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
-
-source("../MainFunctions/ebrahimi_estimator.R")
-source("../MainFunctions/gamma_sar_sample.R")
-source("../MainFunctions/correa_estimator.R")
-source("../MainFunctions/bootstrap_correa_estimator.R")
-source("../MainFunctions/bootstrap_correa_estimator_log_mean.R")
-
-source("../MainFunctions/al_omari_1_estimator.R")
-source("../MainFunctions/bootstrap_al_omari_1_estimator.R")
-
-source("../MainFunctions/entropy_gI0.R")
-source("../MainFunctions/gi0_sample.R")
-
-set.seed(1234567890, kind = "Mersenne-Twister")
-
-R <- 1000
-mu <- 1
-L <- 5
-B <- 2
-alpha1 <- -6
-sample.size <- c(81)
-
-TestStatistics1 <- NULL
-TestStatistics2 <- NULL
-TestStatistics3 <- NULL
-TestStatistics4 <- NULL
-mean_entropy1 <- numeric(length(sample.size))
-mean_entropy2 <- numeric(length(sample.size))
-mean_entropy3 <- numeric(length(sample.size))
-mean_entropy4 <- numeric(length(sample.size))
-for (s in sample.size) {
-  TestStat1 <- numeric(R)
-  TestStat2 <- numeric(R)
-  TestStat3 <- numeric(R)
-  TestStat4 <- numeric(R)
-  
-  
-  for (r in 1:R) {
-    #z <- gi0_sample(mu, alpha1, L, s)
-    z <- gamma_sar_sample(L, mu, s)
-    #TestStat1[r] <- log(mean(z))  - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L)+L + lgamma(L-alpha1) - (L-alpha1)*(digamma(L - alpha1))+(1-alpha1)*digamma(- alpha1)-log(-1 - alpha1)-lgamma(-alpha1) ) 
-    #TestStat1[r] <- log(mean(z))  - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
[…]

### 2024-04-24 Code/R/Programs/data_gi0.R

@@ -1,72 +1,0 @@
-rm(list = ls())
-
-library(ggplot2)
-library(ggsci)
-library(invgamma)
-library(latex2exp)
-if(!require("rstudioapi")) install("rstudioapi")
-setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
-
-source("../MainFunctions/ebrahimi_estimator.R")
-source("../MainFunctions/gamma_sar_sample.R")
-source("../MainFunctions/correa_estimator.R")
-source("../MainFunctions/bootstrap_correa_estimator.R")
-source("../MainFunctions/bootstrap_correa_estimator_log_mean.R")
-
-source("../MainFunctions/al_omari_1_estimator.R")
-source("../MainFunctions/bootstrap_al_omari_1_estimator.R")
-
-source("../MainFunctions/entropy_gI0.R")
-source("../MainFunctions/gi0_sample.R")
-
-set.seed(1234567890, kind="Mersenne-Twister")
-
-R <- 1000
-mu <- 1
-L <- 5
-B <- 2
-alpha1<- -600
-sample.size <- c(9, 25, 49, 81)
-
-
-
-TestStatistics <- NULL
-
-for(s in sample.size){
-  for(r in 1:R){
-    z <- gi0_sample(mu, alpha1, L,  s)
-   
-    #TestStat <- log(mean(z))  - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
-    TestStat <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
-    #TestStat <- bootstrap_correa_estimator(z, B) -log(mean(z))  + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L)+L + lgamma(L-alpha1) - (L-alpha1)*(digamma(L - alpha1))+(1-alpha1)*digamma(- alpha1)-log(-1 - alpha1)-lgamma(-alpha1) ) 
-    TestStatistics <- rbind(TestStatistics,
-                            c(s, TestStat))
-  }
-  mean_entropy1 <- mean(TestStat)
-  cat(" mean", mean_entropy1, "\n" )
-}
-
-TestStatistics <- data.frame(TestStatistics)
-names(TestStatistics) <- c("Sample Size", "Test Statistics")
-
-
-
-
-ggplot(TestStatistics, aes(x = `Test Statistics`, col = factor(`Sample Size`), linetype = factor(`Sample Size`))) +
[…]

### 2024-04-24 Code/R/Programs/entropy-based-test.R

@@ -1,0 +1,73 @@
+# Start the timer
+start_time <- Sys.time()
+
+#Estimators
+source("../../../Code/R/MainFunctions/al_omari_1_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
+
+
+source("../../../Code/R/MainFunctions/correa_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+
+
+source("../../../Code/R/MainFunctions/ebrahimi_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
+
+source("../../../Code/R/Programs/read_ENVI_images.R")
+
+
+#Load and read data from SAR images
+
+# x <- myread.ENVI(file='../../../Data/SAR/panama512/Intensity_VV.img', 
+#                   headerfile='../../../Data/SAR/panama512/Intensity_VV.hdr')
+
+# x <- myread.ENVI(file='../../../Data/SAR/chicago_1024/Intensity_HH.img', 
+#                  headerfile='../../../Data/SAR/chicago_1024/Intensity_HH.hdr')
+# 
+# Load simulated image EX. Phantom
+load("../Programs/Data/Phantom_4_regions.Rdata")
+#save(Z, file="./Data/Phantom_4_regions.Rdata")
+
+
+# Assign the dimensions of the loaded matrix to the variables rows and cols
+# change for x if the data comes SAR images
+
+rows <- nrow(Z)
+cols <- ncol(Z)
+
+# rows <- nrow(x)
+# cols <- ncol(x)
+
+
+
+L <- 5 # Number of looks
+B <- 100 # Replications bootstrap
+window_size <- 7 # sliding window size
+
+
+difference_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+# Iterate over sliding windows
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Select local window
+    window_data <- Z[i:(i + window_size - 1), j:(j + window_size - 1)]#change for x if the data comes SAR images
+   #apply the entropy test using one of the bootstrap estimators above
[…]

### 2024-04-24 Code/R/Programs/functions_sample_bias_mse.R

@@ -269,8 +269,8 @@ generate_plot_gi0_esp <- function(results_gi0, mu_values, selected_estimators, n
     
     plot_bias <- ggplot(df_filtered, aes(x = n, y = Bias, color = Estimator)) +
       geom_hline(yintercept = 0) +
-      geom_point(size = 2) +
-      geom_line(linetype = "solid", linewidth = 0.5) +
+      geom_point(size = 2.5) +
+      geom_line(linetype = "solid", linewidth = 1.5) +
       labs(y = "Bias", x = expression(italic(n))) +
       scale_x_continuous(breaks = c(9, 25, 49, 81, 121)) +  # Añadir esta línea para escala personalizada
       scale_color_manual(values = pal_jama()(7)[1:6], labels = TeX(df_filtered$Estimator)) + # Eliminar labels y TeX
@@ -281,8 +281,8 @@ generate_plot_gi0_esp <- function(results_gi0, mu_values, selected_estimators, n
     
     plot_mse <- ggplot(df_filtered, aes(x = n, y = MSE, color = Estimator)) +
       geom_hline(yintercept = 0) +
-      geom_point(size = 2) +
-      geom_line(linetype = "solid", linewidth = 0.5) +
+      geom_point(size = 2.5) +
+      geom_line(linetype = "solid", linewidth = 1.5) +
       labs(y = "MSE", x = expression(italic(n))) +
       scale_x_continuous(breaks = c(9, 25, 49, 81, 121)) +  # Añadir esta línea
       scale_color_manual(values = pal_jama()(7)[1:6], labels = TeX(df_filtered$Estimator)) + # Eliminar labels y TeX

### 2024-04-24 Code/R/Programs/p-values-CV-test.R

@@ -1,0 +1,58 @@
+
+#rm(list = ls())
+#save( cv_values, x, file = "./Data/CV_results_data_Illinois_crops_1024.Rdata")
+#load("../Programs/Data/CV_results_data_Illinois_crops_1024.Rdata")
+
+#load("../Programs/Data/results_data_simulated_Phantom_7.Rdata")
+
+#load("../Programs/Data/CV_results_data_Mexixo_512.Rdata")
+load("../Programs/Data/CV_results_data_lake_512.Rdata")
+
+# Cargar los datos y parámetros de ajuste de la distribución lognormal
+#Illinois_crops_1024
+# meanlog <- -1.3877655
+# sdlog <-  0.5221934
+
+
+#MEXICO
+# 
+# meanlog <- -1.0042160
+# sdlog <-  0.4241594
+
+ meanlog <- -1.1116401
+ sdlog <-  0.5720475
+
+# Crear una matriz para almacenar los p-valores
+p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))
+
+# Calcular los p-valores para cada dato en la matriz de coeficientes de variación
+for (i in 1:nrow(cv_values)) {
+  for (j in 1:ncol(cv_values)) {
+    cv_value <- cv_values[i, j]
+    
+    # Calcular el p-valor utilizando la función plnorm()
+    p_values_matrix[i, j] <- 1-plnorm(cv_value, meanlog = meanlog, sdlog = sdlog)
+  }
+}
+
+
+#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")
+
+
+
+
+#source("../imagematrix.R")
+source("../imagematrix.R")
+#hist(p_values_matrix)
+#par(mfrow=c(1,2))
+
+plot(imagematrix(equalize(cv_values)))#z.up.le
+plot(imagematrix(p_values_matrix ))
+#plot(imagematrix(p_values_matrix <0.1))
+plot(imagematrix(p_values_matrix >0.1))
+
+#imagematrixPNG(imagematrix(equalize(x)), name = "Phantom_AO_7W_L5_100b.png")
+imagematrixPNG(imagematrix(equalize(cv_values)), name = "cv_lake_512.png")
+
+imagematrixPNG(imagematrix(p_values_matrix), name="cv_pvalues_lake_512.png")
+imagematrixPNG(imagematrix(p_values_matrix>0.05), name="cv_005_pvalues_lake_512.png")

### 2024-04-24 Code/R/Programs/p-values-MnAd-test.R

@@ -1,0 +1,55 @@
+rm(list = ls())
+
+#load("../Programs/Data/results_Phantom_mnad_7.Rdata")
+#save(cd_values_mnad, Z, file = "./Data/results_Phantom_mnad_7.Rdata")
+
+#load("../Programs/Data/MnAD_results_data_Illinois_crops_1024.Rdata")
+#save( cd_values_mnad, x, file = "./Data/MnAD_results_data_mexico_512.Rdata")
+#load("../Programs/Data/MnAD_results_data_mexico_512.Rdata")
+load("../Programs/Data/MnAD_results_data_lake_512.Rdata")
+
+#Illinois_crops
+# meanlog <- -1.5865643
+# sdlog <- 0.5912683
+#mexico
+# meanlog <- -1.1788140
+# sdlog <- 0.5000859
+
+#lake
+meanlog <- -1.2856986
+sdlog <- 0.6665039
+
+# Crear una matriz para almacenar los p-valores
+p_values_matrix <- matrix(NA, nrow = nrow(cd_values_mnad), ncol = ncol(cd_values_mnad))
+
+# Calcular los p-valores para cada dato en la matriz de coeficientes de variación
+for (i in 1:nrow(cd_values_mnad)) {
+  for (j in 1:ncol(cd_values_mnad)) {
+    cd_value_mnad <- cd_values_mnad[i, j]
+    
+    # Calcular el p-valor utilizando la función plnorm()
+    p_values_matrix[i, j] <- 1-plnorm(cd_value_mnad, meanlog = meanlog, sdlog = sdlog)
+  }
+}
+
+# Guardar la matriz de p-valores
+#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")
+
+
+
+
+#source("../imagematrix.R")
+source("../imagematrix.R")
+#hist(p_values_matrix)
+#par(mfrow=c(1,2))
+#plot(imagematrix(p_values_matrix ))
+#plot(imagematrix(equalize(z.up.le)))
+plot(imagematrix(equalize(cd_values_mnad)))#z.up.le
+plot(imagematrix(p_values_matrix ))
+#plot(imagematrix(p_values_matrix <0.1))
+plot(imagematrix(p_values_matrix >0.05))
+
+  imagematrixPNG(imagematrix(equalize(cd_values_mnad)), name = "mnad_lake_512.png")
+# # 
[…]

### 2024-04-24 Code/R/Programs/p-values-entropy-based-test.R

@@ -1,0 +1,55 @@
+rm(list = ls())
+
+#load("./Data/results_Mexico_512_7_AO_300b.Rdata")#
+#load("./Data/results_Phantom_4_regions_AO_7W_L5_100b.Rdata")
+#load("./Data/results_Chicago_1024_9_AO_200b_36L.Rdata")#OK
+#load("./Data/results_Mexico_512_7_AO_300b.Rdata")#OK
+#load("./Data/results_panama_512_AO_9W_L5_100b.Rdata")
+#save(difference_values, x, file = "./Data/results_Panama_512_AO_7x7_L5_200b.Rdata")
+#load("./Data/results_Panama_512_AO_7x7_L5_200b.Rdata")
+load("./Data/results_Lake_512_9W_AO_100b_36L.Rdata")#OK
+calculate_p_values_matrix <- function(data_matrix, mu, sigma) {
+  rows <- nrow(data_matrix)
+  cols <- ncol(data_matrix)
+  
+  p_values_matrix <- matrix(NA, nrow = rows, ncol = cols)
+  
+  for (i in 1:rows) {
+    for (j in 1:cols) {
+      test_difference <- data_matrix[i, j]
+      
+      epsilon <-(test_difference - 0) / (sigma)
+      p_value <- 2 * pnorm(-abs(epsilon))#  
+      
+      p_values_matrix[i, j] <- p_value
+    }
+  }
+  
+  return(p_values_matrix )
+}
+
+
+
+
+mean_difference_values <- mean(difference_values, na.rm = TRUE)
+sd_difference_values <- sd(difference_values, na.rm = TRUE)
+
+
+p_values_matrix <- calculate_p_values_matrix(difference_values, mean_difference_values, sd_difference_values)
+
+#save(p_values_matrix, file = "./Data/results_pvalue_Phantom_4_regions_AO_7W_L5_100b.Rdata")
+
+source("../imagematrix.R")
+hist(p_values_matrix)
+#plot(imagematrix(p_values_matrix),significance_level = 0.05)
+plot(imagematrix(p_values_matrix ))
+plot(imagematrix(p_values_matrix >0.05))
+plot(imagematrix(equalize(difference_values)))
+#plot(imagematrix(equalize(x)))
+
+
+  imagematrixPNG(imagematrix(equalize(x)), name = "lake_512.png")
[…]

### 2024-04-24 Code/R/Programs/p_value_plot_color.R

@@ -1,48 +1,0 @@
-rm(list = ls())
-# if(!require("rstudioapi")) install("rstudioapi")
-# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
-# for normal distribution
-library(ggplot2)
-library(e1071)
-library(nortest)
-library(fields)
-#load("./Data/results_data_Ottawa_100_5.Rdata") # difference_value
-#load("./Data/results_data_Flevoland_300_5.Rdata")
-
-load("./Data/results_data_Flevoland_300_7.Rdata")
-#load("./Data/results_data_Flevoland_300_9.Rdata")
-
-calculate_p_values_matrix <- function(data_matrix, sigma) {
-  rows <- nrow(data_matrix)
-  cols <- ncol(data_matrix)
-  
-  p_values_matrix <- matrix(NA, nrow = rows, ncol = cols)
-  
-  for (i in 1:rows) {
-    for (j in 1:cols) {
-      test_difference <- data_matrix[i, j]
-      
-      epsilon <-(test_difference - 0.0) / (sigma)
-      p_value <-p_value <- 2 * pnorm(abs(epsilon))-1#  
-      
-      p_values_matrix[i, j] <- p_value
-    }
-  }
-  
-  return(p_values_matrix )
-}
-
-
-
-
-mean_difference_values <- mean(difference_values, na.rm = TRUE)
-sd_difference_values <- sd(difference_values, na.rm = TRUE)
-
-
-p_values_matrix <- calculate_p_values_matrix(difference_values, sd_difference_values)
-
-
-source("../imagematrix.R")
-#hist(p_values_matrix)
-plot(imagematrix(p_values_matrix),significance_level = 0.05)
-

### 2024-04-24 Code/R/Programs/plot_pvalue.R

@@ -1,202 +1,0 @@
-# 
- rm(list = ls())
-# if(!require("rstudioapi")) install("rstudioapi")
-# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
-# for normal distribution
-library(ggplot2)
-library(e1071)
-library(nortest)
-
-#load("./Data/results_data_Ottawa_100_5.Rdata") # difference_value
-#load("./Data/results_data_Flevoland_300_5.Rdata")
-
-load("./Data/results_data_Flevoland_300_7.Rdata")
-#load("./Data/results_data_Flevoland_300_9.Rdata")
-
-calculate_p_values_matrix <- function(data_matrix, sigma) {
-  rows <- nrow(data_matrix)
-  cols <- ncol(data_matrix)
-  
-  p_values_matrix <- matrix(NA, nrow = rows, ncol = cols)
-  
-  for (i in 1:rows) {
-    for (j in 1:cols) {
-      test_difference <- data_matrix[i, j]
-      
-      epsilon <- (test_difference - 0.0) / sigma
-      p_value <-2 * pnorm(-abs(epsilon))  
-      
-      p_values_matrix[i, j] <- p_value
-    }
-  }
-  
-  return(p_values_matrix )
-}
-
-
-mean_difference_values <- mean(difference_values, na.rm = TRUE)
-sd_difference_values <- sd(difference_values, na.rm = TRUE)
-
-
-p_values_matrix <- calculate_p_values_matrix(difference_values, sd_difference_values)
-
-save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_300_7_n.Rdata")
-
-aspect_ratio <- ncol(p_values_matrix) / nrow(p_values_matrix)
-
-# Create a sequence of values for x and y axes based on the aspect ratio
-x_values <- seq(0, 1, length.out = ncol(p_values_matrix) + 1)
-y_values <- seq(0, aspect_ratio, length.out = nrow(p_values_matrix) + 1)
-
-# Plot the p_values_matrix with adjusted axes
-image(x = x_values, y = y_values, z = p_values_matrix, 
-      col = colorRampPalette(c("navy", "yellow", "orange"))(100),
-      main = "Heatmap de p-values",
-      xlab = "Columnas",
-      ylab = "Filas")
-
-# Add grid lines to visualize the pixel positions
-abline(v = x_values, h = y_values, col = "gray", lty = 2)
-
[…]

### 2024-04-24 Code/R/Programs/plot_pvalue_cv.R

@@ -1,28 +1,0 @@
-
-load("./Data/results_data_Flevoland_cv_300_5.Rdata")
-alpha <- 5.452
-beta <- 2.061
-
-
-pgamma_inv <- function(x, alpha, beta) {
-  1 - pgamma(1/x, shape = alpha, rate = beta)
-}
-
-
-p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))
-
-for (i in 1:nrow(cv_values)) {
-  for (j in 1:ncol(cv_values)) {
-    cv_value <- cv_values[i, j]
-    
-    
-    p_values_matrix[i, j] <- pgamma_inv(cv_value, alpha, beta)
-  }
-}
-
-
-save(p_values_matrix, file = "./Data/results_pvalue_cv_Flevoland_cv_300_5.Rdata")
-
-
-source("../imagematrix.R")
-plot(imagematrix(p_values_matrix > 0.05))

### 2024-04-24 Code/R/Programs/power_example.R

@@ -1,69 +1,0 @@
-
-
-rm(list = ls())
-
-library(ggplot2)
-library(ggsci)
-library(invgamma)
-library(latex2exp)
-library(data.table)
-source("../MainFunctions/ebrahimi_estimator.R")
-source("../MainFunctions/gamma_sar_sample.R")
-source("../MainFunctions/correa_estimator.R")
-source("../MainFunctions/bootstrap_correa_estimator.R")
-source("../MainFunctions/bootstrap_correa_estimator_log_mean.R")
-
-source("../MainFunctions/al_omari_1_estimator.R")
-source("../MainFunctions/bootstrap_al_omari_1_estimator.R")
-
-source("../MainFunctions/entropy_gI0.R")
-source("../MainFunctions/gi0_sample.R")
-
-set.seed(1234567890, kind = "Mersenne-Twister")
-
-
-
-
-alpha <- 0.05
-
-
-R <- 3000
-mu <- 1
-L <- 5
-B <- 2
-alpha1 <- -600
-
-sample_sizes <- c( 25, 49, 81, 121)
-
-
-power_results <- numeric(length(sample_sizes))
-
-# Escenarios bajo H1 (por ejemplo, clutter heterogéneo)
-for (i in seq_along(sample_sizes)) {
-  s <- sample_sizes[i]
-  reject_H0_count <- 0
-  
-  for (r in 1:R) {
-   
-    z1 <- gi0_sample(1, -600, 5, s)
-    
-   
-    TestStat <- sqrt(R) * (bootstrap_correa_estimator_log_mean(z1, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))) / sd(z1)
-    
-    
-    if (abs(TestStat) > qnorm(1 - alpha/2)) {
-      reject_H0_count <- reject_H0_count + 1
-    }
-  }
-  
-  # Calcular y almacenar el poder (1 - beta)
-  power <- reject_H0_count / R
-  power_results[i] <- power
-  
-  cat(paste("Power (1 - beta) for Sample Size", s, ":", power, "\n"))
-}
-
-# Graficar resultados
-plot(sample_sizes, power_results, type = "b", pch = 16, col = "blue",
-     xlab = "Sample Size", ylab = "Power (1 - beta)",
-     main = "Power Analysis")

### 2024-04-24 Code/R/Programs/test_differences.R

@@ -1,108 +1,0 @@
-rm(list = ls())
-
-library(ggplot2)
-library(ggsci)
-library(invgamma)
-library(latex2exp)
-if(!require("rstudioapi")) install("rstudioapi")
-setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
-
-source("../MainFunctions/ebrahimi_estimator.R")
-source("../MainFunctions/gamma_sar_sample.R")
-source("../MainFunctions/correa_estimator.R")
-source("../MainFunctions/bootstrap_correa_estimator.R")
-source("../MainFunctions/bootstrap_correa_estimator_log_mean.R")
-
-source("../MainFunctions/al_omari_1_estimator.R")
-source("../MainFunctions/bootstrap_al_omari_1_estimator.R")
-
-source("../MainFunctions/entropy_gI0.R")
-source("../MainFunctions/gi0_sample.R")
-
-set.seed(1234567890, kind = "Mersenne-Twister")
-
-R <- 10
-mu <- 1
-L <- 5
-B <- 1
-alpha1 <- -6
-sample.size <- c( 9, 25, 49, 81, 121)
-
-TestStatistics1 <- NULL
-TestStatistics2 <- NULL
-TestStatistics3 <- NULL
-TestStatistics4 <- NULL
-mean_entropy1 <- numeric(length(sample.size))
-mean_entropy2 <- numeric(length(sample.size))
-mean_entropy3 <- numeric(length(sample.size))
-mean_entropy4 <- numeric(length(sample.size))
-for (s in sample.size) {
-  TestStat1 <- numeric(R)
-  TestStat2 <- numeric(R)
-  TestStat3 <- numeric(R)
-  TestStat4 <- numeric(R)
-  
-  
-  for (r in 1:R) {
-    #z <- gi0_sample(mu, alpha1, L, s)
-    z <- gamma_sar_sample(L, mu, s)
-
-    #TestStat1[r] <- -bootstrap_correa_estimator_log_mean(z, B) - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L) + L + lgamma(L - alpha1) - (L - alpha1) * (digamma(L - alpha1)) + (1 - alpha1) * digamma(-alpha1) - log(-1 - alpha1) - lgamma(-alpha1))
-    TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
[…]

### 2024-04-24 Code/R/Programs/test_differences_subplots_gi0.R

@@ -1,179 +1,0 @@
-rm(list = ls())
-
-library(ggplot2)
-
-library(grid)
-library(ggsci)
-library(invgamma)
-library(latex2exp)
-library(gridExtra)
-source("../MainFunctions/ebrahimi_estimator.R")
-source("../MainFunctions/gamma_sar_sample.R")
-source("../MainFunctions/correa_estimator.R")
-source("../MainFunctions/bootstrap_correa_estimator.R")
-source("../MainFunctions/bootstrap_correa_estimator_log_mean.R")
-
-source("../MainFunctions/al_omari_1_estimator.R")
-source("../MainFunctions/bootstrap_al_omari_1_estimator.R")
-
-source("../MainFunctions/entropy_gI0.R")
-source("../MainFunctions/gi0_sample.R")
-
-set.seed(1234567890, kind = "Mersenne-Twister")
-
-R <- 3000
-mu <- 1
-L <- 5
-B <- 2
-sample.size <- c( 81)
-
-alpha1_values <- c( -3, -8, -20, -100)
-
-
-plots_list <- list()
-
-for (alpha_val in alpha1_values) {
-
-  alpha1 <- alpha_val
-  
-  TestStatistics1 <- NULL
-  TestStatistics2 <- NULL
-  
-  mean_entropy1 <- numeric(length(sample.size))
-  mean_entropy2 <- numeric(length(sample.size))
-  
-  for (s in sample.size) {
-    TestStat1 <- numeric(R)
-    TestStat2 <- numeric(R)
-    
-    for (r in 1:R) {
-      z <- gi0_sample(mu, alpha1, L, s)
-      
-      TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
-      TestStat2[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L) - L - lgamma(L - alpha1) + (L - alpha1) * (digamma(L - alpha1))- (1 - alpha1) * digamma(-alpha1) + log(-1 - alpha1) + lgamma(-alpha1))
-      
[…]

### 2024-04-24 Code/R/Programs/tipe1_error_example.R

@@ -1,75 +1,0 @@
-rm(list = ls())
-
-library(ggplot2)
-library(ggsci)
-library(invgamma)
-library(latex2exp)
-library(data.table)
-
-if(!require("rstudioapi")) install("rstudioapi")
-setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
-source("../MainFunctions/ebrahimi_estimator.R")
-source("../MainFunctions/gamma_sar_sample.R")
-source("../MainFunctions/correa_estimator.R")
-source("../MainFunctions/bootstrap_correa_estimator.R")
-source("../MainFunctions/bootstrap_correa_estimator_log_mean.R")
-
-source("../MainFunctions/al_omari_1_estimator.R")
-source("../MainFunctions/bootstrap_al_omari_1_estimator.R")
-
-source("../MainFunctions/entropy_gI0.R")
-source("../MainFunctions/gi0_sample.R")
-
-set.seed(1234567890, kind = "Mersenne-Twister")
-
-
-alpha <- 0.05
-
-
-R <- 100
-mu <- 1
-L <- 5
-B <- 2
-alpha1 <- -6
-
-
-sample_sizes <- c(25, 49, 81, 121)
-
-
-error_type_I_results <- numeric(length(sample_sizes))
-
-
-for (i in seq_along(sample_sizes)) {
-  s <- sample_sizes[i]
-  false_positives_count <- 0
-  
-  for (r in 1:R) {
-    #
-    z0 <- gi0_sample(1, -6, 5, s)
-    
-    # prueba bajo H0
-    TestStat <- sqrt(R) * (bootstrap_correa_estimator_log_mean(z0, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))) / sd(z0)
-    #TestStat <- bootstrap_correa_estimator_log_mean(z0, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L)) 
-    
-
-    
-    # 
-    if (abs(TestStat) > qnorm(1 - alpha/2)) {
-      false_positives_count <- false_positives_count + 1
-    }
-  }
-  
- 
-  cat(paste("False Positives for Sample Size", s, ":", false_positives_count, "\n"))
-  
-  # Calcular y almacenar el error tipo I
-  error_type_I <- false_positives_count / R
-  error_type_I_results[i] <- error_type_I
-  
-  cat(paste("Error Type I for Sample Size", s, ":", error_type_I, "\n"))
-}
-
[…]

### 2024-04-25 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Revised version

@@
   The physical modeling of this kind of data allows to use the Gamma distribution in the presence of fully-developed speckle, i.e., when there are infinitely many independent backscatterers per resolution cell, and none dominates the return.
-This situation is often called "homogeneous" or  "textureless" regions.
+  Such areas are often called "homogeneous" or  "textureless" regions. 
   The $\mathcal{G}_I^0$ distribution is also a widely accepted law for heterogeneous and extremely heterogeneous regions, i.e., areas in which the fully-developed speckle hypotheses do not hold. 
-  We propose three test statistics to distinguish between homogeneous and inhomogeneous regions, i.e. between gamma and \(\mathcal{G}_I^0\) distributed data, both with a known number of looks. 
+  We propose three test statistics to distinguish between homogeneous and inhomogeneous regions, i.e., between gamma and \(\mathcal{G}_I^0\) distributed data, both with a known number of looks. 
   The first test statistic uses a bootstrapped non-parametric estimator of Shannon entropy, which provides a robust assessment in the face of uncertain distributional assumptions.
@@
 # We show that our proposal outperforms its competitors using simulated and SAR data.
-# ACF Which is "our proposal" and which are the "competitors"? # ok
 keywords: |
@@
 knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
-#knitr::opts_chunk$set(echo = FALSE)
+
 library(fitdistrplus)
@@
 library(reshape2)
-#library(plotly)
 library(knitr)
@@
 library(dplyr)
-#options(kableExtra.latex.load_packages = FALSE)
-#library(devtools)
-#devtools::install_github("haozhu233/kableExtra")
 library(kableExtra)
@@
 
+# External functions
 source("../Code/R/MainFunctions/gamma_sar_sample.R")
@@
 source("../Code/R/MainFunctions/bootstrap_al_omari_2_estimator.R")
-#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
+
+#The following source files contain the functions: generate_samples, calculate_bias_mse, generate_plot
 source("../Code/R/Programs/functions_sample_bias_mse.R")# read_ENVI_images
 source("../Code/R/Programs/read_ENVI_images.R")
-
 ```
@@
 
-Speckle is non-Gaussian speckle, thus SAR data require reliable statistical models for accurate processing. 
+Speckle in intensity format is non-Gaussian, thus SAR data require reliable statistical models for accurate processing. 
 The $\mathcal{G}^0$ distribution, which is suitable for SAR data, includes the
@@
 Our work aims to improve the identification of potential roughness features in SAR intensity data.
-<!-- ACF The following sentence is misleading: the gamma law is a consequence of infinitely many backscatterers with none dominating the return, not the other way aroud. Rephrase. -->
-<!-- JA Corrected -->
 Physical modeling of SAR data allows the use of the Gamma distribution in the presence of fully-developed speckle, where an infinite number of independent backscatterers per resolution unit is assumed, commonly referred to as homogeneous regions
@@
 In statistics, Shannon entropy is a crucial descriptive parameter, especially for evaluating data dispersion and performing tests for normality, exponentiality and uniformity&nbsp;\cite{Wieczorkowski1999,Zamanzade2012}.
-Entropy estimation is associated with some practical difficulties, especially when the model is unknown. In these cases, non-parametric methods are used.
-Spacing methods have been discussed as a non-parametric approach in&nbsp;\cite{AlizadehNoughabi2010,Subhash2021}.
-This strategy provides the flexibility to consider a wide range of models without enforcing certain parametric constraints.
-
-The CV, introduced in 1896 by Pearson&nbsp;\cite{Pearson1896}, is a relative dispersion measure widely used in various fields of applied statistics, including sampling, biostatistics, medical and biological research, climatology and other fields&nbsp;\cite{hendricks1936sampling,Tian2005,SubrahmanyaNairy2003,Chankham2024}.
-It facilitates the comparison of variability between different populations and is particularly valuable for comparing variables with different units. 
+Entropy estimation is challenging, especially when the model is unknown. In these cases, non-parametric methods are used.
+Spacing methods have been discussed as a non-parametric approach in Refs.&nbsp;\cite{AlizadehNoughabi2010,Subhash2021}. 
+This strategy is flexible and robust because it does not enforce a model or any parametric constraints.
+
+The coefficient of variation (CV), introduced in 1896 by Pearson&nbsp;\cite{Pearson1896}, is a relative dispersion measure widely used in various fields of applied statistics, including sampling, biostatistics, medical and biological research, climatology and other fields&nbsp;\cite{hendricks1936sampling,Tian2005,SubrahmanyaNairy2003,Chankham2024}.
+It facilitates the comparison of variability between different populations and is particularly valuable for relating variables with different units. 
 This is because when the main purpose is to compare the variations of several variables, the standard deviation can only serve as an adequate measure of variation if all variables are expressed in the same unit of measurement and have identical means.
-If these conditions are not met for the variables under investigation, the CV is the relative measure that is usually used in real applications.
+If these conditions are not met, then the CV is the relative measure that is usually used in real applications. 
 The variable with the highest CV value is the one with the largest relative dispersion around the mean value&nbsp;\cite{Banik2011}.
@@
 The other parameter we study is the Shannon entropy.
-Different models for SAR data have different entropy values, but this fundamental quantity can be also estimated in a model-agnostic way.
+Different levels of roughness, materialized as models for SAR data, have different entropy values, but this fundamental quantity can be also estimated in a model-agnostic way.
 We exploit this property and design a bootstrap-improved non-parametric estimator for the Shannon entropy.
 
-We devise test statistics based on these three estimators: the classical coefficient of variation, a robust version, and the Shannon entropy estimator.
+We devise test statistics based on these three estimators: 
+the classical coefficient of variation, 
+a robust version, 
+and the Shannon entropy estimator.
 We apply these test statistics to generate maps of evidence of homogeneity
 that reveal different types of targets in the SAR data. 
-Through extensive experiments with simulated and SAR data, we demonstrate the superiority of our proposed method over existing approaches.
+We show that our proposed method is superior over existing approaches with simulated data and SAR images.
 
@@
 \begin{align}
-    f_Z(z;L, \mu)&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z)\label{E:gamma1}\\
+    f_Z(z;L, \mu\mid \Gamma_{\text{SAR}})&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z)\label{E:gamma1}\\
     \intertext{ and }
-    f_Z(z; \alpha, \gamma, L)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
+    f_Z(z; \alpha, \gamma, L \mid \mathcal{G}_I^0)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
 \end{align} 
-where \(\mu > 0\) is the mean, \(\gamma > 0\) is the scale, \(\alpha < -1\) measures
-the roughness, \(L \geq 1\) is the number of looks, \(\Gamma(\cdot)\) is
-the gamma function, and \(\mathbbm 1_{A}(z)\) is the indicator function
+where \(\mu > 0\) is the mean, 
+\(\gamma > 0\) is the scale, 
+\(\alpha < 0\) measures the roughness, 
+\(L \geq 1\) is the number of looks, 
+\(\Gamma(\cdot)\) is
+the gamma function, 
+and \(\mathbbm 1_{A}(z)\) is the indicator function
 of the set \(A\).
 
-If we take the law with the density&nbsp;\eqref{E:gi01}, the \(r\)th non-central moment of \(Z\) is expressed as follows:
-\begin{align}
-    E_{\mathcal{G}_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\Gamma(L)}, \quad \alpha <-r. 
+The $r$th order moments of the $\mathcal{G}_I^0$ model are
+\begin{equation}
+E\big(Z^r\mid \mathcal{G}_I^0\big)  = \left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\Gamma(L)}, 
     \label{E:rmom}
-\end{align}
+\end{equation}
+provided $\alpha <-r$, and infinite otherwise.
+Therefore, assuming $\alpha<-1$, its expected value is
+\begin{equation}
+    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
+\end{equation}
 
 Although the \(\mathcal{G}_I^0\) distribution is defined by the parameters \(\alpha\) and \(\gamma\), in the SAR literature&nbsp;\cite{Nascimento2010} the texture \(\alpha\) and the mean \(\mu\) are usually used.
-The expected value \(\mu\) using the expression in&nbsp;\eqref{E:rmom} is
+Reparametrizing&nbsp;\eqref{E:gi01} with \(\mu\), and denoting this model as $G_I^0$ we obtain:
 \begin{equation}
-    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1},
-\end{equation} 
-and we reparametrize&nbsp;\eqref{E:gi01} with \(\mu\) obtaining:
-\begin{equation}
-        f_Z(z; \mu, \alpha, L)=\frac{L^L\Gamma(L-\alpha)}{\big[-\mu(\alpha+1)\big]^{\alpha}\Gamma(-\alpha)\Gamma(L)} \frac{z^{L-1}}{\big[-\mu(\alpha+1)+Lz\big]^{L-\alpha}}.\label{E:gi02}
+        f_Z\big(z; \mu, \alpha, L\mid G_I^0\big) = \frac{L^L\Gamma(L-\alpha)}{\big[-\mu(\alpha+1)\big]^{\alpha}\Gamma(-\alpha)\Gamma(L)} \frac{z^{L-1}}{\big[-\mu(\alpha+1)+Lz\big]^{L-\alpha}}.\label{E:gi02}
 \end{equation}
@@
 	\end{equation*}
-where $m<n/2$ is a positive integer, $Z_{(i+m)}-Z_{(i-m)}$ is the $m$-spacing and $Z_{(1)}\leq Z_{(2)}\leq\ldots\leq Z_{(n)}$ are the order statistics, $Z_{(i)}= Z_{(1)}$ if $i<1$, $Z_{(i)}= Z_{(n)}$ if $i>n$.
+where $m<n/2$ is a positive integer, 
+$Z_{(1)}\leq Z_{(2)}\leq\dots\leq Z_{(n)}$ are the order statistics,
+and $Z_{(i+m)}-Z_{(i-m)}$ is the $m$-spacing, in which $Z_{(i)}= Z_{(1)}$ if $i<1$, $Z_{(i)}= Z_{(n)}$ if $i>n$.
 
 Several authors have explored adaptations to Vasicek's estimator. 
-We consider three estimators known for their superior performance&nbsp;\cite{Cassetti2022}.
+We consider three estimators known for their superior performance&nbsp;\cite{Cassetti2022}:
 
@@
 
-Let us assume that non-parametric entropy estimators
-\(\widehat{H}=\widehat{\theta}(\bm{Z})\) are inherently biased, i.e:\begin{equation}
+Let us assume that the non-parametric entropy estimator
+\(\widehat{H}=\widehat{\theta}(\bm{Z})\) is inherently biased, i.e,:
+\begin{equation}
 \label{Eq:bias1}
 \operatorname{Bias}\big(\widehat{\theta}(\bm{Z})\big) = E\big[\widehat{\theta}(\bm{Z})\big] - \theta \neq 0.
-\end{equation} Our bootstrap-improved estimators are of the form:
+\end{equation} 
+Our bootstrap-improved estimator is of the form:
 \begin{align*}
@@
 \(\mu\in\left\{1, 10\right\}\) and \(L=5\). 
-The results are consistent with the other situations. 
+The results are consistent with other situations. 
 We used $B=200$ bootstrap samples and the heuristic spacing
@@
 save(results_gi0, file = "./Data/resultsgi0_1.Rdata")
-
 ```
@@
 print(combined_plot_gi0)
-
 ```
@@
 \end{align}
-
-We explore a robust alternative to CV, as describedby&nbsp;\cite{Ospina2019}, which incorporates the ratio between the mean absolute deviation from the median (MnAD) and the median, two well-known robust measures of
+The CV can be easily estimated as the ratio of the sample mean to the sample standard deviation.
+
+We explore a robust alternative to estimate the CV, as described by&nbsp;\cite{Ospina2019}: 
+the ratio between the mean absolute deviation from the median (MnAD) and the median, two well-known robust measures of
 scale and location, respectively. 
@@
 \(n^{-1}\sum_{i=1}^n|x_i-\widehat{Q}_2|\), where \(\widehat{Q}_2\)
-is an estimate for the median of the population, which can be approximated by the median of the sample.
+is an estimate for the median of the population, for example, the sample median.
 
@@
 
-Figure&nbsp;\ref{fig:Plot_density} shows the empirical test statistic densities for different sample sizes using \(\widetilde{H}_{\text{AO}}\) estimator, and Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean, SD, variance (Var), skewness (SK), excessive kurtosis (EK) and Anderson--Darling \(p\) values for normality.
+Figure&nbsp;\ref{fig:Plot_density} shows the empirical test statistic densities for different sample sizes using \(\widetilde{H}_{\text{AO}}\) estimator, and Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean,
+standard deviation&nbsp;(SD), 
+variance&nbsp;(Var), 
+skewness&nbsp;(SK), 
+excessive kurtosis&nbsp;(EK) and 
+Anderson--Darling \(p\) values for normality. 
 Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption.
-A low variance as well as a skewness and an excessive kurtosis of almost zero indicate limited dispersion, symmetry and a light tail.
+A low variance as well as a skewness and an excessive kurtosis of almost zero indicate limited dispersion, asymmetry and a light tail.
 Normal QQ plots confirm that there is no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.
@@
 \[
-\varepsilon=\frac{\widetilde{H}-H_{\Gamma_{\text{SAR}}}}{\hat\sigma}.
+\varepsilon=\frac{\widetilde{H}-H_{\Gamma_{\text{SAR}}}}{\widehat\sigma}.
 \]
@@
 
-Similarly, we use another test statistic based on the ratio of the MnAD to the median. This statistic is given by:
+Similarly, we use another test statistic based on the ratio of the MnAD to the median. 
+This statistic is given by:
 \begin{align}
@@
 \end{align}
-These test statistics allow assessing the variability of the data.
-
-The situations in which the use of CV and \(\text{CV}_{\text{MnAD}}\) may be appropriate, i.e. when the observations are positive, the log-normal
+
+We proceed to identify suitable models for these estimators of the CV, and then form test statistics.
+
+The situations in which the use of CV and \(\text{CV}_{\text{MnAD}}\) may be appropriate, i.e., when the observations are positive, the log-normal
 (LN) and the inverse Gaussian distribution (IG) are often more appropriate than the Gamma and Weibull distributions&nbsp;\cite{Chaubey2017,takagi1997application}.
@@
 \end{align}  
-here, $\mu_{\text{LN}}$ and $\sigma_{\text{LN}}$ are the mean and standard deviation of the logarithm.
+with $\mu_{\text{LN}}$ is any real number, and $\sigma_{\text{LN}}$ is positive.
 
@@
 
-Akaike information criterion (AIC) and Bayesian information criterion (BIC) are used to select the best fitting distribution.
-
-The AIC is a fine technique that deals with the trade-off between the goodness-of-fit of the model and the simplicity of the model in terms of the number of model parameters&nbsp;\cite{Burnham2004}. 
+We used the Akaike information criterion (AIC) and Bayesian information criterion (BIC) to select the best fitting distribution.
+
+The AIC deals with the trade-off between the goodness-of-fit and the simplicity of the model in terms of the number of model parameters&nbsp;\cite{Burnham2004}. 
 The model or distribution with the lowest value of AIC is chosen to be the best.
-The BIC assesses goodness-of-fit of a distribution or model, but avoids overfitting by penalising an additional degree of freedom&nbsp;\cite{Dziak2019}. 
+The BIC assesses goodness-of-fit of a distribution or model, but avoids overfitting by penalising additional degrees of freedom&nbsp;\cite{Dziak2019}. 
 The model with the lowest BIC value is chosen as the best.
@@
 
-# Simulation Results {#sec:Results}
-
-This section presents simulations that were performed to obtain an evaluation of the performance of the proposed test statistics.
+# Results {#sec:Results}
+
+This section presents the simulations we performed to evaluate the performance of the proposed test statistics, followed by applications to SAR data.
 
@@
 Figure&nbsp;\ref{fig:sim_Phantom} shows the phantom used for a simulated image with dimensions of $500\times 500$ pixels that consists of four smaller phantoms, each of which exhibits differences between homogeneous and heterogeneous regions.
-The regions are formed by independent draws from the $G^0_I$ distribution, with $L = 5$ and varying $\alpha$.
+This phantom was proposed by&nbsp;\citet{Gomez2017}.
+The observations are independent draws from the $G^0_I$ distribution, with $L = 5$ and varying $\alpha$.
 
@@
 
-## Real SAR Data
-
-We evaluated the proposed test statistics using three real SAR images. 
-For our analysis, we used images of the coast of Jalisco, Mexico, and of Illinois, USA. 
-These images were acquired by the Sentinel-1B satellite operating in C-band, with VV polarization, intensity format, \(L=18\) and \(L=36\)  nominal looks.
-
+## SAR Data
+<!-- ACF Don't use "real" unless it refers to the real part of a complex value -->
+
+We evaluated the proposed test statistics using three SAR images: one of the coast of Jalisco, Mexico, and two of Illinois, USA, acquired by the Sentinel-1B satellite operating in C-band, with VV polarization, intensity format, \(L=18\) and \(L=36\)  nominal looks.
+<!-- ACF Did you check this nominal value? It is interesting to estimate and use the equivalent number of looks -->
+<!-- ACF Provide the spatial resolution -->
 The first two images have a size of \(512 \times 512\) pixels, while the third has \(1024 \times 1024\) pixels  and they contain mountainous areas, agricultural regions, water bodies and  urban areas, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)--(c).

### 2024-04-30 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Final version with corrections made

@@
 funding: |
-  Please add: "This research received no external funding" or "This research 
-  was funded by NAME OF FUNDER grant number XXX."  and ``The APC was funded 
-  by XXX''. Check carefully that the details given are accurate and use the 
-  standard spelling of funding agency names at 
-  \url{https://search.crossref.org/funding}, any errors may affect your future 
-  funding.
+  This research received no external funding.
 institutionalreview: |
@@
  This article was written in Rmarkdown and is fully reproducible. The code and data are accessible at
- \url{https://github.com/rjaneth/identifying-heterogeneity-in-sar-data-with-new-test-statistics} (accessed on 24 April 2024).
+ \url{https://github.com/rjaneth/identifying-heterogeneity-in-sar-data-with-new-test-statistics} (accessed on 30 April 2024).
 # abbreviations:
@@
    - \usepackage{subcaption}
-   - \captionsetup[sub]{labelfont=bf,textfont=bf}
+   - \captionsetup[subfigure]{labelformat=parens, justification=centering}
+   - \usepackage{placeins}
 
@@
 The variable with the highest CV value is the one with the largest relative dispersion around the mean value&nbsp;\cite{Banik2011}.
-The coefficient of variation is the basic measure of heterogeneity in SAR data&nbsp;\cite{oliverquegan98}.
+The coefficient of variation is the basic measure of heterogeneity in SAR data&nbsp;\cite{Touzi1988,oliverquegan98}.
 We study two ways of estimating the coefficient of variation.
@@
 
-```{r Plot_GI0_to_gamma1, echo=FALSE, message=FALSE, warning=FALSE, out.width="70%", fig.show="hold", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ with $L=8$."}
+```{r Plot_GI0_to_gamma1, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="80%",  fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$, with $L=8$."}
 
@@
 
-Several authors&nbsp;\cite{vasicek1976test, Wieczorkowski1999,correa1995new,AlOmari2019} have studied the problem of the non-parametric estimation of $H(Z)$.
+The problem of the non-parametric estimation of $H(Z)$ has been studied by many authors, including&nbsp;\cite{vasicek1976test,Wieczorkowski1999,correa1995new,AlOmari2019}.
 Their proposals use estimators based on differences between order statistics: spacings.
@@
 $$
-\widehat{H}_{\text{AO}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{\omega_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right]
+\widehat{H}_{\text{AO}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{\omega_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
 $$
@@
 Applying this methodology, the original estimators of Correa,
-Ebrahimi and Al-Omari are now referred to as the proposed bootstrap-enhanced versions:
+Ebrahimi and Al-Omari are now referred to as the proposed bootstrap-improved versions:
 \(\widetilde{H}_{\text{C}}\),
@@
 
-```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.pos="hbt",  fig.cap="Bias and MSE, $L=5$ and  $\\alpha=-10$.", fig.width=8, fig.height=5.5}
+```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="95%", fig.pos="hbt",  fig.cap="Bias and MSE, $L=5$ and  $\\alpha=-10$."}
 
@@
 ```{r Table_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-#cat("\\setlength{\\tabcolsep}{0.5pt}\n")
+cat("\\setlength{\\tabcolsep}{6pt}\n")
 load("./Data/resultsgi0_1.Rdata")
@@
 
-colnames(reshaped_results) <- c("$\\mu$", "$n$",  "$\\widehat{H}_{\\text{C}}$", "$\\widehat{H}_{\\text{E}}$","$\\widehat{H}_{\\text{AO}}$",  "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$","$\\widetilde{H}_{\\text{AO}}$",   "$\\widehat{H}_{\\text{C}}$", "$\\widehat{H}_{\\text{E}}$","$\\widehat{H}_{\\text{AO}}$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$","$\\widetilde{H}_{\\text{AO}}$")
+colnames(reshaped_results) <- c("$\\bm{\\mu}$", "$\\bm{n}$",  "$\\bm{\\widehat{H}_{\\text{C}}}$", "$\\bm{\\widehat{H}_{\\text{E}}}$","$\\bm{\\widehat{H}_{\\text{AO}}}$",  "$\\bm{\\widetilde{H}_{\\text{C}}}$", "$\\bm{\\widetilde{H}_{\\text{E}}}$","$\\bm{\\widetilde{H}_{\\text{AO}}}$",   "$\\bm{\\widehat{H}_{\\text{C}}}$", "$\\bm{\\widehat{H}_{\\text{E}}}$","$\\bm{\\widehat{H}_{\\text{AO}}}$", "$\\bm{\\widetilde{H}_{\\text{C}}}$", "$\\bm{\\widetilde{H}_{\\text{E}}}$","$\\bm{\\widetilde{H}_{\\text{AO}}}$")
 
@@
     booktabs = TRUE,
-    align = "lrrrrrrrrrrrrrrr",
+    align = "crllllllllllll",
     escape = FALSE, 
@@
     centering = FALSE,
-    table.envir = "table", position = "H") %>%
+    table.envir = "table",  position="hbt", linesep = "") %>%
     add_header_above(c(" ", " ", "Bias" = 6,  "MSE" = 6)) %>%
     collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
-    row_spec(0,  align = "c")%>%
-    kable_styling(latex_options = "scale_down")
+    row_spec(0,  align = "r")%>%
+    kable_styling(latex_options = "scale_down")#%>%
+   # kable_styling( full_width = T)
   #)
@@
 For a random sample \(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) from a distribution $\mathcal{D}$, a test statistic is proposed.
-It is based on an  empirical distribution that arises  from the difference between non-parametrically estimated entropies $\widetilde{H}(\bm{Z})$ and the analytical entropy of Gamma SAR&nbsp;\eqref{E:E-gamma} evaluated at the logarithm of the sample mean, where $L_0\geq 1$ is known.
+It is based on an  empirical distribution that arises  from the difference between non-parametrically estimated entropies $\widetilde{H}(\bm{Z})$ and the analytical entropy of $\Gamma_{\text{SAR}}$&nbsp;\eqref{E:E-gamma} evaluated at the logarithm of the sample mean, where $L\geq 1$ is known.
 
@@
 \label{Eq:test_e}
-S(\bm{Z};L_0)= \widetilde{H}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L_0)+\ln \widebar{\bm{Z}}\right].
+S(\bm{Z};L)= \widetilde{H}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{\bm{Z}}\right].
 \end{equation}
@@
 This test statistic  aims to assess the behavior of the data under the null hypothesis using the empirical distribution.
-If the data represent fully-developed speckle, the density should center around zero, i.e., $S(\bm{Z};L_0)\approx 0$.
+If the data represent fully-developed speckle, the density should center around zero, i.e., $S(\bm{Z};L)\approx 0$.
 Otherwise, under the alternative hypothesis, the empirical distribution would shift from zero, suggesting significant differences and implying the presence of heterogeneous clutter.
@@
 
-Figure&nbsp;\ref{fig:Plot_density} shows the empirical test statistic densities for different sample sizes using \(\widetilde{H}_{\text{AO}}\) estimator, and Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean,
+The comparison between the bootstrap-improved estimators is shown in Table&nbsp;\ref{tab:table_time}, where the test accuracy under null hypothesis is presented alongside running times. 
+The test accuracy is evaluated through 1000 simulated samples of different sizes, with each size replicated 100 times using bootstrap resampling.
+
+The processing time is an important feature, especially considering the application of these estimators to large datasets of SAR images, as can be seen in Section&nbsp;\ref{sec:Results}.
+
+```{r Simulated_comparative_time2, echo=FALSE, message=FALSE}
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+R <- 1000
+mu <- 1
+B <- 40#100
+
+sample.size <- c(25,49, 81, 121)
+L_values <- c( 2, 8)
+
+bootstrap_estimators <- list(
+  "$\\widetilde{H}_{\\text{C}}$" = bootstrap_correa_estimator,
+  "$\\widetilde{H}_{\\text{E}}$" = bootstrap_ebrahimi_estimator,
+  "$\\widetilde{H}_{\\text{AO}}$" = bootstrap_al_omari_1_estimator
+
+)
+
+all_TestStatistics <- list()
+
+execution_times <- list()
+
+for (estimator_name in names(bootstrap_estimators)) {
+
+  TestStatistics <- list()
+
+  for (L in L_values) {
+    TestStat <- list()
+
+    for (s in sample.size) {
+      TestStat1 <- numeric(R)
+      start_time <- Sys.time() # start time
+
+      for (r in 1:R) {
+        z <- gamma_sar_sample(L, mu, s)
+        TestStat1[r] <- bootstrap_estimators[[estimator_name]](z, B) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+      }
+
+      TestStatistics[[as.character(s)]] <- data.frame("SampleSize" = rep(s, R), "Test_Statistics" = TestStat1)
+
+      end_time <- Sys.time() # end time
+      execution_time <- end_time - start_time # total time
+      execution_times[[paste(estimator_name, L, s)]] <- execution_time # save time
+    }
+
+    all_TestStatistics[[paste(estimator_name, L)]] <- TestStatistics
+  }
+}
+
+save(all_TestStatistics, execution_times, file = "./Data/results_data_time2.Rdata")
+
+```
+
+```{r Table_statistic_time2, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+load("./Data/results_data_time2.Rdata")
+
+combined_results <- data.frame(Estimator = character(),
+                               L = numeric(),
+                               SampleSize = numeric(),
+                               Mean = numeric(),
+                               Time = numeric())
+
+if (length(all_TestStatistics) > 0 & length(execution_times) > 0) {
+  for (estimator_name in names(bootstrap_estimators)) {
+    for (L in L_values) {
+      for (sample_size in sample.size) {
+
+        if (!is.null(all_TestStatistics[[paste(estimator_name, L)]][[as.character(sample_size)]]) &
+            !is.null(execution_times[[paste(estimator_name, L, sample_size)]])) {
+          mean_value <- mean(all_TestStatistics[[paste(estimator_name, L)]][[as.character(sample_size)]][["Test_Statistics"]])
+          time_value <- execution_times[[paste(estimator_name, L, sample_size)]]
+          combined_results <- rbind(combined_results, data.frame(Estimator = estimator_name,
+                                                                 L = L,
+                                                                 SampleSize = sample_size,
+                                                                 Mean = mean_value,
+                                                                 Time = time_value))
+        }
+      }
+    }
+  }
+} else {
+  # 
+  print("No data.")
+}
+
+# time
+combined_results$Time <- gsub(" secs", "", combined_results$Time)
+
+# 
+combined_results$Time <- sprintf("%.2f", as.numeric(combined_results$Time))
+
+#  LaTeX notation
+colnames(combined_results) <- c("\\textbf{Estimator}", "$\\bm{L}$", "$\\bm{n}$", "$S(\\bm{Z}; L)$", "\\textbf{ Time} (s)")
+combined_results[] <- lapply(combined_results, function(x) {
+  if (is.numeric(x)) {
+    if (all(x %% 1 == 0)) {
+      formatted_numbers <- sprintf("$%d$", x)
+    } else {
+      formatted_numbers <- ifelse(x < 0, sprintf("$%.5f$", x), sprintf("$\\phantom{-}%.5f$", x))
+    }
+    return(formatted_numbers)
+  } else {
+    return(x)
+  }
+})
+
+#
+table_result_combined <- knitr::kable(
+  combined_results,
+  caption = "Test accuracy and processing time for each bootstrap-improved estimator. ",
+  format = "latex",
+  booktabs = TRUE,
+  align = "ccccccc",
+  escape = FALSE,
+  digits = 5,
+  label = "table_time",
+  centering = FALSE,
+  table.envir = "table", position="H", linesep = "") %>%
+  row_spec(4,  extra_latex_after = "\\cline{3-5}")%>%
+  row_spec(12,  extra_latex_after = "\\cline{3-5}")%>%
+  row_spec(20,  extra_latex_after = "\\cline{3-5}")%>%
+  collapse_rows(latex_hline = "major", valign = "middle") %>%
+  row_spec(0,  align = "c")%>%
+  kable_styling(latex_options = "scale_down")%>%
+  kable_styling( full_width = T)#%>%
+  #kable_styling(latex_options = c("repeat_header"))
+
+print(table_result_combined)
+```
+
+As visible from Table&nbsp;\ref{tab:table_time}, the accuracy of the test results across the three estimators shows similarities in certain sample sizes. 
+However, practical scenarios in SAR image processing often involve small sample sizes, typically obtained over windows of size $7\times7$.  
+It is also noteworthy that the \(\widetilde{H}_{\text{AO}}\) estimator exhibited the shortest processing time, followed by \(\widetilde{H}_{\text{E}}\) and \(\widetilde{H}_{\text{C}}\).
+Considering this aspect, we select the \(\widetilde{H}_{\text{AO}}\) estimator for subsequent simulations.
+Henceforth,  the test statistical &nbsp;\eqref{Eq:test_e} will be denoted as: \(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\).
+
+We now verify the normality of the data generated by the \(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\) test.
+Figure&nbsp;\ref{fig:Plot_density} shows the empirical  densities for different sample sizes  and Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean, 
 standard deviation&nbsp;(SD), 
@@
 mu <- 1
-B <- 50
-
-sample.size <- c(25,49, 81, 121)
+B <- 5
+
+sample.size <- c(25,49, 81, 121, 200)
 L_values <- c(3,  5, 8, 11)
@@
 
-```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.pos="hbt",  fig.cap="Empirical density  under the null hypothesis.", fig.width=6, fig.height=5.0}
+```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="95%", fig.pos="hbt",  fig.cap="Empirical density  under the null hypothesis.", fig.width=6, fig.height=5.0}
 
@@
   p <- ggplot(combined_data, aes(x = Test_Statistics, col = factor(SampleSize), linetype = factor(SampleSize))) +
-    geom_line(stat = "density", linewidth = 1.0) +
+    geom_line(stat = "density", linewidth = 1.3) +
     scale_color_viridis(discrete = TRUE, option = "C", direction = -1, begin = 0.1, end = 0.8, name = "Sample Size") +
@@
   combined_summary_stats,
-  caption = "Descriptive analysis of $S(\\bm Z; L)$ with $L\\in\\left\\{3,5, 8,11\\right\\}$ and $\\mu=1$.",
+  caption = "Descriptive analysis of $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$ with $L\\in\\left\\{3,5, 8,11\\right\\}$ and $\\mu=1$.",
   format = "latex",
+  #longtable = T,
   booktabs = TRUE,
-  align = "lrrrrrrr",
+  align = "ccrrrrrr",
   escape = FALSE,
@@
   centering = FALSE,
-  table.envir = "table", position = "H") %>%
+  table.envir = "table", position="H", linesep = "") %>%
   #table.env = 'table*' # to span multiple columns
   collapse_rows(latex_hline = "major", valign = "middle") %>%
-  row_spec(0,  align = "c")
+  row_spec(0,  align = "c")%>%
+  kable_styling(latex_options = "scale_down")%>%
+  kable_styling( full_width = T)%>%
+  kable_styling(latex_options = c("repeat_header"))
 
@@
 
-```{r Plot_normality_qq, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.pos="hbt",  fig.cap="Normal QQ-plots for  $n=121$.", fig.width=6, fig.height=5}
+```{r Plot_normality_qq, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="90%", fig.pos="H",  fig.cap="Normal QQ-plots for  $n=121$.", fig.width=6, fig.height=5}
 
@@
 
-After checking the normality of the test statistics, we examined the possibilities of the proposed test in terms of size and power.
+After checking the normality of the data, we examined the possibilities of the proposed test in terms of size and power.
 Under \(\mathcal{H}_0\), the distribution of the test statistic is asymptotically normal.
-Therefore, the \(p\) value is calculated as
+Therefore, the \(p\) values are calculated as
 \(2\Phi(-|\varepsilon|)\), where \(\Phi\) is the standard
-Gaussian cumulative distribution function, and \(\varepsilon\) is the standardized test statistic given by :
+Gaussian cumulative distribution function, and \(\varepsilon\) is the standardized test statistic given by:
 \[
-\varepsilon=\frac{\widetilde{H}-H_{\Gamma_{\text{SAR}}}}{\widehat\sigma}.
+\varepsilon=\frac{\widetilde{H}_{\text{AO}}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{\bm{Z}}\right]}{\widehat\sigma}.
 \]
@@
 \SI{10}{\percent}. 
-In terms of size, \(1000\) simulations were used for different sample sizes from the $\Gamma_{\text{SAR}}$ distribution, with different values of $L$,  $\mu=1$ and \(\widetilde{H}_{\text{AO}}\) estimator.
+In terms of size, \(1000\) simulations were used for different sample sizes from the $\Gamma_{\text{SAR}}$ distribution, with varying values of $L$, and  $\mu=1$. 
 In all cases, the nominal level was achieved. 
-We assessed the test power using \(1000\) simulations for different sample sizes from the $G_I^0$ distribution, with  $\mu=1$, $\alpha=-2$, and \(\widetilde{H}_{\text{AO}}\) estimator.
+We assessed the test power using \(1000\) simulations for different sample sizes from the $G_I^0$ distribution, with  $\mu=1$, and $\alpha=-2$.
 The power generally improves with increasing sample size and number of looks.
@@
   select(L, Sample_Size, `0.01.x`, `0.05.x`, `0.1.x`, `0.01.y`, `0.05.y`, `0.1.y`)
-colnames(combined_results) <- c("$L$", "$n$", "$1\\%$", "$5\\%$", "$10\\%$", "$1\\%$", "$5\\%$", "$10\\%$")
+colnames(combined_results) <- c("$\\bm{L}$", "$\\bm{n}$", "$\\bm{1\\%}$", "$\\bm{5\\%}$", "$\\bm{10\\%}$", "$\\bm{1\\%}$", "$\\bm{5\\%}$", "$\\bm{10\\%}$")
 # LaTeX notation 
@@
   combined_results,
-  caption = "Size and Power of the entropy-based test.",
+  caption = "Size and Power of the $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z})$ test statistic.",
   format = "latex",
   booktabs = TRUE,
-  align = "lcccccccc",
+  align = "ccccccccc",
   escape = FALSE,
@@
   #linesep = "",
-  table.envir = "table", position = "H")%>%
+  table.envir = "table", position="htb", linesep = "")%>%
   add_header_above(c(" ", " ", "Size" = 3,  "Power" = 3)) %>%
   collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
-  row_spec(0,  align = "c")
+  row_spec(0,  align = "c")%>%
+  kable_styling(latex_options = "scale_down")%>%
+  kable_styling( full_width = T)
 print(table_combined_result)
@@
 
-In addition to the entropy-based test, we also propose a test statistic based on the classical CV. This test statistic is defined as follows:
+In addition to the \(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\) test, we also propose a test statistic based on the classical CV. This test statistic is defined as follows:
 \begin{align}
@@
 
-The AIC and BIC results in Tables&nbsp;\ref{tab:table_aic_gamma}--\ref{tab:table_aic_gio_MnADmedian} indicate that the CV and \(\text{CV}_{\text{MnAD}}\) data from different distributed Gamma and \(G_I^0\) synthetic sample sizes match the properties of an LN distribution.
+The AIC and BIC results in Tables&nbsp;\ref{tab:table_aic_gamma}--\ref{tab:table_aic_gio_MnADmedian} indicate that the CV and \(\text{CV}_{\text{MnAD}}\) data from different distributed $\Gamma_{\text{SAR}}$ and \(G_I^0\) synthetic sample sizes match the properties of an LN distribution.
 It is important to note that this conclusion was drawn empirically based on a dictionary of distributions that are analytically tractable and well-defined under biparametric, unimodal, asymmetric, and positive distributions.
@@
     } else {
-      formatted_numbers <- ifelse(x < 0, sprintf("$%.2f$", x), sprintf("$\\phantom{-}%.2f$", x))
+      formatted_numbers <- ifelse(x < 0, sprintf("$%.1f$", x), sprintf("$\\phantom{-}%.1f$", x))
     }
@@
   combined,
-  caption = "AIC and BIC values for evaluating the best distribution with CV data from Gamma SAR.",
+  caption = "AIC and BIC values for evaluating the best distribution with CV data from $\\Gamma_{\\text{SAR}}$.",
   format = "latex",
   booktabs = TRUE,
-  align = "lccccccc",
+  align = "ccccrrrrr",
   escape = FALSE,
@@
   collapse_rows(latex_hline = "major", valign = "middle") %>%
-  row_spec(0,  align = "c")
+  row_spec(0,  align = "c")%>%
+  kable_styling(latex_options = "scale_down")%>%
+  kable_styling( full_width = T)
 
@@
   booktabs = TRUE,
-  align = "lccccccc",
+  align = "cccccccc",
   escape = FALSE,
@@
   combined,
-  caption = "AIC and BIC values for evaluating the best distribution with $\\text{CV}_{\\text{MnAD}}$ data from Gamma SAR.",
+  caption = "AIC and BIC values for evaluating the best distribution with $\\text{CV}_{\\text{MnAD}}$ data from $\\Gamma_{\\text{SAR}}$.",
   format = "latex",
   booktabs = TRUE,
-  align = "lccccccc",
+  align = "cccccccc",
   escape = FALSE,
@@
 B <- 5
-alpha1 <- -2
+#alpha1 <- -2
 
@@
 
-```{r Plot_cv_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with CV data from Gamma SAR, with  $n=49$, $L=5$ and $\\mu=1$.", fig.width=8, fig.height=6}
+```{r Plot_cv_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with CV data from $\\Gamma_{\\text{SAR}}$, with  $n=49$, $L=5$ and $\\mu=1$.", fig.width=8, fig.height=6}
 
@@
 plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
-denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV")
+num_bins <- 86
+
+denscomp(list( fln, fg, fn, fw), n = num_bins, legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV ", xlegend = "topright", ylegend = NULL)
+legend("topright", legend = plot.legend, col = c("darkblue", "#637029","indianred3","darkgrey"), lwd = 3, lty = 1, box.lwd = 1,box.col = "white",bg = "white")
+# denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV")
 qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
@@
 B <- 5
-alpha1 <- -2
+alpha1 <- -3
 
@@
 
-```{r Plot_cv, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with $\\text{CV}_{\\text{MnAD}}$ data from $G_I^0$, with  $n=49$, $L=5$, $\\mu=1$ and $\\alpha=-2$.", fig.width=8, fig.height=6}
+```{r Plot_cv, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with $\\text{CV}$ data from $G_I^0$, with  $n=49$, $L=5$, $\\mu=1$ and $\\alpha=-3$.", fig.width=8, fig.height=6}
 
@@
 plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
-denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV")
+num_bins <- 86
+
+denscomp(list( fln, fg, fn, fw), n = num_bins, legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV ", xlegend = "topright", ylegend = NULL)
+legend("topright", legend = plot.legend, col = c("darkblue", "#637029","indianred3","darkgrey"), lwd = 3, lty = 1, box.lwd = 1,box.col = "white",bg = "white")
+# denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV ")
 qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
@@
 
-```{r Plot_MnADmedian_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with $\\text{CV}_{\\text{MnAD}}$ data from Gamma SAR, with  $n=49$, $L=5$ and $\\mu=1$.", fig.width=8, fig.height=6}
+```{r Plot_MnADmedian_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with $\\text{CV}_{\\text{MnAD}}$ data from $\\Gamma_{\\text{SAR}}$, with  $n=49$, $L=5$ and $\\mu=1$.", fig.width=8, fig.height=6}
 
@@
  plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
-denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV")
+ num_bins <- 60
+
+denscomp(list( fln, fg, fn, fw), n = num_bins, legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV MnAD", xlegend = "topright", ylegend = NULL)
+legend("topright", legend = plot.legend, col = c("darkblue", "#637029","indianred3","darkgrey"), lwd = 3, lty = 1, box.lwd = 1,box.col = "white",bg = "white")
+# denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV MnAD")
 qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
-cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV")
+cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV MnAD")
 ppcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
@@
 #B <- 5
-alpha1 <- -5
+alpha1 <- -3
 
@@
 
-```{r Plot_madmed_gi0_MnADmedian, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.pos="hbt",  fig.cap="Goodness of fit plots for evaluating the best distribution with $CV_{\\text{MnAD}}$ data from $G_I^0$, with  $n=49$, $L=5$, $\\mu=1$ and $\\alpha=-5$.", fig.width=8, fig.height=6}
+```{r Plot_madmed_gi0_MnADmedian, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.pos="hbt",  fig.cap="Goodness of fit plots for evaluating the best distribution with $CV_{\\text{MnAD}}$ data from $G_I^0$, with  $n=49$, $L=5$, $\\mu=1$ and $\\alpha=-3$.", fig.width=8, fig.height=6}
 
@@
 plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
-denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV")
+num_bins <- 86
+
+denscomp(list( fln, fg, fn, fw), n = num_bins, legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV MnAD", xlegend = "topright", ylegend = NULL)
+legend("topright", legend = plot.legend, col = c("darkblue", "#637029","indianred3","darkgrey"), lwd = 3, lty = 1, box.lwd = 1,box.col = "white",bg = "white")
+# denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV MnAD")
 qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
-cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV")
+cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV MnAD")
 ppcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
@@
 
-Figure&nbsp;\ref{fig:sim_Phantom} shows the phantom used for a simulated image with dimensions of $500\times 500$ pixels that consists of four smaller phantoms, each of which exhibits differences between homogeneous and heterogeneous regions.
-This phantom was proposed by&nbsp;\citet{Gomez2017}.
-The observations are independent draws from the $G^0_I$ distribution, with $L = 5$ and varying $\alpha$.
+Figure&nbsp;\ref{fig:sim_Phantom}(a) shows the phantom  with dimensions of $500\times500$ pixels. It was proposed by&nbsp;\citet{Gomez2017}.
+
+Figure&nbsp;\ref{fig:sim_Phantom}(b) shows the simulated image, where each small phantom displaying texture variations. 
+The observations are independent draws from the $G^0_I$ distribution&nbsp;\eqref{E:gi02}, with $L = 5$ and varying $\alpha$ and $\mu$, annotated in the image for each quadrant. 
+Light regions correspond to textured observations (heterogeneous), while darker regions represent textureless areas (homogeneous).
 
@@
 
-```{r sim_Phantom, echo=FALSE, message=FALSE, warning=FALSE, out.width="40%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Simulated image: Light regions in upper/lower left phantoms show homogeneity ($\\alpha=-10$), while dark ones suggest heterogeneity ($\\alpha=-2$).
-Conversely, in upper/lower right phantoms, dark regions mean homogeneity ($\\alpha=-9$), light ones mean heterogeneity ($\\alpha=-3$).
-', fig.width = 4, fig.height = 4}
-knitr::include_graphics("../Figures/PNG/Phantom.png")
-
-```
-
-The three test statistics (entropy-based, ${\text{CV}}$, and ${\text{CV}_{\text{MnAD}}}$) are applied to the simulated image using local sliding windows of size $7\times 7$, as shown in Figures&nbsp;\ref{fig:sim_results}(a)--(c).
-For the first test we considered the \(\widetilde{H}_{\text{AO}}\)  estimator due to its superior performance in simulations and shorter processing time compared to other entropy estimators.
-
-```{r sim_results, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics: (a)  Entropy-based test; (b)  CV test; (c)   $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c('', '', ''), out.width = c( "40mm","40mm", "40mm"),  fig.ncol=3, fig.width = 40, fig.height = 30}
-
-knitr::include_graphics("../Figures/PNG/test-entropy-Phantom_AO_7W_L5_100b.png")
-knitr::include_graphics("../Figures/PNG/cv_values_Phantom.png")
-knitr::include_graphics("../Figures/PNG/mnad_Phantom.png")
-```
-
-The resulting $p$-values for each test  are shown in Figures&nbsp;\ref{fig:sim_SAR_Images}(a)--(c) and Figures&nbsp;\ref{fig:sim_SAR_Images_p05}(a)--(c), respectively. 
-The new images reveal that a lighter  background indicates homogeneity, while darker backgrounds represent heterogeneous areas.
-
-```{r sim_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Map of $p$-values: (a) Entropy-based test; (b)  CV test; (c)  $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c('', '', ''), out.width = c( "40mm","40mm", "40mm"),  fig.ncol=3, fig.width = 40, fig.height = 30}
-
-knitr::include_graphics("../Figures/PNG/H_pvalue_Phantom_AO_7x7_L5_100b.png")
-knitr::include_graphics("../Figures/PNG/cv_p_values_Phantom.png")
-knitr::include_graphics("../Figures/PNG/mnad_p_values_Phantom.png")
-```
-```{r sim_SAR_Images_p05, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value: (a) Entropy-based test; (b) CV test; (c) $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
-knitr::include_graphics("../Figures/PNG/H_005_pvalues_Phantom_AO_7x7.png")
-knitr::include_graphics("../Figures/PNG/nominal_level_005_pvalues-Phantom.png")
-knitr::include_graphics("../Figures/PNG/mnad_005_pvalues-Phantom.png")
+```{r sim_Phantom, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Synthetic dataset: (\\textbf{a}) Phantom.
+(\\textbf{b}) Simulated image varying the $\\alpha$ and $\\mu$ values of each quadrant, with $L=5$.
+',  fig.subcap=c('', ''), out.width = c( "60mm","80mm"),  fig.ncol=2, fig.width = 20, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/Phantom1.png")
+knitr::include_graphics("../Figures/PNG/Phantom_label/Phantom_labels.pdf")
+
+```
+
+The three test statistics (\(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\), $T_\text{CV}$, and $T_{\text{CV}_{\text{MnAD}}}$) are applied to the simulated image using local sliding windows of size $7\times 7$, as shown in Figures&nbsp;\ref{fig:sim_results}(a)--(c).
+
+```{r sim_results, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$.
+(\\textbf{b})  $T_\\text{CV}$.
+(\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+
+knitr::include_graphics("../Figures/PNG/Entropy_Phantom_4_z1_200.png")
+knitr::include_graphics("../Figures/PNG/cv_Phantom_4_z1.png")
+knitr::include_graphics("../Figures/PNG/mnad_Phantom_z1.png")
+```
+
+The resulting $p$-values for each test  are shown in Figures&nbsp;\ref{fig:sim_SAR_Images}(a)--(c). 
+In Figures&nbsp;\ref{fig:sim_SAR_Images_p05}(a)--(c), maps are depicted using a linear gradient composed of two colors: black and white.
+All $p$-values above $0.05$ are represented in white (indicating no evidence to reject the null hypothesis), while those below 0.05 are shown in black (indicating evidence to reject the hypothesis).
+It is evident that
+the $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ performs significantly better than the other tests in identifying heterogeneous areas in the simulated image.
+```{r sim_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Map of $p$-values: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$; (\\textbf{b})  $T_\\text{CV}$.
+(\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+
+knitr::include_graphics("../Figures/PNG/H_pvalue_Phantom_4_z1_200b.png")
+knitr::include_graphics("../Figures/PNG/cv_pvalues_Phantom_4_z1.png")
+knitr::include_graphics("../Figures/PNG/mnad_p_values_Phantom_mnad_7_z1.png")
+```
+```{r sim_SAR_Images_p05, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$; (\\textbf{b})  $T_\\text{CV}$.
+(\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/H_005_Phantom_4_z1_AO_200b.png")
+knitr::include_graphics("../Figures/PNG/cv_005_pvalues_Phantom_4_z1.png")
+knitr::include_graphics("../Figures/PNG/mnad_005_Phantom_7_z1.png")
 
@@
 <!-- ACF Don't use "real" unless it refers to the real part of a complex value -->
-
-We evaluated the proposed test statistics using three SAR images: one of the coast of Jalisco, Mexico, and two of Illinois, USA, acquired by the Sentinel-1B satellite operating in C-band, with VV polarization, intensity format, \(L=18\) and \(L=36\)  nominal looks.
+<!-- JA, OK -->
+We evaluated the proposed test statistics using three SAR images: one of the coast of Jalisco, Mexico (with a spatial resolution of 20 m both along azimuth and range directions) and two of Illinois, USA (with a spatial resolution of 10 m both along azimuth and range directions),  acquired by the Sentinel-1B satellite operating in C-band, with VV polarization and intensity format.
 <!-- ACF Did you check this nominal value? It is interesting to estimate and use the equivalent number of looks -->
 <!-- ACF Provide the spatial resolution -->
+<!-- JA, OK -->
 The first two images have a size of \(512 \times 512\) pixels, while the third has \(1024 \times 1024\) pixels  and they contain mountainous areas, agricultural regions, water bodies and  urban areas, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)--(c).
 
-The three statistical tests are applied to the SAR images using $7\times 7$ local sliding windows, as illustrated in Figures&nbsp;\ref{fig:real_images_test_Mexico}, \ref{fig:test_lake} and&nbsp;\ref{fig:real_images_test_Illinois}.
-
- The $p$-values obtained for each test are presented in Figures&nbsp;\ref{fig:Mexico_pvalue}, \ref{fig:lake_pvalue} and&nbsp;\ref{fig:Illinois_crops_pvalue}, respectively.
-
-In Figures &nbsp;\ref{fig:Mexico_crops_0.05}, \ref{fig:lake_0.05} and&nbsp;\ref{fig:Illinois_crops_0.05}, the maps of $p$-values represent the decisions at a $5\%$ significance level. 
-Values below  $0.05$  are represented by dark areas, indicating evidence to reject the null hypothesis and suggesting heterogeneity in these regions. 
-In contrast, values above 0.05 are represented as white areas, indicating no evidence to reject the fully-developed speckle hypothesis.
-
-```{r real_SAR_Images_coe, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Real SAR images: (a) Coast of Jalisco; (b) Illinois-Region 1; (c) Illinois-Region 2.
-',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm", "40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+```{r real_SAR_Images_coe, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='SAR images: (\\textbf{a}) Coast of Jalisco,with $L=18$.
+(\\textbf{b}) Illinois-Region 1, with $L=36$.
+\\quad \\quad \\quad \\quad \\quad (\\textbf{c}) Illinois-Region 2, with $L=36$.
+',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 knitr::include_graphics("../Figures/PNG/Mexico_512.png")
@@
 ```
-
-```{r real_images_test_Mexico, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics, Coast of Jalisco: (a)  Entropy-based test using $\\widetilde{H}_{\\text{AO}}$ estimator; (b)  CV test; (c)   $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c('', '', ''), out.width = c( "40mm","40mm", "40mm"),  fig.ncol=3, fig.width = 40, fig.height = 30}
+The three statistical tests are applied to the SAR images using $7\times 7$ local sliding windows, as illustrated in Figures&nbsp;\ref{fig:real_images_test_Mexico}, \ref{fig:test_lake} and&nbsp;\ref{fig:real_images_test_Illinois}.
+
+The $p$-values obtained for each test are presented in Figures&nbsp;\ref{fig:Mexico_pvalue}, \ref{fig:lake_pvalue} and&nbsp;\ref{fig:Illinois_crops_pvalue}, respectively.
+
+In Figures &nbsp;\ref{fig:Mexico_crops_0.05}, \ref{fig:lake_0.05} and&nbsp;\ref{fig:Illinois_crops_0.05}, the maps of $p$-values composed of a linear gradient of black and white colors, represent the decisions at a $5\%$ significance level.
+Values below  $0.05$  are represented by dark areas, indicating evidence to reject the null hypothesis and suggesting heterogeneity in these regions. 
+In contrast, values above 0.05 are represented as white areas, indicating no evidence to reject the fully-developed speckle hypothesis.
+```{r real_images_test_Mexico, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Coast of Jalisco: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$.
+(\\textbf{b})  $T_\\text{CV}$.
+(\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 
@@
 
-```{r Mexico_pvalue, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Map of $p$-values, Coast of Jalisco: (a) Entropy-based test; (b)  CV test; (c)  $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+```{r Mexico_pvalue, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Map of $p$-values, Coast of Jalisco: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$.
+(\\textbf{b})  $T_\\text{CV}$.
+(\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 knitr::include_graphics("../Figures/PNG/H_pvalue_Mexico_512_18L_AO_200b.png")
@@
 
-```{r Mexico_crops_0.05, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value for the Coast of Jalisco.
-(a) Entropy-based test; (b) CV test; (c) $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+```{r Mexico_crops_0.05, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Coast of Jalisco.
+(\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$.
+(\\textbf{b}) $T_\\text{CV}$.\\quad \\quad \\quad (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 knitr::include_graphics("../Figures/PNG/H_005__Mexico_512_18L_AO_200b.png")
@@
 
-```{r test_lake, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics, Illinois-Region 1: (a)  Entropy-based test using $\\widetilde{H}_{\\text{AO}}$ estimator; (b)  CV test; (c)   $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c('', '', ''), out.width = c( "40mm","40mm", "40mm"),  fig.ncol=3, fig.width = 40, fig.height = 30}
+```{r test_lake, echo=FALSE, message=FALSE, warning=FALSE,fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Illinois-Region 1: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$.
+(\\textbf{b})  $T_\\text{CV}$.
+(\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 
@@
 
-```{r lake_pvalue, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Map of $p$-values, Illinois-Region 1: (a) Entropy-based test; (b)  CV test; (c)  $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+```{r lake_pvalue, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Map of $p$-values, Illinois-Region 1: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$; (\\textbf{b}) $T_\\text{CV}$.
+(\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 knitr::include_graphics("../Figures/PNG/H_pvalue_lake_512_36L_AO_100b.png")
@@
 
-```{r lake_0.05, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Illinois-Region 1.
-(a) Entropy-based test; (b) CV test; (c) $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+```{r lake_0.05, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Illinois-Region 1.
+(\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$.
+(\\textbf{b}) $T_\\text{CV}$.\\quad \\quad \\quad (\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.',fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 knitr::include_graphics("../Figures/PNG/H_005_lake_512_36L_AO_100b.png")
@@
 
-```{r real_images_test_Illinois, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics, Illinois-Region 2: (a)  Entropy-based test using $\\widetilde{H}_{\\text{AO}}$ estimator; (b)  CV test; (c)   $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c('', '', ''), out.width = c( "40mm","40mm", "40mm"),  fig.ncol=3, fig.width = 40, fig.height = 30}
+```{r real_images_test_Illinois, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Illinois-Region 2: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$.
+(\\textbf{b}) $T_\\text{CV}$.
+(\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 
@@
 
-```{r Illinois_crops_pvalue, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Map of $p$-values, Illinois-Region 2: (a) Entropy-based test; (b)  CV test; (c)  $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+```{r Illinois_crops_pvalue, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Map of $p$-values, Illinois-Region 2: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$.
+(\\textbf{b})  $T_\\text{CV}$.
+(\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 knitr::include_graphics("../Figures/PNG/H_pvalue_Illinois_1024_36L_AO_200b.png")
@@
 ```
-```{r Illinois_crops_0.05, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Illinois-Region 2.
-(a) Entropy-based test; (b) CV test; (c) $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+```{r Illinois_crops_0.05, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Illinois-Region 2.
+(\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$.
+(\\textbf{b}) $T_\\text{CV}$.\\quad \\quad \\quad  (\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),fig.ncol=3, fig.width = 20, fig.height = 10}
 knitr::include_graphics("../Figures/PNG/H_005_pvalues_Illinois_1024_36L_AO_200b.png")
@@
 In general, using Shannon entropy is more meaningful than using the original and robust CV  to capture heterogeneity.
-
-It is justified that the dark areas of the maps based on the $\text{CV}$ and $\text{CV}_{\text{MnAD}}$ tests cover the areas reported for the Shannon entropy-based map.
+It is justified that the dark areas of the maps based on the $T_\text{CV}$ and $T_{\text{CV}_{\text{MnAD}}}$ show coverage patterns similar to reported for the $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ map.
+This suggests that although CV-based tests may produce slightly less pronounced results compared to the entropy-based test, they still demonstrate a comparable ability to detect heterogeneity within SAR images.
 
 It is noticeable that the entropy and CV-based tools predicted heterogeneity regions as well as boundaries where the statistical properties of texture vary. 
+The $T_{\text{CV}_{\text{MnAD}}}$ test was shown to be an effective edge detector.
+It emerges as a robust alternative to the classical CV test, making it less susceptible to the influence of outliers and allowing it to produce more precise edges.
 Considering a higher significance level may increase the sensitivity to edge detection, but it may also increase the risk of detecting false heterogeneous regions.
 
-Moreover, assuming $5\%$ as the threshold for the $p$ values, the dark region produced by the $\text{CV}$ test was lower than produced by the $\text{CV}_{\text{MnAD}}$ and entropy test.
-
-The latter observation is to be expected as the latter tests are robust alternatives to the former test, which is essentially based on the expected value operator that reacts to outliers.
+Additionally, assuming a $5\%$ threshold for $p$-values, in most cases, the heterogeneous regions detected by the $S_{\widetilde{H}{\text{AO}}}(\bm{Z}; L)$ test were more extensive than those detected by the $T_\text{CV}$ and $T_{\text{CV}_{\text{MnAD}}}$ tests.
+This was mainly observable in Figures&nbsp;\ref{fig:sim_SAR_Images_p05}(a), &nbsp;\ref{fig:Mexico_crops_0.05}(a), and &nbsp;\ref{fig:lake_0.05}(a).
 

### 2024-04-30 Code/R/Programs/functions_sample_bias_mse.R

@@ -270,9 +270,9 @@ generate_plot_gi0_esp <- function(results_gi0, mu_values, selected_estimators, n
     plot_bias <- ggplot(df_filtered, aes(x = n, y = Bias, color = Estimator)) +
       geom_hline(yintercept = 0) +
       geom_point(size = 2.5) +
-      geom_line(linetype = "solid", linewidth = 1.5) +
+      geom_line(linetype = "solid", linewidth = 1.3) +
       labs(y = "Bias", x = expression(italic(n))) +
-      scale_x_continuous(breaks = c(9, 25, 49, 81, 121)) +  # Añadir esta línea para escala personalizada
+      scale_x_continuous(breaks = c(9, 25, 49, 81, 121)) +  # AC1adir esta lC-nea para escala personalizada
       scale_color_manual(values = pal_jama()(7)[1:6], labels = TeX(df_filtered$Estimator)) + # Eliminar labels y TeX
       annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu_val)), hjust = 4.0, vjust = -0.1, size = 3) +
       coord_cartesian(clip = 'off') +
@@ -282,9 +282,9 @@ generate_plot_gi0_esp <- function(results_gi0, mu_values, selected_estimators, n
     plot_mse <- ggplot(df_filtered, aes(x = n, y = MSE, color = Estimator)) +
       geom_hline(yintercept = 0) +
       geom_point(size = 2.5) +
-      geom_line(linetype = "solid", linewidth = 1.5) +
+      geom_line(linetype = "solid", linewidth = 1.3) +
       labs(y = "MSE", x = expression(italic(n))) +
-      scale_x_continuous(breaks = c(9, 25, 49, 81, 121)) +  # Añadir esta línea
+      scale_x_continuous(breaks = c(9, 25, 49, 81, 121)) +  # AC1adir esta lC-nea
       scale_color_manual(values = pal_jama()(7)[1:6], labels = TeX(df_filtered$Estimator)) + # Eliminar labels y TeX
       annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu_val)), hjust = 4.0, vjust = -0.1, size = 3) +
       coord_cartesian(clip = 'off') +
@@ -302,7 +302,7 @@ generate_plot_gi0_esp <- function(results_gi0, mu_values, selected_estimators, n
 
 
[…]

### 2024-05-01 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Almost ready to go

@@
 
-Figure&nbsp;\ref{fig:sim_Phantom}(a) shows the phantom  with dimensions of $500\times500$ pixels. It was proposed by&nbsp;\citet{Gomez2017}.
+Figure&nbsp;\ref{fig:sim_Phantom}(a) shows the phantom  with dimensions of $500\times500$ pixels.
+It was proposed by&nbsp;\citet{Gomez2017} as a tool to assess the performance of speckle-reduction filters.
 
@@
 Values close to zero greater than $-3$ suggest extremely textured targets, such as urban zones&nbsp;\cite{Frery2019a}. 
-As the value decreases, it indicates regions with moderate texture (in $\left[-6,-3\right]$), related to forest zones, while values below $-6$ correspond to textureless regions, such as pasture, agricultural fields, and water bodies&nbsp;\cite{Neto2023}.
+As the value decreases, it indicates regions with moderate texture (in the $\left[-6,-3\right]$ region), related to forest zones, while values below $-6$ correspond to textureless regions, such as pasture, agricultural fields, and water bodies&nbsp;\cite{Neto2023}.
 
 ```{r sim_Phantom, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Synthetic dataset: (\\textbf{a}) Phantom.
-(\\textbf{b}) Simulated image varying the $\\alpha$ and $\\mu$ values of each quadrant, with $L=5$.
+(\\textbf{b}) Simulated image, varying $\\alpha$ and $\\mu$, with $L=5$.
 ',  fig.subcap=c('', ''), out.width = c( "60mm","80mm"),  fig.ncol=2, fig.width = 20, fig.height = 10}
@@
 
-The three test statistics (\(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\), $T_\text{CV}$, and $T_{\text{CV}_{\text{MnAD}}}$) are applied to the simulated image using local sliding windows of size $7\times 7$, as shown in Figures&nbsp;\ref{fig:sim_results}(a)--(c).
-
-```{r sim_results, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$.
-(\\textbf{b})  $T_\\text{CV}$.
-(\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+We applied the three test statistics, namely \(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\), $T_\text{CV}$, and $T_{\text{CV}_{\text{MnAD}}}$, 
+to the simulated image using local sliding windows of size $7\times 7$, as shown in Figures&nbsp;\ref{fig:sim_results}(a)--(c).
+
+```{r sim_results, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 
@@
 The resulting $p$-values for each test  are shown in Figures&nbsp;\ref{fig:sim_SAR_Images}(a)--(c). 
-In Figures&nbsp;\ref{fig:sim_SAR_Images_p05}(a)--(c), maps are depicted using a linear gradient composed of two colors: black and white.
-All $p$-values above $0.05$ are represented in white (indicating no evidence to reject the null hypothesis), while those below 0.05 are shown in black (indicating evidence to reject the hypothesis).
-It is evident that
+In Figures&nbsp;\ref{fig:sim_SAR_Images_p05}(a)--(c), maps are depicted using a color table between black, gray levels, and white. 
+All $p$-values above $0.05$ are represented in white (indicating no evidence to reject the null hypothesis), while those below $0.05$ are shown in black (indicating evidence to reject the hypothesis).
+We notice that
 the $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ performs significantly better than the other tests in identifying heterogeneous areas in the simulated image.
-```{r sim_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Map of $p$-values: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$; (\\textbf{b})  $T_\\text{CV}$.
-(\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+
+```{r sim_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Map of $p$-values: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and (\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 
@@
 ```
+
 The three statistical tests are applied to the SAR images using $7\times 7$ local sliding windows, as illustrated in Figures&nbsp;\ref{fig:real_images_test_Mexico}, \ref{fig:test_lake} and&nbsp;\ref{fig:real_images_test_Illinois}.
@@
 
-In Figures &nbsp;\ref{fig:Mexico_crops_0.05}, \ref{fig:lake_0.05} and&nbsp;\ref{fig:Illinois_crops_0.05}, the maps of $p$-values composed of a linear gradient of black and white colors, represent the decisions at a $5\%$ significance level.
+In Figures &nbsp;\ref{fig:Mexico_crops_0.05}, \ref{fig:lake_0.05} and&nbsp;\ref{fig:Illinois_crops_0.05}, the maps of $p$-values composed of a linear gradient of black and white colors, represent the decisions at a \SI{5}{\percent} significance level.
 Values below  $0.05$  are represented by dark areas, indicating evidence to reject the null hypothesis and suggesting heterogeneity in these regions. 
 In contrast, values above 0.05 are represented as white areas, indicating no evidence to reject the fully-developed speckle hypothesis.
-```{r real_images_test_Mexico, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Coast of Jalisco: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$.
-(\\textbf{b})  $T_\\text{CV}$.
-(\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+```{r real_images_test_Mexico, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Coast of Jalisco: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 
@@
 ```{r Mexico_crops_0.05, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Coast of Jalisco.
-(\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$.
-(\\textbf{b}) $T_\\text{CV}$.\\quad \\quad \\quad (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+(\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b}) $T_\\text{CV}$, and (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 knitr::include_graphics("../Figures/PNG/H_005__Mexico_512_18L_AO_200b.png")
@@
 
-```{r test_lake, echo=FALSE, message=FALSE, warning=FALSE,fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Illinois-Region 1: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$.
-(\\textbf{b})  $T_\\text{CV}$.
-(\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+```{r test_lake, echo=FALSE, message=FALSE, warning=FALSE,fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Illinois-Region 1: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 
@@
 
-```{r lake_pvalue, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Map of $p$-values, Illinois-Region 1: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$; (\\textbf{b}) $T_\\text{CV}$.
-(\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+```{r lake_pvalue, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Map of $p$-values, Illinois-Region 1: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b}) $T_\\text{CV}$, and (\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+
 knitr::include_graphics("../Figures/PNG/H_pvalue_lake_512_36L_AO_100b.png")
@@
 ```{r lake_0.05, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Illinois-Region 1.
-(\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$.
-(\\textbf{b}) $T_\\text{CV}$.\\quad \\quad \\quad (\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.',fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+(\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b}) $T_\\text{CV}$, and (\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.', fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+
 knitr::include_graphics("../Figures/PNG/H_005_lake_512_36L_AO_100b.png")
@@
 
-```{r real_images_test_Illinois, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Illinois-Region 2: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$.
-(\\textbf{b}) $T_\\text{CV}$.
-(\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+```{r real_images_test_Illinois, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Illinois-Region 2: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b}) $T_\\text{CV}$, and (\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 
@@
 
-```{r Illinois_crops_pvalue, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Map of $p$-values, Illinois-Region 2: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$.
-(\\textbf{b})  $T_\\text{CV}$.
-(\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+```{r Illinois_crops_pvalue, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Map of $p$-values, Illinois-Region 2: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and (\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 knitr::include_graphics("../Figures/PNG/H_pvalue_Illinois_1024_36L_AO_200b.png")
@@
 ```{r Illinois_crops_0.05, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Illinois-Region 2.
-(\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$.
-(\\textbf{b}) $T_\\text{CV}$.\\quad \\quad \\quad  (\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),fig.ncol=3, fig.width = 20, fig.height = 10}
+(\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b}) $T_\\text{CV}$, and  (\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),fig.ncol=3, fig.width = 20, fig.height = 10}
 knitr::include_graphics("../Figures/PNG/H_005_pvalues_Illinois_1024_36L_AO_200b.png")
@@
 
-Additionally, assuming a $5\%$ threshold for $p$-values, in most cases, the heterogeneous regions detected by the $S_{\widetilde{H}{\text{AO}}}(\bm{Z}; L)$ test were more extensive than those detected by the $T_\text{CV}$ and $T_{\text{CV}_{\text{MnAD}}}$ tests.
+Additionally, assuming a \SI{5}{\percent} threshold for $p$-values, in most cases, the heterogeneous regions detected by the $S_{\widetilde{H}{\text{AO}}}(\bm{Z}; L)$ test were more extensive than those detected by the $T_\text{CV}$ and $T_{\text{CV}_{\text{MnAD}}}$ tests.
 This was mainly observable in Figures&nbsp;\ref{fig:sim_SAR_Images_p05}(a), &nbsp;\ref{fig:Mexico_crops_0.05}(a), and &nbsp;\ref{fig:lake_0.05}(a).

### 2024-05-01 Code/R/Programs/Goodness-of-fit tests.R

@@ -65,19 +65,37 @@ plot.legend <- c("Lognormal", "Gamma", "Normal", "Weibull")
 
 denscomp(list(fln, fg, fn, fw), legendtext = plot.legend, 
          fitcol = c("darkblue", "#637029", "indianred3", "#FDA75F"), 
-         fitlwd = c(3, 3, 3, 3), xlab = "CV")
+         fitlwd = c(3, 3, 3, 3), xlab = "CV", plotstyle="ggplot") +
+  ggplot2::theme_set(ggplot2::theme_minimal() +
+                       ggplot2::theme(text=element_text(family="serif"),
+                    legend.position = "top")
+  )
 
 
 qqcomp(list(fln, fg, fn, fw), legendtext = plot.legend, 
        fitcol = c("darkblue", "#637029", "indianred3", "#FDA75F"), 
-       fitlwd = c(3, 3, 3, 3), xlegend = "topleft", ylegend = NULL)
+       fitlwd = c(3, 3, 3, 3), xlegend = "topleft", ylegend = NULL, plotstyle="ggplot") +
+  ggplot2::theme_set(ggplot2::theme_minimal() +
+                       ggplot2::theme(text=element_text(family="serif"),
+                                      legend.position = "top")
+  )
 
 
 cdfcomp(list(fln, fg, fn, fw), legendtext = plot.legend, 
         fitcol = c("darkblue", "#637029", "indianred3", "#FDA75F"), 
-        fitlwd = c(3, 3, 3, 3), xlab = "CV")
+        fitlwd = c(3, 3, 3, 3), xlab = "CV", plotstyle="ggplot") +
+  ggplot2::theme_set(ggplot2::theme_minimal() +
+                       ggplot2::theme(text=element_text(family="serif"),
+                                      legend.position = "top")
+  )
+)
 
 
 ppcomp(list(fln, fg, fn, fw), legendtext = plot.legend, 
        fitcol = c("darkblue", "#637029", "indianred3", "#FDA75F"), 
-       fitlwd = c(3, 3, 3, 3), xlegend = "topleft", ylegend = NULL)
+       fitlwd = c(3, 3, 3, 3), xlegend = "topleft", ylegend = NULL, plotstyle="ggplot") +
+  ggplot2::theme_set(ggplot2::theme_minimal() +
+                       ggplot2::theme(text=element_text(family="serif"),
+                                      legend.position = "top")
+  )
+)

### 2024-05-01 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Improved Goodness-of-fit figures

@@
 The variable with the highest CV value is the one with the largest relative dispersion around the mean value&nbsp;\cite{Banik2011}.
-The coefficient of variation is the basic measure of heterogeneity in SAR data&nbsp;\cite{Touzi1988,oliverquegan98}.
+The coefficient of variation is the basic measure of heterogeneity in SAR data&nbsp;\cite{Ulaby1986,Touzi1988}.
 We study two ways of estimating the coefficient of variation.
@@
 
-```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="95%", fig.pos="hbt",  fig.cap="Bias and MSE, $L=5$ and  $\\alpha=-10$."}
+```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="95%", fig.pos="hbt",  fig.cap="Bias and MSE of the entropy estimators for the $\\Gamma_{\\text{SAR}}$, with $L=5$."}
 
@@
     reshaped_results,
-    caption = "Bias and MSE of non-parametric entropy estimators and bootstrap versions.",
+    caption = "Bias and MSE of the entropy estimators for the $\\Gamma_{\\text{SAR}}$, with $L=5$.",
     format = "latex",
@@
 
-The comparison between the bootstrap-improved estimators is shown in Table&nbsp;\ref{tab:table_time}, where the test accuracy under null hypothesis is presented alongside running times. 
+The comparison between the bootstrap-improved estimators is shown in Table&nbsp;\ref{tab:table_time}, where the test accuracy under the null hypothesis is presented alongside running times. 
 The test accuracy is evaluated through 1000 simulated samples of different sizes, with each size replicated 100 times using bootstrap resampling.
@@
 We now verify the normality of the data generated by the \(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\) test.
-Figure&nbsp;\ref{fig:Plot_density} shows the empirical  densities for different sample sizes  and Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean, 
+Figure&nbsp;\ref{fig:Plot_density} shows the empirical densities obtained by applying  the $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ test to different sample sizes drawn from the $\Gamma_{\text{SAR}}$ distribution, where $L$ takes values $\left\{3,5, 8,11\right\}$ and $\mu=1$.
+Additionally, Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean,
 standard deviation&nbsp;(SD), 
@@
 
-```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="95%", fig.pos="hbt",  fig.cap="Empirical density  under the null hypothesis.", fig.width=6, fig.height=5.0}
+```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="95%", fig.pos="hbt",  fig.cap="Empirical densities obtained from $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$ test under the null hypothesis.", fig.width=6, fig.height=5.0}
 
@@
   p <- ggplot(combined_data, aes(x = Test_Statistics, col = factor(SampleSize), linetype = factor(SampleSize))) +
-    geom_line(stat = "density", linewidth = 1.3) +
+    geom_line(stat = "density", linewidth = 1.2) +
     scale_color_viridis(discrete = TRUE, option = "C", direction = -1, begin = 0.1, end = 0.8, name = "Sample Size") +
@@
   combined_summary_stats,
-  caption = "Descriptive analysis of $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$ with $L\\in\\left\\{3,5, 8,11\\right\\}$ and $\\mu=1$.",
+  caption = "Descriptive analysis of $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, with $L\\in\\left\\{3,5, 8,11\\right\\}$ and $\\mu=1$.",
   format = "latex",
@@
 Figures&nbsp;\ref{fig:Plot_cv}--\ref{fig:Plot_madmed_gi0_MnADmedian} show empirical and fitted density plots, Q-Q plots, P-P plots as well as empirical and fitted cumulative distribution functions.
-They provide qualitative sources that confirm that the LN distribution is the most appropriate distribution
+They provide qualitative sources that confirm that the LN distribution is the most appropriate distribution.
 
@@
 
-# Simulación y cálculo de resultados
+#
 results_AIC <- data.frame(Test = character(),
@@
 
-#combined$`Inverse Gaussian` <- c("\\multirow{2}{*}{Inverse}", "Gaussian")
-
 # LaTeX notation 
@@
 sample.size <- c(49)
-R <- 15000
+R <- 12000
 mu <- 1
 L <- 5
-B <- 5
+#B <- 5
 #alpha1 <- -2
@@
 
-# Ajustar las distribuciones a los datos
 fln <- fitdist(TestStatistics, "lnorm")
@@
 
-# Graficar las comparaciones
 par(mfrow = c(2, 2), mar = c(4, 4, 2, 1))
 plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
-num_bins <- 86
-
-denscomp(list( fln, fg, fn, fw), n = num_bins, legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV ", xlegend = "topright", ylegend = NULL)
-legend("topright", legend = plot.legend, col = c("darkblue", "#637029","indianred3","darkgrey"), lwd = 3, lty = 1, box.lwd = 1,box.col = "white",bg = "white")
-# denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV")
-qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
-cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV")
-ppcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
+#num_bins <- 86
+
+num_bins <- 60 
+density_plots <- list(
+  denscomp(list(fln, fg, fn, fw), n = num_bins, legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
+           fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
+           fitlty = 1, xlab = expression(CV), plotstyle = "ggplot") +
+    theme_minimal() +
+    theme(text = element_text(family = "serif"), legend.position = "bottom"),
+
+  qqcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
+         fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
+         plotstyle = "ggplot") +
+    theme_minimal() +
+    theme(text = element_text(family = "serif"), legend.position = "bottom"),
+
+  cdfcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
+          fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
+          fitlty = 1, xlab = expression(CV), plotstyle = "ggplot") +
+    theme_minimal() +
+    theme(text = element_text(family = "serif"), legend.position = "bottom"),
+
+  ppcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
+         fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
+         plotstyle = "ggplot") +
+    theme_minimal() +
+    theme(text = element_text(family = "serif"), legend.position = "bottom")
+)
+
+combined_plot1 <- wrap_plots(density_plots, ncol = 2) +
+  plot_layout(guides = "collect")
+
+print(combined_plot1)
 
@@
 B <- 5
-alpha1 <- -3
+alpha1 <- -2
 
@@
 plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
-num_bins <- 86
-
-denscomp(list( fln, fg, fn, fw), n = num_bins, legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV ", xlegend = "topright", ylegend = NULL)
-legend("topright", legend = plot.legend, col = c("darkblue", "#637029","indianred3","darkgrey"), lwd = 3, lty = 1, box.lwd = 1,box.col = "white",bg = "white")
-# denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV ")
-qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
-cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV")
-ppcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
+num_bins <- 60 
+density_plots <- list(
+  denscomp(list(fln, fg, fn, fw), n = num_bins, legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
+           fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
+           fitlty = 1, xlab = expression(CV), plotstyle = "ggplot") +
+    theme_minimal() +
+    theme(text = element_text(family = "serif"), legend.position = "bottom"),
+
+  qqcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
+         fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
+         plotstyle = "ggplot") +
+    theme_minimal() +
+    theme(text = element_text(family = "serif"), legend.position = "bottom"),
+
+  cdfcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
+          fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
+          fitlty = 1, xlab = expression(CV), plotstyle = "ggplot") +
+    theme_minimal() +
+    theme(text = element_text(family = "serif"), legend.position = "bottom"),
+
+  ppcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
+         fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
+         plotstyle = "ggplot") +
+    theme_minimal() +
+    theme(text = element_text(family = "serif"), legend.position = "bottom")
+)
+
+combined_plot1 <- wrap_plots(density_plots, ncol = 2) +
+  plot_layout(guides = "collect")
+
+print(combined_plot1)
 
@@
 L <- 5
-B <- 5
+#B <- 5
 #alpha1 <- -2
@@
 
-# Graficar las comparaciones
 par(mfrow = c(2, 2), mar = c(4, 4, 2, 1))
  plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull")
- num_bins <- 60
-
-denscomp(list( fln, fg, fn, fw), n = num_bins, legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV MnAD", xlegend = "topright", ylegend = NULL)
-legend("topright", legend = plot.legend, col = c("darkblue", "#637029","indianred3","darkgrey"), lwd = 3, lty = 1, box.lwd = 1,box.col = "white",bg = "white")
-# denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV MnAD")
-qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
-cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV MnAD")
-ppcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
+
+num_bins <- 50 
+density_plots <- list(
+  denscomp(list(fln, fg, fn, fw), n = num_bins, legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
+           fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
+           fitlty = 1, xlab = expression(CV[ MnAD ]), plotstyle = "ggplot") +
+    theme_minimal() +
+    theme(text = element_text(family = "serif"), legend.position = "bottom"),
+
+  qqcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
+         fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
+         plotstyle = "ggplot") +
+    theme_minimal() +
+    theme(text = element_text(family = "serif"), legend.position = "bottom"),
+
+  cdfcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
+          fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
+          fitlty = 1, xlab = expression(CV[ MnAD ]), plotstyle = "ggplot") +
+    theme_minimal() +
+    theme(text = element_text(family = "serif"), legend.position = "bottom"),
+
+  ppcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
+         fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
+         plotstyle = "ggplot") +
+    theme_minimal() +
+    theme(text = element_text(family = "serif"), legend.position = "bottom")
+)
+
+combined_plot1 <- wrap_plots(density_plots, ncol = 2) +
+  plot_layout(guides = "collect")
+
+print(combined_plot1)
 
@@
 sample.size <- c(49)
-R <- 12000
+R <- 15000
 mu <- 1
@@
 #B <- 5
-alpha1 <- -3
+alpha1 <- -3.0
 
@@
 
+#   colors <- c("#999999", "#E69F00", "#56B4E9", "#009E80", "#009E72","#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#56B4E9", '#999999','#E69F00', "indianred3","#00AFBB", "#E7B800", "#FC4E07")
+
 # 
@@
 plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
-num_bins <- 86
-
-denscomp(list( fln, fg, fn, fw), n = num_bins, legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV MnAD", xlegend = "topright", ylegend = NULL)
-legend("topright", legend = plot.legend, col = c("darkblue", "#637029","indianred3","darkgrey"), lwd = 3, lty = 1, box.lwd = 1,box.col = "white",bg = "white")
-# denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV MnAD")
-qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
-cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV MnAD")
-ppcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
+num_bins <- 50 
+density_plots <- list(
+  denscomp(list(fln, fg, fn, fw), n = num_bins, legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
+           fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
+           fitlty = 1, xlab = expression(CV[ MnAD ]), plotstyle = "ggplot") +
+    theme_minimal() +
+    theme(text = element_text(family = "serif"), legend.position = "bottom"),
+
+  qqcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
+         fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
+         plotstyle = "ggplot") +
+    theme_minimal() +
+    theme(text = element_text(family = "serif"), legend.position = "bottom"),
+
+  cdfcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
+          fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
+          fitlty = 1, xlab = expression(CV[ MnAD ]), plotstyle = "ggplot") +
+    theme_minimal() +
+    theme(text = element_text(family = "serif"), legend.position = "bottom"),
+
+  ppcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
+         fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
+         plotstyle = "ggplot") +
+    theme_minimal() +
+    theme(text = element_text(family = "serif"), legend.position = "bottom")
+)
+
+combined_plot1 <- wrap_plots(density_plots, ncol = 2) +
+  plot_layout(guides = "collect")
+
+print(combined_plot1)
 
@@
 ```
-```{r sim_SAR_Images_p05, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$; (\\textbf{b})  $T_\\text{CV}$.
-(\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+```{r sim_SAR_Images_p05, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 knitr::include_graphics("../Figures/PNG/H_005_Phantom_4_z1_AO_200b.png")
@@
 ## SAR Data
-<!-- ACF Don't use "real" unless it refers to the real part of a complex value -->
-<!-- JA, OK -->
+
 We evaluated the proposed test statistics using three SAR images: one of the coast of Jalisco, Mexico (with a spatial resolution of 20 m both along azimuth and range directions) and two of Illinois, USA (with a spatial resolution of 10 m both along azimuth and range directions),  acquired by the Sentinel-1B satellite operating in C-band, with VV polarization and intensity format.
@@
 
-```{r real_SAR_Images_coe, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='SAR images: (\\textbf{a}) Coast of Jalisco,with $L=18$.
+```{r real_SAR_Images_coe, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='SAR images: (\\textbf{a}) Coast of Jalisco, with $L=18$.
 (\\textbf{b}) Illinois-Region 1, with $L=36$.
@@
 In contrast, values above 0.05 are represented as white areas, indicating no evidence to reject the fully-developed speckle hypothesis.
-```{r real_images_test_Mexico, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Coast of Jalisco: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+```{r real_images_test_Mexico, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Coast of Jalisco: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and \\quad \\quad \\quad \\quad \\quad (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 
@@
 
-```{r test_lake, echo=FALSE, message=FALSE, warning=FALSE,fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Illinois-Region 1: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+```{r test_lake, echo=FALSE, message=FALSE, warning=FALSE,fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Illinois-Region 1: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and \\quad \\quad \\quad \\quad \\quad (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 
@@
 
-```{r real_images_test_Illinois, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Illinois-Region 2: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b}) $T_\\text{CV}$, and (\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+```{r real_images_test_Illinois, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Illinois-Region 2: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b}) $T_\\text{CV}$, and \\quad \\quad \\quad \\quad \\quad (\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
 

### 2024-05-01 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
little changes

@@
 
-In Figures &nbsp;\ref{fig:Mexico_crops_0.05}, \ref{fig:lake_0.05} and&nbsp;\ref{fig:Illinois_crops_0.05}, the maps of $p$-values composed of a linear gradient of black and white colors, represent the decisions at a \SI{5}{\percent} significance level.
+In Figures&nbsp;\ref{fig:Mexico_crops_0.05}, \ref{fig:lake_0.05} and&nbsp;\ref{fig:Illinois_crops_0.05}, the maps of $p$-values composed of a linear gradient of black and white colors, represent the decisions at a \SI{5}{\percent} significance level.
 Values below  $0.05$  are represented by dark areas, indicating evidence to reject the null hypothesis and suggesting heterogeneity in these regions. 
@@
 Additionally, assuming a \SI{5}{\percent} threshold for $p$-values, in most cases, the heterogeneous regions detected by the $S_{\widetilde{H}{\text{AO}}}(\bm{Z}; L)$ test were more extensive than those detected by the $T_\text{CV}$ and $T_{\text{CV}_{\text{MnAD}}}$ tests.
-This was mainly observable in Figures&nbsp;\ref{fig:sim_SAR_Images_p05}(a), &nbsp;\ref{fig:Mexico_crops_0.05}(a), and &nbsp;\ref{fig:lake_0.05}(a).
+This was mainly observable in Figures&nbsp;\ref{fig:sim_SAR_Images_p05}(a), &nbsp;\ref{fig:Mexico_crops_0.05}(a), and&nbsp;\ref{fig:lake_0.05}(a).
 

### 2024-05-02 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Final touches

@@
     address: |
-      School of Mathematics and Statistics, Victoria University of Wellington, Wellington 6140, New Zealand
+      School of Mathematics and Statistics, Victoria University of Wellington, 6140 New Zealand
 #email: alejandro.frery@vuw.ac.nz
@@
 authorcitation: |
-  Frery, A.C.; Alpala, J.; Nascimento,A.D.C.
-# firstnote to eighthnote
-#firstnote: |
- # Current address: Updated affiliation
-#secondnote: |
-  #These authors contributed equally to this work.
+  Frery, A.C.; Alpala, J.; Nascimento, A.D.C.
 correspondence: |
@@
  Not applicable.
-#informedconsent: |
-  # Any research article describing a study involving humans should contain this 
-  # statement. Please add ``Informed consent was obtained from all subjects 
-  # involved in the study.'' OR ``Patient consent was waived due to REASON 
-  # (please provide a detailed justification).'' OR ``Not applicable'' for 
-  # studies not involving humans. You might also choose to exclude this statement 
-  # if the study did not involve humans.
-
-  # Written informed consent for publication must be obtained from participating 
-  # patients who can be identified (including by the patients themselves). Please 
-  # state ``Written informed consent has been obtained from the patient(s) to 
-  # publish this paper'' if applicable.
 dataavailability: |
@@
  \url{https://github.com/rjaneth/identifying-heterogeneity-in-sar-data-with-new-test-statistics} (accessed on 30 April 2024).
-# abbreviations:
-#   - short: MDPI
-#     long: Multidisciplinary Digital Publishing Institute
-#   - short: DOAJ
-#     long: Directory of open access journals
-#   - short: TLA
-#     long: Three letter acronym
-#   - short: LD 
-#     long: linear dichroism
 
@@
 bibliography: references.bib
-#appendix: appendix.tex
-#endnotes: false
+
 output:
@@
 library(nortest)# AD
-#library(MASS)#
-# model selection AIC and BIC
 
@@
             theme(text=element_text(family="serif"),
-                  legend.position = "bottom")#  top , right , bottom , or left#, panel.grid = element_blank()
+                  legend.position = "bottom")
 )
@@
 source("../Code/R/MainFunctions/ebrahimi_estimator.R")
-#source("../Code/R/MainFunctions/noughabi_arghami_estimator.R")
 source("../Code/R/MainFunctions/vasicek_estimator.R")
@@
 source("../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
-#source("../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.R")
 source("../Code/R/MainFunctions/bootstrap_vasicek_estimator.R")
@@
         legend.position = "bottom")
-
 ```
@@
 ```{r Simulated_data_gi0, echo=FALSE, message=FALSE}
-
 set.seed(1234567890, kind = "Mersenne-Twister")
@@
 
-#print(
- # kbl(
 knitr::kable(
@@
     row_spec(0,  align = "r")%>%
-    kable_styling(latex_options = "scale_down")#%>%
-   # kable_styling( full_width = T)
-  #)
-  #kable_styling(latex_options = c("scale_down"))
-
+    kable_styling(latex_options = "scale_down")
 ```
@@
 
-<!-- ACF This is an important contribution.
-Highlight the rationale: under H0, \widetilde{H} (estimated) and H_{\Gamma_{\text{SAR}}}(L) (fixed) should be close.
-Therefore, their difference should be small.
-Explain why you need \widebar{Z} -->
-<!-- JA Corrected -->
-
 The comparison between the bootstrap-improved estimators is shown in Table&nbsp;\ref{tab:table_time}, where the test accuracy under the null hypothesis is presented alongside running times. 
@@
   "$\\widetilde{H}_{\\text{AO}}$" = bootstrap_al_omari_1_estimator
-
 )
@@
 save(all_TestStatistics, execution_times, file = "./Data/results_data_time2.Rdata")
-
 ```
@@
 }
-
 ```
@@
 print(combined_plot)
-
 ```
@@
 ```{r Table_statistic, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-#cat("\\setlength{\\tabcolsep}{1.0pt}\n")
 
@@
 print(table_result_combined)
-
 ```
@@
 print(combined_plot1)
-
-# }
-
 ```
@@
   centering = FALSE,
-  #linesep = "",
   table.envir = "table", position="htb", linesep = "")%>%
@@
   kable_styling( full_width = T)
+
 print(table_combined_result)
@@
 It is important to note that this conclusion was drawn empirically based on a dictionary of distributions that are analytically tractable and well-defined under biparametric, unimodal, asymmetric, and positive distributions.
-
-<!-- \textcolor{red}{% -->
-<!-- ADCN: Caros, esse é o ponto mais delicado da excelente ideia desse paper em minha opinião.
-Não me oponho a colocarmos a lognormal como uma possibilidade, mas é preciso deixar claro que é uma possibilidade empírica.
-Uma alternativa empírica para uma solução do momento usando distribuições mais desenvolvidas na literatura e que sejam analiticamente tratáveis.
-Estou pensando corretamente?
-Se sim, por que não log-t-student, log-Laplace, power exponential, Log-hyperbolic,....
-(e a lista segue).
-Sugiro talvez indicar (i) a dedução da distribuição assintótica das estatísticas em função de CV e MNAD dando com entrada G0I ($\mathcal{H}_1$) e a Gamma ($\mathcal{H}_0$) como trabalho futuro.
-Do que eu entendi, a suposição da normal assintótica para entropia vem de uma coleção de trabalhos teóricos.
-Já a LN, do que percebi, não.
-Coloquei um comentário em verde.
-Vejam se estão de acordo.
--->
-<!-- } -->
 
@@
 save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC_gamma.Rdata")
-
 ```
@@
 colnames(combined) <- c("\\textbf{Criterion}", "$\\bm{n}$", "\\textbf{Normal}", "\\textbf{Lognormal}", "\\textbf{Gamma}", "\\textbf{Weibull}", "\\textbf{Inverse Gaussian}")
-
-#combined$`Inverse Gaussian` <- c("\\multirow{2}{*}{Inverse}", "Gaussian")
 
@@
 save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC.Rdata")
-
 ```
@@
 colnames(combined) <- c("\\textbf{Criterion}", "$\\bm{n}$", "\\textbf{Normal}", "\\textbf{Lognormal}", "\\textbf{Gamma}", "\\textbf{Weibull}", "\\textbf{Inverse Gaussian}")
-
-# Modificar el nombre de la última columna para que esté en dos líneas
-#combined$`Inverse Gaussian` <- c("\\multirow{2}{*}{Inverse}", "Gaussian")
 
@@
 ```{r Simulated_AIC_BIC_gamma_MnADmedian, echo=FALSE, message=FALSE, warning=FALSE}
-
 set.seed(1234567890, kind = "Mersenne-Twister")
+
 R <- 15000
@@
 sample.sizes <- c(25, 49, 81, 121)
-
-# madmedian <- function(x){
-#   mdn <- median(x)
-#   MAD <- 1.4826 * median(abs(x - mdn))
-#   MAD/mdn
-# }
 
@@
 save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC_gamma_MnADmedian.Rdata")
-
 ```
@@
 
-# madmedian <- function(x){
-#   mdn <- median(x)
-#   MAD <- 1.4826 * median(abs(x - mdn))
-#   return(MAD/mdn)
-# }
-
 MnADmedian <- function(x){
@@
 }
+
 results_AIC <- data.frame(Test = character(),
@@
 save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC_GI0_MnADmedian.Rdata")
-
 ```
@@
 print(combined_plot1)
-
 ```
@@
 L <- 5
-#B <- 5
 alpha1 <- -3.0
@@
 fw <- fitdist(TestStatistics_mad, "weibull")
-
-#   colors <- c("#999999", "#E69F00", "#56B4E9", "#009E80", "#009E72","#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#56B4E9", '#999999','#E69F00', "indianred3","#00AFBB", "#E7B800", "#FC4E07")
 
@@
 knitr::include_graphics("../Figures/PNG/Phantom_label/Phantom_labels.pdf")
-
 ```
@@
 We evaluated the proposed test statistics using three SAR images: one of the coast of Jalisco, Mexico (with a spatial resolution of 20 m both along azimuth and range directions) and two of Illinois, USA (with a spatial resolution of 10 m both along azimuth and range directions),  acquired by the Sentinel-1B satellite operating in C-band, with VV polarization and intensity format.
-<!-- ACF Did you check this nominal value? It is interesting to estimate and use the equivalent number of looks -->
-<!-- ACF Provide the spatial resolution -->
-<!-- JA, OK -->
 The first two images have a size of \(512 \times 512\) pixels, while the third has \(1024 \times 1024\) pixels  and they contain mountainous areas, agricultural regions, water bodies and  urban areas, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)--(c).
@@
 ',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+
 knitr::include_graphics("../Figures/PNG/Mexico_512.png")
@@
 knitr::include_graphics("../Figures/PNG/Illinois_1024_36L.png")
-
 ```
@@
 In contrast, values above 0.05 are represented as white areas, indicating no evidence to reject the fully-developed speckle hypothesis.
+
 ```{r real_images_test_Mexico, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Coast of Jalisco: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and \\quad \\quad \\quad \\quad \\quad (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
@@
 ```
+
 ```{r Illinois_crops_0.05, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Illinois-Region 2.
@@
 In this article, we have provided a practical and theoretical answer to the following physical question: How to detect heterogeneity in SAR images, assuming that the SAR intensity follows the $\Gamma_{\text{SAR}}$ model.
-<!-- Solving this problem is not easy, considering that the texturelessness in the parametric space of $\mathcal{G}^0_I$ means the infinity value, which is neither analytically tractable nor practically provable.
--->
-To this end, we proposed three novel hypothesis tests, one from the Shannon entropy and two others from the variation coefficient variants.
+To this end, we proposed three novel hypothesis tests, one from the Shannon entropy and two from the variation coefficient variants.
 The performance of our proposals was evaluated using a Monte Carlo study. 

### 2024-05-02 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Grammarly edited

@@
   This paper presents a statistical approach to identify the underlying roughness characteristics in synthetic aperture radar (SAR) intensity data. 
-  The physical modeling of this kind of data allows to use the Gamma distribution in the presence of fully-developed speckle, i.e., when there are infinitely many independent backscatterers per resolution cell, and none dominates the return.
+  The physical modeling of this kind of data allows the use of the Gamma distribution in the presence of fully-developed speckle, i.e., when there are infinitely many independent backscatterers per resolution cell, and none dominates the return.
   Such areas are often called "homogeneous" or  "textureless" regions. 
-  The $\mathcal{G}_I^0$ distribution is also a widely accepted law for heterogeneous and extremely heterogeneous regions, i.e., areas in which the fully-developed speckle hypotheses do not hold. 
+  The $\mathcal{G}_I^0$ distribution is also a widely accepted law for heterogeneous and extremely heterogeneous regions, i.e., areas where the fully-developed speckle hypotheses do not hold. 
   We propose three test statistics to distinguish between homogeneous and inhomogeneous regions, i.e., between gamma and \(\mathcal{G}_I^0\) distributed data, both with a known number of looks. 
-  The first test statistic uses a bootstrapped non-parametric estimator of Shannon entropy, which provides a robust assessment in the face of uncertain distributional assumptions.
+  The first test statistic uses a bootstrapped non-parametric estimator of Shannon entropy, providing a robust assessment in uncertain distributional assumptions.
   The second test uses the classical coefficient of variation (CV). 
@@
   We apply our test statistic to create maps of \(p\) values for the homogeneity hypothesis.
-  Finally, we show that our proposal, the entropy-based test, outperforms existing methods such as the classical CV and its alternative variant, in identifying heterogeneity when applied to both simulated and actual data.
-#These maps identify different types of targets.
-# We show that our proposal outperforms its competitors using simulated and SAR data.
+  Finally, we show that our proposal, the entropy-based test, outperforms existing methods, such as the classical CV and its alternative variant, in identifying heterogeneity when applied to both simulated and actual data.
 keywords: |
@@
 dataavailability: |
-  The Sentinel-1  images are made publicly available by European Space Agency via Copernicus Data Space Ecosystem at \url{https://dataspace.copernicus.eu/} (accessed on 24 April 2024).
+  The Sentinel-1  images are made publicly available by the European Space Agency via Copernicus Data Space Ecosystem at \url{https://dataspace.copernicus.eu/} (accessed on 24 April 2024).
 conflictsofinterest: |
@@
 
-Synthetic Aperture Radar (SAR) technology has become an important tool for environmental monitoring and disaster management.
-It provides valuable images under various conditions, including day or night and different weather situations&nbsp;\cite{Moreira2013,Mu2019}.
-However, the effective use of SAR data depends on a thorough understanding of their statistical properties because they are corrupted by speckle.
+Synthetic Aperture Radar (SAR) technology has become essential for environmental monitoring and disaster management.
+It provides valuable images under various conditions, including day or night and weather situations&nbsp;\cite{Moreira2013,Mu2019}.
+However, the effective use of SAR data depends on a thorough understanding of its statistical properties because it is corrupted by speckle.
 This noise-like interference effect is inherent in SAR data due to the coherent nature of the imaging process&nbsp;\cite{Argenti2013}.
 
-Speckle in intensity format is non-Gaussian, thus SAR data require reliable statistical models for accurate processing. 
+Speckle in intensity format is non-Gaussian. Thus, SAR data require reliable statistical models for accurate processing. 
 The $\mathcal{G}^0$ distribution, which is suitable for SAR data, includes the
@@
 Our work aims to improve the identification of potential roughness features in SAR intensity data.
-Physical modeling of SAR data allows the use of the Gamma distribution in the presence of fully-developed speckle, where an infinite number of independent backscatterers per resolution unit is assumed, commonly referred to as homogeneous regions
-
-In this context, we present a set of three novel test statistics that aim to distinguish between homogeneous and non-homogeneous return, in particular between gamma and \(\mathcal{G}^0\) distributed data, assuming the number of looks is known.
+Physical modeling of SAR data allows the use of the Gamma distribution in the presence of fully-developed speckle, where an infinite number of independent backscatterers per resolution unit is assumed, commonly referred to as homogeneous regions.
+
+In this context, we present a set of three novel test statistics that aim to distinguish between homogeneous and non-homogeneous returns, particularly between gamma and \(\mathcal{G}^0\) distributed data, assuming the number of looks is known.
 We use properties such as entropy and coefficient of variation.
@@
 Entropy is a fundamental concept in information theory with far-reaching applications in pattern recognition, statistical physics, image processing, edge detection and SAR image analysis&nbsp;\cite{Presse2013,MohammadDjafari2015,Avval2021, Nascimento2014,Nascimento2019}.
-Shannon introduced it in 1948&nbsp;\cite{Shannon1948} for a random variable as a measure of information and uncertainty.
-In statistics, Shannon entropy is a crucial descriptive parameter, especially for evaluating data dispersion and performing tests for normality, exponentiality and uniformity&nbsp;\cite{Wieczorkowski1999,Zamanzade2012}.
+Shannon introduced it in 1948&nbsp;\cite{Shannon1948} for a random variable to measure information and uncertainty.
+Shannon entropy is a crucial descriptive parameter in statistics, especially for evaluating data dispersion and performing tests for normality, exponentiality and uniformity&nbsp;\cite{Wieczorkowski1999,Zamanzade2012}.
 Entropy estimation is challenging, especially when the model is unknown. In these cases, non-parametric methods are used.
 Spacing methods have been discussed as a non-parametric approach in Refs.&nbsp;\cite{AlizadehNoughabi2010,Subhash2021}. 
-This strategy is flexible and robust because it does not enforce a model or any parametric constraints.
+This strategy is flexible and robust because it does not enforce a model or parametric constraints.
 
@@
 It facilitates the comparison of variability between different populations and is particularly valuable for relating variables with different units. 
-This is because when the main purpose is to compare the variations of several variables, the standard deviation can only serve as an adequate measure of variation if all variables are expressed in the same unit of measurement and have identical means.
+This is because when the primary purpose is to compare the variations of several variables, the standard deviation can only serve as an adequate measure of variation if all variables are expressed in the same unit of measurement and have identical means.
 If these conditions are not met, then the CV is the relative measure that is usually used in real applications. 
-The variable with the highest CV value is the one with the largest relative dispersion around the mean value&nbsp;\cite{Banik2011}.
-The coefficient of variation is the basic measure of heterogeneity in SAR data&nbsp;\cite{Ulaby1986,Touzi1988}.
+The variable with the highest CV value has the largest relative dispersion around the mean value&nbsp;\cite{Banik2011}.
+The coefficient of variation is the primary measure of heterogeneity in SAR data&nbsp;\cite{Ulaby1986,Touzi1988}.
 We study two ways of estimating the coefficient of variation.
@@
 The other parameter we study is the Shannon entropy.
-Different levels of roughness, materialized as models for SAR data, have different entropy values, but this fundamental quantity can be also estimated in a model-agnostic way.
+Different roughness levels materialized as models for SAR data, have different entropy values, but this fundamental quantity can also be estimated in a model-agnostic way.
 We exploit this property and design a bootstrap-improved non-parametric estimator for the Shannon entropy.
@@
 that reveal different types of targets in the SAR data. 
-We show that our proposed method is superior over existing approaches with simulated data and SAR images.
+We show that our proposed method is superior to existing approaches with simulated data and SAR images.
 
@@
 In Section&nbsp;\ref{sec:Results} we present experimental results. 
-Finally, we draw our conclusions in Section&nbsp;\ref{sec:conclusion}.
+Finally, we draw conclusions in Section&nbsp;\ref{sec:conclusion}.
 
@@
 
-The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$  distributions&nbsp;[@Frery1997]. 
-The first is suitable for fully-developed speckle and is a limiting case of the second model, which is interesting due to its versatility in accurately representing regions with different roughness properties&nbsp;[@Cassetti2022].
+The primary models for intensity SAR data include the Gamma and $\mathcal{G}_I^0$  distributions&nbsp;[@Frery1997]. 
+The first is suitable for fully-developed speckle and is a limiting case of the second model.
+This is interesting due to its versatility in accurately representing regions with different roughness properties&nbsp;[@Cassetti2022].
 We denote $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and $Z \sim \mathcal{G}_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the respective probability density
@@
 
-One of the first non-parametric estimators based on spacings was introduced by Vasicek&nbsp;\cite{vasicek1976test}. 
+Vasicek&nbsp;\cite{vasicek1976test} introduced one of the first non-parametric estimators based on spacings. 
 Under the assumption that \(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) is a random sample from the distribution \(F(z)\), the estimator is defined as:
@@
 where  $\widebar{Z}_{(i)}=(2 m+1)^{-1} \sum_{j=i-m}^{i+m} Z_{(j)}$, $m< \frac{n}{2}$, $Z_{(i)}=Z_{(1)}$ for $i<1$ and $Z_{(i)}=Z_{(n)}$ for $i>n$.
-Based on simulation, he showed that his estimator has a smaller mean square error in comparison with Vasicek's approach.
+Based on simulations, he showed that his estimator has a smaller mean square error than Vasicek's approach.
 
@@
 
-These estimators are asymptotically consistent, 
-but we will use improved bootstrap-improved versions because we need them to perform well with small samples.
+These estimators are asymptotically consistent. 
+However, we will use improved bootstrap-improved versions because we need them to perform well with small samples.
 
@@
 
-We aim at testing the following hypotheses: 
+We aim to test the following hypotheses: 
 $$
@@
 We are testing the hypothesis that the data are fully-developed speckle versus the alternative of data with roughness.
-As for the parametric problem, once it is not possible to define the hypothesis $\mathcal{H}_0=\alpha=-\infty$, it is impossible to solve this problem with parametric  inference alternatives (such as likelihood ratio, score, gradient and Wald hypothesis test).
+As for the parametric problem, once it is not possible to define the hypothesis $\mathcal{H}_0=\alpha=-\infty$, it is impossible to solve this problem with parametric inference alternatives (such as likelihood ratio, score, gradient, and Wald hypothesis test).
 The proposed tests to solve this physical problem in SAR systems are described below.
@@
 If the data represent fully-developed speckle, the density should center around zero, i.e., $S(\bm{Z};L)\approx 0$.
-Otherwise, under the alternative hypothesis, the empirical distribution would shift from zero, suggesting significant differences and implying the presence of heterogeneous clutter.
+Otherwise, the empirical distribution would shift from zero under the alternative hypothesis, suggesting significant differences and heterogeneous clutter.
 
@@
 
-The processing time is an important feature, especially considering the application of these estimators to large datasets of SAR images, as can be seen in Section&nbsp;\ref{sec:Results}.
+The processing time is an important feature, especially considering the application of these estimators to large datasets of SAR images, as seen in Section&nbsp;\ref{sec:Results}.
 
@@
 
-As visible from Table&nbsp;\ref{tab:table_time}, the accuracy of the test results across the three estimators shows similarities in certain sample sizes. 
+As visible from Table&nbsp;\ref{tab:table_time}, the accuracy of the test results across the three estimators shows similarities in specific sample sizes. 
 However, practical scenarios in SAR image processing often involve small sample sizes, typically obtained over windows of size $7\times7$.  
@@
 Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption.
-A low variance as well as a skewness and an excessive kurtosis of almost zero indicate limited dispersion, asymmetry and a light tail.
-Normal QQ plots confirm that there is no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.
+A low variance, skewness, and excessive kurtosis of almost zero indicate limited dispersion, asymmetry, and a light tail.
+Normal QQ plots confirm no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.
 
@@
 
-After checking the normality of the data, we examined the possibilities of the proposed test in terms of size and power.
+After checking the data's normality, we examined the proposed test's abilities in terms of size and power.
 Under \(\mathcal{H}_0\), the distribution of the test statistic is asymptotically normal.
@@
 The results are shown in Table&nbsp;\ref{tab:table_size_power}.
-<!-- ACF Please clarify which alternatives you used for the power -->
-<!-- JA Corrected -->
 
@@
 \end{align}
-where $S$ and $\widebar{Z}$ are the sample standard deviation and the sample mean, respectively.
+where $S$ and $\widebar{Z}$ are the sample standard deviation and mean, respectively.
 
@@
 
-We used the Akaike information criterion (AIC) and Bayesian information criterion (BIC) to select the best fitting distribution.
-
-The AIC deals with the trade-off between the goodness-of-fit and the simplicity of the model in terms of the number of model parameters&nbsp;\cite{Burnham2004}. 
+We used the Akaike information criterion (AIC) and the Bayesian information criterion (BIC) to select the best-fitting distribution.
+
+The AIC deals with the trade-off between the goodness-of-fit and the model's simplicity in terms of the number of model parameters&nbsp;\cite{Burnham2004}. 
 The model or distribution with the lowest value of AIC is chosen to be the best.
@@
 The AIC and BIC results in Tables&nbsp;\ref{tab:table_aic_gamma}--\ref{tab:table_aic_gio_MnADmedian} indicate that the CV and \(\text{CV}_{\text{MnAD}}\) data from different distributed $\Gamma_{\text{SAR}}$ and \(G_I^0\) synthetic sample sizes match the properties of an LN distribution.
-It is important to note that this conclusion was drawn empirically based on a dictionary of distributions that are analytically tractable and well-defined under biparametric, unimodal, asymmetric, and positive distributions.
-
-Figures&nbsp;\ref{fig:Plot_cv}--\ref{fig:Plot_madmed_gi0_MnADmedian} show empirical and fitted density plots, Q-Q plots, P-P plots as well as empirical and fitted cumulative distribution functions.
-They provide qualitative sources that confirm that the LN distribution is the most appropriate distribution.
+It is important to note that this conclusion was drawn empirically based on a dictionary of analytically tractable distributions and well-defined under biparametric, unimodal, asymmetric, and positive distributions.
+
+Figures&nbsp;\ref{fig:Plot_cv}--\ref{fig:Plot_madmed_gi0_MnADmedian} show empirical and fitted density plots, Q-Q plots, P-P plots, as well as empirical and fitted cumulative distribution functions.
+They provide qualitative sources confirming that the LN distribution is the most appropriate.
 
@@
 
-This section presents the simulations we performed to evaluate the performance of the proposed test statistics, followed by applications to SAR data.
+This section presents the simulations we performed to evaluate the proposed test statistics' performance, followed by applications to SAR data.
 
@@
 The $\alpha$ parameter of the $G_I^0$ distribution is essential for interpreting texture characteristics. 
-Values close to zero greater than $-3$ suggest extremely textured targets, such as urban zones&nbsp;\cite{Frery2019a}. 
+Values near zero greater than $-3$ suggest extremely textured targets, such as urban zones&nbsp;\cite{Frery2019a}. 
 As the value decreases, it indicates regions with moderate texture (in the $\left[-6,-3\right]$ region), related to forest zones, while values below $-6$ correspond to textureless regions, such as pasture, agricultural fields, and water bodies&nbsp;\cite{Neto2023}.
@@
 
-We evaluated the proposed test statistics using three SAR images: one of the coast of Jalisco, Mexico (with a spatial resolution of 20 m both along azimuth and range directions) and two of Illinois, USA (with a spatial resolution of 10 m both along azimuth and range directions),  acquired by the Sentinel-1B satellite operating in C-band, with VV polarization and intensity format.
-The first two images have a size of \(512 \times 512\) pixels, while the third has \(1024 \times 1024\) pixels  and they contain mountainous areas, agricultural regions, water bodies and  urban areas, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)--(c).
+We evaluated the proposed test statistics using three SAR images: one of the coast of Jalisco, Mexico (with a spatial resolution of 20 m both along azimuth and range directions) and two of Illinois, USA (with a spatial resolution of \SI{10}{\meter} both along azimuth and range directions),  acquired by the Sentinel-1B satellite operating in C-band, with VV polarization and intensity format.
+The first two images have a size of \(512 \times 512\) pixels, while the third has \(1024 \times 1024\) pixels, and they contain mountainous areas, agricultural regions, water bodies, and urban areas, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)--(c).
 
@@
 In Figures&nbsp;\ref{fig:Mexico_crops_0.05}, \ref{fig:lake_0.05} and&nbsp;\ref{fig:Illinois_crops_0.05}, the maps of $p$-values composed of a linear gradient of black and white colors, represent the decisions at a \SI{5}{\percent} significance level.
-Values below  $0.05$  are represented by dark areas, indicating evidence to reject the null hypothesis and suggesting heterogeneity in these regions. 
+Dark areas represent values below  $0.05$, indicating evidence to reject the null hypothesis and suggesting heterogeneity in these regions. 
 In contrast, values above 0.05 are represented as white areas, indicating no evidence to reject the fully-developed speckle hypothesis.
@@
 
-In general, using Shannon entropy is more meaningful than using the original and robust CV  to capture heterogeneity.
-It is justified that the dark areas of the maps based on the $T_\text{CV}$ and $T_{\text{CV}_{\text{MnAD}}}$ show coverage patterns similar to reported for the $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ map.
-This suggests that although CV-based tests may produce slightly less pronounced results compared to the entropy-based test, they still demonstrate a comparable ability to detect heterogeneity within SAR images.
-
-It is noticeable that the entropy and CV-based tools predicted heterogeneity regions as well as boundaries where the statistical properties of texture vary. 
+Using Shannon entropy is more meaningful than using the original and robust CV  to capture heterogeneity.
+It is justified that the dark areas of the maps based on the $T_\text{CV}$ and $T_{\text{CV}_{\text{MnAD}}}$ show coverage patterns similar to those reported for the $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ map.
+This suggests that although CV-based tests may produce slightly less pronounced results than the entropy-based test, they still demonstrate a comparable ability to detect heterogeneity within SAR images.
+
+It is noticeable that the entropy and CV-based tools predicted heterogeneity regions and boundaries where the statistical properties of texture vary. 
 The $T_{\text{CV}_{\text{MnAD}}}$ test was shown to be an effective edge detector.
 It emerges as a robust alternative to the classical CV test, making it less susceptible to the influence of outliers and allowing it to produce more precise edges.
-Considering a higher significance level may increase the sensitivity to edge detection, but it may also increase the risk of detecting false heterogeneous regions.
+Considering a higher significance level may increase the sensitivity to edge detection but also increase the risk of detecting false heterogeneous regions.
 
@@
 
-In this article, we have provided a practical and theoretical answer to the following physical question: How to detect heterogeneity in SAR images, assuming that the SAR intensity follows the $\Gamma_{\text{SAR}}$ model.
+This article provides a practical and theoretical answer to the following physical question: How to detect heterogeneity in SAR images, assuming that the SAR intensity follows the $\Gamma_{\text{SAR}}$ model.
 To this end, we proposed three novel hypothesis tests, one from the Shannon entropy and two from the variation coefficient variants.
@@
 The results showed that the Shannon entropy-based test was more robust than the CV-based tests. 
-In addition, all tests were able to recognize images with different textures and identified edges where the texture type changes.
+In addition, all tests could recognize images with different textures and identify edges where the texture type changes.

### 2024-05-02 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Completed changes, captions and plots

@@
 
-```{r Plot_GI0_to_gamma1, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="80%",  fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$, with $L=8$."}
+```{r Plot_GI0_to_gamma1, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="85%",  fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ when $\\alpha\\to-\\infty$, with $L=8$."}
 
@@
   annotate("text", x = max(mu)+0.2, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
-           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
+           label = TeX("$H_{\\Gamma_{\\tiny{SAR}}}$"), vjust = 0.9, hjust = 0.2, color = "blue")+
   theme_minimal() +
@@
 A low variance, skewness, and excessive kurtosis of almost zero indicate limited dispersion, asymmetry, and a light tail.
-Normal QQ plots confirm no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.
+Normal Q--Q plots confirm no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.
 
@@
 
-```{r Plot_normality_qq, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="90%", fig.pos="H",  fig.cap="Normal QQ-plots for  $n=121$.", fig.width=6, fig.height=5}
+```{r Plot_normality_qq, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="90%", fig.pos="H",  fig.cap="Normal Q--Q plots for  $n=121$.", fig.width=6, fig.height=5}
 
@@
 
-The LN distribution in two parameters has the following density function.
+The biparametric LN distribution has density:
 
@@
 
-Figures&nbsp;\ref{fig:Plot_cv}--\ref{fig:Plot_madmed_gi0_MnADmedian} show empirical and fitted density plots, Q-Q plots, P-P plots, as well as empirical and fitted cumulative distribution functions.
-They provide qualitative sources confirming that the LN distribution is the most appropriate.
+Figures&nbsp;\ref{fig:Plot_cv}--\ref{fig:Plot_madmed_gi0_MnADmedian} show empirical and fitted density plots, Q--Q plots, P--P plots, as well as empirical and fitted cumulative distribution functions.
+They provide qualitative sources that confirm that the LN distribution is the most appropriate distribution.
+As expected, both test statistics work well under the null hypothesis.
+Under the alternative hypothesis, the P--P plot shows that \(\text{CV}_{\text{MnAD}}\) is more robust than CV, although both statistics suffer from the tail effect caused by the distributed $G_I^0$ data.
 
@@
 
-# Guardar los resultados en un archivo .Rdata
 save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC.Rdata")
@@
 
-```{r Plot_cv_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with CV data from $\\Gamma_{\\text{SAR}}$, with  $n=49$, $L=5$ and $\\mu=1$.", fig.width=8, fig.height=6}
+```{r Plot_cv_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with CV data from $\\Gamma_{\\text{SAR}}$ (under the null hypothesis), with $n=49$, $L=5$, and $\\mu=1$.", fig.width=8, fig.height=6}
 
@@
 
-```{r Plot_cv, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with $\\text{CV}$ data from $G_I^0$, with  $n=49$, $L=5$, $\\mu=1$ and $\\alpha=-3$.", fig.width=8, fig.height=6}
+```{r Plot_cv, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with $\\text{CV}$ data from $G_I^0$ (under the alternative hypothesis), with  $n=49$, $L=5$, $\\mu=1$, and $\\alpha=-3$.", fig.width=8, fig.height=6}
 
@@
 
-```{r Plot_MnADmedian_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with $\\text{CV}_{\\text{MnAD}}$ data from $\\Gamma_{\\text{SAR}}$, with  $n=49$, $L=5$ and $\\mu=1$.", fig.width=8, fig.height=6}
+```{r Plot_MnADmedian_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with $\\text{CV}_{\\text{MnAD}}$ data from $\\Gamma_{\\text{SAR}}$ (under the null hypothesis), with  $n=49$, $L=5$, and $\\mu=1$.", fig.width=8, fig.height=6}
 
@@
 
-```{r Plot_madmed_gi0_MnADmedian, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.pos="hbt",  fig.cap="Goodness of fit plots for evaluating the best distribution with $CV_{\\text{MnAD}}$ data from $G_I^0$, with  $n=49$, $L=5$, $\\mu=1$ and $\\alpha=-3$.", fig.width=8, fig.height=6}
+```{r Plot_madmed_gi0_MnADmedian, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.pos="hbt",  fig.cap="Goodness of fit plots for evaluating the best distribution with $CV_{\\text{MnAD}}$ data from $G_I^0$ (under the alternative hypothesis), with  $n=49$, $L=5$, $\\mu=1$, and $\\alpha=-3$.", fig.width=8, fig.height=6}
 

### 2024-05-02 Code/R/Programs/functions_sample_bias_mse.R

@@ -269,8 +269,8 @@ generate_plot_gi0_esp <- function(results_gi0, mu_values, selected_estimators, n
     
     plot_bias <- ggplot(df_filtered, aes(x = n, y = Bias, color = Estimator)) +
       geom_hline(yintercept = 0) +
-      geom_point(size = 2.5) +
-      geom_line(linetype = "solid", linewidth = 1.2) +
+      geom_point(size = 2.4) +
+      geom_line(linetype = "solid", linewidth = 1.2, alpha=.7) +
       labs(y = "Bias", x = expression(italic(n))) +
       scale_x_continuous(breaks = c(9, 25, 49, 81, 121)) +  # AC1adir esta lC-nea para escala personalizada
       scale_color_manual(values = pal_jama()(7)[1:6], labels = TeX(df_filtered$Estimator)) + # Eliminar labels y TeX
@@ -281,8 +281,8 @@ generate_plot_gi0_esp <- function(results_gi0, mu_values, selected_estimators, n
     
     plot_mse <- ggplot(df_filtered, aes(x = n, y = MSE, color = Estimator)) +
       geom_hline(yintercept = 0) +
-      geom_point(size = 2.5) +
-      geom_line(linetype = "solid", linewidth = 1.2) +
+      geom_point(size = 2.4) +
+      geom_line(linetype = "solid", linewidth = 1.2, alpha=.7) +
       labs(y = "MSE", x = expression(italic(n))) +
       scale_x_continuous(breaks = c(9, 25, 49, 81, 121)) +  # AC1adir esta lC-nea
       scale_color_manual(values = pal_jama()(7)[1:6], labels = TeX(df_filtered$Estimator)) + # Eliminar labels y TeX

### 2024-05-03 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
file of time fixed in chunk 6

@@
 
-```{r Simulated_comparative_time2, echo=FALSE, message=FALSE}
+```{r Simulated_comparative_time3, echo=FALSE, message=FALSE}
 set.seed(1234567890, kind = "Mersenne-Twister")
-
 R <- 1000
 mu <- 1
-B <- 40#100
+B <- 40
 
 sample.size <- c(25,49, 81, 121)
-L_values <- c( 2, 8)
+L_values <- c(2, 8)
 
@@
 )
+if (!file.exists("./Data/results_data_time_3.Rdata")) {#Deactivate this line to regenerate the file
+  set.seed(1234567890, kind = "Mersenne-Twister")
 
   all_TestStatistics <- list()
-
   execution_times <- list()
@@
   for (estimator_name in names(bootstrap_estimators)) {
-
     TestStatistics <- list()
@@
 
-save(all_TestStatistics, execution_times, file = "./Data/results_data_time2.Rdata")
-```
-
-```{r Table_statistic_time2, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-load("./Data/results_data_time2.Rdata")
+  save(all_TestStatistics, execution_times, file = "./Data/results_data_time_3.Rdata")
+}
+
+```
+
+```{r Table_statistic_time3, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+load("./Data/results_data_time_3.Rdata")
 

### 2024-05-23 Text/R1-Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
New version R1

--- 2024-05-03 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
@@
   The third test uses an alternative form of estimating the CV based on the ratio of the mean absolute deviation from the median to the median. 
-  We apply our test statistic to create maps of \(p\) values for the homogeneity hypothesis.
+  We apply our test statistic to create maps of \(p\)-values for the homogeneity hypothesis.
   Finally, we show that our proposal, the entropy-based test, outperforms existing methods, such as the classical CV and its alternative variant, in identifying heterogeneity when applied to both simulated and actual data.
@@
 $$
-The authors proved that $\widehat{H}_{\text{E}}(\bm{Z})\xrightarrow{p}H[Z]$, when $m,n\rightarrow\infty$ and  $m/n\rightarrow0$.
 
@@
 
-These estimators are asymptotically consistent. 
+These estimators are asymptotically consistent, i.e., they converge in probability to the true value when $m,n\rightarrow\infty$ and  $m/n\rightarrow0$.
 However, we will use improved bootstrap-improved versions because we need them to perform well with small samples.

### 2024-05-23 Code/R/Programs/Goodness-of-fit tests.R

@@ -67,24 +67,28 @@ density_plots <- list(
   denscomp(list(fln, fg, fn, fw), n = num_bins, legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
            fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
            fitlty = 1, xlab = expression(CV), plotstyle = "ggplot") +
+    geom_line(alpha = 0.7) +
     theme_minimal() +
     theme(text = element_text(family = "serif"), legend.position = "bottom"),
   
   qqcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
          fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
          plotstyle = "ggplot") +
+    geom_line(alpha = 0.7) +
     theme_minimal() +
     theme(text = element_text(family = "serif"), legend.position = "bottom"),
   
   cdfcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
           fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
           fitlty = 1, xlab = expression(CV), plotstyle = "ggplot") +
+    geom_line(alpha = 0.7) +
     theme_minimal() +
     theme(text = element_text(family = "serif"), legend.position = "bottom"),
   
   ppcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
          fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
          plotstyle = "ggplot") +
+    geom_line(alpha = 0.7) +
     theme_minimal() +
     theme(text = element_text(family = "serif"), legend.position = "bottom")
 )

### 2024-05-24 Text/Reviews/ResponsesR0R1-Reviewer1.tex
Response letters

\documentclass[11pt]{report}

\usepackage[pdftex]{geometry}
\geometry{a4paper,left=2.8cm,right=2.8cm,top=1.5cm,bottom=1.5cm,twoside}

\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{graphicx}
	\graphicspath{./Comments/}
\usepackage[many]{tcolorbox}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{subfigure}
\usepackage{bm,bbm}
\usepackage{float}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\newtcolorbox{reviewbox}[1]{
colback = white!5!white,
colframe = purple!75!black,
fonttitle=\bfseries,
title=#1
}

\newtcolorbox{responsebox}[1]{
	colback = white!5!white,
	colframe = white!75!black,
	fonttitle=\bfseries,
	title=#1
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
\large{\textbf{Response Letter to Reviewer \# 1}}

\vglue 0.3cm

\huge{ Identifying Heterogeneity in SAR Data with New Test Statistics\\ (remotesensing-3021303 )}
\end{center}

%\authors
\begin{center}
\textbf{Alejandro C.\ Frery, Janeth Alpala, Abraao D.\ C.\ Nascimento }
\end{center}

\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{2cm}
\noindent Dear Editors
\bigskip

\noindent We are grateful to the reviewers for the valuable comments and the time spent on checking our manuscript. 
We have addressed their comments towards improving the paper contents and presentation. 
Below we detail the changes and updates incorporated into the manuscript in this round of review.

\medskip

%-------------------------------------
\begin{reviewbox}{Comment 1}
Page 2, line 81. When defining L, do you refer to the number of looks or to the equivalent number of looks?

\end{reviewbox}

\begin{responsebox}{Response}

\end{responsebox}

\begin{reviewbox}{Comment 2}
Page 15, line 266. Could you please better define the intensity format? Does it refer to GRD? In that case, which acquisition mode and which final equivalent number of looks? How does this information relates with the L values in Figure 13 caption? It would also be useful to complement the description with the images acquisition date.
\end{reviewbox}

\begin{reviewbox}{Comment 3}
Page 15, Figure 13. In order to ease the interpretation of the results for the 3 sites, it would be useful to show an optical image (the closest's Sentinel-2 available for example) of the corresponding SAR images.
\end{reviewbox}

\begin{reviewbox}{Comment 4}
Page 15, Figure 13 caption. In reference to the L values 18, 36 and 36. Could you please provide more information about how you get those values?
\end{reviewbox}

\begin{reviewbox}{Comment 5}
Page 16, line 269. Could you comment on why you selected a 7x7 window?
\end{reviewbox}

\begin{reviewbox}{Comment 6}
As a suggestion, in order to conduct a more quantitative analysis of the results for each estimator, would you consider comparing the mean and standard deviation values of the different tests among some reference areas in the images? Ideally, a land cover map would serve. Alternatively, you may use some polygons with a clear land cover label (water, vegetation, urban). This would also serve to evaluate the sensitivity of the estimators for classification purposes.
\end{reviewbox}

\begin{reviewbox}{Comment 7}
Some general comments:
\begin{itemize}
	\item in the case you chose an GRD image. Wouldn't it make more sense to apply the operators on an Single Look Complex image so in native SAR coordinates?
	\item could you comment what to expect if doing the same tests employing higher resolution images such as TerraSAR-X's?
	\item could you comment what would be the impact of your work in classification applications with SAR images?
\end{itemize}
\end{reviewbox}

\end{document}

### 2024-05-24 Text/Reviews/ResponsesR0R1-Reviewer2.tex
Response letters

--- 2024-05-24 Text/Reviews/ResponsesR0R1-Reviewer1.tex
@@
 \begin{reviewbox}{Comment 1}
-Page 2, line 81. When defining L, do you refer to the number of looks or to the equivalent number of looks?
+The paper estimates homogeneous areas, and conversely heterogeneous areas, in SAR imagery via speckle statistics by exploiting variations in scattering at the pixel level.
+Teasing out information from this statistical behavior remains an intricate, delicate process; one which you appear to have accomplished.
 
+I have only a few comments and suggestions for clarification that, hopefully, will enhance the readability \& ultimate applicability of the ideas presented.
+
+1.
+The 3rd to the last paragraph in the Introduction seems redundant.
+First entropy is discussed and then the 2 CV estimates, so why return again to entropy?
+(Perhaps some of this paragraph could be incorporated into the previous entropy discussion.)
 \end{reviewbox}
@@
 \begin{reviewbox}{Comment 2}
-Page 15, line 266.
-Could you please better define the intensity format?
-Does it refer to GRD?
-In that case, which acquisition mode and which final equivalent number of looks?
-How does this information relates with the L values in Figure 13 caption?
-It would also be useful to complement the description with the images acquisition date.
+2.
+In Eq.
+(8), the limit of alpha -> -inf is not transparent.
+The first 5 terms match eq.
+(7), and the ln(gamma) \& digamma terms seem to cancel, however, that leaves the ln(-1-alpha) \& L factors.
+A short discussion, or footnote, would help the reader.
 \end{reviewbox}
@@
 \begin{reviewbox}{Comment 3}
-Page 15, Figure 13.
-In order to ease the interpretation of the results for the 3 sites, it would be useful to show an optical image (the closest's Sentinel-2 available for example) of the corresponding SAR images.
+3.
+Fig.
+4 Q-Q plots: Are the dashed green lines fits or theoretical estimates of the distributions?
+What do the different scales imply?
+(Perhaps a larger variance in one of the distributions?) A short note in the caption or clarification in the text would help.
+(The later Q-Q plots all show an x=y line for reference.
+Why the change here?)
 \end{reviewbox}
@@
 \begin{reviewbox}{Comment 4}
-Page 15, Figure 13 caption. In reference to the L values 18, 36 and 36. Could you please provide more information about how you get those values?
+4.
+What does 'nominal levels of 1\%, 5\%, and 10\%' mean?
+And, how are these 'achieved' in all cases?
+This paragraph is the only place where 'nominal levels' are mentioned, please clarify their meaning \& significance.
 \end{reviewbox}
@@
 \begin{reviewbox}{Comment 5}
-Page 16, line 269. Could you comment on why you selected a 7x7 window?
-\end{reviewbox}
-
-\begin{reviewbox}{Comment 6}
-As a suggestion, in order to conduct a more quantitative analysis of the results for each estimator, would you consider comparing the mean and standard deviation values of the different tests among some reference areas in the images?
-Ideally, a land cover map would serve.
-Alternatively, you may use some polygons with a clear land cover label (water, vegetation, urban).
-This would also serve to evaluate the sensitivity of the estimators for classification purposes.
-\end{reviewbox}
-
-\begin{reviewbox}{Comment 7}
-Some general comments:
-\begin{itemize}
-	\item in the case you chose an GRD image. Wouldn't it make more sense to apply the operators on an Single Look Complex image so in native SAR coordinates?
-	\item could you comment what to expect if doing the same tests employing higher resolution images such as TerraSAR-X's?
-	\item could you comment what would be the impact of your work in classification applications with SAR images?
-\end{itemize}
+The mathematics is, by necessity, a bit dense, therefore I've concentrated my comments on the flow of the paper so that the casual reader may readily follow.
+To fully follow, comprehend \& replicate this work will require effort on the reader's part, nonetheless clarification of the above points will assist in understanding the gist of the paper.
 \end{reviewbox}

### 2024-05-24 Text/Reviews/ResponsesR0R1-Reviewer2.tex
Beginning review

@@
 \begin{responsebox}{Response}
-
+We agree.
+We have merged the third-to-last paragraph with the one that discusses the Shannon entropy.
+The new paragraph is
+\begin{quote}
+	\textcolor{blue}{Entropy is a fundamental concept in information theory with far-reaching applications in pattern recognition, statistical physics, image processing, edge detection and SAR image analysis~\cite{Presse2013,MohammadDjafari2015,Avval2021, Nascimento2014,Nascimento2019}.
+		Shannon introduced it in 1948~\cite{Shannon1948} for a random variable to measure information and uncertainty.
+		Shannon entropy is a crucial descriptive parameter in statistics, especially for evaluating data dispersion and performing tests for normality, exponentiality and uniformity~\cite{Wieczorkowski1999,Zamanzade2012}.
+		Entropy estimation is challenging, especially when the model is unknown;
+		in these cases, non-parametric methods, as those based on spacings~\cite{AlizadehNoughabi2010,Subhash2021}, can be used.
+		This strategy is flexible and robust because it does not enforce a model or parametric constraints.
+		Different roughness levels, which materialize as different models for SAR data, have different entropy values.
+		We designed a bootstrap-improved non-parametric estimator for the Shannon entropy.}
+\end{quote}
+Please note that the references are correctly numbered and formatted in the revised manuscript.
 \end{responsebox}
@@
 \end{reviewbox}
+
+\begin{responsebox}{Response}
+	content...
+\end{responsebox}
 
@@
 
+\bibliographystyle{plain}
+\bibliography{../references}
+
 \end{document}

### 2024-05-24 Text/R1-Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Beginning review

@@
 Shannon entropy is a crucial descriptive parameter in statistics, especially for evaluating data dispersion and performing tests for normality, exponentiality and uniformity&nbsp;\cite{Wieczorkowski1999,Zamanzade2012}.
-Entropy estimation is challenging, especially when the model is unknown. In these cases, non-parametric methods are used.
-Spacing methods have been discussed as a non-parametric approach in Refs.&nbsp;\cite{AlizadehNoughabi2010,Subhash2021}. 
+Entropy estimation is challenging, especially when the model is unknown;
+in these cases, non-parametric methods, as those based on spacings&nbsp;\cite{AlizadehNoughabi2010,Subhash2021}, can be used.
 This strategy is flexible and robust because it does not enforce a model or parametric constraints.
+Different roughness levels, which materialize as different models for SAR data, have different entropy values.
+We designed a bootstrap-improved non-parametric estimator for the Shannon entropy.
 
@@
 We study two ways of estimating the coefficient of variation.
-
-The other parameter we study is the Shannon entropy.
-Different roughness levels materialized as models for SAR data, have different entropy values, but this fundamental quantity can also be estimated in a model-agnostic way.
-We exploit this property and design a bootstrap-improved non-parametric estimator for the Shannon entropy.
 
@@
 \(\alpha < 0\) measures the roughness, 
-\(L \geq 1\) is the number of looks, 
+\(L \geq 1\) is the number of looks (either nominal or estimated, thus not restricted to integer values), 
 \(\Gamma(\cdot)\) is

### 2024-05-27 Text/Reviews/ResponsesR0R1-Reviewer1.tex
Beginning review
Updated paper with corrections

@@
 \begin{responsebox}{Response}
-
+We have clarified that
+\begin{quote}
+	\textcolor{blue}{\(L \geq 1\) is the number of looks (either nominal or estimated, thus not restricted to integer values),}
+\end{quote}
 \end{responsebox}
@@
 
+\begin{responsebox}{Response}
+
+We have clarified the intensity format to refer to Ground Range Detected (GRD) data. Also, we have added Table 9 that provides a detailed overview of the SAR images selected.
+
+We have clarified (line 264) that
+\begin{quote}
+	\textcolor{blue}{
+	We evaluated the proposed test statistics using four SAR images: one of Rotterdam, 
+Netherlands, acquired by the TerraSAR-X satellite with Single-look Slant-range Complex 
+(SSC) and high-resolution Spotlight-mode (HS); another of the Coast of Jalisco, Mexico; and
+two of Illinois, USA, acquired by the Sentinel-1B in Ground Range Detected (GRD) format, 
+with ExtraWide-swath mode (EW) and Strip Map mode (SM). Table 9 provides detailed
+parameters of the selected SAR images.
+}
+\end{quote}
+
+\end{responsebox}
+
 \begin{reviewbox}{Comment 3}
@@
 In order to ease the interpretation of the results for the 3 sites, it would be useful to show an optical image (the closest's Sentinel-2 available for example) of the corresponding SAR images.
+\begin{responsebox}{Response}
+ We have added the optical images obtained from Sentinel-2 for the corresponding SAR images.
+These optical images are now shown in Figure 14.
+This addition helps to facilitate the interpretation of the results and more clearly differentiate the homogeneous and heterogeneous regions.
+\end{responsebox}
 \end{reviewbox}
-
 \begin{reviewbox}{Comment 4}
@@
 \end{reviewbox}
+\begin{responsebox}{Response}
+
+In reference to the $L$ values 18, 36, and 36 in the caption of Figure 13, these values represent the number of looks used in our analysis.
+
+We have clarified (line 271) that
+\begin{quote}
+	\textcolor{blue}{
+The number of looks, $L$, was determined from the metadata in SNAP (Sentinel Application Platform), consisting of azimuth looks multiplied by range looks.
+This value also approximates the equivalent number of looks (ENL), calculated through the ratio of the squared sample mean to the sample variance in textureless areas.
+}
+\end{quote}
+
+\end{responsebox}
 
@@
 \end{reviewbox}
+\begin{responsebox}{Response}
+
+In SAR image processing, the selection of window size is crucial.
+Very large windows can average out local details, reducing sensitivity to fine-scale variations, while very small windows may not provide enough data for reliable statistical estimates.
+Our choice of a 7x7 window strikes a balance, capturing detailed local information while ensuring sufficient data points for robust analysis.
+Additionally, practical scenarios in SAR image processing often involve small sample sizes, typically obtained over windows of size 7x7.
+
+We have clarified (line 280) that
+
+\begin{quote}
+	\textcolor{blue}{The three statistical tests are applied to the SAR images using 7 x 7 local sliding 
+windows (This window size is commonly used in practical scenarios, which strikes a balance between capturing detailed local information and ensuring a sufficient number of data points to solid analysis)}
+\end{quote}
+
+\end{responsebox}
 
@@
 
+\begin{responsebox}{Response}
+\begin{itemize}
+ \item We chose to use GRD images for our analysis due to their preprocessing, which includes multilooking, making them suitable for statistical analysis over larger areas.
+While SLC images offer higher resolution, our focus on intensity-based heterogeneity detection is effectively addressed with GRD images.
+Future work could explore the application of our methods on SLC images to potentially leverage their higher resolution.
+We focused on Sentinel-1B GRD images. Our results indicated that the Shannon entropy-based test performed better than the CV-based tests in detecting heterogeneity but with a higher number of looks.
+
+\item In response to your comment, we extended our analysis to include a high-resolution TerraSAR-X image of Rotterdam, acquired in Spotlight mode with a single look and a resolution of 0.85x0.85 meters.
+Our findings showed that the entropy test was less effective in detecting heterogeneity in this high-resolution single-look image compared to the Sentinel-1B images. 
+The performance of the entropy test appears to be influenced significantly by the number of looks.
+In contrast, for the TerraSAR-X image with a single look, the classical CV test was more effective in identifying heterogeneous regions.
+
+\item Our work focuses on identifying heterogeneity in SAR images, which is a crucial aspect of image classification. 
+The entropy-based test and coefficient of variation metrics we propose can improve the differentiation between homogeneous and heterogeneous areas, thus improving the accuracy of classification algorithms.
+By providing robust measures of heterogeneity, our methods can be integrated into classification workflows to better distinguish between different land cover types and detect subtle changes within classes.
+This could be especially beneficial in applications such as environmental monitoring and urban planning.
+\end{itemize}
+
+\end{responsebox}
+
 \end{document}

### 2024-05-27 Text/Reviews/ResponsesR0R1-Reviewer2.tex
Updated paper with corrections

@@
 \begin{responsebox}{Response}
-	content...
+
+This proof has been included as Appendix A1.
+
+We have clarified (line 98) that
+\begin{quote}
+	\textcolor{blue}{
+		In order to clarify the limit behavior when \(\alpha \to -\infty\) in Equation (8), we show in Appendix A.1 that, for \(L=1\) and in the general case, the expression simplifies and the terms involving \(\alpha\) cancel out.
+Thus, the entropy of \(G_I^0\) converges to the entropy \(\Gamma_{\text{SAR}}\).
+}
+\end{quote}
+
 \end{responsebox}
@@
 
+\begin{responsebox}{Response}
+
+Regarding the Q-Q plots in Fig.
+4, the dashed green lines represent theoretical expected quantiles for a normal distribution, serving as a reference for comparison with the observed quantiles.
+The different scales on the axes imply variations in the range of values across different datasets.
+For datasets that exhibit larger variance or different distributions, the scales on the axes may change accordingly to accommodate the range of observed values.
+
+We include a note in the caption to clarify this aspect.
+
+\begin{quote}
+	\textcolor{blue}{
+		Caption Note: The dashed green lines in the Q-Q plots represent theoretical expected quantiles for a normal distribution.
+Variations in the scales of the axes reflect differences in the range of values across datasets.
+}
+\end{quote}
+
+\end{responsebox}
 \begin{reviewbox}{Comment 4}
@@
 \end{reviewbox}
+\begin{responsebox}{Response}
+The term "nominal levels of 1\%, 5\%, and 10\%" refers to the  pre-established significance levels ($\alpha$) at which the hypothesis test is conducted. 
+These levels indicate the probability of committing a Type I error, which is the error of rejecting the null hypothesis when it is actually true.
+
+In hypothesis testing, a test's size (or Type I error rate) is the probability of incorrectly rejecting the null hypothesis. 
+We conducted simulations to evaluate whether the test's actual Type I error rates matched the nominal levels.
+Specifically, we performed $1000$ simulations under the null hypothesis ($\mathcal{H}_0$), where the data follows a $\Gamma_{\text{SAR}}$ distribution.
+For each simulation, we calculated the p-values and determined the proportion of tests that incorrectly rejected the null hypothesis.
+
+The phrase "achieved in all cases" means that the proportion of Type I errors observed in the simulations closely matched the nominal levels ($1\%, 5\%, 10\%$), demonstrating that the test correctly maintains the specified significance levels.
+
+Additionally, we assessed the power of the test, which relates to the Type II error (the error of failing to reject a false null hypothesis). 
+Power is the probability of correctly rejecting the null hypothesis when the alternative hypothesis is true.
+We performed $1000$ simulations under the alternative hypothesis ($\mathcal{H}_A$), where the data follows a $G_I^0$ distribution.
+The power of the test was found to improve with increasing sample size and number of looks, as shown in Table 4.
+
+We have clarified (line 192) that
+\begin{quote}
+	\textcolor{blue}{
+		After checking the data's normality, we examined the proposed test's abilities in terms of size (Type I error rate) and power (probability of correctly rejecting the null hypothesis when the alternative hypothesis is true).
+Under \(\mathcal{H}_0\), the distribution of the test statistic is asymptotically normal.
+Therefore, the \(p\) values are calculated as
+\(2\Phi(-|\varepsilon|)\), where \(\Phi\) is the standard
+%$$\varepsilon=\frac{\widetilde{H}_{\text{AO}}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{\bm{Z}}\right]}{\widehat\sigma}.$$
+We conducted the test at nominal significance levels of $1\%$, $5\%$, and $10\%$. 
+These levels represent the probability of rejecting the null hypothesis when it is actually true (Type I error rates). 
+To verify that the test maintains these nominal levels, we performed $1000$ simulations under the null hypothesis ($\Gamma_{\text{SAR}}$ distribution), with different sample sizes and values of $L$, and $\mu=1$.
+In all cases, the observed Type I error rates were consistent with the nominal levels, indicating that the test maintains the specified significance levels.
+We also evaluated the test's power by performing $1000$ simulations under the alternative hypothesis ($G_I^0$ distribution) with $\mu=1$ and $\alpha=-2$.
+The power generally improves with increasing sample size and number of looks.
+The results are shown in Table 4.
+}
+\end{quote}
+
+\end{responsebox}
 

### 2024-05-27 Text/R1-Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Updated paper with corrections

@@
    - \usepackage{subcaption}
-   - \captionsetup[subfigure]{labelformat=parens, justification=centering}
+   # - \captionsetup[subfigure]{labelformat=parens, justification=centering}
+   - \captionsetup[sub]{position=bottom,
+        labelfont={bf, small, stretch=1.17},
+        labelsep=space,
+        textfont={small, stretch=1.5},
+        aboveskip=1pt, 
+        belowskip=1pt,
+        singlelinecheck=off,
+        justification=centering}   
    - \usepackage{placeins}
@@
 
+In order to clarify the limit behavior when \(\alpha \to -\infty\) in Equation \eqref{E:E-GIO}, we show in Appendix&nbsp;\ref{app:1} that, for \(L=1\) and in the general case, the expression simplifies and the terms involving \(\alpha\) cancel out.
+Thus, the entropy of \(G_I^0\) converges to the entropy \(\Gamma_{\text{SAR}}\).
+
 ## Estimation of the Shannon Entropy
@@
 
-```{r Plot_normality_qq, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="90%", fig.pos="H",  fig.cap="Normal Q--Q plots for  $n=121$.", fig.width=6, fig.height=5}
+```{r Plot_normality_qq, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="90%", fig.pos="H",  fig.cap="Normal Q--Q plots for  $n=121$.
+The dashed green lines in the Q--Q plots represent theoretical expected quantiles for a normal distribution.
+Variations in the scales of the axes reflect differences in the range of values across datasets.", fig.width=6, fig.height=5}
 
@@
 
-After checking the data's normality, we examined the proposed test's abilities in terms of size and power.
+After checking the data's normality, we examined the proposed test's abilities in terms of size (Type I error rate) and power (probability of correctly rejecting the null hypothesis when the alternative hypothesis is true).
+
 Under \(\mathcal{H}_0\), the distribution of the test statistic is asymptotically normal.
@@
 
-We have nominal levels of \SI{1}{\percent}, \SI{5}{\percent}, and
-\SI{10}{\percent}. 
-In terms of size, \(1000\) simulations were used for different sample sizes from the $\Gamma_{\text{SAR}}$ distribution, with varying values of $L$, and  $\mu=1$. 
-In all cases, the nominal level was achieved. 
-We assessed the test power using \(1000\) simulations for different sample sizes from the $G_I^0$ distribution, with  $\mu=1$, and $\alpha=-2$.
+We conducted the test at nominal significance levels of \SI{1}{\percent}, \SI{5}{\percent}, and \SI{10}{\percent}. 
+These levels represent the probability of rejecting the null hypothesis when it is actually true (Type I error rates). 
+To verify that the test maintains these nominal levels, we performed $1000$ simulations under the null hypothesis ($\Gamma_{\text{SAR}}$ distribution), with different sample sizes and values of $L$, and $\mu=1$.
+In all cases, the observed Type I error rates were consistent with the nominal levels, indicating that the test maintains the specified significance levels.
+
+We also evaluated the test's power by performing $1000$ simulations under the alternative hypothesis ($G_I^0$ distribution) with $\mu=1$ and $\alpha=-2$.
 The power generally improves with increasing sample size and number of looks.
@@
 
-We evaluated the proposed test statistics using three SAR images: one of the coast of Jalisco, Mexico (with a spatial resolution of 20 m both along azimuth and range directions) and two of Illinois, USA (with a spatial resolution of \SI{10}{\meter} both along azimuth and range directions),  acquired by the Sentinel-1B satellite operating in C-band, with VV polarization and intensity format.
-The first two images have a size of \(512 \times 512\) pixels, while the third has \(1024 \times 1024\) pixels, and they contain mountainous areas, agricultural regions, water bodies, and urban areas, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)--(c).
-
-```{r real_SAR_Images_coe, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='SAR images: (\\textbf{a}) Coast of Jalisco, with $L=18$.
-(\\textbf{b}) Illinois-Region 1, with $L=36$.
-\\quad \\quad \\quad \\quad \\quad (\\textbf{c}) Illinois-Region 2, with $L=36$.
-',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
-
+<!-- We evaluated the proposed test statistics using three SAR images: one of the coast of Jalisco, Mexico (with a spatial resolution of 20 m both along azimuth and range directions) and two of Illinois, USA (with a spatial resolution of \SI{10}{\meter} both along azimuth and range directions),  acquired by the Sentinel-1B satellite operating in C-band, with VV polarization and intensity format.
+-->
+<!-- The first two images have a size of \(512 \times 512\) pixels, while the third has \(1024 \times 1024\) pixels, and they contain mountainous areas, agricultural regions, water bodies, and urban areas, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)--(d).
+-->
+
+We evaluated the proposed test statistics using four SAR images: one of Rotterdam, Netherlands, acquired by the TerraSAR-X satellite with Single-look Slant-range Complex (SSC) and high-resolution Spotlight-mode (HS); another of the Coast of Jalisco, Mexico; and two of Illinois, USA, acquired by the Sentinel-1B in Ground Range Detected (GRD) format, with Extra Wide-swath mode (EW) and Strip Map mode (SM).
+Table&nbsp;\ref{tab:table_param} provides detailed parameters of the selected SAR images.
+They contain mountainous areas, agricultural regions, water bodies, and urban areas, as shown in Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)--(d).
+
+The number of looks, $L$, was determined from the metadata in SNAP (Sentinel Application Platform), consisting of azimuth looks multiplied by range looks.
+This value also approximates the equivalent number of looks (ENL), calculated through the ratio of the squared sample mean to the sample variance in textureless areas.
+\renewcommand{\arraystretch}{2}   
+```{r parameters_sar, echo=FALSE, message=FALSE, warning=FALSE}
+
+SAR_data <- data.frame(
+  Site = c("Rotterdam", "Coast of Jalisco", "Illinois-Region 1", "Illinois-Region 2"),
+  Mission = c("TerraSAR-X", "Sentinel-1B", "Sentinel-1B", "Sentinel-1B"),
+  Mode = c("HS", "GRD EW", "GRD SM", "GRD SM"),
+  Band = c("X", "C", "C", "C"),
+  Polarization = c("HH", "VV", "VV", "VV"),
+   Size = c("$512\\times512$", "$512\\times512$", "$512\\times512$", "$1024\\times1024$"),
+  L = c(1, 18, 36, 36),
+   Resol = c("$0.85/0.85$", "$40/40$", "$10/10$", "$10/10$"),
+  Date = c("06-12-2018", "29-08-2021", "30-06-2020", "28-08-2021")
+)
+
+colnames(SAR_data) <- c("\\textbf{Site}", "\\textbf{Mission}", "\\textbf{Mode}", "\\textbf{Band}", "\\textbf{Polarization}", "\\textbf{Size}",  "$\\bm{L}$", "\\textbf{Resolution Rg/Az [m]} ", "\\textbf{Adquisition Date}")
+
+SAR_data[] <- lapply(SAR_data, function(x) {
+  if (is.numeric(x)) {
+    if (all(x %% 1 == 0)) {
+      formatted_numbers <- sprintf("$%d$", x)
+    } else {
+      formatted_numbers <- ifelse(x < 0, sprintf("$%.1f$", x), sprintf("$\\phantom{-}%.1f$", x))
+    }
+    return(formatted_numbers)
+  } else {
+    return(x)
+  }
+})
+
+kable(SAR_data, caption = "Parameters of selected SAR images.",
+      format = "latex",
+      booktabs = TRUE,
+      align = "ccccccccc",
+      escape = FALSE,
+      digits = 2,
+      label = "table_param",
+      centering = FALSE,
+      table.envir = "table", position = "H") %>%
+  row_spec(0, align = "c") %>%
+  kable_styling(latex_options = "scale_down", font_size = 13) %>% 
+  kable_styling(full_width = TRUE) %>%
+  column_spec(1, width = "3.5cm") %>%
+  column_spec(2, width = "3cm") %>%
+  column_spec(3, width = "2cm") %>%
+  column_spec(4, width = "1cm") %>%
+  column_spec(5, width = "2cm") %>%
+  column_spec(6, width = "2.5cm") %>%
+  column_spec(7, width = "1cm") %>%
+  column_spec(8, width = "3cm") %>%
+  column_spec(9, width = "3cm")
+
+```
+
+Figures&nbsp;\ref{fig:optical_Images}(a)--(d) show the optical images obtained from Sentinel-2 L2A in true colors (composition of RGB channels) for the corresponding SAR images, with acquisition dates as follows: Rotterdam (20-12-2018), Coast of Jalisco (05-09-2021), Illinois-Region 1 (25-06-2020), and Illinois-Region 2 (01-08-2021).
+These optical images facilitate the interpretation of the results, making it easier to distinguish between homogeneous and heterogeneous regions.
+
+```{r real_SAR_Images_coe, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.align="center",fig.pos = 'H', fig.cap='SAR images: (\\textbf{a}) Rotterdam, (\\textbf{b}) Coast of Jalisco, (\\textbf{c}) Illinois-Region 1, (\\textbf{d}) Illinois-Region 2.',  fig.subcap=c(' ', ' ',' ','' ), out.width = c("45mm","45mm", "45mm", "45mm"),  fig.ncol=2, fig.width = 20, fig.height = 10,fig.hspace=1.5}
+knitr::include_graphics("../Figures/PNG/Rotterdam_1024.png")
 knitr::include_graphics("../Figures/PNG/Mexico_512.png")
@@
 knitr::include_graphics("../Figures/PNG/Illinois_1024_36L.png")
-```
-
-The three statistical tests are applied to the SAR images using $7\times 7$ local sliding windows, as illustrated in Figures&nbsp;\ref{fig:real_images_test_Mexico}, \ref{fig:test_lake} and&nbsp;\ref{fig:real_images_test_Illinois}.
-
-The $p$-values obtained for each test are presented in Figures&nbsp;\ref{fig:Mexico_pvalue}, \ref{fig:lake_pvalue} and&nbsp;\ref{fig:Illinois_crops_pvalue}, respectively.
-
-In Figures&nbsp;\ref{fig:Mexico_crops_0.05}, \ref{fig:lake_0.05} and&nbsp;\ref{fig:Illinois_crops_0.05}, the maps of $p$-values composed of a linear gradient of black and white colors, represent the decisions at a \SI{5}{\percent} significance level.
+
+```
+
+```{r optical_Images, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.align="center",fig.pos = 'H', fig.cap='Optical images: (\\textbf{a}) Rotterdam, (\\textbf{b}) Coast Jalisco, (\\textbf{c}) Illinois-Region 1, (\\textbf{d}) Illinois-Region 2.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm","45mm", "47mm", "42mm"),  fig.ncol=2, fig.width = 40, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/Rotterdam.png")
+knitr::include_graphics("../Figures/PNG/Jalisco_o2.png")
+knitr::include_graphics("../Figures/PNG/Sentinel2_Illinois_lake.png")
+knitr::include_graphics("../Figures/PNG/Sentinel_2021_R2.png")
+```
+
+The three statistical tests are applied to the SAR images using $7\times 7$ local sliding windows (this window size is commonly used in practical scenarios, which strikes a balance between capturing detailed local information and ensuring a sufficient number of data points for solid analysis), as illustrated in Figures&nbsp;\ref{fig:test_Rotterdam}, \ref{fig:real_images_test_Mexico}, \ref{fig:test_lake} and&nbsp;\ref{fig:real_images_test_Illinois}.
+
+The $p$-values obtained for each test are presented in Figures&nbsp;\ref{fig:Rotterdam_pvalue}, \ref{fig:Mexico_pvalue}, \ref{fig:lake_pvalue} and&nbsp;\ref{fig:Illinois_crops_pvalue}, respectively.
+
+In Figures&nbsp;\ref{fig:Rotterdam_0.05}, \ref{fig:Mexico_crops_0.05}, \ref{fig:lake_0.05} and&nbsp;\ref{fig:Illinois_crops_0.05}, the maps of $p$-values composed of a linear gradient of black and white colors, represent the decisions at a \SI{5}{\percent} significance level.
 Dark areas represent values below  $0.05$, indicating evidence to reject the null hypothesis and suggesting heterogeneity in these regions. 
 In contrast, values above 0.05 are represented as white areas, indicating no evidence to reject the fully-developed speckle hypothesis.
+
+```{r test_Rotterdam, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Rotterdam: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+
+knitr::include_graphics("../Figures/PNG/Entropy_AO_Rotterdam_1024.png")
+knitr::include_graphics("../Figures/PNG/cv_Rotterdam.png")
+knitr::include_graphics("../Figures/PNG/mnad_Rotterdam.png")
+```
+
+```{r Rotterdam_pvalue, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Map of $p$-values, Rotterdam: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$.
+(\\textbf{b})  $T_\\text{CV}$.
+(\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/H_pvalue_AO_Rotterdam_1024.png")
+knitr::include_graphics("../Figures/PNG/cv_pvalues_Rotterdam.png")
+knitr::include_graphics("../Figures/PNG/mnad_p_values_Rotterdam.png")
+
+```
+
+```{r Rotterdam_0.05, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Rotterdam.
+(\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b}) $T_\\text{CV}$, and \\quad \\quad \\quad \\quad \\quad (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/H_005_AO_Rotterdam_1024.png")
+knitr::include_graphics("../Figures/PNG/cv_005_pvalues_Rotterdam.png")
+knitr::include_graphics("../Figures/PNG/mnad_005_Rotterdam.png")
+
+```
 
@@
 
-Using Shannon entropy is more meaningful than using the original and robust CV  to capture heterogeneity.
+Using Shannon entropy is more meaningful than using the original and robust CV  to capture heterogeneity, particularly for Sentinel-1B images with a high number of looks.
 It is justified that the dark areas of the maps based on the $T_\text{CV}$ and $T_{\text{CV}_{\text{MnAD}}}$ show coverage patterns similar to those reported for the $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ map.
@@
 
+Conversely, when applying the same tests to a high-resolution TerraSAR-X image of Rotterdam, with a single look, the $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ test detected less heterogeneity compared to the CV-based tests.
+This indicates that the performance of the entropy test depends significantly on the number of looks, performing better with a higher number of looks as in the Sentinel-1B images.
+
 # Conclusion {#sec:conclusion}
@@
 The results showed that they were conservative in estimating the probability of a type I error (false alarm rate) and the test power (probability of detection), which increases with sample size.
-An application to three recent SAR images was performed. 
-The results showed that the Shannon entropy-based test was more robust than the CV-based tests. 
+An application to four recent SAR images was performed. 
+The results showed that the Shannon entropy-based test was more robust than the CV-based tests for Sentinel-1B images.
+For high-resolution images with a single look, such as the TerraSAR-X image, the classical CV test was more effective in detecting heterogeneous regions.
 In addition, all tests could recognize images with different textures and identify edges where the texture type changes.
+
+\appendixtitles{no} 
+\appendixstart
+\appendix
+\section[\appendixname~\thesection]{}
+
+## Limit Behavior of \(H_{G_I^0}\) as \(\alpha \to -\infty\) {#app:1}
+
+To verify that \(H_{G_I^0}(\mu, \alpha, L)\) converges to \(H_{\Gamma_{\text{SAR}}}(L, \mu)\) as \(\alpha \to -\infty\),  we show that the additional terms in \(H_{G_I^0}\) cancel in the limit.
+
+The Shannon entropy for the $G_I^0$ distribution is given by:
+\begin{multline*}
+H_{G_I^0}(\mu, \alpha, L) = H_{\Gamma_{\text{SAR}}}(L, \mu) - \ln \Gamma(L-\alpha) + (L-\alpha) \psi^{(0)}(L-\alpha) \\
+- (1-\alpha) \psi^{(0)}(-\alpha) + \ln (-1-\alpha) + \ln \Gamma(-\alpha) - L.
+\end{multline*}
+We aim to show:
+\[
+\lim_{\alpha \to -\infty} H_{G_I^0}(\mu, \alpha, L) = H_{\Gamma_{\text{SAR}}}(L, \mu).
+\]
+
+The additional terms in \(H_{G_I^0}\) compared to \(H_{\Gamma_{\text{SAR}}}\) are:
+\begin{align}
+\label{E:lim1} \lim_{\alpha\to-\infty} \left[-\ln\Gamma(L-\alpha) + (L-\alpha) \psi^{(0)}(L-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha) \right]-L. 
+ \end{align}
+
+For \(L=1\), this becomes:
+\begin{align}
+\label{E:lim}
+	 \lim_{\alpha\to-\infty} \bigg[\underbrace{-\ln\Gamma(1-\alpha) +\ln (-1-\alpha)+\ln\Gamma(-\alpha)}_{A} + \underbrace{(1-\alpha) \psi^{(0)}(1-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)}_{B}\bigg]-1.
+ \end{align}
+
+Simplifying \(A\) and \(B\):
+
+\begin{align*}
+	A=\ln\frac{(-1-\alpha)\cdot\Gamma(-\alpha)}{\Gamma(1-\alpha)}=\ln\frac{(-1-\alpha)\cdot\Gamma(-\alpha)}{-\alpha\Gamma(-\alpha)}=\ln\frac{-1-\alpha}{-\alpha}=\ln\left(1+\frac{1}{\alpha}\right).
+\end{align*}
+
+\begin{align*}
+	B=(1-\alpha)\left[\psi^{(0)}(1-\alpha)-\psi^{(0)}(-\alpha)\right]&=(1-\alpha)\Bigg[\psi^{(0)}\underbrace{(1-\alpha-1)+\frac{1}{1-\alpha-1}}_{\text{Because}\, \psi^{(0)}(x+1)=\psi^{(0)}(x)+\frac{1}{x}}-\psi^{(0)}(-\alpha)\Bigg]\\
+	&=(1-\alpha)\left[\psi^{(0)}(-\alpha)-\frac{1}{\alpha}-\psi^{(0)}(-\alpha)\right]\\
+	&=-\frac{1}{\alpha}+1.
+\end{align*}
+
+Substituting the simplified expressions of \(A\) and \(B\) into \eqref{E:lim} and taking the limit, we obtain:
+\begin{align*}
+	 \underbrace{\lim_{\alpha\to-\infty}\ln\bigg(1+\frac{1}{\alpha}\bigg)}_{\text{approaches}\,\, 0}-\underbrace{\lim_{\alpha\to-\infty}\frac{1}{\alpha}}_{ \text{approaches}\,\, 0}+\lim_{\alpha\to-\infty}1-1=0.
+ \end{align*}
+
+ For the general case for $L>1$, we use Stirling's approximation for large \(z\):
+ \[
+\Gamma(z) \sim \sqrt{2\pi z} \left(\frac{z}{e}\right)^z,
+\]
+and  \[
+\psi^{(0)}(z) \sim \ln(z) - \frac{1}{2z}. 
+\]
+
+Therefore, the terms of Equation \eqref{E:lim1} approximate to:
+\[
+-\ln\Gamma(L-\alpha) \sim -\frac{1}{2}\ln(2\pi(L-\alpha))-(L-\alpha)\ln(L-\alpha)+(L-\alpha).
+\]
+\[
+(L-\alpha) \psi^{(0)}(L-\alpha) \sim (L-\alpha) \left[\ln(L-\alpha) - \frac{1}{2(L-\alpha)}\right] \sim (L-\alpha) \ln(L-\alpha) - \frac{1}{2}.
+\]
+\[
+-(1-\alpha) \psi^{(0)}(-\alpha) \sim -(1-\alpha) \ln(-\alpha) - \frac{1-\alpha}{2\alpha}.
+\]
+\[\ln\Gamma(-\alpha)\sim \frac{1}{2}\ln(-2\pi\alpha)-\alpha\ln(-\alpha)+\alpha.\]
+
+Then, substituting  these terms in \eqref{E:lim1} and applying limit we obtain:
+
+\begin{multline*}
+  \lim_{\alpha\to-\infty}\bigg[-\frac{1}{2}\ln(2\pi(L-\alpha))-L\ln(L-\alpha)+\alpha\ln(L-\alpha)+L-\alpha+ L\ln(L-\alpha) -\alpha\ln(L-\alpha)\\- \frac{1}{2}
+-\ln(-\alpha)+\alpha\ln(-\alpha)- \frac{1-\alpha}{2\alpha}+ \ln (-1-\alpha)+ \frac{1}{2}\ln(-2\pi\alpha)-\alpha\ln(-\alpha)+\alpha\bigg]-L.
+\end{multline*}
+
+Simplifying each term:
+
+\begin{multline*}
+\lim_{\alpha\to-\infty}\bigg[-\frac{1}{2}\ln(2\pi(L-\alpha))+L- \frac{1}{2}-\ln(-\alpha)- \frac{1-\alpha}{2\alpha}
++ \ln (-(1+\alpha))+ \frac{1}{2}\ln(-2\pi\alpha)\bigg]-L.
+\end{multline*}
+
+\[
+\lim_{\alpha\to-\infty}\bigg[\frac{1}{2}\ln\frac{-\alpha}{L-\alpha}+L- \frac{1}{2}+\frac{\alpha-1}{2\alpha}
++ \ln\frac{1+\alpha}{\alpha} \bigg]-L=\frac{1}{2}\ln(1)+L-\frac{1}{2}+\frac{1}{2}+\ln(1)-L=0.
+\]
+
+Therefore:
+
+\[
+\lim_{\alpha \to -\infty} H_{G_I^0}(\mu, \alpha, L) = H_{\Gamma_{\text{SAR}}}(L, \mu).
+\]

### 2024-05-28 Text/Reviews/ResponsesR0R1-Reviewer1.tex
In progress

@@
 \usepackage{float}
+\usepackage{siunitx}
 
@@
 In order to ease the interpretation of the results for the 3 sites, it would be useful to show an optical image (the closest's Sentinel-2 available for example) of the corresponding SAR images.
+\end{reviewbox}
 \begin{responsebox}{Response}
@@
 \end{responsebox}
-\end{reviewbox}
+
 \begin{reviewbox}{Comment 4}
@@
 	\textcolor{blue}{
-The number of looks, $L$, was determined from the metadata in SNAP (Sentinel Application Platform), consisting of azimuth looks multiplied by range looks.
-This value also approximates the equivalent number of looks (ENL), calculated through the ratio of the squared sample mean to the sample variance in textureless areas.
+We used the number of looks, $L$, informed in the SNAP (Sentinel Application Platform) metadata: the product of azimuth and range looks. 
+This value is close to the equivalent number of looks calculated as the ratio of the squared sample mean to the sample variance in areas with fully-developed speckle.
 }
@@
 Very large windows can average out local details, reducing sensitivity to fine-scale variations, while very small windows may not provide enough data for reliable statistical estimates.
-Our choice of a 7x7 window strikes a balance, capturing detailed local information while ensuring sufficient data points for robust analysis.
-Additionally, practical scenarios in SAR image processing often involve small sample sizes, typically obtained over windows of size 7x7.
+Our choice of a $7\times 7$ window strikes a balance, capturing detailed local information while ensuring sufficient data points for robust analysis.
+Additionally, practical scenarios in SAR image processing often involve small sample sizes, typically obtained over windows of size $7\times 7$.
 
 We have clarified (line 280) that
-
 \begin{quote}
-	\textcolor{blue}{The three statistical tests are applied to the SAR images using 7 x 7 local sliding 
-windows (This window size is commonly used in practical scenarios, which strikes a balance between capturing detailed local information and ensuring a sufficient number of data points to solid analysis)}
+	\textcolor{blue}{The three statistical tests are applied to the SAR images using $7\times 7$ local sliding windows.
+		This window size balances detailed local information and sufficient number of data points, as illustrated in Figures [\dots]}
 \end{quote}
@@
 While SLC images offer higher resolution, our focus on intensity-based heterogeneity detection is effectively addressed with GRD images.
-Future work could explore the application of our methods on SLC images to potentially leverage their higher resolution.
+Future work could explore the application of our methods on SLC images and take advantage of their better spatial resolution.
 We focused on Sentinel-1B GRD images. Our results indicated that the Shannon entropy-based test performed better than the CV-based tests in detecting heterogeneity but with a higher number of looks.
 
-\item In response to your comment, we extended our analysis to include a high-resolution TerraSAR-X image of Rotterdam, acquired in Spotlight mode with a single look and a resolution of 0.85x0.85 meters.
+\item In response to your comment, we extended our analysis to include a high-resolution TerraSAR-X image of Rotterdam, acquired in Spotlight mode with a single look and a resolution of \qtyproduct{0.85x0.85}{\meter}.
 Our findings showed that the entropy test was less effective in detecting heterogeneity in this high-resolution single-look image compared to the Sentinel-1B images. 
@@
 This could be especially beneficial in applications such as environmental monitoring and urban planning.
+We have added the following paragraph to the conclusions:
+\begin{quote}
+	\textcolor{blue}{Despite presenting the results of using the estimators as local filters, we suggest using them in specific samples that visibly contain only one type of land use or land cover. 
+		This type of analysis can assist users in selecting appropriate training samples for classification purposes.}
+\end{quote}
 \end{itemize}

### 2024-05-28 Text/R1-Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics.Rmd
In progress

--- 2024-05-27 Text/R1-Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
@@
 
-In order to clarify the limit behavior when \(\alpha \to -\infty\) in Equation \eqref{E:E-GIO}, we show in Appendix&nbsp;\ref{app:1} that, for \(L=1\) and in the general case, the expression simplifies and the terms involving \(\alpha\) cancel out.
-Thus, the entropy of \(G_I^0\) converges to the entropy \(\Gamma_{\text{SAR}}\).
+Appendix&nbsp;\ref{app:1} provides the proof of the convergence of $H_{G_I^0}(\mu, \alpha, L)$ to $H_{\Gamma_{\text{SAR}}}(L, \mu)$ when
+$\alpha\to -\infty$.
 
@@
 
-The number of looks, $L$, was determined from the metadata in SNAP (Sentinel Application Platform), consisting of azimuth looks multiplied by range looks.
-This value also approximates the equivalent number of looks (ENL), calculated through the ratio of the squared sample mean to the sample variance in textureless areas.
+We used the number of looks, $L$, informed in the SNAP (Sentinel Application Platform) metadata: the product of azimuth and range looks. 
+This value is close to the equivalent number of looks calculated as the ratio of the squared sample mean to the sample variance in areas with fully-developed speckle.
 \renewcommand{\arraystretch}{2}   
@@
 
-colnames(SAR_data) <- c("\\textbf{Site}", "\\textbf{Mission}", "\\textbf{Mode}", "\\textbf{Band}", "\\textbf{Polarization}", "\\textbf{Size}",  "$\\bm{L}$", "\\textbf{Resolution Rg/Az [m]} ", "\\textbf{Adquisition Date}")
+colnames(SAR_data) <- c("\\textbf{Site}", "\\textbf{Mission}", "\\textbf{Mode}", "\\textbf{Band}", "\\textbf{Polarization}", "\\textbf{Size}",  "$\\bm{L}$", "\\textbf{Resolution Rg/Az [m]} ", "\\textbf{Acquisition Date}")
 
@@
 
-The three statistical tests are applied to the SAR images using $7\times 7$ local sliding windows (this window size is commonly used in practical scenarios, which strikes a balance between capturing detailed local information and ensuring a sufficient number of data points for solid analysis), as illustrated in Figures&nbsp;\ref{fig:test_Rotterdam}, \ref{fig:real_images_test_Mexico}, \ref{fig:test_lake} and&nbsp;\ref{fig:real_images_test_Illinois}.
+The three statistical tests are applied to the SAR images using $7\times 7$ local sliding windows.
+This window size balances detailed local information and sufficient number of data points, as illustrated in Figures&nbsp;\ref{fig:test_Rotterdam}, \ref{fig:real_images_test_Mexico}, \ref{fig:test_lake} and&nbsp;\ref{fig:real_images_test_Illinois}.
 
@@
 
+Despite presenting the results of using the estimators as local filters, we suggest using them in specific samples that visibly contain only one type of land use or land cover. 
+This type of analysis can assist users in selecting appropriate training samples for classification purposes.
+
 \appendixtitles{no} 
@@
 \end{multline*}
-We aim to show:
+We aim to show that
 \[
@@
 The additional terms in \(H_{G_I^0}\) compared to \(H_{\Gamma_{\text{SAR}}}\) are:
-\begin{align}
-\label{E:lim1} \lim_{\alpha\to-\infty} \left[-\ln\Gamma(L-\alpha) + (L-\alpha) \psi^{(0)}(L-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha) \right]-L. 
- \end{align}
+\begin{multline}
+\label{E:lim1} \lim_{\alpha\to-\infty} \left[-\ln\Gamma(L-\alpha) + (L-\alpha) \psi^{(0)}(L-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha) \right]\\ -L. 
+ \end{multline}
 
@@
 Simplifying \(A\) and \(B\):
-
 \begin{align*}
-	A=\ln\frac{(-1-\alpha)\cdot\Gamma(-\alpha)}{\Gamma(1-\alpha)}=\ln\frac{(-1-\alpha)\cdot\Gamma(-\alpha)}{-\alpha\Gamma(-\alpha)}=\ln\frac{-1-\alpha}{-\alpha}=\ln\left(1+\frac{1}{\alpha}\right).
+	A=\ln\frac{(-1-\alpha)\Gamma(-\alpha)}{\Gamma(1-\alpha)}=\ln\frac{(-1-\alpha)\Gamma(-\alpha)}{-\alpha\Gamma(-\alpha)}=\ln\frac{-1-\alpha}{-\alpha}=\ln\Big(1+\frac{1}{\alpha}\Big).\\
 \end{align*}
@@
 
-Substituting the simplified expressions of \(A\) and \(B\) into \eqref{E:lim} and taking the limit, we obtain:
+Replacing \(A\) and \(B\) into&nbsp;\eqref{E:lim} and taking the limit, we obtain:
 \begin{align*}
@@
 Therefore, the terms of Equation \eqref{E:lim1} approximate to:
-\[
--\ln\Gamma(L-\alpha) \sim -\frac{1}{2}\ln(2\pi(L-\alpha))-(L-\alpha)\ln(L-\alpha)+(L-\alpha).
-\]
-\[
-(L-\alpha) \psi^{(0)}(L-\alpha) \sim (L-\alpha) \left[\ln(L-\alpha) - \frac{1}{2(L-\alpha)}\right] \sim (L-\alpha) \ln(L-\alpha) - \frac{1}{2}.
-\]
-\[
--(1-\alpha) \psi^{(0)}(-\alpha) \sim -(1-\alpha) \ln(-\alpha) - \frac{1-\alpha}{2\alpha}.
-\]
-\[\ln\Gamma(-\alpha)\sim \frac{1}{2}\ln(-2\pi\alpha)-\alpha\ln(-\alpha)+\alpha.\]
-
-Then, substituting  these terms in \eqref{E:lim1} and applying limit we obtain:
-
+\begin{align*}
+-\ln\Gamma(L-\alpha) &\sim -\frac{1}{2}\ln\big(2\pi(L-\alpha)\big)-(L-\alpha)\ln(L-\alpha)+(L-\alpha),\\
+(L-\alpha) \psi^{(0)}(L-\alpha) & \sim (L-\alpha) \left[\ln(L-\alpha) - \frac{1}{2(L-\alpha)}\right] \sim (L-\alpha) \ln(L-\alpha) - \frac{1}{2},\\
+-(1-\alpha) \psi^{(0)}(-\alpha) &\sim -(1-\alpha) \ln(-\alpha) - \frac{1-\alpha}{2\alpha},
+\intertext{and}
+\ln\Gamma(-\alpha) & \sim \frac{1}{2}\ln(-2\pi\alpha)-\alpha\ln(-\alpha)+\alpha.
+\end{align*}
+Then, replacing these terms in&nbsp;\eqref{E:lim1}, we obtain:
 \begin{multline*}
-  \lim_{\alpha\to-\infty}\bigg[-\frac{1}{2}\ln(2\pi(L-\alpha))-L\ln(L-\alpha)+\alpha\ln(L-\alpha)+L-\alpha+ L\ln(L-\alpha) -\alpha\ln(L-\alpha)\\- \frac{1}{2}
--\ln(-\alpha)+\alpha\ln(-\alpha)- \frac{1-\alpha}{2\alpha}+ \ln (-1-\alpha)+ \frac{1}{2}\ln(-2\pi\alpha)-\alpha\ln(-\alpha)+\alpha\bigg]-L.
+  \lim_{\alpha\to-\infty} \bigg[ -\frac{1}{2}\ln\big(2\pi(L-\alpha)\big)-L\ln(L-\alpha)+\alpha\ln(L-\alpha)+L-\alpha+ L\ln(L-\alpha) -\alpha\ln(L-\alpha)\\- \frac{1}{2}
+-\ln(-\alpha)+\alpha\ln(-\alpha)- \frac{1-\alpha}{2\alpha}+ \ln (-1-\alpha)+ \frac{1}{2}\ln(-2\pi\alpha)-\alpha\ln(-\alpha)+\alpha\bigg] - L.
 \end{multline*}
-
-Simplifying each term:
-
+We, then, simplify the expression to 
 \begin{multline*}
-\lim_{\alpha\to-\infty}\bigg[-\frac{1}{2}\ln(2\pi(L-\alpha))+L- \frac{1}{2}-\ln(-\alpha)- \frac{1-\alpha}{2\alpha}
-+ \ln (-(1+\alpha))+ \frac{1}{2}\ln(-2\pi\alpha)\bigg]-L.
+\lim_{\alpha\to-\infty}\bigg[ -\frac{1}{2}\ln\big(2\pi(L-\alpha)\big) + L- \frac{1}{2}-\ln(-\alpha)- \frac{1-\alpha}{2\alpha}
++ \ln \big(-(1+\alpha)\big)+ \frac{1}{2}\ln(-2\pi\alpha) \bigg]-L.
 \end{multline*}
-
+We now group terms:
 \[
 \lim_{\alpha\to-\infty}\bigg[\frac{1}{2}\ln\frac{-\alpha}{L-\alpha}+L- \frac{1}{2}+\frac{\alpha-1}{2\alpha}
-+ \ln\frac{1+\alpha}{\alpha} \bigg]-L=\frac{1}{2}\ln(1)+L-\frac{1}{2}+\frac{1}{2}+\ln(1)-L=0.
++ \ln\frac{1+\alpha}{\alpha} \bigg]-L=\frac{1}{2}\ln 1 + L-\frac{1}{2}+\frac{1}{2}+\ln 1 -L=0.
 \]
@@
 Therefore:
-
 \[
-\lim_{\alpha \to -\infty} H_{G_I^0}(\mu, \alpha, L) = H_{\Gamma_{\text{SAR}}}(L, \mu).
+\lim_{\alpha \to -\infty} H_{G_I^0}(\mu, \alpha, L) = H_{\Gamma_{\text{SAR}}}(L, \mu),
 \]
+which concludes the proof.

### 2024-05-28 Text/Reviews/ResponsesR0R1-Reviewer1.tex
Progress

@@
 
+\vspace{3em}
 \begin{reviewbox}{Comment 2}
@@
 \begin{responsebox}{Response}
-
 We have clarified the intensity format to refer to Ground Range Detected (GRD) data. Also, we have added Table 9 that provides a detailed overview of the SAR images selected.
@@
 \end{quote}
-
 \end{responsebox}
 
+\vspace{3em}
 \begin{reviewbox}{Comment 3}
@@
 
+\vspace{3em}
 \begin{reviewbox}{Comment 4}
@@
 	\textcolor{blue}{
-We used the number of looks, $L$, informed in the SNAP (Sentinel Application Platform) metadata: the product of azimuth and range looks. 
+We used the number of looks $L$ informed in the SNAP (Sentinel Application Platform) metadata: the product of azimuth and range looks. 
 This value is close to the equivalent number of looks calculated as the ratio of the squared sample mean to the sample variance in areas with fully-developed speckle.
@@
 \end{quote}
-
 \end{responsebox}
 
+\vspace{3em}
 \begin{reviewbox}{Comment 5}
@@
 \end{quote}
-
 \end{responsebox}
 
+\vspace{3em}
 \begin{reviewbox}{Comment 6}
@@
 \end{reviewbox}
+\begin{responsebox}{Response}
+	content...
+\end{responsebox}
 
+\vspace{3em}
 \begin{reviewbox}{Comment 7}
@@
 \end{itemize}
-
 \end{responsebox}

### 2024-05-28 Text/R1-Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Progress

@@
 
-The number of looks, $L$, was determined from the metadata in SNAP (Sentinel Application Platform), consisting of azimuth looks multiplied by range looks.
-This value also approximates the equivalent number of looks (ENL), calculated through the ratio of the squared sample mean to the sample variance in textureless areas.
+We used the number of looks $L$ informed in the SNAP (Sentinel Application Platform) metadata: the product of azimuth and range looks. 
+This value is close to the equivalent number of looks calculated as the ratio of the squared sample mean to the sample variance in areas with fully-developed speckle.
 \renewcommand{\arraystretch}{2}   
@@
 
-\appendixtitles{no} 
+Despite presenting the results of using the estimators as local filters, we suggest using them in specific samples that visibly contain only one type of land use or land cover. 
+This type of analysis can assist users in selecting appropriate training samples for classification purposes.
+
+<!-- \appendixtitles{no}  -->
 \appendixstart
 \appendix
-\section[\appendixname~\thesection]{}
-
-## Limit Behavior of \(H_{G_I^0}\) as \(\alpha \to -\infty\) {#app:1}
+<!-- \section[\appendixname~\thesection]{} -->
+
+# Limit Behavior of \(H_{G_I^0}\) as \(\alpha \to -\infty\) {#app:1}
 

### 2024-05-28 Text/Reviews/ResponsesR0R1-Reviewer1.tex
add quantitative analysis line 314

@@
 \begin{responsebox}{Response}
-	content...
+We conducted a quantitative analysis by comparing the mean values and standard deviations of the different tests in selected reference areas in the image, as recommended.
+
+ We added a new section in the results (line 314).
+The results presented in Table 10 show that the estimators are sensitive to differences in land cover, which is essential for classification purposes.
+Homogeneous (water) areas have lower mean and standard deviation values, while heterogeneous (urban) areas have the highest values.
+
 \end{responsebox}

### 2024-05-28 Text/R1-Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
add quantitative analysis line 314

@@
 
+## Quantitative Analysis of Test Statistics
+In order to conduct a more quantitative analysis of the results, we compared the mean and standard deviation values of the different tests among selected reference areas in the Illinois-Region 2 image.
+These reference areas represent water, vegetation, and urban land covers, as shown in Figure&nbsp;\ref{fig:land_cover}.
+
+We selected labeled polygons (water, vegetation, urban) and conducted 100 sampling iterations with replacement from each category, using window sizes of $11\times11$ pixels.
+For each sample, we applied the corresponding test statistic.
+Finally, we computed the mean and standard deviation of the results obtained from the 100 samples.
+
+\renewcommand{\arraystretch}{1}  
+```{r land_cover, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="50%", fig.align="center",fig.pos = 'H', fig.cap='Image of Illinois-Region 2 with reference samples.
+',   fig.width = 20, fig.height = 10}
+knitr::include_graphics("../Figures/PNG/land_cover.pdf")
+```
+
+The Table&nbsp;\ref{tab:table_M_sd} presents the comparison of the mean and standard deviation values for the three  tests across the reference areas.
+```{r parameters_land, echo=FALSE, message=FALSE, warning=FALSE}
+
+#
+results_comparison_data <- data.frame(
+  Area_of_Reference = c("Water", "Water", "Water", "Vegetation", "Vegetation", "Vegetation", "Urban", "Urban", "Urban"),
+  Statistical_Test = rep(c("$S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$", "$T_\\text{CV}$", "$T_{\\text{CV}_{\\text{MnAD}}}$"), 3),
+  Mean = c("0.05029", "0.15827", "0.13013", "0.36482", "0.29421", "0.24501", "0.82970", "0.56846", "0.47176"),
+  Standard_Deviation = c("0.15415", "0.02584", "0.02183", "0.28489", "0.10957", "0.09829", "0.21910", "0.33938", "0.29486")
+)
+
+colnames(results_comparison_data) <- c("\\textbf{Area of Reference}", "\\textbf{Test Statistic}", "\\textbf{Mean}", "\\textbf{SD}")
+results_comparison_data[] <- lapply(results_comparison_data, function(x) {
+  if (is.numeric(x)) {
+    if (all(x %% 1 == 0)) {
+      formatted_numbers <- sprintf("$%d$", x)
+    } else {
+      formatted_numbers <- ifelse(x < 0, sprintf("$%.5f$", x), sprintf("$\\phantom{-}%.5f$", x))
+    }
+    return(formatted_numbers)
+  } else {
+    return(x)
+  }
+})
+
+kable(results_comparison_data, caption = "Analysis of  test statistics for different areas of reference.",
+      format = "latex",
+      booktabs = TRUE,
+      align = "ccccccccc",
+      escape = FALSE,
+      digits = 5,
+      label = "table_M_sd",
+      centering = FALSE,
+      table.envir = "table", position = "H") %>%
+  row_spec(0, align = "c") %>%
+  collapse_rows(latex_hline = "major", valign = "middle") %>%
+  kable_styling(latex_options = "scale_down", font_size = 9) %>% 
+  kable_styling(full_width = TRUE) %>%
+  column_spec(1, width = "3.5cm") %>%
+  column_spec(2, width = "5cm") %>%
+  column_spec(3, width = "2cm") %>%
+  column_spec(4, width = "2cm")
+
+```
+
+Based on the analysis, $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ appears to be the most sensitive test for classification purposes because it shows the largest distinction in mean values between the different land cover types, indicating it is better at differentiating between homogeneous and heterogeneous areas.
+However, CV and $\text{CV}_{\text{MnAD}}$ are also reliable with lower variability, making them good candidates depending on the specific application.
+
 # Conclusion {#sec:conclusion}

### 2024-05-28 Code/R/Programs/functions_sample_bias_mse.R

@@ -83,73 +83,6 @@ calculate_entropy_and_test <- function(sample_sizes, R, B, mu, alpha, L, estimat
 
 
 
-# Function to calculate entropy and perform hypothesis testing
-# calculate_entropy_and_test <- function(sample_sizes, R, B, mu, alpha, L, estimators) {
-#   true_entropy <- entropy_gamma_sar(L, mu)
-#   output <- data.frame(
-#     SampleSize = integer(0),
-#     Estimator = character(0),
-#     MeanEntropy = numeric(0),
-#     ZStatistic = numeric(0),
-#     PValue = numeric(0)
-#   )
-#   
-#   for (ssize in sample_sizes) {
-#     samples <- generate_samples_gi0(ssize, R, mu, alpha, L)
-#     
-#     for (estimator_name in names(estimators)) {
-#       estimator <- estimators[[estimator_name]]
-#       v.entropy <- numeric(R)
-#       
-#       for (r in 1:R) {
-#         sample <- samples[[r]]
-#         
-#         if (grepl(" ", estimator_name)) {
-#           v.entropy[r] <- estimator(sample, B = B)
-#         } else {
-#           v.entropy[r] <- estimator(sample)
-#         }
-#       }
-#       
-#       mean_entropy <- mean(v.entropy)
-#       
-#       z_statistic <- sqrt(R) * (mean_entropy - true_entropy) / sd(v.entropy)
-#       p_value <- 2 * (1 - pnorm(abs(z_statistic)))
-#       # alpha_t = 0.05
-#       # reject_null <- abs(z_statistic) > qnorm(1 - alpha_t / 2)
-#       # 
-#       # output <- rbind(
-#       #   output,
-#       #   data.frame(
-#       #     SampleSize = ssize,
-#       #     Estimator = estimator_name,
-#       #     MeanEntropy = round(mean_entropy, 5),
-#       #     ZStatistic = round(z_statistic, 5),
-#       #     PValue = round(p_value, 5),
-#       #     RejectNull = reject_null  
-#       #   )
-#       # )
-#       # 
-#       
-#       output <- rbind(
-#         output,
-#         data.frame(
-#           SampleSize = ssize,
-#           Estimator = estimator_name,
-#           MeanEntropy = round(mean_entropy, 5),
-#           ZStatistic = round(z_statistic, 5),
[…]

### 2024-05-28 Text/R1-Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
add change in letter R1

@@
 Based on the analysis, $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ appears to be the most sensitive test for classification purposes because it shows the largest distinction in mean values between the different land cover types, indicating it is better at differentiating between homogeneous and heterogeneous areas.
-However, CV and $\text{CV}_{\text{MnAD}}$ are also reliable with lower variability, making them good candidates depending on the specific application.
+However, CV and $\text{CV}_{\text{MnAD}}$ test are also reliable with a lower variability, making them good candidates depending on the specific application.
 

### 2024-11-22 Text/2024PresentationsChina.tex
Starting with the presentation slides

%!TEX program = xelatex
\documentclass[table,aspectratio=169]{beamer}

%\usefonttheme{professionalfonts}
\usepackage[T1]{fontenc}
\renewcommand*\familydefault{\sfdefault}

\usepackage{beamerthemesplit}
\usepackage{graphicx}
\graphicspath{{./Figures/}}

\usepackage{bm,bbm,bbding}
\usepackage{natbib}
\usepackage{siunitx}
\usepackage{texnames}
\usepackage{algorithm,algpseudocode}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{amsmath}

\definecolor{anti-flashwhite}{rgb}{0.95, 0.95, 0.96}
\definecolor{byzantine}{rgb}{0.74, 0.2, 0.64}
\definecolor{VUWlightgreen}{rgb}{0, .294, .204}
\definecolor{VUWgreen}{rgb}{0, .196, .136}

\usetheme[numbering=fraction]{metropolis}

\setbeamercovered{dynamic}
\setbeamercolor{background canvas}{bg=VUWgreen}
\setbeamercolor{normal text}{fg=anti-flashwhite, bg=VUWgreen}
\setbeamercolor{frametitle}{bg=VUWlightgreen,fg=anti-flashwhite}
\setbeamercolor{footline}{bg=VUWlightgreen}

\makeatletter
\setlength{\metropolis@frametitle@padding}{.5em}% <- default 2.2 ex

\setbeamertemplate{footline}{%
	\begin{beamercolorbox}[wd=\textwidth, sep=.2ex]{footline}% <- default 3ex
		\usebeamerfont{page number in head/foot}%
		\usebeamertemplate*{frame footer}
		\hfill%
		\usebeamertemplate*{frame numbering}
	\end{beamercolorbox}%
}
\makeatother

\setbeamertemplate{frame footer}{\includegraphics[width=1.5cm]{"Logo Offshore Reversed Landscape RGB"}}
\setbeamertemplate{navigation symbols}{}

\AtBeginSubsection[]
{
	\begin{frame}
		\frametitle{Table of Contents}
		\tableofcontents[currentsection,currentsubsection]
	\end{frame}
}

\title{Identifying Heterogeneity in SAR Data with New Test Statistics}
\subtitle{There are no too old problems}
\author{Alejandro C.\ Frery}
\institute{Victoria University of Wellington\\
	School of Mathematics and Statistics\\
	New Zealand}
\date{November, 2024}

\begin{document}

	\setsansfont[BoldFont={Avenir Heavy}]{Avenir Book}

	\frame{\titlepage}

	\begin{frame}
		This is a joint work with Prof.\ Abraão Nascimento and MSc.\ Janeth Alpala (it is part of her PhD project), from Universidade Federal de Pernambuco, Brazil.
	\end{frame}

	\begin{frame}{Starting point}
		\begin{itemize}[<+->]
			\item Synthetic Aperture Radar (SAR) technology is essential for environmental monitoring and disaster management. 
			\item It provides
			images under various conditions, including day or night and adverse weather
			situations~\citep{Moreira2013,Mu2019}. 
			\item The effective use of SAR
			data relies on understanding of their statistical properties
			because it is corrupted by speckle: a noise-like interference effect~\citep{Argenti2013}.
		\end{itemize}
	\end{frame}

	\begin{frame}[standout]
		\frametitle{Takeaways}
		You may forget about the technical contents of this talk, but remember:
		\begin{itemize}[<+->]
			\item There are no ``too old'' problems that cannot be revisited.
			\item The data statistical properties always bring valuable information.
			\item A careful mathematical manipulation often leads to new exciting results.
		\end{itemize}
	\end{frame}

	\begin{frame}[allowframebreaks,allowdisplaybreaks]
		\bibliographystyle{agsm}
		\bibliography{references} 	
	\end{frame}

	\begin{frame}[standout]
		\frametitle{The End}
		\begin{columns}
			\begin{column}{.4\linewidth}
				\centering
				\includegraphics[width=.7\linewidth]{QRCode-WebPageVUW}\\	\includegraphics[width=\linewidth]{"Logo Offshore Reversed Landscape RGB"}
			\end{column}
			\begin{column}{.6\linewidth}
				Thanks for your kind attention!

				Questions?
			\end{column}
		\end{columns}

	\end{frame}

\end{document}

### 2024-11-22 Text/2024PresentationsChina.tex
Fresh run of RMarkdown R1 file
Plots for the slides

@@
 \title{Identifying Heterogeneity in SAR Data with New Test Statistics}
-\subtitle{There are no too old problems}
+\subtitle{No problem is too old, and you don't always need deep learning}
 \author{Alejandro C.\ Frery}
@@
 	because it is corrupted by speckle: a noise-like interference effect~\citep{Argenti2013}.
+	\item Speckle in intensity format is non-Gaussian. 
+	\item The
+	\(\mathcal{G}^0\) distribution is suitable for SAR data and includes
+	the Gamma law as the limiting case for fully-developed
+	speckle~\citep{Ferreira2020}.
+	\item We improve the identification of potential roughness
+	features in SAR intensity data, i.e., departures from the Gamma distribution (fully-developed
+	speckle).
 \end{itemize}
+\end{frame}
+
+\begin{frame}{The problem}
+\centering
+\includegraphics[width=55mm]{../Figures/PNG/Rotterdam_1024}\hskip1em
+\includegraphics[width=55mm]{../Figures/PNG/lake_512}
+
+Apart from the brightness, notice that different types of areas have distinct roughness.
+\end{frame}
+
+\begin{frame}{Statistical models}
+The main models are the Gamma (suitable for fully-developed speckle) and
+\(\mathcal{G}_I^0\) (able to describe roughness) distributions~\citep{Frery1997}.
+
+They are characterized by the probability
+density functions (pdfs): 
+\begin{align}
+	f_Z(z;L, \mu\mid \Gamma_{\text{SAR}})&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z)\label{E:gamma1}\\
+	\intertext{ and }
+	f_Z(z; \alpha, \gamma, L \mid \mathcal{G}_I^0)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
+\end{align} 
+where \(\mu > 0\) is the mean, \(\gamma > 0\) is the scale,
+\(\alpha < 0\) measures the roughness, \(L \geq 1\) is the number of
+looks, \(\Gamma(\cdot)\) is the gamma function, and
+\(\mathbbm 1_{A}(z)\) is the indicator function of the set \(A\).
+\end{frame}
+
+\begin{frame}{The statistical approach}
+\begin{columns}
+	\begin{column}{.63\linewidth}
+{\includegraphics<1>[width=\linewidth]{../Figures/PDF/GammaGI0Densities}}
+{\includegraphics<2>[width=\linewidth]{../Figures/PDF/GammaGI0DensitiesSemilog}}
+	\end{column}
+	\begin{column}{.3\linewidth}
+	We need to identify the model that best describes the data.
+
+	But it is a challenging task because
+	\begin{itemize}
+		\item Samples are small, and
+		\item Parameter estimators are tricky.
+	\end{itemize}
+	\end{column}
+\end{columns}
 \end{frame}
@@
 \begin{itemize}[<+->]
-			\item There are no ``too old'' problems that cannot be revisited.
+	\item No problem is too old to be revisited.
 	\item The data statistical properties always bring valuable information.
 	\item A careful mathematical manipulation often leads to new exciting results.
+	\item Reproducibility goes a long way!
 \end{itemize}

### 2024-11-23 Text/2024PresentationsChina.tex
Progressing

@@
 \usepackage{amsmath}
+\usepackage{mathabx}
+\usepackage{scalerel,stackengine}
+\stackMath
+\newcommand\reallywidehat[1]{%
+	\savestack{\tmpbox}{\stretchto{%
+			\scaleto{%
+				\scalerel*[\widthof{\ensuremath{#1}}]{\kern-.6pt\bigwedge\kern-.6pt}%
+				{\rule[-\textheight/2]{1ex}{\textheight}}%WIDTH-LIMITED BIG WEDGE
+			}{\textheight}% 
+		}{0.5ex}}%
+	\stackon[1pt]{#1}{\tmpbox}%
+}
+\parskip 1ex
 
@@
 	\item The
-	\(\mathcal{G}^0\) distribution is suitable for SAR data and includes
+	\({G}^0\) distribution is suitable for SAR data and includes
 	the Gamma law as the limiting case for fully-developed
@@
 
-\begin{frame}{Statistical models}
+\begin{frame}[allowframebreaks]{Statistical models}
 The main models are the Gamma (suitable for fully-developed speckle) and
-\(\mathcal{G}_I^0\) (able to describe roughness) distributions~\citep{Frery1997}.
+\({G}_I^0\) (able to describe roughness) distributions~\citep{Frery1997}.
 
@@
 	\intertext{ and }
-	f_Z(z; \alpha, \gamma, L \mid \mathcal{G}_I^0)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
+	f_Z\big(z; \mu, \alpha, L\mid G_I^0\big) &= \frac{L^L\Gamma(L-\alpha)}{\big[-\mu(\alpha+1)\big]^{\alpha}\Gamma(-\alpha)\Gamma(L)} \frac{z^{L-1}}{\big[-\mu(\alpha+1)+Lz\big]^{L-\alpha}}\mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
 \end{align} 
-where \(\mu > 0\) is the mean, \(\gamma > 0\) is the scale,
+where \(\mu > 0\) is the mean,
 \(\alpha < 0\) measures the roughness, \(L \geq 1\) is the number of
@@
 \(\mathbbm 1_{A}(z)\) is the indicator function of the set \(A\).
+
+\citet{Frery1997} proved that the $\Gamma_{\text{SAR}}$ model is a particular case of the $G_I^0$ distribution.
+In effect, for a given $\mu$ fixed,
+$$
+f_Z\big(z; \mu, \alpha, L\mid G_I^0\big)
+\longrightarrow 
+f_Z(z;L, \mu\mid \Gamma_{\text{SAR}}) 
+$$
+when $\alpha\to-\infty$.
 \end{frame}
@@
 \end{columns}
+\end{frame}
+
+\begin{frame}{The usual approach: I}
+Assume the equivalent number of looks $L$ is known.
+
+The coefficient of variation under the $\Gamma_{\text{SAR}}$ models is:
+\begin{align}
+	\text{CV}\mid \Gamma_{\text{SAR}} =
+	\frac{\sigma}{\mu} =
+	 \frac{1}{\sqrt{L}}.
+\end{align}
+
+Procedure:
+\begin{enumerate}
+	\item Collect (typically small) samples $\bm x_1, \bm x_2, \dots, \bm x_m$.
+	\item Compute the sample coefficients of variation $\text{CV}(\bm x_1),\text{CV}(\bm x_2), \dots, \text{CV}(\bm x_m)$.
+	\item Decide for heterogeneity those samples ``too far'' from $1/\sqrt{L}$.
+\end{enumerate}
+
+But, what is ``too far''?
+\end{frame}
+
+\begin{frame}{The usual approach: I}
+We are tempted to form a statistical test using the coefficient of variation as the test statistic.
+
+Consider the random sample $\bm X=(X_1,X_2,\dots,X_n)$ that, under the null hypothesis has $\Gamma_{\text{SAR}}$ distribution.
+Then, we need the distribution of
+\begin{equation}
+\widehat{\text{CV}}(\bm X) = \frac{\frac1n \sum_{\ell=1}^n X_\ell}{\sqrt{\frac1n \sum_{\ell=1}^n \big(X_\ell-\overline{\bm X}\big)^2}}.
+\label{eq:CV}
+\end{equation}
+
+Although we know that $\bar{\bm X}$ and $\widehat{\text{CV}}(\overline X) $ are independent \citep{OnaCharacterizationoftheGammaDistributiontheIndependenceoftheSampleMeanandtheSampleCoefficientofVariation}, we don't know the distribution of~\eqref{eq:CV}.
+\end{frame}
+
+\begin{frame}{The usual approach: II}
+The coefficient of variation is so widespread that \citet{Ospina2019} proposed alternative ways of computing it.
+
+They replaced the mean by the median, and the standard deviation by the mean absolute deviation from the median (MnAD), two well-known robust measures of location and 
+scale, respectively.
+
+Their estimator becomes
+\begin{equation}
+\widecheck{\text{CV}}(\bm X) = \frac{\widehat{Q}_2(\bm X)}{\frac1n \sum_{\ell=1}^n|X_i-\widehat{Q}_2(\bm X)|}.
+\end{equation}
+
+It is robust, we don't know its distribution under the $\Gamma_{\text{SAR}}$ model.
+\end{frame}
+
+\begin{frame}[allowframebreaks]{Our proposal's rationale}
+The entropy is a powerful descriptor.
+It has been used for SAR data, among others, by
+\citet{Ferreira2020} for segmentation, by
+\citet{Cassetti2022} for classification, and by 
+\citet{EntropyBasedNonLocalMeansFilterforSingleLookSARSpeckleReduction} for noise reduction.
+
+Specifically, the Shannon entropy of the model $F$, characterized by the probability density function $f$ is
+$$
+H(F) = -\int f(x) \ln\big(f(x)\big) dx.
+$$
+
+There are other types of entropy, e.g., Rényi and Tsallis, and also the Fisher information measure~\citep{AsymptoticDistributionofCertainTypesofEntropyundertheMultinomialLaw}.
+These quantities have not been explored for roughness assessment (\alert{hint!}).
+
+The Shannon entropy of
+\(\Gamma_{\text{SAR}}\) in~\eqref{E:gamma1} and \(G_I^0\) 
+in~\eqref{E:gi01}: 
+\begin{equation}
+	\label{E:E-gamma}
+	H_{\Gamma_{\text{SAR}}}(L, \mu) =   L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu, 
+\end{equation} \begin{multline}
+	\label{E:E-GIO}
+	H_{G_I^0}(\mu, \alpha, L) =L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) +\ln \mu -\ln\Gamma(L-\alpha)\\
+	+ (L-\alpha) \psi^{(0)}(L-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L,
+\end{multline} where \(\psi^{(0)}(\cdot)\) is the digamma function.
+
+\alert{They are different!
+Check \citet{IdentifyingHeterogeneityinSARDatawithNewTestStatistics} for details.} Therefore, some empirical version of~\eqref{E:E-gamma} could be used to form a test statistic.
+
+Now, assume that we have a good estimator for the Shannon entropy, say $\widehat{H_{\Gamma_{\text{SAR}}}}$.
+Under the $\Gamma_{\text{SAR}}$ model, we expect it to be close to~\eqref{E:E-gamma}.
+Such estimator estimates
+$$
+\widehat{H_{\Gamma_{\text{SAR}}}} = \reallywidehat{L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu}
+$$
+
+Now we build a test statistic:
+\begin{align*}
+	S(\bm Z; L) = & \hskip1ex\reallywidehat{L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu} - \mbox{}\\
+	& \hskip1ex L + \ln L - \ln\Gamma(L) - (1-L)\psi^{(0)}(L) - \ln \widehat{\mu}\\
+	= & \hskip1ex \widehat{H_{\Gamma_{\text{SAR}}}} - L + \ln L - \ln\Gamma(L) - (1-L)\psi^{(0)}(L) - \ln \widehat{\mu}.
+\end{align*}
+This test statistic is close to zero under the null hypothesis (homogeneity, fully developed speckle, the $\Gamma_{\text{SAR}}$ model).
+
+Now we must choose suitable estimators $\widehat{H_{\Gamma_{\text{SAR}}}}$ and $\widehat{\mu}$.
+\end{frame}
+
+\begin{frame}{Estimating the Shannon entropy}
+The Shannon entropy's maximum likelihood estimator under the $\Gamma_{\text{SAR}}$ model is
+$$
+\widehat{H_{\Gamma_{\text{SAR}}}} = L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \widehat{\ln \mu},
+$$
+where $\widehat{\ln \mu}$ is the natural logarithm of the sample mean.
+
+We are also interested in non-parametric alternatives.
+
+Recall the definition of the Shannon entropy:
+\begin{align*}
+	H(F) &= -\int f(x) \ln\big(f(x)\big) dx.
+\end{align*}
 \end{frame}
@@
 \end{columns}
+\end{frame}
 
+\begin{frame}[allowframebreaks]{Appendix}
+
+	The Shannon entropy of a probability distribution with cumulative distribution function (CDF) \( F(x) \) and probability density function (PDF) \( f(x) = F'(x) \) is:
+	\[
+-\int_{-\infty}^\infty f(x) \ln f(x) \, dx = \int_0^1 \ln \left( \frac{d}{dy} F^{-1}(y) \right) \, dy.
+	\]
+
+\begin{description}
+	\item[Change of variable:]	The inverse function \( F^{-1}(y) \) satisfies \( F(F^{-1}(y)) = y \), where \( y \in [0, 1] \).
+Using the change of variable \( y = F(x) \), we have \( x = F^{-1}(y) \), and the derivative of \( x \) with respect to \( y \) is:
+	\[
+	\frac{dx}{dy} = \frac{1}{F'(x)} = \frac{1}{F'(F^{-1}(y))}.
+	\]
+	\item[Transform the Entropy Integral:] 	Substituting \( x = F^{-1}(y) \) into the entropy integral, we write:
+	\[
+	H = -\int_{-\infty}^\infty f(x) \ln f(x) \, dx.
+	\]
+	Using the change of variable \( y = F(x) \), \( f(x) = F'(x) \), and \( dx = \frac{dy}{F'(F^{-1}(y))} \), the integral becomes:
+	\[
+	H = -\int_0^1 F'(F^{-1}(y)) \ln F'(F^{-1}(y)) \cdot \frac{1}{F'(F^{-1}(y))} \, dy.
+	\]
+	\item[Simplify the Expression:] 	Simplifying the terms yields:
+	\[
+	H = -\int_0^1 \ln F'(F^{-1}(y)) \, dy.
+	\]
+	\item[Relate to the Derivative of \( F^{-1} \)] 	From the inverse function theorem, the derivative of \( F^{-1}(y) \) is:
+	\[
+	\frac{d}{dy} F^{-1}(y) = \frac{1}{F'(F^{-1}(y))}.
+	\]
+	Taking the logarithm and flipping the sign, we find:
+	\[
+	\ln F'(F^{-1}(y)) = -\ln \left( \frac{d}{dy} F^{-1}(y) \right).
+	\]
+	Substituting this into the entropy integral gives:
+	\[
+	H = \int_0^1 \ln \left( \frac{d}{dy} F^{-1}(y) \right) \, dy.
+	\] 
+\end{description}	
 \end{frame}

### 2024-11-23 Text/2024PresentationsChina.tex
Update 2024PresentationsChina.tex

@@
 \begin{enumerate}
-	\item Collect (typically small) samples $\bm x_1, \bm x_2, \dots, \bm x_m$.
-	\item Compute the sample coefficients of variation $\text{CV}(\bm x_1),\text{CV}(\bm x_2), \dots, \text{CV}(\bm x_m)$.
+	\item Collect (typically small) samples $\bm z_1, \bm z_2, \dots, \bm z_m$.
+	\item Compute the sample coefficients of variation $\text{CV}(\bm z_1),\text{CV}(\bm z_2), \dots, \text{CV}(\bm z_m)$.
 	\item Decide for heterogeneity those samples ``too far'' from $1/\sqrt{L}$.
@@
 
-Consider the random sample $\bm X=(X_1,X_2,\dots,X_n)$ that, under the null hypothesis has $\Gamma_{\text{SAR}}$ distribution.
+Consider the random sample $\bm Z=(Z_1,Z_2,\dots,Z_n)$ that, under the null hypothesis has $\Gamma_{\text{SAR}}$ distribution.
 Then, we need the distribution of
 \begin{equation}
-\widehat{\text{CV}}(\bm X) = \frac{\frac1n \sum_{\ell=1}^n X_\ell}{\sqrt{\frac1n \sum_{\ell=1}^n \big(X_\ell-\overline{\bm X}\big)^2}}.
+\widehat{\text{CV}}(\bm Z) = \frac{\frac1n \sum_{\ell=1}^n Z_\ell}{\sqrt{\frac1n \sum_{\ell=1}^n \big(Z_\ell-\overline{\bm Z}\big)^2}}.
 \label{eq:CV}
@@
 \begin{equation}
-\widecheck{\text{CV}}(\bm X) = \frac{\widehat{Q}_2(\bm X)}{\frac1n \sum_{\ell=1}^n|X_i-\widehat{Q}_2(\bm X)|}.
+\widecheck{\text{CV}}(\bm Z) = \frac{\widehat{Q}_2(\bm Z)}{\frac1n \sum_{\ell=1}^n \big|Z_i-\widehat{Q}_2(\bm Z)\big|}.
 \end{equation}
@@
 $$
-H(F) = -\int f(x) \ln\big(f(x)\big) dx.
+H(F) = -\int_{-\infty}^\infty f(x) \ln\big(f(x)\big) dx.
 $$
@@
 
-\begin{frame}{Estimating the Shannon entropy}
+\begin{frame}[allowframebreaks]{Estimating the Shannon entropy}
 The Shannon entropy's maximum likelihood estimator under the $\Gamma_{\text{SAR}}$ model is
@@
 \begin{align*}
-	H(F) &= -\int f(x) \ln\big(f(x)\big) dx.
+	H(F) = -\int_{-\infty}^\infty f(x) \ln\big(f(x)\big) dx.
 \end{align*}
+This can be written as
+$$
+H(F) = \int_{0}^{1} \ln \Big( \frac{d}{dy} F^{-1}(y) \Big) \, dy.
+$$
+See the proof in the Appendix.
+
+Now, given the random sample $\bm Z=(Z_1,Z_2,\dots,Z_n)$ and its sorted version $Z_{(1)},Z_{(2)},\dots,Z_{(n)}$, we can 
+\begin{itemize}
+	\item estimate $F^{-1}$ by the empirical cumulative distribution function,
+	\item approximate the derivative with finite differences (called ``spacings''),
+	\item approximate the integral with a summation.
+\end{itemize}
+
+There are several versions of entropy estimators based on spacings.
+We found that the best in terms of bias and mean square error is the one proposed by
+\citet{IbrahimAlOmari2014}:
+ \[
+	\widehat{H}_{\text{AO}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{\omega_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
+	\] where \[
+	\omega_i= \begin{cases}3/2 & \text { if }\quad 1 \leq i \leq m, \\ 2 & \text { if }\quad m+1 \leq i \leq n-m, \\ 3/2 & \text { if } \quad n-m+1 \leq i \leq n,\end{cases}
+	\] 
+	in which \(m=\big[\sqrt{n}+0.5\big]\), \(Z_{(i-m)}=Z_{(1)}\) for \(i \leq m\), and
+	\(Z_{(i+m)}=Z_{(n)}\) for \(i \geq n-m\).
+
+This estimator is asymptotically consistent, i.e., it converges in
+probability to the true value when \(m,n\rightarrow\infty\) and
+\(m/n\rightarrow0\).
+
+However, we will use an improved bootstrap-improved
+version $\widetilde{H}_{\text{AO}}(\bm Z)$ because it performs better with small samples.
+See details in \citet{IdentifyingHeterogeneityinSARDatawithNewTestStatistics}.
+\end{frame}
+
+\begin{frame}{Finally\dots}
+	We have three test statistics:
+	\begin{align*}
+		S_{\widehat{\text{CV}}}(\bm Z;L) &= \frac{\frac1n \sum_{\ell=1}^n Z_\ell}{\sqrt{\frac1n \sum_{\ell=1}^n \big(Z_\ell-\overline{\bm Z}\big)^2}} - \frac1{\sqrt{L}} \\
+		S_{\widehat{\text{CV}_{\text{MnAD}}}} (\bm Z;L) &= \frac{\widehat{Q}_2(\bm Z)}{\frac1n \sum_{\ell=1}^n|X_i-\widehat{Q}_2(\bm Z)|}-\frac1{\sqrt{L}},\\
+		S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L) & = \widetilde{H}_{\text{AO}}(\bm Z) - L + \ln L - \ln\Gamma(L) - (1-L)\psi^{(0)}(L) - \ln \widehat{\mu}
+	\end{align*}
+
+We don't know their distributions, but we know that they should be close to zero under the null hypothesis (homogeneity, fully developed speckle).
+
+We tested their size (error Type~I) and power (error Type~II) and finite-size distribution under the null hypothesis.
+\alert{The winner is\dots}
 \end{frame}
@@
 
-\begin{frame}[allowframebreaks]{Appendix}
+\begin{frame}[allowframebreaks]{Appendix}\label{App:Proof}
 
@@
 \end{document}
+
+Title: Identifying Heterogeneity in SAR Data with New Test Statistics
+
+Abstract: We will discuss a statistical approach to identify the underlying roughness characteristics in synthetic aperture radar (SAR) intensity data.
+The physical modeling of this kind of data allows the use of the Gamma distribution in the presence of fully-developed speckle, i.e., when there are infinitely many independent backscatterers per resolution cell, and none dominates the return.
+Such areas are often called ``homogeneous'' or ``textureless'' regions.
+The GI0 distribution is also a widely accepted law for heterogeneous and extremely heterogeneous regions.
+We propose three test statistics to distinguish between homogeneous and inhomogeneous regions with a known number of looks.
+The first test statistic uses a bootstrapped non-parametric estimator of Shannon entropy, providing a robust assessment in uncertain distributional assumptions.
+The second test uses the classical coefficient of variation (CV).
+The third test uses an alternative form of estimating the CV based on the ratio of the mean
+absolute deviation from the median to the median.
+
+Bio: Alejandro C.
+Frery received in 1983 a B.Sc.
+in Electronic and Electrical Engineering from the Universidad de Mendoza.
+His M.Sc.
+degree was in Applied Mathematics (Statistics) from the Instituto de Matemática Pura e Aplicada (IMPA, Rio de Janeiro, 1990), and his Ph.D.
+degree was in Applied Computing from the Instituto Nacional de Pesquisas Espaciais (INPE, São José dos Campos, Brazil, 1993).
+His research interests are data visualisation, statistical computing, and stochastic modelling, with signal and image processing and networks applications.
+
+He has held a ``Huashan Scholar'' position at Xidian University, Xi'an, China, since 2019.
+Since May 2020, he has been a Statistics and Data Science Professor at the School of Mathematics and Statistics, Victoria University of Wellington, New Zealand.
+
+Prof.
+Frery is also a member of the International Society for Photogrammetry and Remote Sensing (ISPRS), the New Zealand Statistical Association, and the Statistical Society of Australia.
+In 2018, he received the IEEE GRSS Regional Leader Award.
+After serving as Associate Editor for over five years, Prof.
+Frery was the Editor-in-Chief of the IEEE Geoscience and Remote Sensing Letters from 2014 to 2018.
+He was an IEEE Geoscience and Remote Sensing Society (GRSS) Distinguished Lecturer from 2015 to 2019.
+He served as this Society's AdCom (Advisory Committee) member, in charge of Future Publications, Plagiarism and Regional Symposia from 2019 to 2022.
+Since 2023, he has been the Vice-President of Publications.

### 2024-11-23 Text/2024PresentationsChina.tex
Update 2024PresentationsChina.tex

@@
 
+{\setbeamercolor{background canvas}{bg=anti-flashwhite}
+\begin{frame}{The test based on the Shannon entropy}
+\centering
+\includegraphics[width=0.7\linewidth]{R1-Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_density-1}
+\end{frame}
+}
+
+{\setbeamercolor{background canvas}{bg=anti-flashwhite}
+\begin{frame}{Application to simulated data}
+\centering
+\includegraphics[width=.42\linewidth]{../Figures/PNG/Phantom1}
+\includegraphics[width=.57\linewidth]{../Figures/PNG/Phantom_label/Phantom_labels}
+\end{frame}
+}
+
+{\setbeamercolor{background canvas}{bg=anti-flashwhite}
+\begin{frame}{Application to simulated data: $S_{\widehat{\text{CV}}}$, $S_{\widehat{\text{CV}_{\text{MnAD}}}}$, and $S_{\widetilde{H}_{\text{AO}}}$ $p$-values}
+\centering
+{\includegraphics[width=.32\linewidth]{../Figures/PNG/cv_pvalues_Phantom_4_z1} }
+{\includegraphics[width=.32\linewidth]{../Figures/PNG/mnad_p_values_Phantom_mnad_7_z1} }
+{\includegraphics[width=.32\linewidth]{../Figures/PNG/H_pvalue_Phantom_4_z1_200b} }
+\end{frame}
+}
+
+{\setbeamercolor{background canvas}{bg=anti-flashwhite}
+\begin{frame}{Application to Sentinel~2 data}
+\centering
+\includegraphics[width=.335\linewidth]{../Figures/PNG/Sentinel2_Illinois_lake}
+\includegraphics[width=.32\linewidth]{../Figures/PNG/lake_512}
+\includegraphics[width=.32\linewidth]{../Figures/PNG/H_pvalue_lake_512_36L_AO_100b}
+\end{frame}
+}
+
 \begin{frame}[standout]

### 2024-11-24 Text/2024PresentationsChina.tex
Happy with the slides

@@
 
-%\usefonttheme{professionalfonts}
 \usepackage[T1]{fontenc}
-\renewcommand*\familydefault{\sfdefault}
+\usefonttheme{serif}
 
-\usepackage{beamerthemesplit}
+%\usepackage{beamerthemesplit}
 \usepackage{graphicx}
-\graphicspath{{./Figures/}}
+\graphicspath{{./Figures/PNG/}}
 
@@
 \usepackage{texnames}
-\usepackage{algorithm,algpseudocode}
 \usepackage{multirow}
@@
 
-Although we know that $\bar{\bm X}$ and $\widehat{\text{CV}}(\overline X) $ are independent \citep{OnaCharacterizationoftheGammaDistributiontheIndependenceoftheSampleMeanandtheSampleCoefficientofVariation}, we don't know the distribution of~\eqref{eq:CV}.
+Although we know that $\overline{\bm X}$ and $\widehat{\text{CV}}(\overline X) $ are independent \citep{OnaCharacterizationoftheGammaDistributiontheIndependenceoftheSampleMeanandtheSampleCoefficientofVariation}, we don't know the distribution of~\eqref{eq:CV}.
 \end{frame}
@@
 
-It is robust, we don't know its distribution under the $\Gamma_{\text{SAR}}$ model.
+It is robust, but we don't know its distribution under the $\Gamma_{\text{SAR}}$ model.
 \end{frame}
@@
 \begin{itemize}
-	\item estimate $F^{-1}$ by the empirical cumulative distribution function,
+	\item estimate $F$ by the empirical cumulative distribution function,
 	\item approximate the derivative with finite differences (called ``spacings''),
@@
 \centering
-{\includegraphics[width=.32\linewidth]{../Figures/PNG/cv_pvalues_Phantom_4_z1} }
-{\includegraphics[width=.32\linewidth]{../Figures/PNG/mnad_p_values_Phantom_mnad_7_z1} }
-{\includegraphics[width=.32\linewidth]{../Figures/PNG/H_pvalue_Phantom_4_z1_200b} }
+{\includegraphics[width=.33\linewidth]{../Figures/PNG/cv_pvalues_Phantom_4_z1} }
+{\includegraphics[width=.33\linewidth]{../Figures/PNG/mnad_p_values_Phantom_mnad_7_z1} }
+{\includegraphics[width=.33\linewidth]{../Figures/PNG/H_pvalue_Phantom_4_z1_200b} }
 \end{frame}
@@
 {\setbeamercolor{background canvas}{bg=anti-flashwhite}
-\begin{frame}{Application to Sentinel~2 data}
+	\begin{frame}{Rotterdam: optical and Sentinel~2 data}
+		\centering
+\includegraphics[width=.48\linewidth]{../Figures/PNG/Rotterdam} 
+\includegraphics[width=.48\linewidth]{../Figures/PNG/Rotterdam_1024}
+	\end{frame}
+}
+
+{\setbeamercolor{background canvas}{bg=anti-flashwhite}
+	\begin{frame}{Rotterdam: $S_{\widehat{\text{CV}}}$, $S_{\widehat{\text{CV}_{\text{MnAD}}}}$, and $S_{\widetilde{H}_{\text{AO}}}$ $p$-values}
+		\centering
+\visible<1->{\includegraphics[width=.32\linewidth]{../Figures/PNG/cv_Rotterdam}}
+\visible<2->{\includegraphics[width=.32\linewidth]{../Figures/PNG/mnad_Rotterdam}}
+\visible<3->{\includegraphics[width=.32\linewidth]{../Figures/PNG/Entropy_AO_Rotterdam_1024}}
+	\end{frame}
+}
+
+{\setbeamercolor{background canvas}{bg=anti-flashwhite}
+\begin{frame}{Illinois: optical, Sentinel~2, and $p$-values}
 \centering

### 2024-11-24 Text/2024PresentationsChina.tex
Update 2024PresentationsChina.tex

@@
 \centering
-{\includegraphics[width=.33\linewidth]{../Figures/PNG/cv_pvalues_Phantom_4_z1} }
-{\includegraphics[width=.33\linewidth]{../Figures/PNG/mnad_p_values_Phantom_mnad_7_z1} }
-{\includegraphics[width=.33\linewidth]{../Figures/PNG/H_pvalue_Phantom_4_z1_200b} }
+{\includegraphics[width=.32\linewidth]{../Figures/PNG/cv_pvalues_Phantom_4_z1} }
+{\includegraphics[width=.32\linewidth]{../Figures/PNG/mnad_p_values_Phantom_mnad_7_z1} }
+{\includegraphics[width=.32\linewidth]{../Figures/PNG/H_pvalue_Phantom_4_z1_200b} }
 \end{frame}
@@
 {\setbeamercolor{background canvas}{bg=anti-flashwhite}
-	\begin{frame}{Rotterdam: $S_{\widehat{\text{CV}}}$, $S_{\widehat{\text{CV}_{\text{MnAD}}}}$, and $S_{\widetilde{H}_{\text{AO}}}$ $p$-values}
+	\begin{frame}{Rotterdam: test statistics $S_{\widehat{\text{CV}}}$, $S_{\widehat{\text{CV}_{\text{MnAD}}}}$, and $S_{\widetilde{H}_{\text{AO}}}$}
 		\centering
@@
 \visible<3->{\includegraphics[width=.32\linewidth]{../Figures/PNG/Entropy_AO_Rotterdam_1024}}
+	\end{frame}
+}
+
+{\setbeamercolor{background canvas}{bg=anti-flashwhite}
+	\begin{frame}{Rotterdam: $S_{\widehat{\text{CV}}}$, $S_{\widehat{\text{CV}_{\text{MnAD}}}}$, and $S_{\widetilde{H}_{\text{AO}}}$ $p$-values}
+		\centering
+		\visible<1->{\includegraphics[width=45mm]{../Figures/PNG/cv_pvalues_Rotterdam} }
+		\visible<2->{\includegraphics[width=45mm]{../Figures/PNG/mnad_p_values_Rotterdam} }
+		\visible<3->{\includegraphics[width=45mm]{../Figures/PNG/H_pvalue_AO_Rotterdam_1024} }
 	\end{frame}

### 2024-11-24 Text/2024PresentationsChina.tex
Update 2024PresentationsChina.tex

@@
 
-\usepackage{bm,bbm,bbding}
+\usepackage{bm,bbm}
 \usepackage{natbib}
 \usepackage{siunitx}
-\usepackage{texnames}
-\usepackage{multirow}
 \usepackage{booktabs}
@@
 
-\alert{They are different!
-Check \citet{IdentifyingHeterogeneityinSARDatawithNewTestStatistics} for details.} Therefore, some empirical version of~\eqref{E:E-gamma} could be used to form a test statistic.
+As expected, $H_{G_I^0}(\mu, \alpha, L)\to H_{\Gamma_{\text{SAR}}}(L, \mu)$ when $\alpha\to-\infty$.
+\alert{But they are different!}
+Check \citet{IdentifyingHeterogeneityinSARDatawithNewTestStatistics} for details.
+
+Therefore, some empirical version of~\eqref{E:E-gamma} could be used to form a test statistic.
 
@@
 \end{frame}
+
+{\setbeamercolor{background canvas}{bg=anti-flashwhite}
+	\begin{frame}{What we want to measure}
+		\centering
+\includegraphics[width=0.78\linewidth]{R1-Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_GI0_to_gamma1-1}
+	\end{frame}
+}
 
@@
 	\item A careful mathematical manipulation often leads to new exciting results.
-	\item Reproducibility goes a long way!
+	\item The reproducible article (including these slides) is available \href{https://github.com/rjaneth/identifying-heterogeneity-in-sar-data-with-new-test-statistics}{\alert{here}}.
+Reproducibility goes a long way!
 \end{itemize}
@@
 \bibliography{references} 	
-\end{frame}
-
-\begin{frame}[standout]
-\frametitle{The End}
-\begin{columns}
-	\begin{column}{.4\linewidth}
-		\centering
-		\includegraphics[width=.7\linewidth]{QRCode-WebPageVUW}\\	\includegraphics[width=\linewidth]{"Logo Offshore Reversed Landscape RGB"}
-	\end{column}
-	\begin{column}{.6\linewidth}
-		Thanks for your kind attention!
-
-		Questions?
-	\end{column}
-\end{columns}
 \end{frame}
@@
 
+\begin{frame}[standout]
+	\frametitle{The End}
+	\begin{columns}
+		\begin{column}{.4\linewidth}
+			\centering
+			\includegraphics[width=.7\linewidth]{QRCode-WebPageVUW}\\	\includegraphics[width=\linewidth]{"Logo Offshore Reversed Landscape RGB"}
+		\end{column}
+		\begin{column}{.6\linewidth}
+			Thanks for your kind attention!
+
+			Questions?
+		\end{column}
+	\end{columns}
+\end{frame}
+
 \end{document}

### 2024-11-24 Text/2024PresentationsChina.tex
Update 2024PresentationsChina.tex

@@
 Recall the definition of the Shannon entropy:
-\begin{align*}
+\begin{equation*}
 	H(F) = -\int_{-\infty}^\infty f(x) \ln\big(f(x)\big) dx.
-\end{align*}
-This can be written as
+\end{equation*}
+
+We want an estimator for $H(F)$, for example
 $$
-H(F) = \int_{0}^{1} \ln \Big( \frac{d}{dy} F^{-1}(y) \Big) \, dy.
+\widehat{H}(F) = H(\widehat{F}) = -\int_{-\infty}^\infty \widehat{f}(x) \ln\big(\widehat{f}(x)\big) dx,
+$$
+but how will we estimate $f$?
+
+Two ways to estimate $f$:
+\begin{itemize}
+	\item estimating the parameters $\widehat{f}(x;\bm\theta) = f(x;\widehat{\bm \theta})$,
+	\item estimating the density in a non-parametric way.
+\end{itemize}
+
+Parameter estimation $f(x;\widehat{\bm \theta})$ is \alert{inadequate}, because we are not sure which is the best model.
+
+Density estimation $\widehat{f}$ is \alert{tricky} because we want to work with small samples.
+
+\framebreak
+
+The Shannon entropy can be written as
+$$
+H(F) = 
+-\int_{-\infty}^\infty f(x) \ln\big(f(x)\big) dx =
+\int_{0}^{1} \ln \Big( \frac{d}{dy} F^{-1}(y) \Big) \, dy.
 $$
@@
 	\item estimate $F$ by the empirical cumulative distribution function,
+	\item its inverse, the quantile function $F^{-1}$, by the order statistics
 	\item approximate the derivative with finite differences (called ``spacings''),
@@
 
-However, we will use an improved bootstrap-improved
+However, we will use a bootstrap-improved
 version $\widetilde{H}_{\text{AO}}(\bm Z)$ because it performs better with small samples.

### 2024-11-24 Text/2024PresentationsChina.tex
Update 2024PresentationsChina.tex

@@
 	\item estimate $F$ by the empirical cumulative distribution function,
-	\item its inverse, the quantile function $F^{-1}$, by the order statistics
-	\item approximate the derivative with finite differences (called ``spacings''),
-	\item approximate the integral with a summation.
+	\item its inverse, the quantile function $F^{-1}$, by the \alert{order statistics}
+	\item approximate the derivative with finite differences (called \alert{``spacings''}),
+	\item approximate the integral with a \alert{summation}.
 \end{itemize}
 
-There are several versions of entropy estimators based on spacings.
+\citet{vasicek1976test} proposed estimators based on spacings ($m$), followed by several other versions.
 We found that the best in terms of bias and mean square error is the one proposed by

### 2024-11-24 Text/2024PresentationsChina.tex
Slides are finished

@@
 
+\begin{frame}{Conclusions}
+We proposed a new test statistic for the null hypothesis that the data follow a Gamma distribution, i.e., they are fully developed speckle or come from textureless areas.
+Noteworthy points:
+\begin{itemize}[<+->]
+	\item The test statistic estimates the Shannon entropy non-parametrically,
+	\item It has excellent size (small Type~I error) and power (small Type~II error),
+	\item It produces a map of $p$ values,
+	\item It correctly identifies trees as not homogeneous, but also not extremely heterogeneous, differently from  tests based on the coefficient of variation.
+\end{itemize}
+\end{frame}
+
 \begin{frame}[standout]

### 2024-11-24 Text/2024PresentationsChina.tex
Update slides: added densities for three tests

@@
 
+%{\setbeamercolor{background canvas}{bg=anti-flashwhite}
+%\begin{frame}{The test based on the Shannon entropy}
+%\centering
+%\includegraphics[width=0.7\linewidth]{R1-Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_density-1}
+%\end{frame}
+%}
+{\setbeamercolor{background canvas}{bg=anti-flashwhite}
+\begin{frame}{The test based on the CV}
+\centering
+\includegraphics[width=0.9\linewidth]{R1-Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_density_test_cv-1}
+\end{frame}
+}
+
+{\setbeamercolor{background canvas}{bg=anti-flashwhite}
+\begin{frame}{The test based on the $\text{CV}_{\text{MnAD}}$}
+\centering
+\includegraphics[width=0.9\linewidth]{R1-Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_density_test_MnAD-1}
+\end{frame}
+}
+
 {\setbeamercolor{background canvas}{bg=anti-flashwhite}
@@
 \centering
-\includegraphics[width=0.7\linewidth]{R1-Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_density-1}
+\includegraphics[width=0.9\linewidth]{R1-Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_density_test_entropy-1}
 \end{frame}

### 2024-12-14 Text/2024PresentationsChina.tex
improved and updated slides

@@
 New Zealand}
-\date{November, 2024}
+\date{December, 2024}
 
@@
 \begin{frame}{The usual approach: I}
-We are tempted to form a statistical test using the coefficient of variation as the test statistic.
+We are tempted to form a test statistic using the coefficient of variation.
 
 Consider the random sample $\bm Z=(Z_1,Z_2,\dots,Z_n)$ that, under the null hypothesis has $\Gamma_{\text{SAR}}$ distribution.
-Then, we need the distribution of
+Our test statistic is
 \begin{equation}
-\widehat{\text{CV}}(\bm Z) = \frac{\frac1n \sum_{\ell=1}^n Z_\ell}{\sqrt{\frac1n \sum_{\ell=1}^n \big(Z_\ell-\overline{\bm Z}\big)^2}}.
-\label{eq:CV}
+S_{\widehat{\text{CV}}}(\bm Z;L) = \overbrace{\frac{\frac1n \sum_{\ell=1}^n Z_\ell}{\sqrt{\frac1n \sum_{\ell=1}^n \big(Z_\ell-\overline{\bm Z}\big)^2}}}^{\widehat{\text{CV}}(\bm Z)} - \underbrace{\frac{1}{\sqrt{L}}}_{\text{CV}\mid \Gamma_{\text{SAR}}} .
+\label{eq:SCV}
 \end{equation}
 
-Although we know that $\overline{\bm X}$ and $\widehat{\text{CV}}(\overline X) $ are independent \citep{OnaCharacterizationoftheGammaDistributiontheIndependenceoftheSampleMeanandtheSampleCoefficientofVariation}, we don't know the distribution of~\eqref{eq:CV}.
+Although we know that $\overline{\bm X}$ and $\widehat{\text{CV}}(\overline X) $ are independent \citep{OnaCharacterizationoftheGammaDistributiontheIndependenceoftheSampleMeanandtheSampleCoefficientofVariation}, we don't know the distribution of~\eqref{eq:SCV}.
 \end{frame}
@@
 
-Their estimator becomes
+Our robust test statistic becomes
 \begin{equation}
-\widecheck{\text{CV}}(\bm Z) = \frac{\widehat{Q}_2(\bm Z)}{\frac1n \sum_{\ell=1}^n \big|Z_i-\widehat{Q}_2(\bm Z)\big|}.
+S_{\widecheck{\text{CV}}}(\bm Z;L) = \frac{\widehat{Q}_2(\bm Z)}{\frac1n \sum_{\ell=1}^n \big|Z_i-\widehat{Q}_2(\bm Z)\big|} - \frac{1}{\sqrt{L}}.
 \end{equation}
@@
 
-Now, assume that we have a good estimator for the Shannon entropy, say $\widehat{H_{\Gamma_{\text{SAR}}}}$.
+Assume we have an estimator $\widehat{H}$ for the Shannon entropy of \alert{any} model.
 Under the $\Gamma_{\text{SAR}}$ model, we expect it to be close to~\eqref{E:E-gamma}.
@@
 $$
-\widehat{H_{\Gamma_{\text{SAR}}}} = \reallywidehat{L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu}
+\widehat{H}\mid {\Gamma_{\text{SAR}}} (L,\mu) = \widehat{H_{\Gamma_{\text{SAR}}}}  = \reallywidehat{L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu}
 $$
@@
 	& \hskip1ex L + \ln L - \ln\Gamma(L) - (1-L)\psi^{(0)}(L) - \ln \widehat{\mu}\\
-	= & \hskip1ex \widehat{H_{\Gamma_{\text{SAR}}}} - L + \ln L - \ln\Gamma(L) - (1-L)\psi^{(0)}(L) - \ln \widehat{\mu}.
+	= & \hskip1ex \widehat{H} - L + \ln L - \ln\Gamma(L) - (1-L)\psi^{(0)}(L) - \ln \widehat{\mu}.
 \end{align*}
@@
 
-Now we must choose suitable estimators $\widehat{H_{\Gamma_{\text{SAR}}}}$ and $\widehat{\mu}$.
+Now we must choose suitable estimators $\widehat{H}$ and $\widehat{\mu}$.
 \end{frame}
@@
 where $\widehat{\ln \mu}$ is the natural logarithm of the sample mean.
-
-We are also interested in non-parametric alternatives.
 
@@
 		S_{\widehat{\text{CV}}}(\bm Z;L) &= \frac{\frac1n \sum_{\ell=1}^n Z_\ell}{\sqrt{\frac1n \sum_{\ell=1}^n \big(Z_\ell-\overline{\bm Z}\big)^2}} - \frac1{\sqrt{L}} \\
-		S_{\widehat{\text{CV}_{\text{MnAD}}}} (\bm Z;L) &= \frac{\widehat{Q}_2(\bm Z)}{\frac1n \sum_{\ell=1}^n|X_i-\widehat{Q}_2(\bm Z)|}-\frac1{\sqrt{L}},\\
+		S_{\widecheck{\text{CV}}}(\bm Z;L) &= \frac{\widehat{Q}_2(\bm Z)}{\frac1n \sum_{\ell=1}^n|X_i-\widehat{Q}_2(\bm Z)|}-\frac1{\sqrt{L}},\\
 		S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L) & = \widetilde{H}_{\text{AO}}(\bm Z) - L + \ln L - \ln\Gamma(L) - (1-L)\psi^{(0)}(L) - \ln \widehat{\mu}
@@
 
-We tested their size (error Type~I) and power (error Type~II) and finite-size distribution under the null hypothesis.
-\alert{The winner is\dots}
+We tested their size (error Type~I under the null hypothesis) 
+and power (error Type~II under the $G_I^0$ model) and finite-size distributions.
 \end{frame}
